### 2015-08-18 intro.tex
start to build the eco-model

% !Mode:: "TeX:UTF-8"
% !TEX root = Eco-Model.tex
\section{test}

### 2015-09-22 head.tex
初步

% !TEX root = Eco-Model.tex

\title{Cloud Manufacturing Ecosystem - Scheduling And Evolving}

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In the Cloud Manufacturing Ecosystem, a benign mode and methodology for massive services schedule is
required, in order for the collaboration within the whole Industry Chain. This paper studied the data of the
resources and services and modeled the services scheduling problem in the chain. With the Big Data
analysis on the Cloud Platform, optimal assessment/schedule methods were developed, which could
gradually evolve the ecosystem to an optimal situation. 
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Cloud Manufacturing \sep Ecosystem \sep scheduling
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

### 2015-09-23 discussion.tex
struct done

% !TEX root = Eco-Model.tex
\section{Discussion} % (fold)
\label{sec:discussion}

% section discussion (end)

### 2015-09-23 envolve.tex
struct done

% !TEX root = Eco-Model.tex
\section{Envolve} % (fold)
\label{sec:envolve}

% section envolve (end)

### 2015-09-23 head.tex
reconstruct logically

@@
 \begin{abstract}
-In the Cloud Manufacturing Ecosystem, a benign mode and methodology for massive services schedule is
-required, in order for the collaboration within the whole Industry Chain. This paper studied the data of the
-resources and services and modeled the services scheduling problem in the chain. With the Big Data
-analysis on the Cloud Platform, optimal assessment/schedule methods were developed, which could
+In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were contructed by resources is required, in order for the collaboration within the whole Industry Chain.
+This paper 
+\begin{inparaenum}[1)]
+\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
+\item modeled the services scheduling matter in the chain;
+\item designed a simulation for the Cloud Manufacturing Ecosystem;
+\item opened some Ecosystem related issues. 
+\end{inparaenum}
+With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
 gradually evolve the ecosystem to an optimal situation.
+
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-Cloud Manufacturing \sep Ecosystem \sep scheduling
+Cloud Manufacturing \sep Ecosystem \sep simulation \sep scheduling \sep optimization
 %% MSC codes here, in the form: \MSC code \sep code

### 2015-09-23 schedule.tex
reconstruct logically

% !TEX root = Eco-Model.tex
\section{Resources Scheduling} % (fold)
\label{sec:model}

\subsection{Service Construct} % (fold)
\label{sub:service_construct}

% subsection service_construct (end)

\subsection{Matching} % (fold)
\label{sub:matching}

% subsection matching (end)

\subsection{Oredr Flow} % (fold)
\label{sub:oredr_flow}

% subsection oredr_flow (end)

\subsection{Rating and Recommand System} % (fold)
\label{sub:rating_&_recommand_system}

% subsection rating_&_recommand_system (end)

\subsection{Decision Making Support} % (fold)
\label{sub:decision_making_support}

% subsection decision_making_support (end)

\subsection{Scheduling} % (fold)
\label{sub:scheduling}

% subsection scheduling (end)
% section model (end)

### 2015-09-25 head.tex
just begin

@@
 \begin{abstract}
-In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were contructed by resources is required, in order for the collaboration within the whole Industry Chain.
+In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were constructed standardly by resources is required, in order for the collaboration within the whole Industry Chain.
 This paper 

### 2015-09-27 schedule.tex
just begin
init on mac

@@
 
-\subsection{Service Construct} % (fold)
-\label{sub:service_construct}
+In order to properly accomplish the proposed tasks with optimal allocation of the manufacturing resources, a series of methodologies were combined to assist the resources scheduling process in Cloud Manufacturing Ecosystem.
 
-% subsection service_construct (end)
+Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Decision Making Support}, \textit{Rating Schema}, \textit{Recommand System} and \textit{Matching Regulation}, which are going to explained in detail respectively.
 
-\subsection{Matching} % (fold)
-\label{sub:matching}
-
-% subsection matching (end)
-
-\subsection{Oredr Flow} % (fold)
-\label{sub:oredr_flow}
-
-% subsection oredr_flow (end)
-
-\subsection{Rating and Recommand System} % (fold)
-\label{sub:rating_&_recommand_system}
-
-% subsection rating_&_recommand_system (end)
+The scheduling effect can be estimated and observed through \textit{Service Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.
 
@@
 
-\subsection{Scheduling} % (fold)
-\label{sub:scheduling}
+\subsection{Rating Schema} % (fold)
+\label{sub:rating_schema}
 
-% subsection scheduling (end)
+% subsection rating_schema (end)
+
+\subsection{Recommand System} % (fold)
+\label{sub:recommand_system}
+
+% subsection recommand_system (end)
+
+\subsection{Matching Regulation} % (fold)
+\label{sub:matching_regulation}
+
+% subsection matching_regulation (end)
+
+\subsection{Service Dashboard} % (fold)
+\label{sub:service_dashboard}
+
+% subsection service_dashboard (end)
 % section model (end)

### 2015-09-28 poster.tex
add poster and beamer

%  The AAU Poster Theme.
%  2013-05-08 v. 1.1.0
%  Copyright 2013 by Jesper Kjær Nielsen <jkn@es.aau.dk>
%
%  This is free software: you can redistribute it and/or modify
%  it under the terms of the GNU General Public License as published by
%  the Free Software Foundation, either version 3 of the License, or
%  (at your option) any later version.
%
%  This is distributed in the hope that it will be useful,
%  but WITHOUT ANY WARRANTY; without even the implied warranty of
%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%  GNU General Public License for more details.
%
%  You can find the GNU General Public License at <http://www.gnu.org/licenses/>.
\documentclass[a0paper,portrait]{"../templates/Aalborg University Poster/baposter"}
\graphicspath{{figures/}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Language, Encoding and Fonts
% http://en.wikibooks.org/wiki/LaTeX/Internationalization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Select encoding of your inputs. Depends on
% your operating system and its default input
% encoding. Typically, you should use
%   Linux  : utf8 (most modern Linux distributions)
%            latin1 
%   Windows: ansinew
%            latin1 (works in most cases)
%   Mac    : applemac
% Notice that you can manually change the input
% encoding of your files by selecting "save as"
% an select the desired input encoding. 
\usepackage[utf8]{inputenc}
% Make latex understand and use the typographic
% rules of the language used in the document.
\usepackage[english]{babel}
% Use the vector font Latin Modern which is going
% to be the default font in latex in the future.
\usepackage{helvet}
% Change the default font family from roman to sans serif
\renewcommand{\familydefault}{\sfdefault} % for text
\usepackage[helvet]{sfmath} % for math
% Choose the font encoding
\usepackage[T1]{fontenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Graphics and Tables
% http://en.wikibooks.org/wiki/LaTeX/Importing_Graphics
% http://en.wikibooks.org/wiki/LaTeX/Tables
% http://pgfplots.sourceforge.net/
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You cannot use floats in the baposter theme.
% We therefore load the caption package which provides
% the command \captionof
% Set up how figure and table captions are displayed
\usepackage{caption}
\captionsetup{
  font=small,% set font size to footnotesize
  labelfont=bf % bold label (e.g., Figure 3.2) font
}
% Make the standard latex tables look so much better
\usepackage{array,booktabs}
% For creating beautiful plots
\usepackage{pgfplots}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Mathematics
% http://en.wikibooks.org/wiki/LaTeX/Mathematics
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Defines new environments such as equation,
% align and split 
\usepackage{amsmath}
% Adds new math symbols
\usepackage{amssymb}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Colours
% http://en.wikibooks.org/wiki/LaTeX/Colors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\selectcolormodel{RGB}
% define the three aau colors
\definecolor{aaublue1}{RGB}{33,26,82}% dark blue
\definecolor{aaublue2}{RGB}{113,109,143} % light blue
\definecolor{aaublue3}{RGB}{194,193,204} % lighter blue

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lists
% http://en.wikibooks.org/wiki/LaTeX/List_Structures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Easier configuration of lists
\usepackage{enumitem}
%configure itemize
\setlist{%
  topsep=0pt,% set space before and after list
  noitemsep,% remove space between items
  labelindent=\parindent,% set the label indentation to the paragraph indentation
  leftmargin=*,% remove the left margin
  font=\color{aaublue1}\normalfont, %set the colour of all bullets, numbers and descriptions to aaublue1
}
% use set<itemize,enumerate,description> if you have an older latex distribution
\setitemize[1]{label={\raise1.25pt\hbox{$\blacktriangleright$}}}
\setitemize[2]{label={\scriptsize\raise1.25pt\hbox{$\blacktriangleright$}}}
\setitemize[3]{label={\raise1.25pt\hbox{$\star$}}}
\setitemize[4]{label={-}}
%\setenumerate[1]{label={\theenumi.}}
%\setenumerate[2]{label={(\theenumii)}}
%\setenumerate[3]{label={\theenumiii.}}
%\setenumerate[4]{label={\theenumiv.}}
%\setdescription{font=\color{aaublue1}\normalfont\bfseries}

% use setlist[<itemize,enumerate,description>,<level>] if you have a newer latex distribution
%\setlist[itemize,1]{label={\raise1.25pt\hbox{$\blacktriangleright$}}}
%\setlist[itemize,2]{label={\scriptsize\raise1.25pt\hbox{$\blacktriangleright$}}}
%\setlist[itemize,3]{label={\raise1.25pt\hbox{$\star$}}}
%\setlist[itemize,4]{label={-}}
%\setlist[enumerate,1]{label={\theenumi.}}
%\setlist[enumerate,2]{label={(\theenumii)}}
%\setlist[enumerate,3]{label={\theenumiii.}}
%\setlist[enumerate,4]{label={\theenumiv.}}
%\setlist[description]{font=\color{aaublue1}\normalfont\bfseries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Misc
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% change/remove some names
\addto{\captionsenglish}{
  %remove the title of the bibliograhpy
  \renewcommand{\refname}{\vspace{-0.7em}}
  %change Figure to Fig. in figure captions
  \renewcommand{\figurename}{Fig.}
}
% create links
\usepackage{url}
%note that the hyperref package is currently incompatible with the baposter class

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\alert}[1]{{\color{aaublue1}#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document Start 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some changes that cannot be made in the preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set the background of the poster
\background{
  \begin{tikzpicture}[remember picture,overlay]%
    %the poster background color
    \fill[fill=aaublue3] (current page.north west) rectangle (current page.south east);
    %the header
    \fill [fill=aaublue1] (current page.north west) rectangle ([yshift=-\headerheight] current page.north east);
  \end{tikzpicture}
}
% if you want to reduce the space before and after equations, use and adjust
% the following lines
%\addtolength{\abovedisplayskip}{-2mm}
%\addtolength{\belowdisplayskip}{-2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% General poster setup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
  %general options for the poster
  grid=false,
  columns=3,
%  colspacing=4.2mm,
  headerheight=0.1\textheight,
  background=user,
%  bgColorOne=red!42, %is used when background != user and none
%  bgColortwo=green!42, %is used when background is shaded
  eyecatcher=true,
  %posterbox options
  headerborder=closed,
  borderColor=aaublue1,
  headershape=rectangle,
  headershade=plain,
  headerColorOne=aaublue1,
%  headerColortwo=yellow!42, %is used when the header background is shaded
  textborder=rectangle,
  boxshade=plain,
  boxColorOne=white,
%  boxColorTwo=cyan!42,%is used when the text background is shaded
  headerFontColor=white,
  headerfont=\Large\sf\bf,
  linewidth=1pt
}
%the Eye Catcher (the logo on the left)
{
  %this can be commented out or replaced by a company/department logo
  \makebox[1pt]{
  \includegraphics[
    trim =-222 0 0 0,
    height=0.75\headerheight]{QSY}
  }
}
%the poster title
{\color{white}\bf
  The AAU Poster Theme
}
%the author(s)
{\color{white}\small
  \vspace{1em} Jesper Kjær Nielsen\\[0.5em]
  Dept.\ of Electronic Systems, Aalborg University, Denmark\\
  jkn@es.aau.dk
}

{
  \makebox[-1pt]{}
}
%the logo (the logo on the right)
%{
  %this can be commented out or replaced by a company/department logo
%  \includegraphics[height=0.75\headerheight]{QSY}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% the actual content of the poster begins here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{posterbox}[name=intro,column=0,row=0]{Introduction}
\begin{itemize}
  \item Posters are often used at conferences for presenting exciting new research results.
  \item So far no official AAU poster theme is available to the researchers and students at Aalborg University (AAU).
  \item The present theme changes this.
  \item The theme is a particular configuration of the \alert{baposter} poster template \cite{baposter} which you can find here \url{http://www.brian-amberg.de/uni/poster/} and must have installed in order to use the AAU poster theme.
\end{itemize}
\end{posterbox}

\begin{posterbox}[name=usage,column=0,below=intro]{Usage}
\begin{itemize}
  \item To use the AAU poster theme, place the {\tt aauposter.tex} file in your preferred folder and modify the file to your needs.
  \item You can read more about how you can modify the theme in the documentation for the baposter template which you can find here \url{http://www.brian-amberg.de/uni/poster/}.
\end{itemize}
\end{posterbox}

\begin{posterbox}[name=lists,column=0,below=usage]{Lists}
Itemize
\begin{itemize}
  \item item 1
    \begin{itemize}
      \item subitem 1
        \begin{itemize}
          \item subsubitem 1
            \begin{itemize}
              \item subsubsubitem 1
              \item subsubsubitem 2
            \end{itemize}
          \item subsubitem 2
        \end{itemize}
      \item subitem 2
    \end{itemize}
  \item item 2
\end{itemize}
Enumerate
\begin{enumerate}
  \item item 1
    \begin{enumerate}
      \item subitem 1
        \begin{enumerate}
          \item subsubitem 1
            \begin{enumerate}
              \item subsubsubitem 1
              \item subsubsubitem 2
            \end{enumerate}
          \item subsubitem 2
        \end{enumerate}
      \item subitem 2
    \end{enumerate}
  \item item 2
\end{enumerate}
Description
\begin{description}
  \item[desc 1] item 1
    \begin{description}
      \item[desc 1] subitem 1
        \begin{description}
          \item[desc 1] subsubitem 1
            \begin{description}
              \item[desc 1] subsubsubitem 1
              \item[desc 2] subsubsubitem 2
            \end{description}
          \item[desc 2] subsubitem 2
        \end{description}
      \item[desc 2] subitem 2
    \end{description}
  \item[desc 2] item 2
\end{description}
\end{posterbox}

\begin{posterbox}[name=equation,column=0,below=lists,above=bottom]{Equations}
Here is an example of an equation
\begin{equation}
  f_X(x|\mu,\sigma^2) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left\{\frac{1}{2\sigma^2}(x-\mu)^2\right\}
\end{equation}
\end{posterbox}

\begin{posterbox}[name=install,span=2,column=1,row=0]{Installation}
You can either make a local or a global installation of the baposter poster template \cite{baposter}.
\begin{description}
  \item[Local:] Place the {\tt baposter.cls} file in the same folder as the poster file {\tt aauposter.tex}
  \item[Global:] Place the {\tt baposter.cls} file in your local latex-directory tree. This is by default {\tt <somewhere>/textmf/tex/latex/baposter} where {\tt <somewhere>} is
  \begin{description}
    \item[GNU/Linux:] {\tt/home/<username>}
    \item[Windows XP:] {\tt c:\textbackslash Document and Settings\textbackslash<username>}
    \item[Windows Vista+:] {\tt c:\textbackslash Users\textbackslash<username>}
    \item[Mac OSX] {\tt/home/<username>/Library}
  \end{description}
  On GNU/Linux and Windows, you have to update the filename database after placing {\tt baposter.cls} in the correct folder. This is done by
  \begin{description}
    \item[GNU/Linux:] {\tt \$ texhash \textasciitilde /texmf}
    \item[Windows with MiKTeX] Open the MiKTeX Settings dialog and click 'Refresh FNDB'.
    \item[Windows with TeX Live] Open the TeX Live Manager dialog and select 'Update filename database' under 'Actions'.
  \end{description}
\end{description}
\end{posterbox}

\begin{posterbox}[name=figures,column=1,below=install,above=bottom]{Figures and Tables}
You cannot use floats in the baposter template. However, you can use figure captions by using {\tt \textbackslash captionof} instead of {\tt \textbackslash caption}. This is demonstrated in Fig.~\ref{fig:figlabel}. Moreover, you can also use {\tt \textbackslash label} and {\tt \textbackslash ref} to make references to your figures and/or tables.
\begin{center}
  \includegraphics[scale = 0.5]{ZJDX}
  \captionof{figure}{Here is a figure caption}
  \label{fig:figlabel}
\end{center}
As you can see, the text background is not white. If your figures do not have a transparent background, this may look too ugly for you. You can of course change the background colour through the {\tt boxColorOne} option. Alternatively, you can make the background transparent. In Matlab, the following example demonstrates how this is done\par
{\tt
f1 = figure(1);\\
set(f1,'Color','none');
}\par
You can also use {\tt pgfplots} \cite{pgfplots} for plotting your Matlab data. This is not that hard and the resulting plots are much nicer than Matlab plots, so I will strongly recommend that you have a look at {\tt pgfplots} right here \url{http://sourceforge.net/projects/pgfplots/}.
\begin{center}
  \begin{tabular}{c c c}
    \toprule
    header 1 & header 2 & header 3\\
    \midrule
    data (1,1) & data (1,2) & data (1,3)\\
    data (2,1) & data (2,2) & data (2,3)\\
    data (3,1) & data (3,2) & data (3,3)\\
    \bottomrule
  \end{tabular}
  \captionof{table}{A very simple table with booktabs}
  \label{tab:tablabel}
\end{center}
\end{posterbox}

\begin{posterbox}[name=problems,column=2,below=install]{Known Problems}
  \begin{itemize}
    \item The math matrix environment {\tt \textbackslash begin\{matrix\} ... \textbackslash end\{matrix\}} causes an error. I do not know why. Use the array environment until the problem is resolved.
  \end{itemize}
\end{posterbox}

\begin{posterbox}[name=feedback,column=2,below=problems]{Feedback}
  \begin{itemize}
    \item The AAU poster theme v. 1.1.0 has been tested with baposter v. 2.0, and it can be downloaded from my AAU website \cite{jknaau} or my personal website \cite{jknsqrt-1}.
    \item If you find a bug in the AAU theme (and not in the baposter template), please do not hesitate to contact me. There is a FAQ at the baposter website \cite{baposter}, if you should have any problems with it.
  \end{itemize}
\end{posterbox}

\begin{posterbox}[name=refs,column=2,below=feedback,above=bottom]{Bibliography}
% In the last box, you will usually have a list of references
% The bibliography automatically adds the title "References", but
% this have been removed in the preamble

% use either ......
%\bibliographystyle{../templates/Elsevier/elsarticle-num}
%\bibliographystyle{../templates/Elsevier/elsarticle-harv}
%\bibliographystyle{../templates/Elsevier/elsarticle-num-names}
%\bibliographystyle{../templates/Elsevier/model1a-num-names}
%\bibliographystyle{../templates/Elsevier/model1b-num-names}
%\bibliographystyle{../templates/Elsevier/model1c-num-names}
%\bibliographystyle{../templates/Elsevier/model1-num-names}
%\bibliographystyle{../templates/Elsevier/model2-names}
%\bibliographystyle{../templates/Elsevier/model3a-num-names}
%\bibliographystyle{../templates/Elsevier/model3-num-names}
%\bibliographystyle{../templates/Elsevier/model4-names}
%\bibliographystyle{../templates/Elsevier/model5-names}
%\bibliographystyle{../templates/Elsevier/model6-num-names}
\bibliographystyle{abbrv}
\nocite{*}    
\bibliography{references}
%\begin{thebibliography}{1}% Simple bibliography with widest label of 1
%\itemsep=-0.01em% Save space between the separation
%\setlength{\baselineskip}{0.4em}% Save space with longer lines
%\bibitem{baposter} Brian Amberg: \emph{LaTeX Poster Template}, \url{http://www.brian-amberg.de/uni/poster/} 
%\bibitem{pgfplots} Christian Feuersänger: \emph{PGFPlots - A LaTeX Package to create normal/logarithmic plots in two and three dimensions}, \url{http://pgfplots.sourceforge.net/} 
%\bibitem{jknaau} Jesper Kjær Nielsen: \emph{Official AAU Beamer Theme, Poster Theme, and Report Template}, \url{http://kom.aau.dk/~jkn/latex/latex.php}
%\bibitem{jknsqrt-1} Jesper Kjær Nielsen: \emph{Official AAU Beamer Theme, Poster Theme, and Report Template}, \url{http://sqrt-1.dk/latex/latex.php}
%\end{thebibliography}

% ...... or
%  \bibliographystyle{IEEEbib}
%  \bibliography{IEEEabrv,mybib,mybib2} 
\end{posterbox}

\end{poster}
\end{document}

### 2015-09-28 figures/flow1.tex
主要学习画图

% !TEX root = flow_head.tex
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=6mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, diamond, aspect=2, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [proc, densely dotted, it] (p0) {New trigger message thread};
% Use join to connect a node to the previous one 
\node [term, join]      {Trigger scheduler};
\node [proc, join] (p1) {Get quota $k > 1$};
\node [proc, join]      {Open queue};
\node [proc, join]      {Dispatch message};
\node [test, join] (t1) {Got msg?};
% No join for exits from test nodes - connections have more complex
% requirements
% We continue until all the blocks are positioned
\node [proc] (p2) {$k \mathbin{{-}{=}} 1$};
\node [proc, join] (p3) {Dispatch message};
\node [test, join] (t2) {Got msg?};
\node [test] (t3) {Capacity?};
\node [test] (t4) {$k \mathbin{{-}{=}} 1$};
% We position the next block explicitly as the first block in the
% second column.  The chain 'comes along with us'. The distance
% between columns has already been defined, so we don't need to
% specify it.
\node [proc, fill=lcfree!25, right=of p1] (p4) {Reset congestion};
\node [proc, join=by free] {Set \textsc{mq} wait flag};
\node [proc, join=by free] (p5) {Dispatch message};
\node [test, join=by free] (t5) {Got msg?};
\node [test] (t6) {Capacity?};
% Some more nodes specifically positioned (we could have avoided this,
% but try it and you'll see the result is ugly).
\node [test] (t7) [right=of t2] {$k \mathbin{{-}{=}} 1$};
\node [proc, fill=lccong!25, right=of t3] (p8) {Set congestion};
\node [proc, join=by cong, right=of t4] (p9) {Close queue};
\node [term, join] (p10) {Exit trigger message thread};
% -------------------------------------------------
% Now we place the coordinate nodes for the connectors with angles, or
% with annotations. We also mark them for debugging.
\node [coord, right=of t1] (c1)  {}; %\cmark{1}   
\node [coord, right=of t3] (c3)  {}; \cmark{3}   
\node [coord, right=of t6] (c6)  {}; \cmark{6}   
\node [coord, right=of t7] (c7)  {}; \cmark{7}   
\node [coord, left=of t4]  (c4)  {}; \cmark{4}   
\node [coord, right=of t4] (c4r) {}; \cmark[r]{4}
\node [coord, left=of t7]  (c5)  {}; \cmark{5}   
% -------------------------------------------------
% A couple of boxes have annotations
\node [above=0mm of p4, it] {(Queue was empty)};
\node [above=0mm of p8, it] {(Queue was not empty)};
% -------------------------------------------------
% All the other connections come out of tests and need annotating
% First, the straight north-south connections. In each case, we first
% draw a path with a (consistently positioned) annotation node, then
% we draw the arrow itself.
\path (t1.south) to node [near start, xshift=1em] {$y$} (p2);
  \draw [*->,lcnorm] (t1.south) -- (p2);
\path (t2.south) to node [near start, xshift=1em] {$y$} (t3); 
  \draw [*->,lcnorm] (t2.south) -- (t3);
\path (t3.south) to node [near start, xshift=1em] {$y$} (t4); 
  \draw [*->,lcnorm] (t3.south) -- (t4);
\path (t5.south) to node [near start, xshift=1em] {$y$} (t6); 
  \draw [*->,lcfree] (t5.south) -- (t6);
\path (t6.south) to node [near start, xshift=1em] {$y$} (t7); 
  \draw [*->,lcfree] (t6.south) -- (t7); 
% ------------------------------------------------- 
% Now the straight east-west connections. To provide consistent
% positioning of the test exit annotations, we have positioned
% coordinates for the vertical part of the connectors. The annotation
% text is positioned on a path to the coordinate, and then the whole
% connector is drawn to its destination box.
\path (t3.east) to node [near start, yshift=1em] {$n$} (c3); 
  \draw [o->,lccong] (t3.east) -- (p8);
\path (t4.east) to node [yshift=-1em] {$k \leq 0$} (c4r); 
  \draw [o->,lcnorm] (t4.east) -- (p9);
% -------------------------------------------------
% Finally, the twisty connectors. Again, we place the annotation
% first, then draw the connector
\path (t1.east) to node [near start, yshift=1em] {$n$} (c1); 
  \draw [o->,lcfree] (t1.east) -- (c1) |- (p4);
\path (t2.east) -| node [very near start, yshift=1em] {$n$} (c1); 
  \draw [o-,lcfree] (t2.east) -| (c1);
\path (t4.west) to node [yshift=-1em] {$k>0$} (c4); 
  \draw [*->,lcnorm] (t4.west) -- (c4) |- (p3);
\path (t5.east) -| node [very near start, yshift=1em] {$n$} (c6); 
  \draw [o->,lcfree] (t5.east) -| (c6); 
\path (t6.east) to node [near start, yshift=1em] {$n$} (c6); 
  \draw [o->,lcfree] (t6.east) -| (c7); 
\path (t7.east) to node [yshift=-1em] {$k \leq 0$} (c7); 
  \draw [o->,lcfree] (t7.east) -- (c7)  |- (p9);
\path (t7.west) to node [yshift=-1em] {$k>0$} (c5); 
  \draw [*->,lcfree] (t7.west) -- (c5) |- (p5);
% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,MediumPurple4, dotted, thick, shorten >=1mm]
  (p9.south) -- ++(10mm,-3mm)  -- ++(22mm,0) 
  |- node [black, near end, yshift=0.75em, it]
    {(When message + resources available)} (p0);
% -------------------------------------------------
\end{tikzpicture}

### 2015-09-29 figures/platformstruct.tex
add a figure mind map

% !TEX root = ..\Eco-Model.tex
\begin{tikzpicture}
[mindmap,
every node/.style={concept, text=white, execute at begin node=\hskip0pt,circular drop shadow},
root concept/.append style={concept color=black, fill=white, line width=1ex, text=black, font=\Large\scshape},
grow cyclic,
level 1/.append style={level distance=4.5cm,sibling angle=90, font=\scshape},
level 2/.append style={level distance=3cm,sibling angle=45, font=\scriptsize\bf},
level 3/.append style={level distance=2cm,sibling angle=60, font=\scriptsize\bf},
level 4/.append style={level distance=1cm,sibling angle=60, font=\tiny\bf}]
\node [root concept] {Cloud Manufacturing Ecosystem}  % root
child [concept color = gray]{ node {Schedule}
child { node {Recommand System}}
child { node {Decision Making Support}}
child { node {Ranking Schema}}
child { node {Match Regualtion}}
}
child [concept color = gray]{ node {User}
  child { node {Submit Order}}
  child { node {Provide Resource}}
  child { node {Make Transaction}}
  child { node {Evalute Others}}
  }
child [concept color = gray]{ node {Envolve}
  child { node {Optimization}
    child { node {Manufacturing}}
    child { node {Industrial Chain}}
    }
  child { node {Member}
    child { node {Introduce}}
    child { node {Eliminate}}
    }
  child { node {Adjust User Proportion}}
  child { node {Development Guidance}}
  }
child [concept color = gray]{ node {Platform}
  child { node {Authority Control}}
  child { node {Transaction Bridge}}
  child { node {Dashbord}
    child { node {Service}}
    child { node {Task}}
    child { node {User}}
    }
  child { node {Administrate}}
  child { node {Hub}
    child { node {Service}}
    child { node {Resource}}
    child { node {Ranking}}
    }
  }
;
\end{tikzpicture}

### 2015-09-29 head.tex
add a figure mind map

@@
 \end{inparaenum}
-With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
+With the help of Data Science tools on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
 gradually evolve the ecosystem to an optimal situation.

### 2015-09-30 figures/order_flow.tex
add flowchart

--- 2015-09-28 figures/flow1.tex
@@
 % Start by placing the nodes
-\node [proc, densely dotted, it] (p0) {New trigger message thread};
-% Use join to connect a node to the previous one 
-\node [term, join]      {Trigger scheduler};
-\node [proc, join] (p1) {Get quota $k > 1$};
-\node [proc, join]      {Open queue};
-\node [proc, join]      {Dispatch message};
-\node [test, join] (t1) {Got msg?};
-% No join for exits from test nodes - connections have more complex
-% requirements
-% We continue until all the blocks are positioned
-\node [proc] (p2) {$k \mathbin{{-}{=}} 1$};
-\node [proc, join] (p3) {Dispatch message};
-\node [test, join] (t2) {Got msg?};
-\node [test] (t3) {Capacity?};
-\node [test] (t4) {$k \mathbin{{-}{=}} 1$};
-% We position the next block explicitly as the first block in the
-% second column.  The chain 'comes along with us'. The distance
-% between columns has already been defined, so we don't need to
-% specify it.
-\node [proc, fill=lcfree!25, right=of p1] (p4) {Reset congestion};
-\node [proc, join=by free] {Set \textsc{mq} wait flag};
-\node [proc, join=by free] (p5) {Dispatch message};
-\node [test, join=by free] (t5) {Got msg?};
-\node [test] (t6) {Capacity?};
-% Some more nodes specifically positioned (we could have avoided this,
-% but try it and you'll see the result is ugly).
-\node [test] (t7) [right=of t2] {$k \mathbin{{-}{=}} 1$};
-\node [proc, fill=lccong!25, right=of t3] (p8) {Set congestion};
-\node [proc, join=by cong, right=of t4] (p9) {Close queue};
-\node [term, join] (p10) {Exit trigger message thread};
-% -------------------------------------------------
-% Now we place the coordinate nodes for the connectors with angles, or
-% with annotations. We also mark them for debugging.
-\node [coord, right=of t1] (c1)  {}; %\cmark{1}   
-\node [coord, right=of t3] (c3)  {}; \cmark{3}   
-\node [coord, right=of t6] (c6)  {}; \cmark{6}   
-\node [coord, right=of t7] (c7)  {}; \cmark{7}   
-\node [coord, left=of t4]  (c4)  {}; \cmark{4}   
-\node [coord, right=of t4] (c4r) {}; \cmark[r]{4}
-\node [coord, left=of t7]  (c5)  {}; \cmark{5}   
-% -------------------------------------------------
-% A couple of boxes have annotations
-\node [above=0mm of p4, it] {(Queue was empty)};
-\node [above=0mm of p8, it] {(Queue was not empty)};
-% -------------------------------------------------
-% All the other connections come out of tests and need annotating
-% First, the straight north-south connections. In each case, we first
-% draw a path with a (consistently positioned) annotation node, then
-% we draw the arrow itself.
-\path (t1.south) to node [near start, xshift=1em] {$y$} (p2);
-  \draw [*->,lcnorm] (t1.south) -- (p2);
-\path (t2.south) to node [near start, xshift=1em] {$y$} (t3); 
-  \draw [*->,lcnorm] (t2.south) -- (t3);
-\path (t3.south) to node [near start, xshift=1em] {$y$} (t4); 
-  \draw [*->,lcnorm] (t3.south) -- (t4);
-\path (t5.south) to node [near start, xshift=1em] {$y$} (t6); 
-  \draw [*->,lcfree] (t5.south) -- (t6);
-\path (t6.south) to node [near start, xshift=1em] {$y$} (t7); 
-  \draw [*->,lcfree] (t6.south) -- (t7); 
-% ------------------------------------------------- 
-% Now the straight east-west connections. To provide consistent
-% positioning of the test exit annotations, we have positioned
-% coordinates for the vertical part of the connectors. The annotation
-% text is positioned on a path to the coordinate, and then the whole
-% connector is drawn to its destination box.
-\path (t3.east) to node [near start, yshift=1em] {$n$} (c3); 
-  \draw [o->,lccong] (t3.east) -- (p8);
-\path (t4.east) to node [yshift=-1em] {$k \leq 0$} (c4r); 
-  \draw [o->,lcnorm] (t4.east) -- (p9);
-% -------------------------------------------------
-% Finally, the twisty connectors. Again, we place the annotation
-% first, then draw the connector
-\path (t1.east) to node [near start, yshift=1em] {$n$} (c1); 
-  \draw [o->,lcfree] (t1.east) -- (c1) |- (p4);
-\path (t2.east) -| node [very near start, yshift=1em] {$n$} (c1); 
-  \draw [o-,lcfree] (t2.east) -| (c1);
-\path (t4.west) to node [yshift=-1em] {$k>0$} (c4); 
-  \draw [*->,lcnorm] (t4.west) -- (c4) |- (p3);
-\path (t5.east) -| node [very near start, yshift=1em] {$n$} (c6); 
-  \draw [o->,lcfree] (t5.east) -| (c6); 
-\path (t6.east) to node [near start, yshift=1em] {$n$} (c6); 
-  \draw [o->,lcfree] (t6.east) -| (c7); 
-\path (t7.east) to node [yshift=-1em] {$k \leq 0$} (c7); 
-  \draw [o->,lcfree] (t7.east) -- (c7)  |- (p9);
-\path (t7.west) to node [yshift=-1em] {$k>0$} (c5); 
-  \draw [*->,lcfree] (t7.west) -- (c5) |- (p5);
-% -------------------------------------------------
-% A last flourish which breaks all the rules
-\draw [->,MediumPurple4, dotted, thick, shorten >=1mm]
-  (p9.south) -- ++(10mm,-3mm)  -- ++(22mm,0) 
-  |- node [black, near end, yshift=0.75em, it]
-    {(When message + resources available)} (p0);
-% -------------------------------------------------
+\node [term] {Be Submitted};
 \end{tikzpicture}

### 2015-09-30 figures/order_flow.tex
add the flowchart of order flow

@@
   coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
+  sky/.style={coordinate, on chain, on grid, node distance=6mm and 60mm},
   % nmark node style is used for coordinate debugging marks
@@
 \node [term]              {Be Submitted};
+\node [proc, join]        {Constrcut into Tasks};
+\node [proc, join]  (p1)  {Evaluate the Seller};
+\node [test, join]  (t1)  {Transact?};
+\node [test]        (t2)  {Task Remain?};
+\node [test]        (t3)  {Outsourcing?};
+\node [proc]        (p2)  {Process Task and Submit Result};
+\node [test, join]  (t4)  {Order Finish?};
+\node [term]        (m1)  {End Smothly};
+
+\node [sky, right=of p1] (c5) {};%\cmark{5}
+\node [proc, right=of t1] (p3)  {Select Next Seller};
+\node [test]        (t5)  {Partly or Whole?};
+\node [proc]        (p5)  {Process Un-Outsouring Part and Submit Result};
+\node [test, join]  (t6)  {Process Smothly?};
+\node [proc]        (p4)  {Submit Outsourcing Part};
+\node [coord, yshift=2.5mm]       (c4)  {}; %\cmark{4}
+\node [term, right=of m1] (m2)  {End with Error};
+
+\node [coord, left=of t2] (c1) {}; %\cmark{1}
+\node [coord, right=of t3](c2) {}; %\cmark{2}
+\node [coord, right=of t4](c3) {}; %\cmark{3}
+\node [coord, right=of t5, xshift=3mm](c6) {}; %\cmark{6}
+\node [coord, left=of c4, xshift=-1mm](c8) {}; %\cmark{8}
+
+\path (t1.east) to node [near start, yshift=1em] {$n$} (p3);
+  \draw [o->, lcnorm] (t1.east) -- (p3);
+  \draw [->, lcnorm] (p3) |- (c5);
+\path (t1.south) to node [near start, xshift=1em] {$y$} (t2);
+  \draw [*->, lcnorm] (t1.south) -- (t2);
+\path (t2.west) to node [near start, yshift=1em]  {$n$} (p2.west);
+  \draw [o->, lcnorm] (t2.west) -- (c1) |- (p2.west);
+\path (t2.south) to node [near start, xshift=1em] {$y$} (t3);
+  \draw [*->, lcnorm] (t2.south)  -- (t3);
+\path (t3.east) to node [near start, yshift=1em] {$y$}  (c2);
+  \draw [*->, lcnorm] (t3.east) -| (c2) |- (t5.west);
+\path (t3.south) to node [near start, xshift=1em] {$n$} (p2);
+  \draw [o->, lcnorm] (t3.south) -- (p2);
+\path (t4.south) to node [near start, xshift=1em] {$y$} (m1);
+  \draw [*->, lcnorm] (t4.south) -- (m1);
+\path (t4.east) to node [near start, yshift=-1em] {$n$} (c3);
+  \draw [o->, lcnorm] (t4.east) -- (c3) |- (c4) -- (m2);
+\path (t5.east) to node [near start, yshift=1em] {whole} (c6);
+\path (t5.south) to node [near start, xshift=2em] {partly} (p5);
+  \draw [o->, lcnorm] (t5.east) -- (c6) |- (p1);
+  \draw [*->, lcnorm] (t5.south) -- (p5);
+\path (t6.south) to node [near start, xshift=1em] {$y$} (p4);
+\path (t6.west) to node [near start, yshift=1em] {$n$} (c8);
+  \draw [o->, lcnorm] (t6.west) -| (c8); 
+  \draw [*->, lcnorm] (t6.south) -- (p4);
+  \draw [->, lcnorm] (p4.east) -| (c6);
 \end{tikzpicture}

### 2015-09-30 figures/user_rank.tex
untrack flow_head.pdf
two of the flow chart are done

--- 2015-09-30 figures/order_flow.tex
@@
-% !TEX root = flow_head.tex
+% !TEX root = ../Eco-Model.tex
 \begin{tikzpicture}[%
@@
 % Start by placing the nodes
-\node [term] {Be Submitted};
+\node [term, fill = lcfree!25]              (m1)  {Be Introduced};
+\node [proc, join]        (p8)  {Get Initial Rank $R$};
+\node [coord, yshift=2mm] (c1)  {}; %\cmark{1}
+\node [test, yshift=2mm]  (t1)  {Transact?};
+\node [proc, yshift=-2mm] (p1)  {Increase $R$};
+
+\node [coord, yshift=0mm] (c7)  {}; %\cmark{7}
+
+\node [test, yshift=0mm] (t2)  {All Tasks Done?};
+\node [proc]              (p2)  {Process Un-Outsourceing Task};
+\node [test]              (t3)  {Accepted?};
+\node [proc]              (p3)  {Pass the Outsouring Task};
+\node [test, join]        (t4)  {Task Done?};
+
+\node [proc, right=of t1] (p4)  {Wait};
+\node [proc]              (p5)  {Compete to Get Task};
+\node [test, join]        (t5)  {Make it?};
+
+\node [coord, yshift=2mm] (c4)  {}; %\cmark{4}
+
+\node [test, yshift=2mm]  (t6)  {Outsourcing?};
+\node [test]              (t7)  {Partly or Whole?};
+\node [proc]              (p6)  {Submit Outsourcing Request};
+\node [proc]              (p7)  {Decrease $R$};
+\node [test, join]        (t8)  {$R < R_{base}$?};
+\node [term, fill=lccong!25]              (m2)  {Eliminate};
+
+\node [coord, left=of p1] (c2)  {}; %\cmark{2}
+\node [coord, right=of t5](c3)  {}; %\cmark{3}
+\node [coord, right=of p2](c5)  {}; %\cmark{5}
+\node [coord, right=of t3](c6)  {}; %\cmark{6}
+\node [coord, left=of c7] (c8)  {}; %\cmark{8}
+\node [coord, right=of t4](c9)  {}; %\cmark{9}
+
+\draw [->, lcnorm] (p4) |- (c1);
+\draw [->, lcnorm] (p8) -- (t1);
+\draw [->, lcnorm] (p1) --(c2) |- (c1);
+\draw [->, lcnorm] (p2) -- (t2);
+\draw [->, lcnorm] (p6) -| (c6) -- (t3);
+
+\path (t1.east)   to node [near start, yshift=1em] {$n$} (p4);
+\path (t1.south)  to node [near start, xshift=1em] {$y$} (p1);
+  \draw [o->, lcnorm] (t1.east) -- (p4);
+  \draw [*->, lcnorm] (t1.south) |- (p5);
+\path (t2.east)   to node [near start, yshift=-1em]{$n$} ++(2mm,0);
+\path (t2.north)  to node [near start, xshift=1em] {$y$} (p1);
+  \draw [o->, lcnorm] (t2.east) -- (c4) ;
+  \draw [*->, lcnorm] (t2.north) -- (p1);
+\path (t5.east)   to node [near start, yshift=1em] {$n$} (c3);
+\path (t5.south)  to node [near start, xshift=1em] {$y$} (t6);
+  \draw [o->, lcnorm] (t5.east) -- (c3) |- (p4);
+  \draw [*->, lcnorm] (t5.south) -- (t6);
+\path (t6.west)   to node [near start, yshift=-1em]{$n$} (c5);
+\path (t6.south)  to node [near start, xshift=1em] {$y$} (t7);
+  \draw [*->, lcnorm] (t6.south) -- (t7);
+  \draw [o->, lcnorm] (t6.west) -| (c5) -- (p2);
+\path (t7.west)   to node [near start, yshift=1em] {partly} ++(-1mm,0);
+\path (t7.south)  to node [near start, xshift=2em] {whole} (p6);
+  \draw [*->, lcnorm] (t7.west) -| (c5);
+  \draw [o->, lcnorm] (t7.south) -- (p6);
+\path (t8.east)   to node [near start, yshift=1em] {$n$} ++(1mm,0);
+\path (t8.south)  to node [near start, xshift=1em] {$y$} (m2);
+ \draw [o->, lcnorm] (t8.east) -| (c3);
+ \draw [*->, lcnorm] (t8.south) -- (m2);
+\path (t3.north)  to node [near start, xshift=1em] {$n$} (p2);
+\path (t3.south)  to node [near start, xshift=1em] {$y$} (p3);
+  \draw [o->, lcnorm] (t3.north) -- (p2);
+  \draw [*->, lcnorm] (t3.south) -- (p3);
+\path (t4.west)   to node [near start, yshift=1em] {$y$} ++(-1mm,0);
+\path (t4.east)   to node [near start, yshift=1em] {$n$} (c9);
+  \draw [*->, lcnorm] (t4.west) -| (c8) -- (c7);
+  \draw [o->, lcnorm] (t4.east) -- (c9) |- (p7);
 \end{tikzpicture}

### 2015-10-02 schedule.tex
20150927
give up simulation

@@
 % !TEX root = Eco-Model.tex
-\section{Resources Scheduling} % (fold)
-\label{sec:model}
+\section{Services Scheduling} % (fold)
+\label{sec:schedule}
 
-In order to properly accomplish the proposed tasks with optimal allocation of the manufacturing resources, a series of methodologies were combined to assist the resources scheduling process in Cloud Manufacturing Ecosystem.
+In order to properly accomplish the proposed tasks with optimal allocation of the manufacturing resources, a series of methodologies were combined to assist the manufacturing services scheduling process in Cloud Manufacturing Ecosystem, since manufacturing serivices are contrusted from manufacturing resources.
+
+OAS
 
@@
 % subsection decision_making_support (end)
-
-\subsection{Rating Schema} % (fold)
-\label{sub:rating_schema}
-
-% subsection rating_schema (end)
-
-\subsection{Recommand System} % (fold)
-\label{sub:recommand_system}
-
-% subsection recommand_system (end)
 

### 2015-10-02 figures/platformstruct.tex
add some node to the platform structure figure

@@
 child [concept color = gray]{ node {Schedule}
-child { node {Recommand System}}
+child { node {Service Standardization}}
 child { node {Decision Making Support}}
-child { node {Ranking Schema}}
+child { node {Platform Assistance}}
 child { node {Match Regualtion}}
@@
     }
-  child { node {Adjust User Proportion}}
+  child { node {Adjust User Proportion}
+    child { node {Rating}}
+    child { node {Recommand}}
+    }
   child { node {Development Guidance}}
@@
     }
+  child { node {Scheduling Assistance}}
 }

### 2015-10-02 schedule.tex
add some node to the platform structure figure

@@
 
-Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Decision Making Support}, \textit{Rating Schema}, \textit{Recommand System} and \textit{Matching Regulation}, which are going to explained in detail respectively.
+Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Service Standardization}, \textit{Decision Making Support}, \textit{Matching Regulation} and \textit{Platform Assistance} which are going to explained in detail respectively.
 
 The scheduling effect can be estimated and observed through \textit{Service Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.
+
+\subsection{Service Standardization} % (fold)
+\label{sub:service_standardization}
+
+% subsection service_standardization (end)
 
@@
 
+\subsection{Platform Assistance} % (fold)
+\label{sub:platform_assistance}
+
+% subsection platform_assistance (end)
+
 \subsection{Service Dashboard} % (fold)

### 2015-10-02 figures/simple_order_flow.tex
add simple order flow

% !TEX root = ../Eco-Model.tex
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going right,    % General flow is top-to-bottom
    node distance=6mm and 10mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, rectangle},
  proc/.style={base, text width=6em, minimum height=8em},
  term/.style={base, text width=5em, rounded corners, minimum height = 3ex},
  dproc/.style={proc, minimum height = 20ex},
  gathe/.style={draw, on chain, on grid, align=center, circle, minimum height=4ex, text width=0.5em, node distance=10mm and 8mm},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  sky/.style={coordinate, on chain, on grid, node distance=6mm and 60mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [term, fill = lcfree!25]              {Order};
\node [proc, join=by free]  (p1) {Task Hub};
\node [proc, dashed] (d) {};
\node [term, xshift = 12mm] (oc) {Order Check};
\node [term, join=by cong, fill = lccong!25]  {Submit};

\node [gathe, right=of d,yshift=5mm, xshift= 15mm] (g1) {};
\node [term, below=of d, yshift=15.5mm] (u1) {User 1};
\node [term, below=of u1] (u2) {User 2};
\node [below=-1mm of u2] (u3) {$\vdots$};
\node [term,below=of u3, yshift=-1mm] (u4) {User n};
\node [below=of u4,yshift=2.6mm] {User Cluster};
\node [gathe, below=of g1] (g2) {};
\node [coord, above=of g1, yshift=8mm] (c1) {};

\draw [->, lccong] (g2) -- (oc.west);
\draw [->, lcnorm] (p1) -- (u1.west);
\draw [->, lcnorm] (p1) -- (u2.west);
\draw [->, lcnorm] (p1) -- (u4.west);

\draw [->, lcnorm] (u1.east) -- (g1.west);
\draw [->, lccong] (u1.east) -- (g2.west);
\draw [->, lcnorm] (u2.east) -- (g1.west);
\draw [->, lccong] (u2.east) -- (g2.west);
\draw [->, lcnorm] (u4.east) -- (g1.west);
\draw [->, lccong] (u4.east) -- (g2.west);
\draw [->, lcnorm] (g1) -- (c1) -- node [black, near end, yshift=0.75em, it]
    {(Outsourcing)} ++(-3.5cm,0) -| (p1) ;

\end{tikzpicture}

### 2015-10-02 schedule.tex
add simple order flow

@@
 OAS  
-
+\begin{figure}[!h]
+\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
+\caption{Primary Flow of Order}
+\label{fig:orderflow}
+\end{figure}
 Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Service Standardization}, \textit{Decision Making Support}, \textit{Matching Regulation} and \textit{Platform Assistance} which are going to explained in detail respectively.

### 2015-10-02 schedule.tex
start the schedule and evolve modules.

--- 2015-10-02 schedule.tex
@@
 
-OAS
+===================================
+
+A scheduling methodology for production services is presented
+by [59]. Order decomposition into tasks, the selection of one or several
+service providers to perform them, and the scheduling of the whole
+manufacturing process is considered. In [60], a resource scheduling
+framework is proposed. On the basis of stochastic advanced Petri net,
+queue balancing cutover (QBC) strategy is put forward as a solution to
+the issue of request dispatching. The scheduling of collaborative
+design tasks is described in [61], presenting a new immune genetic
+algorithm. Improved searching diversity based on immune strategy, but
+also adaptive adjustment for probabilities of crossover and mutation
+with low time complexity are achieved with this concept.
+
+==================================
 
@@
 \label{sub:service_standardization}
+Service standardization based mainly on  resource virtualization and encapsulation, where many models and methods were build on software and hardware like \cite{Li2011,Wu2011,Li2011a,Liu2011}.
+However, even if these resources were contrcuted into services with these models or methods, the difficulty of services scheduling changed slightly, for the absence of service standardization and similar type of services always turn out in different apperances.
 
+Standardization is a process of Principal Component Analysis, like Guo et al.\cite{Guo2011} mined the correlation relationship of service composition in Cloud Manufacturing, we can use Online Learning\cite{Shalev-Shwartz2011} to mine out service prototypes and to refine them as case arrives by, where the sequential study cases are the continuous transactions.
 % subsection service_standardization (end)
@@
 
+OAS  
+\begin{figure}[!h]
+%\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
+\caption{Primary Flow of Order}
+\label{fig:orderflow}
+\end{figure}
+
 % subsection decision_making_support (end)
@@
 \label{sub:matching_regulation}
+There are two main parts, recommendation for resource matching and resource prediction, of resources recommendation module that we will discuss in \autoref{sub:recommand_system}, and the first one depicted the situation where user in buyer role will always encounter.
 
+In order to recommand poper manufacturing service with the order user submitted, service search engine should adopt a series of well designed matching regulations.
+Platform will collect the hit or miss data that feeded back from user, to train the classifier.
 % subsection matching_regulation (end)
@@
 \label{sub:platform_assistance}
-
+a guide for scheduling 
 % subsection platform_assistance (end)
@@
 \label{sub:service_dashboard}
-
+a monitor
 % subsection service_dashboard (end)

### 2015-10-03 schedule.tex
start the Decision Making Support

@@
 
-===================================
+Most studies on the service scheduling issue in Cloud Manufacturing like Lartigau et al.\cite{Lartigau2012} considered the whole Cloud Manufacturing system as one giant enterprise, so that it's easy to transform the problem into the classical flexible job shop problem.
+However, the heteroid Users in Cloud Manufacturing always not have the consistent objects.
+Hence, we should take the look at personalized scheduling support in both self-oriented and platform-auxiliary scheduling.
+(See \autoref{sub:decision_making_support} and \ref{sub:platform_assistance} respectively)
 
-A scheduling methodology for production services is presented
-by [59]. Order decomposition into tasks, the selection of one or several
-service providers to perform them, and the scheduling of the whole
-manufacturing process is considered. In [60], a resource scheduling
-framework is proposed. On the basis of stochastic advanced Petri net,
-queue balancing cutover (QBC) strategy is put forward as a solution to
-the issue of request dispatching. The scheduling of collaborative
-design tasks is described in [61], presenting a new immune genetic
-algorithm. Improved searching diversity based on immune strategy, but
-also adaptive adjustment for probabilities of crossover and mutation
-with low time complexity are achieved with this concept.
-
-==================================
-
-Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Service Standardization}, \textit{Decision Making Support}, \textit{Matching Regulation} and \textit{Platform Assistance} which are going to explained in detail respectively.
+Most of the related methodologies can be archived into \textbf{four} main modules, namely
+\begin{inparaenum}[1)]
+\item Service Standardization,
+\item Decision Making Support,
+\item Matching Regulation and
+\item Platform Assistance,
+\end{inparaenum} which are going to be explained in detail respectively.
 
@@
 
-In order to recommand poper manufacturing service with the order user submitted, service search engine should adopt a series of well designed matching regulations.
+In order to recommand poper manufacturing service with the order user submitted, Cloud Manufacturing platfrom should provide best-match solution, thus service search engine need to adopt a series of well designed matching regulations.
 Platform will collect the hit or miss data that feeded back from user, to train the classifier.

### 2015-10-03 schedule.tex
oas

@@
 \begin{inparaenum}[1)]
-\item Service Standardization,
-\item Decision Making Support,
-\item Matching Regulation and
-\item Platform Assistance,
+\item Service standardization;
+\item Decision making support;
+\item Matching regulation and
+\item Platform assistance,
 \end{inparaenum} which are going to be explained in detail respectively.
@@
 
-OAS  
+For users in Cloud Manufacturing platfrom, their main acitvities are related to orders, no matter buyer or seller role they play in. The principal flow of order is shown in \autoref{fig:orderflow}, 
 \begin{figure}[!h]
-%\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
-\caption{Primary Flow of Order}
+\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
+\caption{Principal Flow of Order}
 \label{fig:orderflow}
 \end{figure}
+users will make many decisions for
+\begin{inparaenum}[1)]
+\item Order acceptance;
+\item Task decomposition;
+\item Task (re-)outsourscing;
+\item Seller selection;
+\item Manufacturing arrangement
+\end{inparaenum}
+and so forth.
+
+Among these decisions, Order acceptance, Seller selection and Manufacturing arrangement can be descript as a classic order acceptance and scheduling problem, which has received increasing attention in recent years\cite{Og˘uz2010,Nobibon2011,Cesaret2012}.
+Task decomposition and (re-)outsourscing
 

### 2015-10-03 envolve.tex
reconstruct logically
init on mac
start to deal with the user rank
give up simulation
add simple order flow
start the schedule and evolve modules.
first submit

@@
 % !TEX root = Eco-Model.tex
-\section{Envolve} % (fold)
+\section{Manufacturing Ecosystem Envolving} % (fold)
 \label{sec:envolve}
+\subsection{Envolving Aim and Main Factors} % (fold)
+\label{sub:envolving_aim}
+The aim of envolving in the Ecosystem is to optimize the utilize of manufacturing resources, find the adaptive operation mode for enterprises and filter out the underisable enterprises.
+In the process of envolving related
+main factors including:
+\begin{inparaenum}[1)]
+\item Rating Schema;
+\item Recommand System and
+\item Criterion of User Introduction and Elimination
+\end{inparaenum}
 
+\subsection{Rating Schema} % (fold)
+\label{sub:rating_schema}
+Rating user's rank is the base of Recommand System, from the time users were introduced in the system, their rank changing flow can be viewed like \autoref{fig:userrank}, 
+\begin{figure}[!h]
+\centering\small
+\resizebox{0.6\textwidth}{!}{\input{figures/user_rank}}
+\caption{Primary Flow of User Rank}
+\label{fig:userrank}
+\end{figure}
+rating schema will be developed via the flow.
+
+Elo Rating System\cite{Elo1978} is a classic rating system for the ranking of chessplayer, most modern rating systems are derived from Elo's model:
+
+\begin{numcases}{}
+E_A = \frac{1}{1+10^{\frac{R_B-R_A}{400}}} \label{equ:elo1}\\
+R_A := R_A + K(S_A - E_A) \label{equ:elo2} \\
+E_B = \frac{1}{1+10^{\frac{R_A-R_B}{400}}} \label{equ:elo3} \\
+R_B := R_B + K(S_B - E_B) \label{equ:elo4} 
+\end{numcases}
+In \eqref{equ:elo1} - \eqref{equ:elo4}, $R_A$ and $R_B$ represent the rating of user $A$ and $B$, $E_A$ and $E_B$ represent the expected score of user $A$ and $B$ while $S_A$ and $S_B$ represent the actual score of them.
+
+The assumption in the modle is that user's rank transfer from loser to winer, but there is no winner or loser in any transactions, so the modle should be reformed to suit the system.
+% subsection rating_schema (end)
+
+\subsection{Recommand System} % (fold)
+\label{sub:recommand_system}
+There are two scenarios in recommendation: \begin{inparaenum}[1)]
+\item Service Searching and
+\item Platform priority setting.
+\end{inparaenum}
+The first one is familar with the common use of recommend system, which use Collaboration Filtering method widely.
+Without no doubt, Collaboration Filtering Algorithm is the most popular algorithm in the recommand system, this algorithm use the history data of users' translations and their rated ratings, to archive customers and items simultaneously, then to make the recommendations.
+Let $r_{ui}$ be the rating made by user $u$ of item $i$ and $\hat{r}_{ui}$, the Latent Factor model\cite{koren2008factorization} using Collaboration Filtering algorithm goes like:
+
+\begin{numcases}{}
+\min_{p_*,q_*,b_*}\sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
+\label{equ:latent1}\\
+\hat{r}_{ui} = b_{ui} + p^T_uq_i \label{equ:latent2}\\
+b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
+\kappa =\{(u,i)|r_{ui}\text{is known}\} \label{equ:latent4}
+\end{numcases}
+This model \eqref{equ:latent1} - \eqref{equ:elo4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet.
+\eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector.
+This model can be solved by Gradient Descent method and $p_*,q_*,b_*$ are the optimal value.
+
+The second one is also commonly used in nowadays business mode like Uber, administrator in platform analysed the resource load and other information of resource situation, made high priority of newly or low loaded resources by bonus to buysers.
+
+% subsection recommand_system (end)
+
+\subsection{User Introduction and Elimination} % (fold)
+\label{sub:control}
+Finally, administrators make the strategy for introduction and elimination of users, they can easily set a baseline and assess the user to make the decision.  
+% subsection control (end)
 % section envolve (end)

### 2015-10-03 schedule.tex
first submit

@@
 
-The scheduling effect can be estimated and observed through \textit{Service Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.
+The scheduling effect can be estimated and observed through \textit{Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.
 
@@
 Among these decisions, Order acceptance, Seller selection and Manufacturing arrangement can be descript as a classic order acceptance and scheduling problem, which has received increasing attention in recent years\cite{Og˘uz2010,Nobibon2011,Cesaret2012}.
-Task decomposition and (re-)outsourscing
+Task decomposition and (re-)outsourscing can be descript as the decision making problem for users.
+Within the permission users get, they can tune the proportion of outsourscing.
 
@@
 \label{sub:platform_assistance}
-a guide for scheduling 
+Platform-auxiliary part of services scheduling is about the priority setting for tasks to be deal or for services to select, both are merely recommendation in the global view from administrator.
+Users can get bonus if they take the priority setting, but they won't get punishment if they don't.
+As a result, two main issues have came: \begin{inparaenum}[1)]
+\item How to make priority setting recommendation and
+\item How to make decisions with the recommendation?
+\end{inparaenum}
 % subsection platform_assistance (end)
 
-\subsection{Service Dashboard} % (fold)
+\subsection{Dashboard} % (fold)
 \label{sub:service_dashboard}
-a monitor
+Platform provides the Dashbord module for users to check the services usage and order process, comprehensive rank information, credit status and so on.
 % subsection service_dashboard (end)

### 2015-10-05 envolve.tex
ref the right equ

@@
 \end{numcases}
-This model \eqref{equ:latent1} - \eqref{equ:elo4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet.
+This model \eqref{equ:latent1} - \eqref{equ:latent4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet.
 \eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector.

### 2015-10-05 beamer/intro.tex
start the beamer

% !TEX root = ../beamer.tex
\section{Introduction}

\subsection{lalala}

\begin{frame}{First Slide Title}{Optional Subtitle}
  \begin{itemize}
  \item {
    My first point.
  }
  \item {
    My second point.
  }
  \end{itemize}
\end{frame}

\subsection{Second Subsection}

% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{Second Slide Title}
  \begin{itemize}
  \item {
    First item.
    \pause % The slide will pause after showing the first item
  }
  \item {   
    Second item.
  }
  % You can also specify when the content should appear
  % by using <n->:
  \item<3-> {
    Third item.
  }
  \item<4-> {
    Fourth item.
  }
  % or you can use the \uncover command to reveal general
  % content (not just \items):
  \item<5-> {
    Fifth item. \uncover<6->{Extra text in the fifth item.}
  }
  \end{itemize}
\end{frame}

### 2015-10-05 beamer/preliminary.tex
start the beamer

% !TEX root = ../beamer.tex
\section{Preliminary}

\subsection{Another Subsection}

\begin{frame}{Blocks}
\begin{block}{Block Title}
You can also highlight sections of your presentation in a block, with it's own title
\end{block}
\begin{theorem}
There are separate environments for theorems, examples, definitions and proofs.
\end{theorem}
\begin{example}
Here is an example of an example block.
\end{example}
\end{frame}

% Placing a * after \section means it will not show in the
% outline or table of contents.

### 2015-10-05 beamer/summary.tex
start the beamer

% !TEX root = ../beamer.tex
\section*{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}

  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}

### 2015-10-07 beamer/envolve.tex
main struct

% !TEX root = ../beamer.tex
\section{Manufacturing Ecosystem Envolving}
\subsection{Envolving Aim \& Main Factors}
\begin{frame}{Manufacturing Ecosystem Envolving}{Envolving Aim \& Main Factors}

\end{frame}

\subsection{Rating Schema}
\begin{frame}{Manufacturing Ecosystem Envolving}{Rating Schema}

\end{frame}

\subsection{Recommand System}
\begin{frame}{Manufacturing Ecosystem Envolving}{Recommand System}

\end{frame}

\subsection{User Introduction \& Elimination}
\begin{frame}{Manufacturing Ecosystem Envolving}{User Introduction \& Elimination}

\end{frame}

### 2015-10-07 beamer/schedule.tex
main struct

% !TEX root = ../beamer.tex
\section{Services Scheduling}
\subsection{Standardization}
\begin{frame}{Services Scheduling}{Main}

\end{frame}
\subsection{Decision Making Support}
\begin{frame}{Services Scheduling}{Decision Making Support}

\end{frame}

\subsection{Matching Regualtion}
\begin{frame}{Services Scheduling}{Matching Regualtion}

\end{frame}

\subsection{Platform Assistance}
\begin{frame}{Services Scheduling}{Platform Assistance}

\end{frame}

### 2015-10-14 beamer/envolve.tex
init beamer

@@
 \subsection{Envolving Aim \& Main Factors}
-\begin{frame}{Manufacturing Ecosystem Envolving}{Envolving Aim \& Main Factors}
-
+\begin{frame}{Envolving Aim \& Main Factors}{Manufacturing Ecosystem Envolving}
+\onslide<+->{The aim of envolving in the Ecosystem is to: \begin{itemize}
+\item optimize the utilize of manufacturing resources
+\item find the adaptive operating model for enterprises
+\item filter out the underisable enterprises.
+\end{itemize}}
+\onslide<+->{
+\begin{block}{Main Factors for Envolving}
+\begin{itemize}
+\item Rating Schema;
+\item Recommand System and
+\item Criterion of User Introduction and Elimination
+\end{itemize}
+\end{block}}
 \end{frame}
@@
 \subsection{Rating Schema}
-\begin{frame}{Manufacturing Ecosystem Envolving}{Rating Schema}
-
+\begin{frame}{Rating Schema}{Manufacturing Ecosystem Envolving}
+\onslide<+->{Rating user's rank is the base of Recommand System, so the rating schema should be designed. Most modern rating systems are derived from Elo's model:}
+\onslide<+->{\begin{numcases}{}
+E_A = \frac{1}{1+10^{\frac{R_B-R_A}{400}}} \\
+R_A := R_A + K(S_A - E_A) \\
+E_B = \frac{1}{1+10^{\frac{R_A-R_B}{400}}} \\
+R_B := R_B + K(S_B - E_B)
+\end{numcases}}
 \end{frame}
@@
 \subsection{Recommand System}
-\begin{frame}{Manufacturing Ecosystem Envolving}{Recommand System}
-
+\begin{frame}{Recommand System}{Manufacturing Ecosystem Envolving}
+\onslide<+->{There are two scenarios in recommendation:
+\begin{itemize}
+\item Service Searching
+\item Platform priority setting
+\end{itemize}
+}
+\onslide<+->{
+	Collaboration Filtering is popular method used in recommand system:
+	\begin{equation}
+	\begin{split}
+	\min_{p_*,q_*,b_*} & \sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 \\
+		& + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
+	\end{split}
+	\end{equation}
+	\begin{numcases}{}
+	\hat{r}_{ui} = b_{ui} + p^T_uq_i \\
+	b_{ui} = \mu + b_u + b_i  \\
+	\kappa =\{(u,i)|r_{ui} \text{is known}\} 
+	\end{numcases}
+}
 \end{frame}
@@
 \subsection{User Introduction \& Elimination}
-\begin{frame}{Manufacturing Ecosystem Envolving}{User Introduction \& Elimination}
+\begin{frame}{User Introduction \& Elimination}{Manufacturing Ecosystem Envolving}
+\onslide<+->{
+	Ecosystem envolving need a good user introduction and elimination method with:
+}
+\onslide<+->{
+	\begin{block}{Envolving}
+	\begin{itemize}
+	\item Reinforcement Learning
+	\item Control
+	\end{itemize}
+	\end{block}
+}
+\end{frame}
 
+\subsection{Envision of the Ecosystem}
+\begin{frame}{Envision}{After a long running time and the system seems stable}
+\onslide<+->{
+	With poper scheduling and envolving, Cloud Manufacturing Ecosystem running with a stable mode:
+	\begin{block}{Stable System Envision}
+	\begin{itemize}
+		\item Less-Popular manufacturing services are utilized instead of idleness with Coupon
+		\item Products are manufactured with appropriate resource
+		\item High rank users in different type of manufacturing resource lead the industrial chain
+		\item Good operating models appear and being refined with time goes by
+	\end{itemize}
+	\end{block}
+}
 \end{frame}

### 2015-10-14 beamer/intro.tex
main struct
init beamer

@@
 
-\subsection{lalala}
+\subsection{Cloud Manufacturing}
+\begin{frame}{Brief Introduction}{Cloud Manufacturing}
+\onslide<+->{Cloud manufacturing combines technologies such as
+\begin{itemize}
+\item Internet of Things
+\item Cloud computing
+\item Semantic Web
+\item Virtualisation
+\item Service-oriented technologies
+\end{itemize}
+}
 
-\begin{frame}{First Slide Title}{Optional Subtitle}
+\onslide<+->{Aims the manufacturing process to be
 \begin{itemize}
-  \item {
-    My first point.
-  }
-  \item {
-    My second point.
-  }
-  \end{itemize}
+\item networked
+\item intelligent
+\item service-oriented
+\item knowledge-based
+\item energy efficient
+\end{itemize}}
 \end{frame}
 
-\subsection{Second Subsection}
+\subsection{Current Items}
 
-% You can reveal the parts of a slide one at a time
-% with the \pause command:
-\begin{frame}{Second Slide Title}
+\begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
+\textbf{Item}: \textit{Key Technologies Research on Cloud Manufacturing Platform for Group Enterprises (No. 2015AA042101)}
+\begin{block}{Main Tasks}
   \begin{itemize}
-  \item {
-    First item.
-    \pause % The slide will pause after showing the first item
-  }
-  \item {   
-    Second item.
-  }
-  % You can also specify when the content should appear
-  % by using <n->:
-  \item<3-> {
-    Third item.
-  }
-  \item<4-> {
-    Fourth item.
-  }
-  % or you can use the \uncover command to reveal general
-  % content (not just \items):
-  \item<5-> {
-    Fifth item. \uncover<6->{Extra text in the fifth item.}
-  }
+  \item Business model and standard making in group enterprises;
+  \item Multi-tenancy technology for on-demand useage;
+  \item Platform development for enterprises (Cooperate);
+  \item Application demonstration (Cooperate).
   \end{itemize}
+\end{block}
 \end{frame}
+
+\begin{frame}{Current Items}{National Natural Science Fundation, China}
+\textbf{Item}: \textit{BOSS based Product Manufacturing-service Modeling and Cloud Platform Guided Service-network Evolving (No. 71571161)}
+\begin{block}{Main Tasks}
+\begin{itemize}
+\item Methodology study for standard Manufacturing-service;
+\item Methodology study for Manufacturing-service evalution;
+\item Optimize the matching for service and task;
+\item Explore the evolution of Manufacturing-service.
+\end{itemize}
+\end{block}
+\end{frame}

### 2015-10-14 beamer/preliminary.tex
init beamer

@@
 
-\subsection{Another Subsection}
+\subsection{Cloud Manufacturing}
+\begin{frame}{Ecosystem Main Struct}{Cloud Manufacturing}
+\only<1>{
+	\begin{figure}
+	\centering
+	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
+	\caption{Princiapl Struct of Cloud Manufacturing Ecosystem}
+	\end{figure}
+}
+\only<2>{
+	\begin{figure}
+	\centering
+	\includegraphics[height=0.82\textheight,viewport=40 0 450 250,clip=true]{figures/platformstruct.pdf}
+	\end{figure}
+}
+\only<3>{
+	\begin{figure}
+	\centering
+	\includegraphics[height=0.82\textheight,viewport=0 160 500 450,clip=true]{figures/platformstruct.pdf}
+	\end{figure}
+}
+\end{frame}
 
-\begin{frame}{Blocks}
-\begin{block}{Block Title}
-You can also highlight sections of your presentation in a block, with it's own title
+\begin{frame}{Standardization \& Decomposition}{Service \& Task}
+\onslide<+->{
+	Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub. 
+}
+\onslide<+->{
+	\begin{block}{Related Methods}
+	\begin{itemize}
+	\item Resource Virtualization
+	\item Construct Virtual Resource into Service Unit
+	\item Service Standardization
+	\item Order Decomposition into Tasks
+	\end{itemize}
 	\end{block}
-\begin{theorem}
-There are separate environments for theorems, examples, definitions and proofs.
-\end{theorem}
-\begin{example}
-Here is an example of an example block.
-\end{example}
+}
 \end{frame}
+
+\subsection{Roles}
+\begin{frame}{Usual Names}{Roles}
+\onslide<+->{\small
+	\begin{description}
+	\item[User] The main role in Cloud Manufacturing, usually acts as Seller or Buyer;
+	\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service;
+	\item[Buyer] The temporary role in a transaction, which submits the allocated part of manufacturing task;
+	\item[Administrator] The role that gets the work for the operation and maintenance of the platform.
+	\end{description}
+}
+\onslide<+->{
+\begin{table}[htbp]
+  \centering\scriptsize
+    \begin{tabular}{lcc}
+    \toprule
+        &  Seller & Buyer  \\
+    \midrule
+    Generalized User & $\surd$ & $\surd$  \\
+    Enterprise User & $\surd$ &  \\
+    Customer User& & $\surd$ \\
+    \bottomrule
+    \end{tabular}%
+\end{table}
+}
+\end{frame}
+
+\subsection{Operating Model}
+\begin{frame}{Overview}{Operating Model}
+\only<1>{The style the Cloud Manufacturing Ecosystem appears mainly depends on the way the operating model takes, therefore, research on features and issues in the Ecosystem would be taken within the scope of operating model we are going to set up in:
+\begin{block}{Operating Model Components}
+\begin{itemize}
+\item Order Flow
+\item User Rank
+\item Platform
+\end{itemize}
+\end{block}}
+\only<2>{\begin{figure}
+\tiny\centering\resizebox{\textwidth}{!}{
+\input{figures/operatingmodel.tex}}
+\caption{Overview of the Operating Model}
+\end{figure}}
+\end{frame}
+
+\begin{frame}{Order Flow}{Operating Model}
+\only<1>{Each order appears when Users make transaction in the platform, it might then go through different paths:
+\begin{figure}
+\tiny\centering
+\resizebox{\textwidth}{!}{\input{figures/simple_order_flow.tex}}
+\caption{Simple Flow Chart of Order}
+\end{figure}
+}
+\end{frame}
+
+\begin{frame}{User Rank}{Operating Model}
+\onslide<+->{User Rank provides the basis to make the recommandation and to get more permission, the rank will increase or decrease by good or bad performance in each transaction}
+\onslide<+->{
+\begin{equation}
+  \begin{cases}
+      Rank_{[T+1]} = Rank_{[T]} + Gain - Lose, & T \geqslant 1\\
+      Rank_{[0]} = Rank_{[init]}
+  \end{cases}
+\end{equation}
+}
+\end{frame}
+
+\begin{frame}{Platform}{Operating Model}
+\onslide<+->{
+	Cloud Manufacturing Platform is mantained by Administrators with:
+}
+\onslide<+->{
+	\begin{block}{Platform Maintenances}
+	\begin{itemize}
+	\item Decompose Orders into Tasks
+	\item Construct Standard Services
+	\item Introduce/Eliminate Users
+	\item Distribute Permissions
+	\item Adjust Resource Useage by Recommandations and Bonus
+	\end{itemize}
+	\end{block}
+}
+\end{frame}
+
+\subsection{Data Science Tools}
+\begin{frame}{Data Science Tools}
+\onslide<+->{In such Cloud Manufacturing Operating Model, there comes massive amount of data:\begin{itemize}
+  \item Transaction histroy;
+  \item Ranking histroy;
+  \item Status of resources, services, orders and tasks;
+  \item Decision pattern and so on.
+\end{itemize}}
+\onslide<+->{
+	A bunch of Data Science Tools can be helpful:
+	\begin{block}{Useful Data Science Tools}
+	\begin{itemize}
+	\item Data Analysis (collection, cleaning, modeling\&algorithms)
+	\item Data Warehousing
+	\item Machine Learning
+	\item Social Network Anaysis
+	\end{itemize}
+	\end{block}
+}
+\end{frame}
+
+%\begin{frame}{Blocks}
+%\begin{block}{Block Title}
+%You can also highlight sections of your presentation in a block, with it's own title
+%\end{block}
+%\begin{theorem}
+%There are separate environments for theorems, examples, definitions and proofs.
+%\end{theorem}
+%\begin{example}
+%Here is an example of an example block.
+%\end{example}
+%\end{frame}
 

### 2015-10-14 beamer/schedule.tex
init beamer

@@
 \subsection{Standardization}
-\begin{frame}{Services Scheduling}{Main}
+\begin{frame}{Support Module}{Service Standardization}
+\onslide<+->{The basic support modules for Service Standardization include:
+\begin{block}{Basic Modules}
+\begin{itemize}
+\item Resource Virtualization \& Encapsulation
+\item Clustering Method
+\item Refine Method
+\end{itemize}
+\end{block}}
 
+\onslide<+->{
+Important support Service Scheduling process modules:
+\begin{block}{Support Moudles}
+\begin{itemize}
+\item Decision Making Support
+\item Matching Regualtion
+\item Platform Assistance
+\end{itemize}
+\end{block}
+}
 \end{frame}
+
 \subsection{Decision Making Support}
-\begin{frame}{Services Scheduling}{Decision Making Support}
-
+\begin{frame}{Decision Making Support}{Services Scheduling}
+\onslide<+->{
+	Users in Cloud Manufacturing platfrom will make decision for:
+}
+\onslide<+->{
+	\begin{itemize}
+	\item Order acceptance;
+	\item Task decomposition;
+	\item Task (re-)outsourscing;
+	\item Seller selection;
+	\item Manufacturing arrangement.
+	\end{itemize}
+}
 \end{frame}
@@
 \subsection{Matching Regualtion}
-\begin{frame}{Services Scheduling}{Matching Regualtion}
-
+\begin{frame}{Matching Regualtion}{Services Scheduling}
+\onslide<+->{
+	In order to recommand poper manufacturing service with the order user submitted, Cloud Manufacturing platfrom should provide best-match solution, thus service search engine need to adopt a series of well designed matching regulations.
+}
 \end{frame}
@@
 \subsection{Platform Assistance}
-\begin{frame}{Services Scheduling}{Platform Assistance}
-
+\begin{frame}{Platform Assistance}{Services Scheduling}
+\onslide<+->{
+	Administrator assist platform to set priority for tasks and services, so the user will considerd:
+}
+\onslide<+->{
+	\begin{itemize}
+	\item How to make priority setting recommendation
+	\item How to make decisions with the recommendation
+	\end{itemize}
+}
 \end{frame}

### 2015-10-14 envolve.tex
init beamer

@@
 \label{sub:envolving_aim}
-The aim of envolving in the Ecosystem is to optimize the utilize of manufacturing resources, find the adaptive operation mode for enterprises and filter out the underisable enterprises.
+The aim of envolving in the Ecosystem is to optimize the utilize of manufacturing resources, find the adaptive operating model for enterprises and filter out the underisable enterprises.
 In the process of envolving related
@@
 b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
-\kappa =\{(u,i)|r_{ui}\text{is known}\} \label{equ:latent4}
+\kappa =\{(u,i)|r_{ui} \text{is known}\} \label{equ:latent4}
 \end{numcases}
@@
 % subsection control (end)
+
+\subsection{Reinforcement Learning and Control} % (fold)
+\label{sub:reinforcement_learning_and_control}
+test figure
+
+% subsection reinforcement_learning_and_control (end)
 % section envolve (end)

### 2015-10-14 figures/operatingmodel.tex
init beamer

% !TEX root = flow_head.tex
\begin{tikzpicture}[
 >=triangle 60,              % Nice arrows; your taste may be different
 start chain=going right,    % General flow is top-to-bottom
 node distance=12em and 3em, % Global setup of box spacing
 every join/.style={norm},   % Default linetype for connecting boxes
]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  every node/.style={rectangle split, rectangle split parts=2, rectangle split horizontal, rectangle split part fill={lccong!25, yellow!10}, draw, anchor=center, minimum height=9em, on chain, on grid, text width=2em},
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  Arrow/.style={thick, decoration={markings,mark=at position
   1 with {\arrow[semithick]{open triangle 60}}},
   double distance=1.4pt, shorten >= 5.5pt,
   preaction = {decorate},
   postaction = {draw,line width=1.4pt, white,shorten >= 4.5pt},fill = lcnorm!25},
  test/.style={base, diamond, aspect=2, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm, thick},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}},
  tw/.style={text width=9.5em},
  th/.style={text width=2em}
}

\newcommand{\one}[1]{\nodepart[th]{one}\rotatebox{90}{\bf\shortstack{#1}}}
\newcommand{\two}{\nodepart[tw]{two}}

\node (n1)
{	
	\one{Submit\\ Order}
	\two
	\begin{inparaenum}
	\item 1.Original\\
	\item 2.Outsourcing\\
	\item 3.Platform Coupon
	\end{inparaenum}
};

\node[join] (n2) 
{
	\one{Standard\\ Construct}
	\two
	\begin{inparaenum}
	\item 1.Order $\to$ Task\\
	\item 2.Sercice Bundle\\
	\item 3.Task Position
	\end{inparaenum}
};

\node[join] (n3)
{
	\one{Match\\ Service}
	\two
	\begin{inparaenum}
	\item 1.Recommandation\\
	\item 2.Service Status\\
	\item 3.Bonus\\
	\item 4.Seller Rank
	\end{inparaenum}
};

\node[below=of n3,join] (n4)
{
	\one{Confirm\\ by Other}
	\two
	\begin{inparaenum}
	\item 1.Accept Tasks\\
	\item 2.Check Due-date\\
	\item 3.Buyer Rank
	\end{inparaenum}
};

\node[below=of n2,join] (n5)
{
	\one{Manufacture\\
	\& Delivery}
	\two
	\begin{inparaenum}
	\item 1.Finish Job\\
	\item 2.Outsourcing\\
	\item 3.Pieces $\to$ Product
	\end{inparaenum}
};

\node[below=of n1,join] (n6)
{
	\one{Mutual\\ Rating}
	\two
	\begin{inparaenum}
	\item 1.Rate Seller\\
	\item 2.Rate Buyer\\
	\item 3.Change Rank\\
	\item 4.Affect Recommand
	\end{inparaenum}
};
\end{tikzpicture}

### 2015-10-14 figures/simple_order_flow.tex
init beamer

@@
     start chain=going right,    % General flow is top-to-bottom
-    node distance=6mm and 10mm, % Global setup of box spacing
+    node distance=1.6em and 2.5em, % Global setup of box spacing
     every join/.style={norm},   % Default linetype for connecting boxes
@@
 
-\node [gathe, right=of d,yshift=5mm, xshift= 15mm] (g1) {};
-\node [term, below=of d, yshift=15.5mm] (u1) {User 1};
+\node [gathe, right=of d,yshift=5mm, xshift= 4em] (g1) {};
+\node [term, below=of d, yshift=4.1em] (u1) {User 1};
 \node [term, below=of u1] (u2) {User 2};
@@
 \node [gathe, below=of g1] (g2) {};
-\node [coord, above=of g1, yshift=8mm] (c1) {};
+\node [coord, above=of g1, yshift=2em] (c1) {};
 
@@
 \draw [->, lcnorm] (g1) -- (c1) -- node [black, near end, yshift=0.75em, it]
-    {(Outsourcing)} ++(-3.5cm,0) -| (p1) ;
+    {(Outsourcing)} ++(-9em,0) -| (p1) ;
 

### 2015-10-14 schedule.tex
init beamer

@@
 \label{sub:matching_regulation}
-There are two main parts, recommendation for resource matching and resource prediction, of resources recommendation module that we will discuss in \autoref{sub:recommand_system}, and the first one depicted the situation where user in buyer role will always encounter.
+There are two main parts, recommendation for resource matching and idle resource, of resources recommendation module that we will discuss in \autoref{sub:recommand_system}, and the first one depicted the situation where user in buyer role will always encounter.
 

### 2015-10-22 beamer/intro.tex
modify the first version

@@
 \begin{frame}{Brief Introduction}{Cloud Manufacturing}
-\onslide<+->{Cloud manufacturing combines technologies such as
+\onslide<+->{Cloud manufacturing technologies including
 \begin{itemize}
@@
 }
-
 \onslide<+->{Aims the manufacturing process to be
@@
 
+\begin{frame}{Initial Results}{Cloud Manufacturing}
+\only<1>{\begin{figure}
+\centering
+\includegraphics[width=0.95\textwidth]{figures/mainpage.png}
+\caption{\href{http://mie.zju.edu.cn/cloud/}{Portal Web}}
+\end{figure}}
+\only<2>{
+	\begin{block}{Main Component of Cloud Manufacturing prototype system}
+		\begin{itemize}
+			\item Platform portal system
+			\item Order/Task management system
+			\item Resource/Service management system
+			\item Knowledgement management system
+			\item Commercial application sharing system
+		\end{itemize}	
+	\end{block}
+}
+\end{frame}
+
 \subsection{Current Items}
@@
 \begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
-\textbf{Item}: \textit{Key Technologies Research on Cloud Manufacturing Platform for Group Enterprises (No. 2015AA042101)}
+\textbf{Foundation Item}: \textit{Key Technologies Research on Cloud Manufacturing Platform for Group Enterprises (No. 2015AA042101)}
 \begin{block}{Main Tasks}
   \begin{itemize}
-  \item Business model and standard making in group enterprises;
-  \item Multi-tenancy technology for on-demand useage;
+  \item Business model and standard formulating in group enterprises;
+  \item Multi-tenancy technology for on-demand usage;
   \item Platform development for enterprises (Cooperate);
@@
 \end{frame}
+\begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
+	\begin{figure}
+		\centering
+		\includegraphics[height=0.85\textheight]{figures/techrouteorange.pdf}
+		\caption{Technology Roadmap}
+	\end{figure}
+\end{frame}
 
-\begin{frame}{Current Items}{National Natural Science Fundation, China}
-\textbf{Item}: \textit{BOSS based Product Manufacturing-service Modeling and Cloud Platform Guided Service-network Evolving (No. 71571161)}
+\begin{frame}{Current Items}{National Natural Science Foundation, China}
+\textbf{Foundation Item}: \textit{BOSS based Product Manufacturing-service Modeling and Cloud Platform Guided Service-network Evolving (No. 71571161)}
 \begin{block}{Main Tasks}
@@
 \end{frame}
+\begin{frame}{Current Items}{National Natural Science Foundation, China}
+	\begin{figure}
+		\centering
+		\includegraphics[height=0.85\textheight]{figures/nsf.pdf}
+		\caption{Main technical research relationship map}	
+	\end{figure}
+\end{frame}

### 2015-10-22 beamer/preliminary.tex
modify the first version

@@
 \subsection{Cloud Manufacturing}
-\begin{frame}{Ecosystem Main Struct}{Cloud Manufacturing}
+\begin{frame}{Ecosystem Main Structure}{Cloud Manufacturing}
 \only<1>{
@@
 	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
-	\caption{Princiapl Struct of Cloud Manufacturing Ecosystem}
+	\caption{Princiapl Structure of Cloud Manufacturing Ecosystem}
 	\end{figure}
 }
+\iffalse
 \only<2>{
@@
 	\centering
-	\includegraphics[height=0.82\textheight,viewport=40 0 450 250,clip=true]{figures/platformstruct.pdf}
+	\includegraphics[height=0.82\textheight,viewport=40 0 500 250,clip=true]{figures/platformstruct.pdf}
 	\end{figure}
@@
 }
+\fi
 \end{frame}
 
-\begin{frame}{Standardization \& Decomposition}{Service \& Task}
+\begin{frame}{Service Standardization}{Cloud Manufacturing}
+\begin{figure}
+\centering
+\includegraphics[height=0.85\textheight]{figures/boss.pdf}
+\caption{Standard Service Tree Illustration}
+\end{figure}
+\iffalse
 \onslide<+->{
@@
 }
+\fi
 \end{frame}
@@
 \tiny\centering\resizebox{\textwidth}{!}{
-\input{figures/operatingmodel.tex}}
-\caption{Overview of the Operating Model}
+\input{figures/sellerflow.tex}}
+\caption{Seller Flow in Operating Model}
+\end{figure}}
+\only<3>{\begin{figure}
+\tiny\centering\resizebox{\textwidth}{!}{
+\input{figures/buyerflow.tex}}
+\caption{Buyer Flow in Operating Model}
 \end{figure}}
@@
 \tiny\centering
-\resizebox{\textwidth}{!}{\input{figures/simple_order_flow.tex}}
+%\resizebox{\textwidth}{!}{\input{figures/order_flow.tex}
+\includegraphics[height=0.9\textheight,angle=90]{figures/orderflow.pdf}
+%}
 \caption{Simple Flow Chart of Order}

### 2015-10-22 figures/platformstruct.tex
modify the first version

--- 2015-09-29 figures/platformstruct.tex
@@
 child [concept color = gray]{ node {User}
+  child { node {Seller}
+    child { node {Provide Resources}}
+    child { node {Schedule Orders}}
+    child { node {Outsource Orders}}
+    child { node {Evaluate Buyer}}
+  }
+  child
+  child { node {Buyer}
     child { node {Submit Order}}
-  child { node {Provide Resource}}
-  child { node {Make Transaction}}
-  child { node {Evalute Others}}
+    child { node {Choose Seller}}
+    child { node {Evaluate Seller}}
   }
-child [concept color = gray]{ node {Envolve}
+  }
+child [concept color = gray]{ node {Evolve}
   child { node {Optimization}

### 2015-11-16 beamer/envolve.tex
add reinforcement learning
commit after come back

@@
 % !TEX root = ../beamer.tex
-\section{Manufacturing Ecosystem Envolving}
-\subsection{Envolving Aim \& Main Factors}
+\section{Manufacturing Ecosystem Evolution}
+\subsection{Evolution Aim \& Main Factors}
 \begin{frame}{Envolving Aim \& Main Factors}{Manufacturing Ecosystem Envolving}
-\onslide<+->{The aim of envolving in the Ecosystem is to: \begin{itemize}
+\only<1-2>{The evolution  aim in the Ecosystem is to: \begin{itemize}
 \item optimize the utilize of manufacturing resources
 \item find the adaptive operating model for enterprises
-\item filter out the underisable enterprises.
+\item filter out the undesirable enterprises.
 \end{itemize}}
-\onslide<+->{
-\begin{block}{Main Factors for Envolving}
+\only<2>{
+\begin{block}{Main Factors for Evolution}
 \begin{itemize}
 \item Rating Schema;
-\item Recommand System and
+\item Recommand System;
 \item Criterion of User Introduction and Elimination
@@
 \end{block}}
+\only<3>{
+	\begin{figure}\centering
+		\includegraphics[width =\textwidth]{figures/wanting.png}
+		\caption{The Ideal Model of the System}
+	\end{figure}
+}
 \end{frame}
@@
 \begin{frame}{Rating Schema}{Manufacturing Ecosystem Envolving}
-\onslide<+->{Rating user's rank is the base of Recommand System, so the rating schema should be designed. Most modern rating systems are derived from Elo's model:}
+\onslide<+->{Rating user's rank is the base of Recommand System, so the rating schema should be designed. Most modern rating systems are derived from Elo's model}
 \onslide<+->{\begin{numcases}{}
@@
 \subsection{Recommand System}
-\begin{frame}{Recommand System}{Manufacturing Ecosystem Envolving}
+\begin{frame}{Recommandation System}{Manufacturing Ecosystem Evolution}
 \onslide<+->{There are two scenarios in recommendation:
@@
 \onslide<+->{
-	Collaboration Filtering is popular method used in recommand system:
+	Collaboration Filtering is a popular method used in recommand system:
 	\begin{equation}
@@
 \onslide<+->{
-	\begin{block}{Envolving}
+	\begin{block}{Evolution}
 	\begin{itemize}
@@
 \onslide<+->{
-	With poper scheduling and envolving, Cloud Manufacturing Ecosystem running with a stable mode:
+	With poper scheduling and evolution, Cloud Manufacturing Ecosystem running with a stable mode:
 	\begin{block}{Stable System Envision}
 	\begin{itemize}
-		\item Less-Popular manufacturing services are utilized instead of idleness with Coupon
-		\item Products are manufactured with appropriate resource
-		\item High rank users in different type of manufacturing resource lead the industrial chain
-		\item Good operating models appear and being refined with time goes by
+		\item Less-Popular manufacturing services are utilization instead of idleness with Coupon
+		\item Products are manufactured with appropriate resources
+		\item High rank users in different types of manufacturing resource lead the industrial chain
+		\item Good operating models improved with time goes by
 	\end{itemize}
@@
 \end{frame}
+
+\subsection{Simple Demo} % (fold)
+\label{sub:simple_demo}
+\begin{frame}{Simple Demo}
+\only<1>{
+Based on Elo model, we focus on the how sellers' ranks will
+change with different specifications.
+
+If we set $Q_A=10^{\frac{R_A}{400}}$ and $Q_B=10^{\frac{R_B}{400}}$, we have:
+$$
+\begin{cases}
+E_A = \frac{Q_A}{Q_A + Q_B}\\
+E_B = \frac{Q_B}{Q_B + Q_A}
+\end{cases}
+$$}
+\only<2>{
+For entity in the ecosystem(seller) $i,k$ ($i,k=1,2,\dots,n$), we assume that:
+$$
+\begin{cases}
+Q_A = Q_i\\
+Q_B = \frac{\sum_{k}\alpha_{ik}Q_k}{\sum_{k}\alpha_{ik}}
+\end{cases}
+$$
+Where $\alpha_{ik}$ is the threating coefficient, the bigger the values is, the heigher $k$ threatens $i$.
+
+\begin{center}
+\href{localhost:8888}{\large Demo}
+\end{center}
+}
+\end{frame}
+% subsection simple_demo (end)
+\iffalse
+\subsection{Reinforcement Learning and Control} % (fold)
+\label{sub:reinforcement_learning_and_control}
+\begin{frame}{Aim}{Reinforcement Learning}
+\begin{block}{The aim}
+\begin{itemize}
+	\item Uncover the right action for user
+	\item Uncover the right action for administrator to make adjustments
+	\item From the view of user
+	\item From the view of industrial chain
+\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}{Main Parts}{Reinforcement Learning}
+\begin{block}{Main parts and steps}
+\begin{itemize}
+	\item Define states
+	\item Design actions
+	\item Set reward function
+	\item Design state simulation
+	\item Simulate
+\end{itemize}
+\end{block}
+\end{frame}
+\fi

### 2015-11-16 beamer/preliminary.tex
mutual rating
commit after come back

@@
 	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
-	\caption{Princiapl Structure of Cloud Manufacturing Ecosystem}
+	\caption{Principal Structure of Cloud Manufacturing Ecosystem}
 	\end{figure}
@@
 	\begin{description}
-	\item[User] The main role in Cloud Manufacturing, usually acts as Seller or Buyer;
+	\item[User] The main role in Cloud Manufacturing, usually acts as a Seller or a Buyer;
 	\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service;
@@
 \begin{frame}{User Rank}{Operating Model}
-\onslide<+->{User Rank provides the basis to make the recommandation and to get more permission, the rank will increase or decrease by good or bad performance in each transaction}
+\onslide<+->{
+The recommendation for tasks or services will be easily permissible, if their owner got high user rank,
+the rank will change for their performance in every transaction }
 \onslide<+->{
@@
 }
+\onslide<+->{
+	This equation set shows a simple user rank change style for both a seller and a buyer.
+}
 \end{frame}
 
+\begin{frame}{Rank Change}{Operating Model}
+\onslide<+->{
+	\begin{figure}
+	\centering
+	\includegraphics[trim=0 20 0 0,height=0.85\textheight]{figures/mutual.pdf}
+	\caption{Mutual Evaluation for Input}
+	\end{figure}
+}
+\end{frame}
+
+\iffalse
 \begin{frame}{Platform}{Operating Model}
@@
 \end{frame}
-
+\fi
 %\begin{frame}{Blocks}

### 2015-11-16 beamer/schedule.tex
commit after come back

@@
 \item Clustering Method
-\item Refine Method
+\item Imporvement Method
 \end{itemize}
@@
 Important support Service Scheduling process modules:
-\begin{block}{Support Moudles}
+\begin{block}{Support Modules}
 \begin{itemize}
@@
 \onslide<+->{
-	Users in Cloud Manufacturing platfrom will make decision for:
+	Decisions that users make in Cloud Manufacturing platform include:
 }
@@
 \onslide<+->{
-	Administrator assist platform to set priority for tasks and services, so the user will considerd:
+	Administrator assists platform to set priority for taks or services, so two aspects should be considered for users:
 }

### 2016-02-27 method.tex
修改文档的结构

% !TEX root = Eco-Model.tex
\section{Methodological Approach} % (fold)
\label{sec:methodological_approach}

\subsection{Model Assumptions and Notation} % (fold)
\label{sub:model_assumptions}

% subsection model_assumptions (end)

\subsection{Mathematical Formulation} % (fold)
\label{sub:mathematical_formulation}

% subsection mathematical_formulation (end)

\subsection{Model Validation} % (fold)
\label{sub:model_validation}

% subsection model_validation (end)

% section methodological_approach (end)

### 2016-02-27 result.tex
修改文档的结构

% !TEX root = Eco-Model.tex
\section{Numerical Results} % (fold)
\label{sec:numerical_results}

\subsection{effect of 1} % (fold)
\label{sub:effect_of_1}

% subsection effect_of_1 (end)

\subsection{effect of 2} % (fold)
\label{sub:effect_of_2}

% subsection effect_of_2 (end)

% xxx

% section numerical_results (end)

### 2016-02-27 head.tex
give up simulation

--- 2015-09-23 head.tex
@@
 
-\title{Cloud Manufacturing Ecosystem - Scheduling And Evolving}
+\title{Net title
+%Cloud Manufacturing Ecosystem - Scheduling And Evolving
+}
 
@@
 \begin{abstract}
-In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were contructed by resources is required, in order for the collaboration within the whole Industry Chain.
-This paper 
-\begin{inparaenum}[1)]
-\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
-\item modeled the services scheduling matter in the chain;
-\item designed a simulation for the Cloud Manufacturing Ecosystem;
-\item opened some Ecosystem related issues. 
-\end{inparaenum}
-With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
-gradually evolve the ecosystem to an optimal situation.
+New abstract
+% In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were constructed standardly by resources is required, in order for the collaboration within the whole Industry Chain.
+%This paper 
+%\begin{inparaenum}[1)]
+%\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
+%\item modeled the services scheduling matter in the chain;
+%\item designed evolving modules for the Cloud Manufacturing Ecosystem;
+%\item opened some Ecosystem related issues. 
+%\end{inparaenum}
+%With the help of Data Science tools on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
+%gradually evolve the ecosystem to an optimal situation.
 
@@
 %% keywords here, in the form: keyword \sep keyword
-Cloud Manufacturing \sep Ecosystem \sep simulation \sep scheduling \sep optimization
+new \sep key \sep words
+%Cloud Manufacturing  Ecosystem \sep scheduling \sep evolving \sep optimization
 %% MSC codes here, in the form: \MSC code \sep code

### 2016-02-27 review.tex

% !TEX root = Eco-Model.tex
\section{Literature Review} % (fold)
\label{sec:literature_review}

% section literature_review (end)

### 2016-02-27 background.tex
修改框架

% !TEX root = Eco-Model.tex
\section{Problem Background} % (fold)
\label{sec:problem_background}

% section problem_background (end)

### 2016-03-07 background.tex
细微调整结构框架，准备开始框架修改和文献综述并行。
阶段性定框架
add the enterprise model
start the report

@@
 
+\subsection{Cloud Manufacturing Ecosystem} % (fold)
+\label{sub:cloud_manufacturing_ecosystem}
+
+Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions.
+For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on
+
+\subsubsection{Enterprise Business Mode}
+
+\subsubsection{Resource Sharing Mechanism}
+
+\subsubsection{Ecosystem Adjustment}
+
+% subsection cloud_manufacturing_ecosystem (end)
+
+\subsection{Main Copmlexity Concepts} % (fold)
+\label{sub:main_copmlexity_concepts}
+
+\subsubsection{Self-organization}
+
+\subsubsection{Emergence}
+
+\subsubsection{Co-evolution}
+
+\subsubsection{Adaption}
+% subsection main_copmlexity_concepts (end)
+
+\subsection{Ecosystem Evolvement} % (fold)
+\label{sub:ecosystem_evolvement}
+
+% subsection ecosystem_evolvement (end)
+
+\subsection{Optimal Guidance} % (fold)
+\label{sub:optimal_guidance}
+
+% subsection optimal_guidance (end)
 % section problem_background (end)

### 2016-03-07 method.tex
增加生态系统功能框架，文献综述
阶段性定框架
add the enterprise model
start the report

@@
 
-\subsection{Model Assumptions and Notation} % (fold)
-\label{sub:model_assumptions}
+\subsection{Modeling} % (fold)
+\label{sub:modeling}
 
-% subsection model_assumptions (end)
+\subsubsection{Assumptions and Notation}
+
+Ecosystem application model including:
+\subsubsection{Enterprise Model}
+
+The Model can be described with two main parts, namely object itself(attribute) and the interaction with other enterprises(function or method)
+
+Users from platform managers, enterpirse users, customers. Even though they characteristic can be overlaped. just inherent it.
+
+Enterprise can be described as the object with attributes like 
+\begin{itemize}
+	\item Rank(reputation)
+	\item Resources(type, quantity, quality)
+	\item Capbility
+	\item Processing Status
+\end{itemize}
+
+\subsubsection{System Model}
+\begin{itemize}
+	\item Coevolution
+	\item Self-organization
+	\item Emergence	
+	\item Adaption
+\end{itemize}
+
+Coevolution consist of:
+\begin{itemize}
+	\item Scarcity of customers
+	\item Conscious choice that enables the organizations to change
+	\item Interconnectedness of the enables the organizations to change
+	\item Feedback processes that carry the long-term consequences of coevolution
+\end{itemize}
+
+\subsubsection{Management Model}
+
+% subsection modeling (end)
 
@@
 \label{sub:mathematical_formulation}
-
+\subsubsection{Comprehended Model}
 % subsection mathematical_formulation (end)

### 2016-03-07 review.tex
细微调整结构框架，准备开始框架修改和文献综述并行。
阶段性定框架
add the enterprise model
start the report

@@
 
+\subsection{Business Mode} % (fold)
+\label{sub:business_mode}
+
+% subsection business_mode (end)
+
+\subsection{Cloud Manufacturing} % (fold)
+\label{sub:cloud_manufacturing}
+% This definition is quite abstract and thus despite its corretness not very useful.
+from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.
+
+Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al.
+2012;Valilai and Houshmand 2013)
+% subsection cloud_manufacturing (end)
+
+\subsection{Manufacturing Ecosystem} % (fold)
+\label{sub:manufacturing_ecosystem}
+% xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.
+
+% From a bionomic perspective, organisms and organizations are nodes in networks of relationships.
+As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network.
+\subsubsection{Different Ecosystem Analogies}
+
+\subsubsection{Manufacturing System}
+% Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.
+
+% coevolved to form a vast living ecosystem
+
+% 4 different stages for ecosystem:
+% birth, expansion, leadership, final(self-renew or death)
+
+% the major difference between ecological and social system is the role of conscious choice.
+
+% Accoring to xxx there are three critical success factors of a business ecosystem.
+% First, productivity
+% Second, Robustness
+% Third, have the ability to create niches and opportunities for new firms.
+
+% Complexity relevant concepts
+
+% Self-organization
+% Emergence
+% Coevolution
+% adaptation
+
+% subsection manufacturing_ecosystem (end)
+
+\subsection{Complex System} % (fold)
+\label{sub:complex_system}
+\subsubsection{System Dynamic}
+
+\subsubsection{Cellular Automata}
+% subsection complex_system (end)
 % section literature_review (end)

### 2016-03-23 background.tex
添系统框架参考图
test the figures

@@
 \label{sub:cloud_manufacturing_ecosystem}
+As an application of Networked Manufacturing, Cloud Mfg ...
+\begin{figure}
+\includegraphics[scale = .6, trim = 0 15 0 0]{Cloud_Mfg_Structure.pdf}
+\caption{Cloud Manufacturing Architecture with Main Flows}
+\label{fig:structure}
+\end{figure}
+
+As shown in \autoref{fig:structure}, the architecture of Cloud Mfg is mainly comprised by three parts, namely User, Platform and Physical Base, some of whose subparts are connected by (material or information) flows.
+With the supplementary illustration in \autoref{fig:supplementary}
+
+\begin{figure}[!htpd]
+\includegraphics[scale = .6, trim = 0 15 0 0]{supplementary.pdf}
+\caption{Supplementay Illustration of \autoref{fig:structure}}
+\label{fig:supplementary}
+\end{figure}
 

### 2016-03-23 background.tex
start writting
开始描述所提的云制造框架结构

--- 2016-03-07 background.tex
@@
 \label{sub:cloud_manufacturing_ecosystem}
+As an application of Networked Manufacturing, Cloud Manufacturing proposed by ...
+
+(problems background to form the ecosystem)
+
+Combined with the problem background and other scholars' previous work, we proposed an improved framework that suits for Cloud Manufacturing environment as shown in \autoref{fig:structure}.
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale = .6, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
+\caption{Cloud Manufacturing Architecture with Main Flows}
+\label{fig:structure}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
+\caption{Supplementay Illustration of \autoref{fig:structure}}
+\label{fig:supplementary}
+\end{figure}
+
+The architecture of Cloud Manufacturing is mainly comprised by three parts, namely, \begin{inparaenum}[1)]
+\item User,
+\item Platform and
+\item Physical Base
+\end{inparaenum}, some of whose subparts are connected by material or information flows.
+With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in Cloud Manufacturing environment with the forementioned flows that marked by circled number (i.e.
+\textcircled{\small{1}}), a simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:
 

### 2016-03-24 background.tex
描述完框架图
接下来列出要做什么，逐步完成

@@
 
+The architecture of Cloud Manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
+\item User,
+\item Platform and
+\item Physical Base
+\end{inparaenum}, that are connected by material or information flows. A simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:
+\begin{compactdesc}
+\item [User] part describes the main roles in the Cloud Manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view.
+Meanwhile, these roles can also be classified into enterprise user and customer, from the practical point of view.
+Both functional and practical are important perspective for later analysis in following sections.
+\item [Platform] part consists of 3 main layers namely \begin{inparaenum}[1)]
+\item Application/Interface Layer,
+\item Service Layer and 
+\item Resource \& Production Layer
+\end{inparaenum}.
+Service is the core idea of Cloud Manufacturing, so Service Layer is the core of the Cloud Manufacturing platform.
+With the help of related technology in servitization, manufacturing resource and production can be encapsulated into services, then these services can be acquired by users with the well designed applications or interfaces.
+\item [Physical Base] part includes the basic infrastructure, resource and production.
+It's worth mentioning that part of resources and production can even be virtualized with some services the platform provides.
+\end{compactdesc}
+
 \begin{figure}[htbp]
@@
 \includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
-\caption{Supplementay Illustration of \autoref{fig:structure}}
+\caption{Supplementay Illustration for \autoref{fig:structure}}
 \label{fig:supplementary}
@@
 
-The architecture of Cloud Manufacturing is mainly comprised by three parts, namely, \begin{inparaenum}[1)]
-\item User,
-\item Platform and
-\item Physical Base
-\end{inparaenum}, some of whose subparts are connected by material or information flows.
 With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in Cloud Manufacturing environment with the forementioned flows that marked by circled number (i.e.
-\textcircled{\small{1}}), a simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:
+\textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the Cloud Manufacturing system.
+In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively.
+The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a system view.
 

### 2016-03-24 review.tex
adjust the structure
描述完框架图
接下来列出要做什么，逐步完成

@@
 2012;Valilai and Houshmand 2013)
+
+\textbf{Services and Tasks}
+
+Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub.
+In order to complete orders precisely, order will be splited into tasks.
+Similarly, resources will be bundled into services for the quick searhing.
+
+\textbf{Roles}
+
+Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
+\item Users/Customers,
+\item Application providers and
+\item Physical resource providers.
+\end{inparaenum}
+However, the roles in real world always not go like this model, since it parted roles only by their functions.
+While, users could get different function roles depend on what transaction they take, we should make some modifiacations on this model.
+
+Before the emendation of the roles, some related standard name should be taken:
+\begin{asparadesc}
+\item[User] The main role in Cloud Manufacturing, which is combined of Seller and Buyer as shown in \autoref{tab:categoryuser}, usually acts as Seller or Buyer according to the specific transaction;
+\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service and makes a evalution about the Buyer after the transaction;
+\item[Buyer] The temporary role in a transaction, which submits the allocated part of manufacturing task and makes a evalution about the Seller after the transaction;
+\item[Administrator] The role that gets the work for the operation and maintenance of the platform, has indirectly impact on the Ecosystem.
+\end{asparadesc}
+\begin{table}[htbp]
+  \centering\small
+  \caption{Category of Users}
+    \begin{tabularx}{\textwidth}{llccX}
+    \toprule
+        &  & Seller & Buyer & Description \\
+    \midrule
+    Generalized & User & $\surd$ & $\surd$ & Act as Seller or Buyer according to the specific transaction. \\
+    Enterprise & User & $\surd$ & &  Provides the allocated part of manufacturing services and makes a evalution about the Buyer after the transaction. \\
+    Customer & User& & $\surd$ &  Submits the allocated part of manufacturing tasks and makes a evalution about the Seller after the transaction.\\
+    \bottomrule
+    \end{tabularx}%
+  \label{tab:categoryuser}%
+\end{table}%
+As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.
+
+Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.
+
 % subsection cloud_manufacturing (end)
@@
 \subsubsection{Cellular Automata}
+
+\subsubsection{Agent-based Modeling}
 % subsection complex_system (end)

### 2016-04-05 background.tex
添加了逻辑图，改善文章结构，主要在方法上

@@
 % !TEX root = Eco-Model.tex
-\section{Problem Background} % (fold)
-\label{sec:problem_background}
+\section{Background} % (fold)
+\label{sec:background}
 
-\subsection{Cloud Manufacturing Ecosystem} % (fold)
-\label{sub:cloud_manufacturing_ecosystem}
-As an application of Networked Manufacturing, Cloud Manufacturing proposed by ...
+\subsection{Origin and description of the research problem} % (fold)
+\label{sub:origin_and_description_of_the_problem}
+
+As an application of networked manufacturing, cloud manufacturing proposed by ...
 
 (problems background to form the ecosystem)
+% subsection origin_and_description_of_the_problem (end)
 
-Combined with the problem background and other scholars' previous work, we proposed an improved framework that suits for Cloud Manufacturing environment as shown in \autoref{fig:structure}.
+\subsection{Cloud manufacturing ecosystem} % (fold)
+\label{sub:cloud_manufacturing_ecosystem}
+
+\subsubsection{Cloud manufacturing ecosystem architecture}
+
+Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment as shown in \autoref{fig:structure}.
 \begin{figure}[htbp]
@@
 \includegraphics[scale = .6, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
-\caption{Cloud Manufacturing Architecture with Main Flows}
+\caption{Cloud manufacturing architecture with main flows}
 \label{fig:structure}
@@
 
-The architecture of Cloud Manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
-\item User,
-\item Platform and
-\item Physical Base
-\end{inparaenum}, that are connected by material or information flows. A simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:
+The architecture of cloud manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
+\item user,
+\item platform and
+\item physical base
+\end{inparaenum}, that are connected by material or information flows. A simple version of conception for cloud manufacturing architecture we study here can be described as follows:
 \begin{compactdesc}
-\item [User] part describes the main roles in the Cloud Manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view.
+\item [User] part describes the main roles in the cloud manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view.
 Meanwhile, these roles can also be classified into enterprise user and customer, from the practical point of view.
 Both functional and practical are important perspective for later analysis in following sections.
-\item [Platform] part consists of 3 main layers namely \begin{inparaenum}[1)]
-\item Application/Interface Layer,
-\item Service Layer and 
-\item Resource \& Production Layer
+\item [Platform] part consists of 3 main layers namely
+	\begin{inparaenum}[1)]
+	\item application/interface layer,
+	\item service layer and 
+	\item resource \& production layer
 	\end{inparaenum}.
-Service is the core idea of Cloud Manufacturing, so Service Layer is the core of the Cloud Manufacturing platform.
+Service is the core concept in cloud manufacturing, so service layer is the core in the cloud manufacturing platform.
 With the help of related technology in servitization, manufacturing resource and production can be encapsulated into services, then these services can be acquired by users with the well designed applications or interfaces.
@@
 \includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
-\caption{Supplementay Illustration for \autoref{fig:structure}}
+\caption{Supplementay illustration for \autoref{fig:structure}}
 \label{fig:supplementary}
@@
 
-With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in Cloud Manufacturing environment with the forementioned flows that marked by circled number (i.e.
-\textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the Cloud Manufacturing system.
+With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in cloud manufacturing environment with the forementioned flows that marked by circled number (i.e.
+\textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the cloud manufacturing system.
 In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively.
-The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a system view.
+The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a systematic view.
 
+\subsubsection{Operation model}
+% 放那两张流程图，以说明流程。分别作为平台及企业自生的运作模式
+\begin{figure}[!h]
+\centering\small
+% \subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
+% \subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
+\resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
+\caption{Simple Flow Chart of Order}
+\label{fig:simpleorderflow}
+\end{figure}
+\subsubsection{Main features in the ecosystem}
+% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。
+As shown in \autoref{fig:structure}, 
+Rating system, decision support system, recommender system,
+detail info will seen in
 Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions.
@@
 
-\subsubsection{Enterprise Business Mode}
-
-\subsubsection{Resource Sharing Mechanism}
-
-\subsubsection{Ecosystem Adjustment}
-
 % subsection cloud_manufacturing_ecosystem (end)
 
-\subsection{Main Copmlexity Concepts} % (fold)
-\label{sub:main_copmlexity_concepts}
+\subsection{Main complexity concepts} % (fold)
+\label{sub:main_complexity_concepts}
 
@@
 \subsubsection{Adaption}
-% subsection main_copmlexity_concepts (end)
+% subsection main_complexity_concepts (end)
 
-\subsection{Ecosystem Evolvement} % (fold)
+\subsection{Ecosystem evolvement} % (fold)
 \label{sub:ecosystem_evolvement}
@@
 
-\subsection{Optimal Guidance} % (fold)
+\subsection{Optimal guidance} % (fold)
 \label{sub:optimal_guidance}
@@
 % subsection optimal_guidance (end)
-% section problem_background (end)
+% section background (end)

### 2016-04-05 method.tex
adjust the structure
modify the section to valide
添加了逻辑图，改善文章结构，主要在方法上

@@
 % !TEX root = Eco-Model.tex
-\section{Methodological Approach} % (fold)
+\section{Methodological approach} % (fold)
 \label{sec:methodological_approach}
@@
 
-\subsubsection{Assumptions and Notation}
+\subsubsection{Assumptions and notation}
 
 Ecosystem application model including:
-\subsubsection{Enterprise Model}
+\subsubsection{Enterprise model}
 
@@
 \end{itemize}
+
+\subsubsection{Main modules design}
+\label{subsub:main_modules}
 
@@
 
-\subsubsection{Management Model}
-
 % subsection modeling (end)
 
-\subsection{Mathematical Formulation} % (fold)
-\label{sub:mathematical_formulation}
-\subsubsection{Comprehended Model}
-% subsection mathematical_formulation (end)
+% \subsection{Mathematical Formulation} % (fold)
+% \label{sub:mathematical_formulation}
+% \subsubsection{Comprehended Model}
+% % subsection mathematical_formulation (end)
 
-\subsection{Model Validation} % (fold)
-\label{sub:model_validation}
+% \subsection{Verification and Validation} % (fold)
+% \label{sub:verification_and_validation}
 
-% subsection model_validation (end)
+% % subsection verification_and_validation (end)
 
+\subsection{Agent-based modeling and simulation} % (fold)
+\label{sub:agent_based_modeling_and_simulation}
+\subsubsection{Agent design}
+
+\subsubsection{Logical process}
+\begin{figure}[htbp]
+\centering\small
+\subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
+\subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
+% \resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
+\caption{Simple Flow Chart of Order}
+% \label{fig:simpleorderflow}
+\end{figure}
+
+\subsubsection{Interaction among agents}
+some mathematical formulation display here to describe the whole ecosystem wide phenomenon, like Little formulation.
+
+\subsubsection{Verification and validation}
+% subsection agent_based_model_and_simulation (end)
 % section methodological_approach (end)

### 2016-05-08 intro.tex
要开始写生态模型了，准备会议以及POMS
去除子文件的其他导言
初步
struct done
init on mac
start the schedule and evolve modules.
增加文章结构

@@
-% !Mode:: "TeX:UTF-8"
 % !TEX root = Eco-Model.tex
-\section{test}
+\section{Introduction}
+First of all, just say something about the cloud mfg shortly,
+then, tell something about the aim or the meaning of the research,
+and how is the recent research work, what's new of your work
+
+The intro should cover 
+\begin{itemize}
+	\item Theme or Topic (keep it simple, do not begin with research question or hypothesis. Define technical terms and constructs concepts.)
+	\item Academic Importance (lack of previous research on the topic highlighting the gaps, inconsistencies, avoid the comprehensive view.)
+	\item Literature (recent studies. last 5 years. )
+	\item Knowledge Gap (specific knowledge gaps, inconsistencies, and controversies in the literature. motivate the importance of the study.)
+	\item Research Question and Objectives (guide the study units of analysis used in the paper)
+	\item Outline Structure (a brief outline of the flow of the entire paper)
+\end{itemize}

### 2016-05-08 review.tex
添加了逻辑图，改善文章结构，主要在方法上
add a references
增加文章结构

@@
 % !TEX root = Eco-Model.tex
-\section{Literature Review} % (fold)
+\section{Literature review} % (fold)
 \label{sec:literature_review}
-
-\subsection{Business Mode} % (fold)
-\label{sub:business_mode}
-
-% subsection business_mode (end)
-
-\subsection{Cloud Manufacturing} % (fold)
+demonstrates that you know the field, justifies the reason for your research, allows you establish your theoretical and needs to be done.
+\subsection{Cloud manufacturing} % (fold)
 \label{sub:cloud_manufacturing}
@@
 from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.
+
+In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}
 
@@
 
-\subsection{Manufacturing Ecosystem} % (fold)
+\subsection{Manufacturing ecosystem} % (fold)
 \label{sub:manufacturing_ecosystem}
@@
 As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network.
-\subsubsection{Different Ecosystem Analogies}
+\subsubsection{Different ecosystem analogies}
 
-\subsubsection{Manufacturing System}
+\subsubsection{Manufacturing system}
 % Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.
@@
 % adaptation
+\subsubsection{E}
 

### 2016-05-18 discussion.tex
修改文档的结构
明确各agent 的划分，设计meta agent
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点

@@
 % !TEX root = Eco-Model.tex
-\section{Discussion} % (fold)
-\label{sec:discussion}
+\section{Contributions, Limitations, and Future Research} % (fold)
+\label{sec:contributions_limitations_and_future_research}
 
-% section discussion (end)
+On the other hand, it means, that even if many indicators for the collaboration perspectives are applied it has to be regarded that they will not be able to draw a complete and objective picture of the collaboration performance.
+% section contributions_limitations_and_future_research (end)

### 2016-05-19 head.tex
细微调整结构框架，准备开始框架修改和文献综述并行。
start the report
添加了逻辑图，改善文章结构，主要在方法上
add the abstract
add ref item
一些新的想法

@@
 
-\title{Net title
+\title{The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture
 %Cloud Manufacturing Ecosystem - Scheduling And Evolving
@@
 New abstract
-% In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were constructed standardly by resources is required, in order for the collaboration within the whole Industry Chain.
-%This paper 
-%\begin{inparaenum}[1)]
-%\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
-%\item modeled the services scheduling matter in the chain;
-%\item designed evolving modules for the Cloud Manufacturing Ecosystem;
-%\item opened some Ecosystem related issues. 
-%\end{inparaenum}
-%With the help of Data Science tools on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
-%gradually evolve the ecosystem to an optimal situation.
+% 提出了 Cloud Manufacturing Ecosystem 概念，建立相应的生态系统模型，从系统中的各个角色，（需要一个指标）建立系统动力学方程。通过仿真手段验证模型，结合已有的云平台原型系统，给出相关应用。
+% 云制造的实施和应用提供了一种全新的制造业生态系统，该生态系统由成员（企业用户、管理员）及环境（）组成。为了探究生态系统中，制造业的运作模式（相关决策），优化产业链，形成良性发展的制造生态，通过基于Agent 的建模，来刻画该系统中的个体行为，并通过仿真技术，模拟演化规律。
+
+% 云制造生态系统中，不同的企业具有不同的生态位
+% 该系统的输入
+% 输出
+% 调控方式
+
+% 通过仿真，我们发现。。。
+
+The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
+% 关键是系统动力学模型的建立。
 

### 2016-05-20 background.tex
修改结构，开始写
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点
new

@@
 
-\subsection{Origin and description of the research problem} % (fold)
-\label{sub:origin_and_description_of_the_problem}
-
 As an application of networked manufacturing, cloud manufacturing proposed by ...
@@
 (problems background to form the ecosystem)
-% subsection origin_and_description_of_the_problem (end)
 
-\subsection{Cloud manufacturing ecosystem} % (fold)
-\label{sub:cloud_manufacturing_ecosystem}
+\subsection{Cloud manufacturing} % (fold)
+\label{sub:cloud_manufacturing}
 
-\subsubsection{Cloud manufacturing ecosystem architecture}
+\subsubsection{Cloud manufacturing architecture}
 
@@
 \subsubsection{Operation model}
+\label{ssub:operation_model}
 % 放那两张流程图，以说明流程。分别作为平台及企业自生的运作模式
+\begin{figure}[htbp]
+\centering
+\subfloat[Demander]{\includegraphics[width=0.8\textwidth]{figures/demander_main_process}\label{fig:demanderprocess}}\\
+\subfloat[Provider]{\includegraphics[width=0.8\textwidth]{figures/provider_main_process}\label{fig:providerprocess}}
+\caption{Main operational processes}
+\end{figure}
+
 \begin{figure}[!h]
@@
 \end{figure}
-\subsubsection{Main features in the ecosystem}
+
+% subsection cloud_manufacturing(end)
+
+% \subsection{Main complexity concepts} % (fold)
+% \label{sub:main_complexity_concepts}
+
+% \subsubsection{Self-organization}
+
+% \subsubsection{Emergence}
+
+% \subsubsection{Co-evolution}
+
+% \subsubsection{Adaption}
+% % subsection main_complexity_concepts (end)
+
+\subsection{The evolution of manufacturing ecosystem} % (fold)
+\label{sub:the_evolution_of_manufacturing_ecosystem}
+Before the realization of the operation model mentioned above(\autoref{ssub:operation_model}), we will analyse the evolution path in both macro and micro view of manufacturing ecosystem w.r.t.
+the domain in cloud manufacturing..
+\subsubsection{Macroscopic evolution} % (fold)
+\label{ssub:macroscopic_evolution}
+
+% subsubsection microscopic_evolution (end)
+\subsubsection{Microscopic evolution} % (fold)
+\label{ssub:microscopic_evolution}
+
+% subsubsection macroscopic_evolution (end)
+
+\subsection{Main topics and their academic importance}
 % 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。
@@
 
-% subsection cloud_manufacturing_ecosystem (end)
-
-\subsection{Main complexity concepts} % (fold)
-\label{sub:main_complexity_concepts}
-
-\subsubsection{Self-organization}
-
-\subsubsection{Emergence}
-
-\subsubsection{Co-evolution}
-
-\subsubsection{Adaption}
-% subsection main_complexity_concepts (end)
-
-\subsection{Ecosystem evolvement} % (fold)
-\label{sub:ecosystem_evolvement}
-
-% subsection ecosystem_evolvement (end)
-
-\subsection{Optimal guidance} % (fold)
-\label{sub:optimal_guidance}
-
-% subsection optimal_guidance (end)
+% subsection the_evolution_of_manufacturing_ecosystem (end)
 % section background (end)

### 2016-05-23 background.tex
modify the background and part of review

@@
 \begin{compactdesc}
-\item [User] part describes the main roles in the cloud manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view.
-Meanwhile, these roles can also be classified into enterprise user and customer, from the practical point of view.
+\item [User] part describes the generalized role who takes part in the trading activities in the cloud manufacturing system, such as manufacturing service provider and manufacturing service demander, whom can be called as provider and demander for short respectively, from the functional point of view.
+Meanwhile, these part can also be classified into enterprise user and customer, from the practical point of view.
+In addition, it's possible for user to act as both demander and provider simultaneously if administrator give the authority to the user, so we can categorize the user in 3 basic types as described in \autoref{fig:usertype} and \autoref{tab:usertype}.
 Both functional and practical are important perspective for later analysis in following sections.
-\item [Platform] part consists of 3 main layers namely
+\item [Platform] is operating with the control of administrator and this part consists of 3 main layers namely
 	\begin{inparaenum}[1)]
@@
 	\centering
+	\includegraphics[width=.7\textwidth]{usertype.pdf}
+	\caption{Simple explanation of user type}
+	\label{fig:usertype}
+\end{figure}
+
+\begin{table}[htbp]
+	\caption{Simple explanation of user type}
+	\label{tab:usertype}
+	\centering
+
+	\begin{tabularx}{\textwidth}{llX}
+	\toprule
+	\textbf{Type} & \textbf{Name} &  \textbf{Concise Description}\\
+	\midrule
+	I			& Pure demander &  Submit manufacturing tasks and make evaluation of provider.\\
+	II 			& Complex user 	&  Usually a pure provider submit part of its task, it becomes the complex user and changes the operation model of the user.\\
+	III 		& Pure provider &  Provide manufacturing services and makes evaluation demander.\\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+% Before the emendation of the roles, some related standard name should be taken:
+
+As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.
+
+Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.
+
+\begin{figure}[htbp]
+\centering
 \includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
-\caption{Supplementay illustration for \autoref{fig:structure}}
+\caption{Supplementary illustration for \autoref{fig:structure}}
 \label{fig:supplementary}
@@
 
-With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in cloud manufacturing environment with the forementioned flows that marked by circled number (i.e.
+With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in cloud manufacturing environment with the fore-mentioned flows that marked by circled number (i.e.
 \textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the cloud manufacturing system.
 In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively.
-The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a systematic view.
+The overlap among application districts implies the complexity of the system, so that we will analyze these applications coordinately from a systematic view.
 
-\subsubsection{Operation model}
-\label{ssub:operation_model}
-% 放那两张流程图，以说明流程。分别作为平台及企业自生的运作模式
+\subsubsection{Operation model of platform}
+\label{ssub:operation_model_of_platform}
+Platform carries most of the activities illustrated in \autoref{fig:supplementary}, so it's important to design an operation model for administrator to manage these activities.
+This model enables modules that appeared in xxx such as \textit{service packager}, \textit{task decomposer} , \textit{service search engine}, etc., but we only study the modules in for they're the core in the evolutionary process in this paper.
+
+\begin{table}[tb]
+	\caption{Core modules in operation model of platform}
+	\label{tab:core_module_in_platform}
+	\centering
+
+	\begin{tabularx}{\textwidth}{llX}
+	\toprule
+
+	\textbf{Module} & \multicolumn{2}{l}{\textbf{Function with concise description}}  \\
+	\midrule
+	\multirow{2}*{Population controller}		& Adder: 		& To introduce resource provider into the system\\
+												& Subtracter: 	& To eliminate resource provider from the system\\
+	\hline
+	\multirow{2}*{Authority tuner}				& Raiser:	& Raise the authority value of the provider \\
+												& Reducer: & Reduce the authority value of the provider\\
+	\hline
+	\multirow{3}*{Recommender}					& Matcher: & Match task with a bunch of alternative services \\
+												& Adjuster: & Change provider's rank based on history\\
+												& Promoter: & To promote fresh resource provider \\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+\subsubsection{Operation model of users}
+\label{subs:Operation model of users}
+business model is emerging as a new unit of analysis; business models emphasize a system-level, holistic approach to explaining how firms do business; firm activities play an important role in the various conceptualizations of business models that have been proposed; business models seek to explain how value is created, not just how it is captured.
 \begin{figure}[htbp]
@@
 \label{sub:the_evolution_of_manufacturing_ecosystem}
-Before the realization of the operation model mentioned above(\autoref{ssub:operation_model}), we will analyse the evolution path in both macro and micro view of manufacturing ecosystem w.r.t.
+Before the realization of the operation model mentioned above(\autoref{subs:Operation model of users}), we will analyze the evolution path in both macro and micro view of manufacturing ecosystem w.r.t.
 the domain in cloud manufacturing..
@@
 \subsection{Main topics and their academic importance}
-% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。
+% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。 目前云制造缺乏相关运作式的讨论，而商业模式中的不同行为会影响、改变、涌现。
 As shown in \autoref{fig:structure},

### 2016-05-23 review.tex
修改结构，开始写
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点
明确各agent 的划分，设计meta agent
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点
new
start to study the operation model
modify the background and part of review

--- 2016-03-07 review.tex
@@
 % !TEX root = Eco-Model.tex
-\section{Literature Review} % (fold)
+\section{Literature review and the knowledge gap} % (fold)
 \label{sec:literature_review}
+demonstrates that you know the field, justifies the reason for your research, allows you establish your theoretical and needs to be done.
 
-\subsection{Business Mode} % (fold)
-\label{sub:business_mode}
-
-% subsection business_mode (end)
-
-\subsection{Cloud Manufacturing} % (fold)
-\label{sub:cloud_manufacturing}
+XXX has been studied extensively in the literature....
+\subsection{Cloud manufacturing} % (fold)
+\label{sub:cloud_manufacturing review}
 % This definition is quite abstract and thus despite its corretness not very useful.
@@
 
+In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}
+
 Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al.
 2012;Valilai and Houshmand 2013)
+
+\textbf{Services and Tasks}
+
+Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub.
+In order to complete orders precisely, order will be splited into tasks.
+Similarly, resources will be bundled into services for the quick searhing.
+
+\textbf{Roles}
+
+Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
+\item Users/Customers,
+\item Application providers and
+\item Physical resource providers.
+\end{inparaenum}
+However, the roles in real world always not go like this model, since it parted roles only by their functions.
+While, users could get different function roles depend on what transaction they take, we should make some modifiacations on this model.
+
 % subsection cloud_manufacturing (end)
 
-\subsection{Manufacturing Ecosystem} % (fold)
+\subsection{Manufacturing ecosystem} % (fold)
 \label{sub:manufacturing_ecosystem}
@@
 
-\subsection{Complex System} % (fold)
+\subsection{Operation model in cloud manufacturing}
+\label{sub:Operation model in cloud manufacturing}
+
+\subsection{Study of evolution on related fields} % (fold) 这段标题后期需要修改，要描述的是和演化相关的内容。
 \label{sub:complex_system}
@@
 
-\subsubsection{Cellular Automata}
+\subsubsection{Agent-based Modeling}
 % subsection complex_system (end)

### 2016-05-24 background.tex
describe operation model and microscopic evolution

@@
 
+\subsection{List of basic terminology} % (fold)
+\label{sub:list_of_basic_terminology}
+here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
+\begin{itemize}
+	\item order
+	\item task
+	\item resource
+	\item capacity
+	\item service
+	\item 
+\end{itemize}
+% subsection list_of_basic_terminology (end)
+
 \subsection{Cloud manufacturing} % (fold)
@@
 \subsubsection{Cloud manufacturing architecture}
-
+\label{subs:cloud manufacturing architecture}
 Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment as shown in \autoref{fig:structure}.
@@
 \begin{compactdesc}
-\item [User] part describes the generalized role who takes part in the trading activities in the cloud manufacturing system, such as manufacturing service provider and manufacturing service demander, whom can be called as provider and demander for short respectively, from the functional point of view.
+\item [User] part describes the generalized role who takes part in the trading activities in the cloud manufacturing system, basic role of user are manufacturing service provider and manufacturing service demander, whom can be called as \textit{provider} and \textit{demander} for short respectively, from the functional point of view.
 Meanwhile, these part can also be classified into enterprise user and customer, from the practical point of view.
@@
 \label{subs:Operation model of users}
-business model is emerging as a new unit of analysis; business models emphasize a system-level, holistic approach to explaining how firms do business; firm activities play an important role in the various conceptualizations of business models that have been proposed; business models seek to explain how value is created, not just how it is captured.
+The \textit{demander} mentioned in \autoref{subs:cloud manufacturing architecture} publishes its demand as order that can be decomposed into tasks by \textit{task decomposer} module in platform, while the \textit{provider} mentioned in \autoref{subs:cloud manufacturing architecture} publishes its resource as capacity that can be packaged into services by \textit{service packager} module in Platform.
+In order to do more accurate study on users, we classified users into 3 basic types as shown in \autoref{fig:usertype}.
+With concise explanation in \autoref{tab:usertype}, we can illustrate the operation model in \autoref{fig:useroperation}.
+
 \begin{figure}[htbp]
 \centering
-\subfloat[Demander]{\includegraphics[width=0.8\textwidth]{figures/demander_main_process}\label{fig:demanderprocess}}\\
-\subfloat[Provider]{\includegraphics[width=0.8\textwidth]{figures/provider_main_process}\label{fig:providerprocess}}
+\subfloat[Pure demander]{\includegraphics[width=0.75\textwidth]{demander_main_process}\label{fig:demanderprocess}}\\
+\subfloat[Complex user]{\includegraphics[width=0.75\textwidth]{complex_main_process}\label{fig:complexprocess}}\\
+\subfloat[Pure Provider]{\includegraphics[width=0.75\textwidth]{provider_main_process}\label{fig:providerprocess}}
 \caption{Main operational processes}
+\label{fig:useroperation}
 \end{figure}
 
-\begin{figure}[!h]
-\centering\small
-% \subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
-% \subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
-\resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
-\caption{Simple Flow Chart of Order}
-\label{fig:simpleorderflow}
-\end{figure}
+The main operational process of pure demander(\autoref{fig:demanderprocess}) starts with its decomposed task.
+Then, with the help of \textit{recommender} module, pure demander search and select appropriate service, trade with the one or multi service provider according to the \textit{task decomposer}, receive the product delivered by the provider at due date and commit the review of the product.
+The committed review will affect the authority value of the provider, that good review raise the value and vise versa.
 
-% subsection cloud_manufacturing(end)
+The main operational process of pure provider(\autoref{fig:providerprocess}) starts with a task call, then pure provider process the task with its resource.
+After the accomplishment of the task, pure provider deliver products to demander from the call.
+It will also commit the review of the demander and make a modification of its service area.
+By the way, this modification of provider's service area play key role in the evolution of user we will discuss in \autoref{ssub:microscopic_evolution}.
 
-% \subsection{Main complexity concepts} % (fold)
-% \label{sub:main_complexity_concepts}
-
-% \subsubsection{Self-organization}
-
-% \subsubsection{Emergence}
-
-% \subsubsection{Co-evolution}
-
-% \subsubsection{Adaption}
-% % subsection main_complexity_concepts (end)
+The main operational process of complex user(\autoref{fig:complexprocess}) combines the two above process with additional decision step.
+This decision split the task into two parts, that one of them will be processed by itself as a provider user and the other one will be processed by other provider as if the complex user act as a demander.
+This operational process relies heavily on the service area of the complex user, so the modification of service area is the key to the study.
 
@@
 \label{sub:the_evolution_of_manufacturing_ecosystem}
-Before the realization of the operation model mentioned above(\autoref{subs:Operation model of users}), we will analyze the evolution path in both macro and micro view of manufacturing ecosystem w.r.t.
-the domain in cloud manufacturing..
+Before the realization of the operation model mentioned above(\autoref{subs:Operation model of users}), we will analyze the evolution path in both micro and macro view of manufacturing ecosystem w.r.t.
+the domain in cloud manufacturing.
+
+\subsubsection{Microscopic evolution} % (fold)
+\label{ssub:microscopic_evolution}
+
+User is the basic activity unit in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
+\item type,
+\item status and 
+\item niche width
+\end{inparaenum}, 
+all these changes contribute to microscopic evolution of the ecosystem.
+More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper.
+\autoref{tab:userchange} concludes the appearances that we will study in this paper.
+
+\begin{table}[htbp]
+	\caption{Users' changes}
+	\label{tab:userchange}
+	\centering
+	\begin{tabularx}{\textwidth}{llX}
+	\toprule
+	\textbf{Change} & \multicolumn{2}{l}{\textbf{Appearance with concise description}}\\
+	\midrule
+	\multirow{3}*{Type}			& Complex user $\to$ Pure demander: & User stop provide its resource\\
+								& Complex user $\to$ Pure provider: & User shrink service area that only contains its own service \\
+								& Pure provider $\to$ Complex user: & User extend service area that starts to contain service from others' \\
+	\midrule
+	\multirow{4}*{Status} 		& Pure demander enter ecosystem: &	One pure demander starts to publish orders\\
+								& Pure demander exit ecosystem: & One pure demander be banned to publish orders\\
+								& Pure provider enter ecosystem: & Administrator introduces one provider into the ecosystem\\
+								& Pure provider exit ecosystem: & Administrator eliminates one provider form the ecosystem\\
+	\midrule
+	\multirow{2}*{Niche width} 	& Widen: & One provider extends its service area\\
+								& Narrow down:  & One provider shrinks its service area\\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+% subsubsection macroscopic_evolution (end)
+
 \subsubsection{Macroscopic evolution} % (fold)
@@
 % subsubsection microscopic_evolution (end)
-\subsubsection{Microscopic evolution} % (fold)
-\label{ssub:microscopic_evolution}
-
-% subsubsection macroscopic_evolution (end)
 

### 2016-05-25 background.tex
change the background

@@
 
-User is the basic activity unit in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
+User is the basic activity individual in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
 \item type,
@@
 
-% subsubsection macroscopic_evolution (end)
+% subsubsection microscopic_evolution (end)
 
@@
 
-% subsubsection microscopic_evolution (end)
+Individual evolution will lead to the evolution of the whole ecosystem and the overall effect is greater than the sum of these individuals.
+the amount, diversity, operation pattern recognition and service cycle rate are the topics of macroscopic evolution.
+
+% subsubsection macroscopic_evolution (end)
 

### 2016-06-02 background.tex
添加新条目

@@
 	\item order
-	\item task
+	\item task correspond to capacity
 	\item resource
-	\item capacity
-	\item service
+	\item capacity is the function of a resource. like quantity
+	\item service is the bundle of capacities.
 	\item 
@@
 
+platform model is about the part of decision making	agent of platform.
+
 \subsubsection{Operation model of users}
@@
 
+user's model is the part of decision making agent of users.
+
 \subsection{The evolution of manufacturing ecosystem} % (fold)
@@
 the domain in cloud manufacturing.
+The overall evolution process is illustrated in \autoref{fig:overallevolution},
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{evolutionview}
+	\caption{Overall evolution process}
+	\label{fig:overallevolution}
+\end{figure}
+the microscopic evolution corresponds to the change of user status while the macroscopic evolution corresponds to the change of the system status.
 
@@
 
-User is the basic activity individual in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
+by both type of agents, more on user agent, the platform agent will change a individual by affect the individual's decision, not directly means.
+
+User is the basic activity individual in the manufacturing ecosystem, and their \begin{inparaenum}[1)]
 \item type,
@@
 \item niche width
-\end{inparaenum}, 
-all these changes contribute to microscopic evolution of the ecosystem.
+\end{inparaenum} will be changed by the decision they've made. 
+All these changes contribute to microscopic evolution of the ecosystem.
 More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper.
@@
 \label{ssub:macroscopic_evolution}
+Comes form both of the agents. more on platform agent.
+indirect: the group effect.
 
 Individual evolution will lead to the evolution of the whole ecosystem and the overall effect is greater than the sum of these individuals.
+
 the amount, diversity, operation pattern recognition and service cycle rate are the topics of macroscopic evolution.
+
+\begin{table}[htbp]
+ 	\caption{Macroscopic evolution}
+ 	\label{tab:macroevolution}
+ 	\centering
+ 	\begin{tabularx}{\textwidth}{llX}
+ 	\toprule
+ 	\textbf{column 1} & \multicolumn{2}{l}{\textbf{Appearance with concise description}} \\
+ 	\midrule
+ 	Amount & & \\
+ 	Diversity & & \\
+ 	Service cycle rate & & \\
+ 	\bottomrule
+ 	\end{tabularx}
+ \end{table}
 
@@
 As shown in \autoref{fig:structure},
+
+the core is about the decision making all the time, individuals' decision making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution
+
 Rating system, decision support system, recommender system,
@@
 
+so, the topic here is the design of both decision making agents.
 % subsection the_evolution_of_manufacturing_ecosystem (end)

### 2016-06-02 head.tex
添加新条目

@@
 % 通过仿真，我们发现。。。
+In this paper, ....
+
+Basically, (present what have done)
+
+we do not use any utility function for the modeling; however, a unique method is proposed for eliciting the information from decision makers.
+The proposed model is applicable for a wide variety of multi-attribute decision making problems and can be used for  future ranking or selection without managers' judgment effort.
+Simulation of the managers' decisions is demonstrated in detail and the design and implementation of the model are illustrated by case study.
 

### 2016-06-02 method.tex
明确各agent 的划分，设计meta agent
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点
new
添加新条目

@@
 
-\subsection{Modeling} % (fold)
-\label{sub:modeling}
+This section starts with a brief overview of ABMS. Then .... Finally ... 
+i.e. the swarm model of the system.
 
-\subsubsection{Assumptions and notation}
+In a word, the center of the research is the design of the user agent, and the core of the agent is to make decisions. so the core of the evolution is to make decision?
 
-Ecosystem application model including:
-\subsubsection{Enterprise model}
+core of the paper: agent simulation, decision making.
 
-The Model can be described with two main parts, namely object itself(attribute) and the interaction with other enterprises(function or method)
-
-Users from platform managers, enterpirse users, customers. Even though they characteristic can be overlaped. just inherent it.
-
-Enterprise can be described as the object with attributes like 
-\begin{itemize}
-	\item Rank(reputation)
-	\item Resources(type, quantity, quality)
-	\item Capbility
-	\item Processing Status
-\end{itemize}
-
-\subsubsection{Main modules design}
-\label{subsub:main_modules}
-
-\subsubsection{System Model}
-\begin{itemize}
-	\item Coevolution
-	\item Self-organization
-	\item Emergence	
-	\item Adaption
-\end{itemize}
-
-Coevolution consist of:
-\begin{itemize}
-	\item Scarcity of customers
-	\item Conscious choice that enables the organizations to change
-	\item Interconnectedness of the enables the organizations to change
-	\item Feedback processes that carry the long-term consequences of coevolution
-\end{itemize}
-
-% subsection modeling (end)
-
-% \subsection{Mathematical Formulation} % (fold)
-% \label{sub:mathematical_formulation}
-% \subsubsection{Comprehended Model}
-% % subsection mathematical_formulation (end)
-
-% \subsection{Verification and Validation} % (fold)
-% \label{sub:verification_and_validation}
-
-% % subsection verification_and_validation (end)
-
-\subsection{Agent-based modeling and simulation} % (fold)
-\label{sub:agent_based_modeling_and_simulation}
-\subsubsection{Agent design}
-
-\subsubsection{Logical process}
+\subsection{Framework of Agent-based modeling} % (fold)
+\label{sub:framework of agent based modeling}
 \begin{figure}[htbp]
@@
 
+\subsubsection{Assumptions and notation}
+
+\subsection{Agents in the ecosystem model} % (fold)
+\label{sub:agents_in_the_ecosystem_model}
+Using UML 
+% subsection agents_in_the_ecosystem_model (end)
+
+\subsubsection{Meta agent} % (fold)
+\label{ssub:meta_agent}
+is a decision maker
+% subsubsection meta_agent (end)
+
+\subsubsection{User agent} % (fold)
+\label{ssub:user_agent}
+
+% subsubsection user_agent (end)
+
+\subsubsection{Platform agent} % (fold)
+\label{ssub:platform_agent}
+
+% subsubsection platform_agent (end)
+
+\subsection{Ecosystem model} % (fold)
+\label{sub:ecosystem model}
+
+% subsection model_realization (end)
+
+\subsubsection{Main modules design}
+\label{subsub:main_modules}
+inherent relationships, execution sequence/queue.
+
+for service provider to modify their service area, i.e. breadth and depth.
+
+Decision making involves choosing some course of action among various alternatives. For a decision maker, fulfilling the con
+
+\subsubsection{System Model}
+\begin{itemize}
+    \item Co-evolution
+    \item Self-organization
+    \item Emergence 
+    \item Adaption
+\end{itemize}
+
+Assumptions:
+\begin{enumerate}
+    \item substitute transport with time consume
+    \item manufacturing agent randomly show up in the map
+\end{enumerate}
+
+Co-evolution consist of:
+\begin{itemize}
+    \item Scarcity of customers
+    \item Conscious choice that enables the organizations to change
+    \item Interconnectedness of the enables the organizations to change
+    \item Feedback processes that carry the long-term consequences of co-evolution
+\end{itemize}
+
+% subsection modeling (end)
+
+\subsection{Simulation design} % (fold)
+\label{sub:simulation_design}
+
+% subsection simulation_design (end)
+
+\subsection{Agent-based modeling and simulation} % (fold)
+\label{sub:agent_based_modeling_and_simulation}
+\subsubsection{Agent design}
+
+\subsubsection{Logical process}
+
 \subsubsection{Interaction among agents}
@@
 
-\subsubsection{Verification and validation}
 % subsection agent_based_model_and_simulation (end)

### 2016-06-23 head.tex
modify the abstract

--- 2016-05-19 head.tex
@@
 \begin{abstract}
-New abstract
+In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product.
+This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
+However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components come along with them, the heterogeneous of resource's type, quality, price, processing velocity leads to hard taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
+Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.
+
 % 提出了 Cloud Manufacturing Ecosystem 概念，建立相应的生态系统模型，从系统中的各个角色，（需要一个指标）建立系统动力学方程。通过仿真手段验证模型，结合已有的云平台原型系统，给出相关应用。
@@
 
-The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
+% highlight the novel aspects of the work, indicating the relevance of the paper to the conference topics
+
+% What I do yet :
+% Construct the ecosystem frame work
+% study the manufacturing cooperation method with each other.
+% Design the trading the method
+% Simulation (agent-based model) and analysis.
+
+ % Supplier evaluation and selection constitutes a central issue in supply chain management (SCM).
+How- ever, the data on which to base the corresponding choices in real life problems are often imprecise or vague, which has led to the introduction of fuzzy approaches.
+Predictive intelligent-based techniques, such as Artificial Neural Network (ANN) and Adaptive Neuro Fuzzy Inference System (ANFIS), have been recently applied in different research fields to model fuzzy multi-criteria decision processes where the understanding and learning of the relationships between the input and output data are the key to select suitable solutions.
+In this paper, a hybrid ANFIS-ANN model is proposed to assist managers in their sup- plier evaluation process.
+After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers’ performance are determined by ANFIS.
+Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers’ performance based on the most effective criteria.
+A case study is presented to illustrate the main steps of the model and show its accuracy in prediction.
+A battery of parametric tests and sensitivity analyses has been implemented to evaluate the overall performance of several models based on different effective criteria combinations.
+
+In this paper, ....
+
+% Basically, (present what have done)
+
+% we do not use any utility function for the modeling; however, a unique method is proposed for eliciting the information from decision makers.
+The proposed model is applicable for a wide variety of multi-attribute decision making problems and can be used for  future ranking or selection without managers' judgment effort.
+Simulation of the managers' decisions is demonstrated in detail and the design and implementation of the model are illustrated by case study.
+
+% The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
 % 关键是系统动力学模型的建立。

### 2016-06-26 head.tex
test
ready for modify

@@
 In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product.
-This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
-However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components come along with them, the heterogeneous of resource's type, quality, price, processing velocity leads to hard taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
+This shopping model makes it possible to centralised manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
+However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
 Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.

### 2016-06-26 head.tex
start the abstract structure
make up asap

@@
 In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product.
-This shopping model makes it possible to centralised manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
+This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
 However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
-Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.
+Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the provider, and gradually, these individual transitions will brings the evolution to the ecosystem.
+
+In this paper,
+(study the resource servitization in the transitions way)
+(propose a operation model for user to describe the transitions in the system) 
+(in the god view as evolution to see the service pattern in a statistic view)
+(simulate all this in an agent-bade method)
+(evaluate which service pattern is effective for the resource user and environment friendly)
+(make a proper explanation of all the emergency of the evolution)
 

### 2016-06-27 head.tex
修改摘要

@@
 
-In this paper,
-(study the resource servitization in the transitions way)
-(propose a operation model for user to describe the transitions in the system) 
-(in the god view as evolution to see the service pattern in a statistic view)
-(simulate all this in an agent-bade method)
-(evaluate which service pattern is effective for the resource user and environment friendly)
-(make a proper explanation of all the emergency of the evolution)
+In this paper, we proposed an operation model for users to support their transitions in the manufacturing ecosystem, and we also proposed an adjustment method to guide these transitions to make a manufacturing service pattern evolution.
+With the help of Repast Simphony, we designed an agent-based model to simulate the ecosystem.
+As the simulation output, the emergence resource servitization and optimization pattern implies the effectiveness and validity of the proposed operation model and adjustment method that can be adopted in the real Cloud Manufacturing world.
 

### 2016-06-29 envolve.tex
add reinforcement learning
完成摘要初稿

@@
 
-Elo Rating System\cite{Elo1978} is a classic rating system for the ranking of chessplayer, most modern rating systems are derived from Elo's model:
+Elo Rating System\cite{Elo1978} is a classic rating system for the ranking of chess-player, most modern rating systems are derived from Elo's model:
 
@@
 
-\subsection{Reinforcement Learning and Control} % (fold)
-\label{sub:reinforcement_learning_and_control}
-test figure
-
 % subsection reinforcement_learning_and_control (end)

### 2016-06-29 head.tex
完成摘要初稿

--- 2016-06-26 head.tex
@@
 \begin{abstract}
-In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product.
-This shopping model makes it possible to centralised manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
+In Cloud Manufacturing, user do manufacturing business with well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product.
+This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
+
 However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
-Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.
+Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the individual in the ecosystem, then the manufacturing service pattern will appear with these transitions.
 
-% 提出了 Cloud Manufacturing Ecosystem 概念，建立相应的生态系统模型，从系统中的各个角色，（需要一个指标）建立系统动力学方程。通过仿真手段验证模型，结合已有的云平台原型系统，给出相关应用。
-% 云制造的实施和应用提供了一种全新的制造业生态系统，该生态系统由成员（企业用户、管理员）及环境（）组成。为了探究生态系统中，制造业的运作模式（相关决策），优化产业链，形成良性发展的制造生态，通过基于Agent 的建模，来刻画该系统中的个体行为，并通过仿真技术，模拟演化规律。
+In this paper, we proposed an operation model for users to support their transitions by means of expanding or shrinking their scope of manufacturing service in the manufacturing ecosystem, and we also proposed an adjustment approach, which depends on the ranking value of user, for the system to restrict the expanding or shrinking procedure and to control the number of users.
+Gradually this adjustment will guide evolution of the ecosystem, meanwhile, good service pattern will be discovered for the user to survival.
 
-% 云制造生态系统中，不同的企业具有不同的生态位
-% 该系统的输入
-% 输出
-% 调控方式
-
-% 通过仿真，我们发现。。。
+With the help of Repast Simphony, we designed an agent-based model to simulate the evolution process of the ecosystem.
+As the simulation output, manufacturing resource's quality is improving and its diversity is increasing with the evolution process goes by, the emergence pattern of service and resource optimization implies the effectiveness and validity of the proposed operation model and adjustment approach, user's rank-based transitions does improve the utilization of manufacturing resource.
 
@@
 In this paper, a hybrid ANFIS-ANN model is proposed to assist managers in their sup- plier evaluation process.
-After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers’ performance are determined by ANFIS.
-Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers’ performance based on the most effective criteria.
+After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers¡¯ performance are determined by ANFIS.
+Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers¡¯ performance based on the most effective criteria.
 A case study is presented to illustrate the main steps of the model and show its accuracy in prediction.
 A battery of parametric tests and sensitivity analyses has been implemented to evaluate the overall performance of several models based on different effective criteria combinations.
-
-In this paper, ....
 
@@
 % The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
-% 关键是系统动力学模型的建立。
 

### 2016-07-02 head.tex
首先 要区分框架，包括总体和具体运行框架。抓住一个点。明确系统的输入和输出，控制的目标函数之类的。

@@
 \begin{abstract}
-In Cloud Manufacturing, user do manufacturing business with well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product.
+In Cloud Manufacturing, users engage in manufacturing business through the well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product.
 This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.

### 2016-07-05 head.tex
提交摘要的版本

@@
 
-\author[label1]{Author}
-\address[label1]{ZJU}
+\author[label1]{Shengkai Chen}
+% \address[label1]{ZJU}
+% \address[label1]{Address One}
+\address[label1]{Zhejiang University, Institute of manufacturing engineering and automation, Hangzhou City, Zhejiang Province, China}
+
+% \fntext[label4]{Small city}
+
 \begin{abstract}
 In Cloud Manufacturing, users engage in manufacturing business through the well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product.
-This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
+This business model allows centralized management of distributed massive manufacturing resources, and could potentially reduce the idle rate of those resources.
 
-However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
-Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the individual in the ecosystem, then the manufacturing service pattern will appear with these transitions.
+However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model, makes it hard to meet demander's need.
+Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the individual in the ecosystem.
+As a consequence, the emergence of manufacturing service pattern will be accompanied by these transitions.
 
-In this paper, we proposed an operation model for users to support their transitions by means of expanding or shrinking their scope of manufacturing service in the manufacturing ecosystem, and we also proposed an adjustment approach, which depends on the ranking value of user, for the system to restrict the expanding or shrinking procedure and to control the number of users.
-Gradually this adjustment will guide evolution of the ecosystem, meanwhile, good service pattern will be discovered for the user to survival.
+In this paper, the author proposed an operation model for users to support their transitions by means of expanding or shrinking their scope of manufacturing service in the manufacturing ecosystem, and the author also proposed an adjustment approach, which depends on the ranking value of user, for the system to restrict the expanding or shrinking procedure and to control the number of users.
+Gradually this adjustment will guide the evolution of the ecosystem, meanwhile, good service pattern will be discovered by the user to survival.
 
-With the help of Repast Simphony, we designed an agent-based model to simulate the evolution process of the ecosystem.
-As the simulation output, manufacturing resource's quality is improving and its diversity is increasing with the evolution process goes by, the emergence pattern of service and resource optimization implies the effectiveness and validity of the proposed operation model and adjustment approach, user's rank-based transitions does improve the utilization of manufacturing resource.
+With the help of Repast Simphony, the author designed an agent-based model to simulate the evolution process.
+As the simulation output, manufacturing resource's quality is improving and its diversity is increasing as the evolution process goes by.
+The emergence pattern of service and resource optimization implies the effectiveness and validity of the proposed operation model and adjustment approach, user's rank-based transitions does improve the utilization of manufacturing resource.
 
@@
 %% keywords here, in the form: keyword \sep keyword
-new \sep key \sep words
+Cloud manufacturing ecosystem \sep
+Resource servitization and optimization\sep
+Service pattern recognition\sep
+Manufacturing evolution\sep
+Agent-based simulation
+
 %Cloud Manufacturing  Ecosystem \sep scheduling \sep evolving \sep optimization

### 2016-07-19 method.tex
add an assumption that one provider can push one order once
specify the suppose

@@
 \subsubsection{Assumptions and notation}
+\begin{itemize}
+    \item one provider can publish only one order at one time;
+    \item service quality give the initial rank, the product quality depends on the service quality, review depends on the service quality, and the rank depends on the review;
+    \item when it comes to rank value, we refer two different rank values: user rank(provider) and service rank, their relationship should be determined.
+\end{itemize}
 
@@
 
-\subsubsection{User agent} % (fold)
-\label{ssub:user_agent}
+\subsubsection{Demander agent} % (fold)
+\label{ssub:demander_agent}
+After pricing, chose the provider and the amount considering the time limit of the project and the budget.
+% subsubsection demander_agent (end)
 
-% subsubsection user_agent (end)
+\subsubsection{Provider agent} % (fold)
+\label{ssub:provider_agent}
+Pricing function specify two main parts:
+unit cost and
+provided amount
+% subsubsection provider_agent (end)
+
+\subsubsection{Complex user agent} % (fold)
+\label{ssub:complex_user_agent}
+
+% subsubsection complex_user_agent (end)
 
@@
 \label{ssub:platform_agent}
-
+matching the 
 % subsubsection platform_agent (end)

### 2016-07-20 head.tex

@@
 
-% highlight the novel aspects of the work, indicating the relevance of the paper to the conference topics
-
-% What I do yet :
-% Construct the ecosystem frame work
-% study the manufacturing cooperation method with each other.
-% Design the trading the method
-% Simulation (agent-based model) and analysis.
-
-% Supplier evaluation and selection constitutes a central issue in supply chain management (SCM).
-How- ever, the data on which to base the corresponding choices in real life problems are often imprecise or vague, which has led to the introduction of fuzzy approaches.
-Predictive intelligent-based techniques, such as Artificial Neural Network (ANN) and Adaptive Neuro Fuzzy Inference System (ANFIS), have been recently applied in different research fields to model fuzzy multi-criteria decision processes where the understanding and learning of the relationships between the input and output data are the key to select suitable solutions.
-In this paper, a hybrid ANFIS-ANN model is proposed to assist managers in their sup- plier evaluation process.
-After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers¡¯ performance are determined by ANFIS.
-Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers¡¯ performance based on the most effective criteria.
-A case study is presented to illustrate the main steps of the model and show its accuracy in prediction.
-A battery of parametric tests and sensitivity analyses has been implemented to evaluate the overall performance of several models based on different effective criteria combinations.
-
-% Basically, (present what have done)
-
-% we do not use any utility function for the modeling; however, a unique method is proposed for eliciting the information from decision makers.
-The proposed model is applicable for a wide variety of multi-attribute decision making problems and can be used for  future ranking or selection without managers' judgment effort.
-Simulation of the managers' decisions is demonstrated in detail and the design and implementation of the model are illustrated by case study.
-
-% The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
-
 \end{abstract}
@@
 \begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
 Cloud manufacturing ecosystem \sep
@@
 
-%Cloud Manufacturing  Ecosystem \sep scheduling \sep evolving \sep optimization
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
 \end{keyword}

### 2016-08-19 method.tex
start to structure the paper
tell the philosophy

@@
 matching the 
+\begin{figure}
+
+\begin{tikzpicture}
+\begin{class}[text width=8cm]{Job}{0,0}
+    \attribute{needCapacity : Map}
+    \operation{lala(haha): void}
+\end{class}
+\end{tikzpicture}
+\caption{Test UML Diagram}
+
+\end{figure}
 % subsubsection platform_agent (end)
@@
 % subsection model_realization (end)
+
+\subsubsection{Design philosopher} % (fold)
+\label{ssub:design_philosopher}
+platform create demander and provider
+demander, a subclass of user, generate need i.e. create order (the defined task bunch)
+    task is a subclass of job, need to be processed with specified resource type and amount(type,amount) , have its process time.
+provider, a subclass of user, provider resource with different type and capacity, these resources can be allocated to task job and service-call job, service-call is subclass of job, which is the job to combined to create service.
+
+the two type of job, task and service call, have something in common that need to be processd with resource. for task, the resource is renewable, for service-call, the resource is unrenewable.
+
+service can be generated after the finish of service-call, so it belongs to the user who generate the service-call. service more like a contract
+
+service-call come out driven by the task need, when a task appears frequently, provider proposed the job that have the same configuration.
+so the service generated by the service-call will suit for the specificed task.
+
+good for service: efficieny, do not have to coordinated anymore, flexibe wile process with task, with the outsource trick, slice the taks, co-worked by all the useful resources.
+bad for service: task-oriented, can only process specified task,
+
+% subsubsection design_philosopher (end)
+
+\subsubsection{Main functions} % (fold)
+\label{ssub:main_functions}
+service - task outsource
+% subsubsection main_functions (end)
+
+\subsubsection{Main problem} % (fold)
+\label{ssub:main_problem}
+
+% subsubsection main_problem (end)
+
+\subsubsection{Main flow design} % (fold)
+\label{ssub:main_flow_design}
+\begin{itemize}
+    \item generate provider and demander
+    \item generate order (with task)
+    \item generate resources
+    \item process tasks (with only resource)
+    \item organize service
+    \item process task (plus service)
+    \item Review and elimination of provider and service
+\end{itemize}
+% subsubsection main_flow_design (end)
 

### 2016-08-20 design.tex
tell the design philosophy

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
The manufacturing ecosystem we proposed in this paper consists of the structure of cloud manufacturing, the operation mode and the controlling rules. Before the detailed interpretation for these parts, we describe some basic settings as follows.

\subsubsection{Master plan} % (fold)
\label{ssub:master_plam}
A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots,t_{in}\right\}$ of tasks which have to be processed. The tasks are interrelated by kinds of constraints. First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors, how to construct the predecessor will be explained later. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation transmits and enhances these constraints.
A single resource($r_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\,A\right\}$given by the platform. While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $r_k$ has a limited capacity of $C_k$ at any point in time.
A single service($s_l$) is a composition of all resources in set $R_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$Q_{k,ij}=Q_l$) without resource coordinating any more. While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.
A single service-call($sc_l$) comes out after the finish of one frequent task, so it have the same resource configuration the frequent task. Service-call can only be performed via resource cooperation with duration $p_l$, because the identity of resource, the capacity cannot be return to the resource after the finish of service-call, so the service-call brings new constrains to the related resources.  
% subsubsection master_plan (end)

\subsubsection{Assumptions, nomenclature} % (fold)
\label{ssub:assumptions_nomenclature}

% subsubsection assumptions_nomenclature (end)
% subsection preliminaries (end)

\subsection{Operation mode} % (fold)
\label{sub:operation_mode}

% subsection operation_mode (end)

\subsection{Interactions and decisions} % (fold)
\label{sub:interactions_and_decisions}

% subsection interactions_and_decisions (end)

\subsection{Controlling rules} % (fold)
\label{sub:controlling_rules}

% subsection controlling_rules (end)

\subsection{Tricky problems} % (fold)
\label{sub:tricky_problems}

% subsection tricky_problems (end)
% section design_of_the_ecosystem (end)

### 2016-08-20 design.tex
start to tell the story
assumptation, equation, module, review, intro, review module

@@
 \label{ssub:master_plam}
+With the cloud manufacturing platform operating, demander comes, signs up and publish orders.
+Match module in platform informs the task messages in the order to every matched resources and services.
+After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
+Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before.
+Most of resource related decision making are well controlled by platform with the review module.
+
 A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots,t_{in}\right\}$ of tasks which have to be processed.
@@
 Third, resources cooperation transmits and enhances these constraints.
-A single resource($r_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\,A\right\}$given by the platform.
-While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
+
+A single resource($r_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\,A\right\}$ given by the platform.
+While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
 Each resource $r_k$ has a limited capacity of $C_k$ at any point in time.
+
 A single service($s_l$) is a composition of all resources in set $R_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$Q_{k,ij}=Q_l$) without resource coordinating any more.
@@
 Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.
+
 A single service-call($sc_l$) comes out after the finish of one frequent task, so it have the same resource configuration the frequent task.
 Service-call can only be performed via resource cooperation with duration $p_l$, because the identity of resource, the capacity cannot be return to the resource after the finish of service-call, so the service-call brings new constrains to the related resources.
+Unlike the task, the amount of one type resource required in the service-call can be pieced together from more than one resource as long as they are in the same type.
+
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration}--\ref{tab:simpleresourceconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+  \caption{Simple job configuration}
+    \begin{tabular}{cccccc}
+    \toprule
+    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Duration}} \\
+    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+    \midrule
+    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
+    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
+    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
+    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
+    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:simplejobconfiguration}%
+\end{table}%
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+  \caption{Simple resource configuration}
+    \begin{tabular}{ccc}
+    \toprule
+    Resource & Type  & Capacity \\
+    \midrule
+    $r_1$ & 1     & 10 \\
+    $r_2$ & 2     & 10 \\
+    $r_3$ & 3     & 10 \\
+    $r_4$ & 3     & 10 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:simpleresourceconfiguration}%
+\end{table}%
+\begin{figure}[htbp]
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
+	\caption{Simple instance schedule chart}
+	\label{fig:scheduleChart}
+\end{figure}
+This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period.
+Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.
+
 % subsubsection master_plan (end)
@@
 \label{ssub:assumptions_nomenclature}
+job
+order
+task
+service-call
+abstract machine
+resource
+service
+demander
+provider
+platform
+rank
+hardness
 
+detailed design will be explained in the following sections.
 % subsubsection assumptions_nomenclature (end)
@@
 \label{sub:tricky_problems}
-
+The job lock
 % subsection tricky_problems (end)

### 2016-08-20 figures/scheduleChart.tex
start to tell the story
assumptation, equation, module, review, intro, review module

% !TEX root = flow_head.tex

\begin{tikzpicture}
\foreach \x in {0,6,12,18}
	\draw [->,thick] (15.7cm,\x cm) node{t} (0,\x cm) -- +(15.5cm, 0) ;
\foreach \x in {0,6,12,18}
	\draw [->,thick] (0,\x cm) -- +(0,5.2 cm);
\foreach \x in {0,6,12,18}
	\draw[yshift=5.35cm] (0,\x cm) node{Capacity};
\foreach \x in {1,2,3,4}
	\draw[yshift=23.5cm] (7.5cm,-6*\x cm) node{$r_\x$};
\foreach \x in {1,...,15}
	\foreach \y in {0,6,12,18}
		\draw (\x cm,\y cm) -- +(0,2mm);
\foreach \x in {1,...,15}
	\foreach \y in {0,6,12,18}
		\draw[yshift=-2mm] (\x cm,\y cm) node{$\x$};
\foreach \y in {0,6,12,18}
	\foreach \x in {1,...,10}
		\draw[yshift=\y cm] (0,0.5*\x cm) -- +(2mm,0) (-3mm,0.5*\x cm) node{$\x$};

\fill[blue!20!,yshift=18cm] (5cm,4cm) rectangle (7cm,5cm);
\draw[yshift=18cm] (2cm,0) rectangle (5cm,3cm) (5cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (3.5cm,1.6cm) node{$t_3$} (6.5cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$};
\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm);
\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$};
\draw[dotted,yshift=12cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$};
\draw[dotted,yshift=6cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (2cm,0) rectangle (5cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (3.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}

### 2016-08-21 design.tex
add nomecalture

@@
 \label{ssub:assumptions_nomenclature}
+
+\begin{table}[!h]
+  \begin{framed}
+    \nomenclature{$A$}{radius of}
+    \nomenclature{$B$}{position of}
+    \nomenclature{$C$}{further nomenclature}
+    \printnomenclature
+  \end{framed}
+\end{table}
+
 job
@@
 
+\subsection{Interactions and decisions} % (fold)
+\label{sub:interactions_and_decisions}
+\subsubsection{Demander}
+\label{subs:Demander}
+For Task
+
+\subsubsection{Provider}
+\label{subs:Provider}
+For Resource
+
+For Service-call
+
+For Service
+
+% subsection interactions_and_decisions (end)
+
 \subsection{Operation mode} % (fold)
 \label{sub:operation_mode}
+Outsource
 
@@
 
-\subsection{Interactions and decisions} % (fold)
-\label{sub:interactions_and_decisions}
-
-% subsection interactions_and_decisions (end)
-
 \subsection{Controlling rules} % (fold)
 \label{sub:controlling_rules}
-
+Platform control the provider
 % subsection controlling_rules (end)

### 2016-08-21 design.tex
overall main design finished

--- 2016-08-20 design.tex
@@
 
-A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots,t_{in}\right\}$ of tasks which have to be processed.
+A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks which have to be processed.
 The tasks are interrelated by kinds of constraints.
@@
 
-A single resource($r_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\,A\right\}$ given by the platform.
+A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform.
 While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
-Each resource $r_k$ has a limited capacity of $C_k$ at any point in time.
+Each resource $mr_k$ has a limited capacity of $C_k(\tau)$ at any point in time $\tau$.
 
-A single service($s_l$) is a composition of all resources in set $R_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$Q_{k,ij}=Q_l$) without resource coordinating any more.
+A single service($s_l$) is a composition of all resources in set $R_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more.
 While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
@@
 
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration}--\ref{tab:simpleresourceconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
-\begin{table}[htbp]
-  \centering
-  \scriptsize
-  \caption{Simple job configuration}
-    \begin{tabular}{cccccc}
-    \toprule
-    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Duration}} \\
-    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
-    \midrule
-    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
-    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
-    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
-    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
-    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:simplejobconfiguration}%
-\end{table}%
+Specifically, a simple instance with configuration \autoref{tab:simpleresourceconfiguration}--\ref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
 \begin{table}[htbp]
@@
 \end{table}%
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+  \caption{Simple job configuration}
+    \begin{tabular}{cccccc}
+    \toprule
+    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
+    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+    \midrule
+    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
+    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
+    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
+    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
+    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:simplejobconfiguration}%
+\end{table}%
 \begin{figure}[htbp]
@@
 	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
-	\caption{Simple instance schedule chart}
+	\caption{Simple instance schedule chart with 4 resources}
 	\label{fig:scheduleChart}
@@
 \label{ssub:assumptions_nomenclature}
-job
-order
-task
-service-call
-abstract machine
-resource
-service
-demander
-provider
-platform
-rank
-hardness
+Assumptions about quality
+about time
 
-detailed design will be explained in the following sections.
+\begin{table}[!h]
+\begin{tabularx}{\textwidth}{|lX|}
+    \hline
+    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
+    \multicolumn{2}{|l|}{} \\
+	$o_i$ & Order that come with demander \\
+	$\mathcal{T}_i$ & Task set of $o_i$ \\
+	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
+	$p_{ij}$ & Process duration of $t_{ij}$\\
+	$r_i$ & Release time of $o_i$\\
+	$mr_k$ & Resource that come with provider \\
+	$\delta_k$ & Quality of resource $mr_k$ \\
+	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
+	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
+	$\mathcal{L}_{k,\tau}$ & The set of job queue of $mr_k$ at $\tau$\\ 
+	$\mathcal{A}$ & Resource type set \\
+	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
+	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
+	$sc_l$ & Service-call generated by provider\\
+	$p_l$ & Process duration of $sc_l$\\
+	$r_l$ & Release time of $sc_l$\\
+	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
+	$ms_l$ & Service that generated after the finish of $sc_l$\\
+	$\Delta_l$ & Overall quality of servicev $ms_l$\\
+	$\bm{mr}_l$ & Resource member set of $ms_l$\\
+	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
+	$\mathcal{L}_{l,\tau}$ & The set of job queue of $ms_l$ at $\tau$\\
+	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
+	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
+	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
+	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
+	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
+	$R(\cdot)$ & Rank inquire function about provider\\
+	$F(\cdot)$ & Owner inquire function about resource or service\\
+	$P(\cdot)$ & Type inquire function about resource\\
+	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
+    \hline
+\end{tabularx}
+\end{table}
+
+For the continuous coming of provider, demander, order, task, etc., the amount of them can not be determined at any time point, so we doesn't restrict the upper bound for subscript index amount of all these variables, and we will study the decision separately for these individual at the given time point $\tau$.
+Detailed design will be explained in the following sections.
 % subsubsection assumptions_nomenclature (end)
@@
 
+\subsection{Interactions and decisions} % (fold)
+\label{sub:interactions_and_decisions}
+\subsubsection{Demander}
+\label{subs:Demander}
+Demander makes decision about resources and services selection for the task.
+Without loss of generalization, we suppose at time period $\tau$, demander received bunch of matched resource and services as candidates for the performance of the published order $o_i$, it's obvious that $\tau \ge r_{i}$.
+The decision making for any task included in $o_i$, let's take $t_{ij}$, can be described in one of the following 3 situation:
+
+\begin{asparaenum}
+\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
+\suspend{asparaenum}
+\begin{equation}
+\max_{\forall l}\left\{ \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right\}
+\end{equation}
+\begin{numcases}{\text{s.t.}}
+ ms_l \in \mathcal{S}_{ij,\tau} & \\
+\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
+\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
+\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & 
+\end{numcases}
+
+\resume{asparaenum}
+\item  $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$, while $\abs{\mathcal{S}_{ij,\tau}}=0$.
+\suspend{asparaenum}
+
+\begin{equation}
+\max_{\forall \bm{k}}\left\{ \delta_{\bm{k}}, 
+R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
+\right\}
+\end{equation}
+\begin{numcases}{\text{s.t.}}
+q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \\
+R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \\
+mr_{k_{\alpha}} \in \mathcal{R}_{\alpha,\tau} & \\
+\mathcal{R}_{ij} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
+\bm{k} = \left[k_1,k_2,\dots,k_\alpha,\dots\right] & \\ 
+\forall\alpha\in\mathcal{A}_{ij} &
+\end{numcases}
+For each required resource type $\alpha$
+
+\resume{asparaenum}
+\item  $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$, while $\abs{\mathcal{S}_{ij,\tau}}>0$.
+\end{asparaenum}
+
+\begin{equation}
+\max_{m\in\{l^*,\bm{k}^*\}} \left\{ \Delta_m, 
+Rank_m, \mathcal{L}_m \right\}
+\end{equation}
+\begin{numcases}{\text{s.t.}}
+q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \\
+R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \\
+mr_{k_{\alpha}} \in \mathcal{R}_{\alpha,\tau} & \\
+\mathcal{R}_{ij} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
+\bm{k} = \left[k_1,k_2,\dots,k_\alpha,\dots\right] & \\ 
+\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left\{ \delta_{\bm{k}}, 
+R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
+\right\}\right) & \\
+Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
+\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
+\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
+\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
+\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
+\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
+\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
+ms_l \in \mathcal{S}_{ij,\tau} & \\
+\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
+\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
+\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
+l^* = \arg\left( \max_{\forall l}\left\{ \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right\}  \right) & \\
+Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
+\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
+\forall\alpha\in\mathcal{A}_{ij} & 
+\end{numcases}
+
+\subsubsection{Provider}
+\label{subs:Provider}
+Provider makes decision for job response with regard to its resources and service, the job here means task and service-call.
+As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks.
+Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:
+
+\begin{asparaenum}
+\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
+\suspend{asparaenum}
+\begin{numcases}{}
+A_{k,\tau} \ge q_{\alpha,ij} &\\
+P(mr_k) = \alpha &
+\end{numcases}
+If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$.
+If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$.
+The available will be return back after the finish of $t_{ij}$.
+\resume{asparaenum}
+\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
+\suspend{asparaenum}
+\begin{numcases}{}
+C_{k,\tau} > 0 & \\
+P(mr_k) = \alpha
+\end{numcases}
+If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$.
+If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
+\begin{numcases}{}
+C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
+C_{k,\tau} := 0 & otherwise
+\end{numcases}
+
+Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed.
+Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
+\begin{numcases}{}
+\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
+R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
+\end{numcases}
+\resume{asparaenum}
+\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$
+\end{asparaenum}
+Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
+\begin{numcases}{}
+q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
+\mathcal{A}_{ij} = \mathcal{B}_l
+\end{numcases}
+
+This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
+\begin{numcases}{}
+q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
+\mathcal{A}_{ij} = \mathcal{A}_l
+\end{numcases}
+% subsection interactions_and_decisions (end)
+
 \subsection{Operation mode} % (fold)
 \label{sub:operation_mode}
+The chief concern about operation mode for provider is the outsource mode and schedule method
 
@@
 
-\subsection{Interactions and decisions} % (fold)
-\label{sub:interactions_and_decisions}
-
-% subsection interactions_and_decisions (end)
-
 \subsection{Controlling rules} % (fold)
 \label{sub:controlling_rules}
-
+Platform control the provider by the rank value and the review module
 % subsection controlling_rules (end)
@@
 The job lock
+
+add predecessor job when sc in to job queue,
+
+after the finish of all the job in job queue to start the performance of sc
+
+make the task which was prepared in one resource ahead to other jobs in the cooperated resources 
 % subsection tricky_problems (end)

### 2016-08-22 design.tex
resource schedule done

@@
 Assumptions about quality
+
 about time
+
+schedule and outsource are event driven decision making
 
@@
 	$r_i$ & Release time of $o_i$\\
+	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
+	$f_{i}$ & Finish time of $o_i$\\
+	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
 	$mr_k$ & Resource that come with provider \\
@@
 	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
-	$\mathcal{L}_{k,\tau}$ & The set of job queue of $mr_k$ at $\tau$\\ 
+	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
+	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
+	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
+	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
 	$\mathcal{A}$ & Resource type set \\
@@
 	$r_l$ & Release time of $sc_l$\\
+	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
 	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
@@
 	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
-	$\mathcal{L}_{l,\tau}$ & The set of job queue of $ms_l$ at $\tau$\\
+	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
+	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
 	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
@@
 \begin{equation}
-\max_{\forall l}\left\{ \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right\}
+\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)
 \end{equation}
 \begin{numcases}{\text{s.t.}}
- ms_l \in \mathcal{S}_{ij,\tau} & \\
 \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
 \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
-\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & 
+\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
+l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & 
 \end{numcases}
@@
 \begin{equation}
-\max_{\forall \bm{k}}\left\{ \delta_{\bm{k}}, 
+\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
 R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
-\right\}
+\right)
 \end{equation}
+
 \begin{numcases}{\text{s.t.}}
-q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \\
-R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \\
-mr_{k_{\alpha}} \in \mathcal{R}_{\alpha,\tau} & \\
-\mathcal{R}_{ij} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
-\bm{k} = \left[k_1,k_2,\dots,k_\alpha,\dots\right] & \\ 
-\forall\alpha\in\mathcal{A}_{ij} &
+q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\\
+R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\\
+\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
+\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \\
+k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$
 \end{numcases}
@@
 
-\begin{equation}
-\max_{m\in\{l^*,\bm{k}^*\}} \left\{ \Delta_m, 
-Rank_m, \mathcal{L}_m \right\}
-\end{equation}
-\begin{numcases}{\text{s.t.}}
-q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \\
-R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \\
-mr_{k_{\alpha}} \in \mathcal{R}_{\alpha,\tau} & \\
-\mathcal{R}_{ij} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
-\bm{k} = \left[k_1,k_2,\dots,k_\alpha,\dots\right] & \\ 
-\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left\{ \delta_{\bm{k}}, 
+\begin{gather}
+\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
+Rank_m, \mathcal{L}_m \right) \\ 
+\text{s.t.}\notag
+\end{gather}
+\begin{numcases}{}
+q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
+R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
+\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
+\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
+k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
+\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
 R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
-\right\}\right) & \\
+\right)\right) & \\
 Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
@@
 \bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
-ms_l \in \mathcal{S}_{ij,\tau} & \\
 \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
@@
 \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
-l^* = \arg\left( \max_{\forall l}\left\{ \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right\}  \right) & \\
+l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
+l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
 Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
 \mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
-\forall\alpha\in\mathcal{A}_{ij} & 
+m \in \left\{ l^*,\bm{k}^* \right\}
 \end{numcases}
@@
 \label{subs:Provider}
-Provider makes decision for job response with regard to its resources and service, the job here means task and service-call.
+Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call.
 As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks.
@@
 \resume{asparaenum}
-\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$
+\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
 \end{asparaenum}
@@
 \label{sub:operation_mode}
-The chief concern about operation mode for provider is the outsource mode and schedule method
+The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure.
+Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:
+\begin{asparaenum}
+\item Assign new task $t_{ij}$ in $mr_k$.
+\suspend{asparaenum}
+
+With the select decision of $t_{ij}$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
+\begin{equation}
+	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau},sc \text{ is service-call} \right\} \cup \mathcal{G}_{k,\tau}
+\end{equation}
+Then, the provider will add $t_{ij}$ to queue or process buffer according to:
+\begin{numcases}{}
+\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0$ and $A_{k,\tau}\ge q_{\alpha,ij}$ \\
+\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
+\end{numcases}
+
+\resume{asparaenum}
+\item Assign new service-call $sc_l$ in $mr_k$.
+\suspend{asparaenum}
+
+With the select decision of $sc_l$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
+\begin{equation}
+	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{G}_{k,\tau}
+\end{equation}
+Then, the provider will add $sc_l$ to queue or process buffer according to:
+\begin{numcases}{}
+\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_l\} & if $\abs{\mathcal{L}_{k,\tau}\cup\mathcal{G}_{k,\tau}}=0$ \\
+\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
+\end{numcases}
+
+\resume{asparaenum}
+\item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
+\suspend{asparaenum}
+
+The assignment of new service-call will not driven these decision making event because of the resource capacity consuming feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
+\begin{figure}[htbp]
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{figures/service-call}}
+	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
+	\label{fig:simplejoblist}
+\end{figure}
+Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
+
+A schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right],n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}}$.
+Since the task in $\mathcal{L}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, type subscript $\alpha$ can be ignored for all the job assigned here matches the resource type, so the schedule model is:
+
+\begin{equation}
+\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right)
+\end{equation}
+\begin{numcases}{\text{s.t.}}
+L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\right\} & \\
+f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\\
+G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \\
+f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \\
+\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \\
+% \bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_{\abs{\mathcal{L}^{(s)}_{k,\tau_0}}}\right] & \\
+f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
+\end{numcases}
+\resume{asparaenum}
+\item Schedule the task in $\mathcal{L}_{l,\tau}$
+\suspend{asparaenum}
+
+\resume{asparaenum}
+\item Outsource the task in $\mathcal{L}_{l,
+\tau}$ and $\mathcal{P}_{l,\tau}$
+\end{asparaenum}
 

### 2016-08-22 design.tex
start to design the rank and reviw

@@
 \sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \\
-% \bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_{\abs{\mathcal{L}^{(s)}_{k,\tau_0}}}\right] & \\
 f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
 \end{numcases}
-\resume{asparaenum}
-\item Schedule the task in $\mathcal{L}_{l,\tau}$
-\suspend{asparaenum}
+
+Like the RCPSP
 
 \resume{asparaenum}
-\item Outsource the task in $\mathcal{L}_{l,
-\tau}$ and $\mathcal{P}_{l,\tau}$
+\item Outsource the task in both active and inactive status.
 \end{asparaenum}
+
+Since only matched task can be assigned and processed in the certain service, the decision making about schedule tasks in service $ms_l$ is a simple problem that it is similar to 1 machine scheduling problem, so we will not discuss the situation about schedule the task in $\mathcal{L}_{l,\tau}$ here.
+However, service can perform task in a flexible mode, provider can outsource the task in both active and inactive status.
+
+For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status will decrease.
+This decision highly depends on the estimate of performance status in other resources and services.
 
@@
 \label{sub:controlling_rules}
-Platform control the provider by the rank value and the review module
+The decision makings explained above are controlled by review and ranking mechanism provided by platform, the provider who have higher rank value will be safer to stay in the ecosystem, have more chance to succeed in generating services, his services and resources will get more preference.
+Hence, here we will explain the setting and changing in the rank value:
+\begin{asparaenum}
+\item Rank value setting
+\suspend{asparaenum}
+
+\resume{asparaenum} 
+\item Rank value changing
+\end{asparaenum}
+
 % subsection controlling_rules (end)

### 2016-08-23 design.tex
specified the design

@@
 	$p_{ij}$ & Process duration of $t_{ij}$\\
+	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
 	$r_i$ & Release time of $o_i$\\
@@
 	$mr_k$ & Resource that come with provider \\
-	$\delta_k$ & Quality of resource $mr_k$ \\
+	$\delta_k$ & Product quality produced via resource $mr_k$ \\
 	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
@@
 	$ms_l$ & Service that generated after the finish of $sc_l$\\
-	$\Delta_l$ & Overall quality of servicev $ms_l$\\
+	$\Delta_l$ & Product quality produced via service $ms_l$\\
 	$\bm{mr}_l$ & Resource member set of $ms_l$\\
@@
 	$F(\cdot)$ & Owner inquire function about resource or service\\
-	$P(\cdot)$ & Type inquire function about resource\\
+	$P(\cdot)$ & Type inquire function about resource type\\
 	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
@@
 \begin{numcases}{}
-\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0$ and $A_{k,\tau}\ge q_{\alpha,ij}$ \\
+\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \\
 \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
@@
 The decision makings explained above are controlled by review and ranking mechanism provided by platform, the provider who have higher rank value will be safer to stay in the ecosystem, have more chance to succeed in generating services, his services and resources will get more preference.
-Hence, here we will explain the setting and changing in the rank value:
+Hence, here we will explain some controlling rules related to the rank value changing:
 \begin{asparaenum}
-\item Rank value setting
+\item Review from demander when his task $t_{ij}$ was finished by resource cooperation $mr_{\bm{k}}$:
 \suspend{asparaenum}
 
+We will ignore resource type subscript $\alpha$ here for the reason that resources perform the task already meet the type needs.
+With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
+\begin{numcases}{}
+rank := rank +
+\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
+\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} &\\
+\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
+\end{numcases}
+
 \resume{asparaenum} 
-\item Rank value changing
+\item Review from demander when his task $t_{ij}$ was finished by service $ms_l$:
+\suspend{asparaenum}
+Rank value changing with regard to service can be determined easier:
+\begin{equation}
+	rank := rank + \frac{ \left(\sum_{q\in\bm{q}_l}p_{ij}\cdot q \right)\left( \Delta_l -\gamma_{ij}\right) }{ e^{\left( f_{ij} - p_{ji} -r_{ij} \right)} }
+\end{equation}
+
+\resume{asparaenum}
+\item Eliminate resource or service on the platform
 \end{asparaenum}
 
+This decision making is a control method for platform to keep the performance of tasks with content quality and efficiency.
+We denote the list of all resources with type $\alpha$ as $\bm{mr}_\alpha$ and the list of all services as $\bm{ms}$ at time $\tau$, after the sort these lists according to the scarcity and quality, the unqualified resources and services.
+Scarcity can be defined as:
+\begin{numcases}{}
+\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} }& $\alpha\in\mathcal{A}$\\
+\abs{\mathcal{L}_{l,\tau}}
+\end{numcases}
 % subsection controlling_rules (end)
@@
 \label{sub:tricky_problems}
-The job lock
+Even though the schedule mode exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
+Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock},
+\begin{figure}[htbp]
+	\centering
+	\resizebox{.85\textwidth}{!}{\input{figures/job-lock}}
+	\caption{Simple illustration of job lock problem}
+	\label{fig:joblock}
+\end{figure}
+$t_{i2}$ is active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is active in $mr_1$ and inactive in $mr_2$, because of the capacity limit, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and will they will block the other tasks from being processed.
 
-add predecessor job when sc in to job queue,
-
-after the finish of all the job in job queue to start the performance of sc
-
-make the task which was prepared in one resource ahead to other jobs in the cooperated resources 
+The method to solve the job-lock problem is to add the status changed task to the predecessor set of all the other tasks in the same inactive queue list.
 % subsection tricky_problems (end)

### 2016-08-23 figures/job-lock.tex
specified the design

% !TEX root = flow_head.tex
\begin{tikzpicture}

\fill[blue!20!,yshift=1.5cm] (3cm,0) rectangle (4cm,1cm);
\fill[blue!20!] (2cm,0) rectangle (3cm,1cm);
\draw[thick,yshift=1.5cm] (0,0) rectangle (4cm,1cm) (6.5cm,0) rectangle (11.5cm,1cm) (3cm,0) rectangle (4cm,1cm);
\draw[yshift=2cm] (-5mm,0) node{$mr_1$} (1.5cm,0) node{$t_{i1}$} (9cm,0) node{$t_{i2}$} (6cm,0) node{$\cdots$} (12cm,0) node{$\cdots$};
\draw[thick,dotted,xshift=5cm] (0,-5mm) -- (0,3.5cm);
\draw[thick] (0,0) rectangle (3cm,1cm) (6.5cm,0) rectangle (10.5cm,1cm) (2cm,0) rectangle (3cm,1cm);
\draw[yshift=0.5cm] (-5mm,0) node{$mr_2$}  (1cm,0) node{$t_{i2}$} (8.5cm,0) node{$t_{i1}$} (6cm,0) node{$\cdots$} (11cm,0) node{$\cdots$};
\draw[yshift=3cm] (2cm,0) node{active} (9.5cm,0) node{inactive};

\end{tikzpicture}

### 2016-08-23 figures/job-lock.tex
modify the joblock figure

@@
 \fill[blue!20!] (2cm,0) rectangle (3cm,1cm);
-\draw[thick,yshift=1.5cm] (0,0) rectangle (4cm,1cm) (6.5cm,0) rectangle (11.5cm,1cm) (3cm,0) rectangle (4cm,1cm);
-\draw[yshift=2cm] (-5mm,0) node{$mr_1$} (1.5cm,0) node{$t_{i1}$} (9cm,0) node{$t_{i2}$} (6cm,0) node{$\cdots$} (12cm,0) node{$\cdots$};
+\draw[thick,yshift=1.5cm] (0,0) rectangle (4cm,1cm) (6.5cm,0) rectangle (8.5cm,1cm) (3cm,0) rectangle (4cm,1cm);
+\draw[yshift=2cm] (-5mm,0) node{$mr_1$} (1.5cm,0) node{$t_{i1}$} (7.5cm,0) node{$t_{i2}$} (6cm,0) node{$\cdots$} (9cm,0) node{$\cdots$};
 \draw[thick,dotted,xshift=5cm] (0,-5mm) -- (0,3.5cm);
-\draw[thick] (0,0) rectangle (3cm,1cm) (6.5cm,0) rectangle (10.5cm,1cm) (2cm,0) rectangle (3cm,1cm);
-\draw[yshift=0.5cm] (-5mm,0) node{$mr_2$}  (1cm,0) node{$t_{i2}$} (8.5cm,0) node{$t_{i1}$} (6cm,0) node{$\cdots$} (11cm,0) node{$\cdots$};
-\draw[yshift=3cm] (2cm,0) node{active} (9.5cm,0) node{inactive};
+\draw[thick] (0,0) rectangle (3cm,1cm) (6.5cm,0) rectangle (9.5cm,1cm) (2cm,0) rectangle (3cm,1cm);
+\draw[yshift=0.5cm] (-5mm,0) node{$mr_2$}  (1cm,0) node{$t_{i2}$} (8cm,0) node{$t_{i1}$} (6cm,0) node{$\cdots$} (10cm,0) node{$\cdots$};
+\draw[yshift=3cm] (2cm,0) node{active} (8cm,0) node{inactive};
 

### 2016-08-25 background.tex
add picture
start to structure the paper
tell the philosophy
rearrange the paper structure

@@
 	\item capacity is the function of a resource. like quantity
-	\item service is the bundle of capacities.
+	\item service is the bundle of capacities. the proportion of the capacities.
 	\item 
@@
 \centering
-\includegraphics[scale = .6, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
+\includegraphics[scale = .3, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
 \caption{Cloud manufacturing architecture with main flows}
@@
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=.7\textwidth]{usertype.pdf}
-	\caption{Simple explanation of user type}
-	\label{fig:usertype}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=.7\textwidth]{usertype.pdf}
+% 	\caption{Simple explanation of user type}
+% 	\label{fig:usertype}
+% \end{figure}
 
-\begin{table}[htbp]
-	\caption{Simple explanation of user type}
-	\label{tab:usertype}
-	\centering
-
-	\begin{tabularx}{\textwidth}{llX}
-	\toprule
-	\textbf{Type} & \textbf{Name} &  \textbf{Concise Description}\\
-	\midrule
-	I			& Pure demander &  Submit manufacturing tasks and make evaluation of provider.\\
-	II 			& Complex user 	&  Usually a pure provider submit part of its task, it becomes the complex user and changes the operation model of the user.\\
-	III 		& Pure provider &  Provide manufacturing services and makes evaluation demander.\\
-	\bottomrule
-	\end{tabularx}
-\end{table}
+% \begin{table}[htbp]
+% 	\caption{Simple explanation of user type}
+% 	\label{tab:usertype}
+% 	\centering
+% 	\tiny
+% 	\begin{tabularx}{\textwidth}{llX}
+% 	\toprule
+% 	\textbf{Type} & \textbf{Name} &  \textbf{Concise Description}\\
+% 	\midrule
+% 	I			& Pure demander &  Submit manufacturing tasks and make evaluation of provider.\\
+% 	II 			& Complex user 	&  Usually a pure provider submit part of its task, it becomes the complex user and changes the operation model of the user.\\
+% 	III 		& Pure provider &  Provide manufacturing services and makes evaluation demander.\\
+% 	\bottomrule
+% 	\end{tabularx}
+% \end{table}
 % Before the emendation of the roles, some related standard name should be taken:
@@
 \centering
-\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
+\includegraphics[scale = .3, trim = 0 15 0 10]{supplementary.pdf}
 \caption{Supplementary illustration for \autoref{fig:structure}}
@@
 	\centering
-
+	\scriptsize
 	\begin{tabularx}{\textwidth}{llX}
@@
 
-\begin{figure}[htbp]
-\centering
-\subfloat[Pure demander]{\includegraphics[width=0.75\textwidth]{demander_main_process}\label{fig:demanderprocess}}\\
-\subfloat[Complex user]{\includegraphics[width=0.75\textwidth]{complex_main_process}\label{fig:complexprocess}}\\
-\subfloat[Pure Provider]{\includegraphics[width=0.75\textwidth]{provider_main_process}\label{fig:providerprocess}}
-\caption{Main operational processes}
-\label{fig:useroperation}
-\end{figure}
+% \begin{figure}[htbp]
+% \centering
+% \subfloat[Pure demander]{\includegraphics[width=0.75\textwidth]{demander_main_process}\label{fig:demanderprocess}}\\
+% \subfloat[Complex user]{\includegraphics[width=0.75\textwidth]{complex_main_process}\label{fig:complexprocess}}\\
+% \subfloat[Pure Provider]{\includegraphics[width=0.75\textwidth]{provider_main_process}\label{fig:providerprocess}}
+% \caption{Main operational processes}
+% \label{fig:useroperation}
+% \end{figure}
 
@@
 
-\begin{table}[htbp]
-	\caption{Users' changes}
-	\label{tab:userchange}
-	\centering
-	\begin{tabularx}{\textwidth}{llX}
-	\toprule
-	\textbf{Change} & \multicolumn{2}{l}{\textbf{Appearance with concise description}}\\
-	\midrule
-	\multirow{3}*{Type}			& Complex user $\to$ Pure demander: & User stop provide its resource\\
-								& Complex user $\to$ Pure provider: & User shrink service area that only contains its own service \\
-								& Pure provider $\to$ Complex user: & User extend service area that starts to contain service from others' \\
-	\midrule
-	\multirow{4}*{Status} 		& Pure demander enter ecosystem: &	One pure demander starts to publish orders\\
-								& Pure demander exit ecosystem: & One pure demander be banned to publish orders\\
-								& Pure provider enter ecosystem: & Administrator introduces one provider into the ecosystem\\
-								& Pure provider exit ecosystem: & Administrator eliminates one provider form the ecosystem\\
-	\midrule
-	\multirow{2}*{Niche width} 	& Widen: & One provider extends its service area\\
-								& Narrow down:  & One provider shrinks its service area\\
-	\bottomrule
-	\end{tabularx}
-\end{table}
+% \begin{table}[htbp]
+% 	\caption{Users' changes}
+% 	\label{tab:userchange}
+% 	\centering
+% 	\scriptsize
+% 	\begin{tabularx}{\textwidth}{llX}
+% 	\toprule
+% 	\textbf{Change} & \multicolumn{2}{l}{\textbf{Appearance with concise description}}\\
+% 	\midrule
+% 	\multirow{3}*{Type}			& Complex user $\to$ Pure demander: & User stop provide its resource\\
+% 								& Complex user $\to$ Pure provider: & User shrink service area that only contains its own service \\
+% 								& Pure provider $\to$ Complex user: & User extend service area that starts to contain service from others' \\
+% 	\midrule
+% 	\multirow{4}*{Status} 		& Pure demander enter ecosystem: &	One pure demander starts to publish orders\\
+% 								& Pure demander exit ecosystem: & One pure demander be banned to publish orders\\
+% 								& Pure provider enter ecosystem: & Administrator introduces one provider into the ecosystem\\
+% 								& Pure provider exit ecosystem: & Administrator eliminates one provider form the ecosystem\\
+% 	\midrule
+% 	\multirow{2}*{Niche width} 	& Widen: & One provider extends its service area\\
+% 								& Narrow down:  & One provider shrinks its service area\\
+% 	\bottomrule
+% 	\end{tabularx}
+% \end{table}
 
@@
  	\centering
+ 	\scriptsize
  	\begin{tabularx}{\textwidth}{llX}

### 2016-08-25 figures/scheduleChart.tex
add nomecalture
rearrange the paper structure

@@
 
-\fill[blue!20!,yshift=18cm] (5cm,4cm) rectangle (7cm,5cm);
-\draw[yshift=18cm] (2cm,0) rectangle (5cm,3cm) (5cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (3.5cm,1.6cm) node{$t_3$} (6.5cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$};
-\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm);
-\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$};
+\fill[blue!20!,yshift=18cm] (6cm,4cm) rectangle (7cm,5cm);
+\draw[yshift=18cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
+\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
+\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
 \draw[dotted,yshift=12cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
-\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$};
+\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
 \draw[dotted,yshift=6cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
-\draw (0,3.5cm) rectangle (1cm,5cm) (2cm,0) rectangle (5cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (3.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$};
+\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
 \draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);

### 2016-08-25 design.tex
rearrange the paper structure
start to design 6 experiments

@@
 \label{ssub:master_plam}
-With the cloud manufacturing platform operating, demander comes, signs up and publish orders.
-Match module in platform informs the task messages in the order to every matched resources and services.
+With the cloud manufacturing platform operating, demander comes, signs up and publish orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations.
+Match module in platform informs the task messages to every matched resources and services.
 After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
@@
     $t_3$ & 6     & 0     & 5     & 2     & 3 \\
+    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
+    $t_5$ & 1 & 0 & 3 & 2 & 3\\
     $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
@@
 
-\begin{table}[!h]
+resources are renewable
+
+\begin{table}[htbp]
 \begin{tabularx}{\textwidth}{|lX|}
@@
 \suspend{asparaenum}
-\begin{numcases}{}
+\begin{subnumcases}{}
 A_{k,\tau} \ge q_{\alpha,ij} &\\
 P(mr_k) = \alpha & 
-\end{numcases}
+\end{subnumcases}
 If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$.
@@
 \suspend{asparaenum}
-\begin{numcases}{}
+\begin{subnumcases}{}
 C_{k,\tau} > 0 & \\
 P(mr_k) = \alpha
-\end{numcases}
+\end{subnumcases}
 If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$.
 If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
-\begin{numcases}{}
+\begin{subnumcases}{}
 C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
 C_{k,\tau} := 0 & otherwise
-\end{numcases}
+\end{subnumcases}
 
@@
 Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
-\begin{numcases}{}
+\begin{subnumcases}{}
 \sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
 R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
-\end{numcases}
+\end{subnumcases}
 \resume{asparaenum}
@@
 Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
-\begin{numcases}{}
+\begin{subnumcases}{}
 q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
 \mathcal{A}_{ij} = \mathcal{B}_l
-\end{numcases}
+\end{subnumcases}
 
 This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
-\begin{numcases}{}
+\begin{subnumcases}{}
 q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
 \mathcal{A}_{ij} = \mathcal{A}_l
-\end{numcases}
+\end{subnumcases}
 % subsection interactions_and_decisions (end)
@@
 Then, the provider will add $t_{ij}$ to queue or process buffer according to:
-\begin{numcases}{}
+\begin{subnumcases}{}
 \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \\
 \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
-\end{numcases}
+\end{subnumcases}
 
@@
 Then, the provider will add $sc_l$ to queue or process buffer according to:
-\begin{numcases}{}
+\begin{subnumcases}{}
 \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_l\} & if $\abs{\mathcal{L}_{k,\tau}\cup\mathcal{G}_{k,\tau}}=0$ \\
 \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
-\end{numcases}
+\end{subnumcases}
 
@@
 f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \\
-\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \\
+\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
 f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
@@
 
-Like the RCPSP
+Like the RCPSP.
+Since \autoref{eq:caplimitwithtime} is a time dependent function the schedule model cannot be
+solved with mixed integer programming (MIP) techniques. In order to solve
+the RCPSP with MIP{solvers such as CPLEX (cf. Bixby 1996), one has to
+employ the 0{1 problem formulation of Pritsker et al. (1969).}}
 
@@
 With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
-\begin{numcases}{}
+\begin{subnumcases}{}
 rank := rank +
@@
 \delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
-\end{numcases}
+\end{subnumcases}
 
@@
 Scarcity can be defined as:
-\begin{numcases}{}
-\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} }& $\alpha\in\mathcal{A}$\\
-\abs{\mathcal{L}_{l,\tau}}
-\end{numcases}
+\begin{subnumcases}{}
+\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} } & $\alpha\in\mathcal{A}$ \label{eq:resourcescarcity}\\ 
+\abs{\mathcal{L}_{l,\tau}} \label{eq:servicescarcity}
+\end{subnumcases}
+
+The scarcity of one service can be calculated with \autoref{eq:servicescarcity} while the scarcity of one type of resource can be calculated with \autoref{eq:resourcescarcity}.
 % subsection controlling_rules (end)

### 2016-08-25 result.tex
阶段性定框架
添加新条目
re arrange
rearrange the paper structure
start to design 6 experiments

@@
 % !TEX root = Eco-Model.tex
-\section{Numerical Results} % (fold)
-\label{sec:numerical_results}
+\section{Experiment and result Analysis} % (fold)
+\label{sec:Experiment_results}
 
-\subsection{effect of 1} % (fold)
-\label{sub:effect_of_1}
+Entities in the manufacturing ecosystem we designed above have these traits, they are: \begin{inparaenum}
+\item autonomous and self-directed, 
+\item social, interacting with other entities, 
+\item controlled by the environment, 
+\item self-contained.
+\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study of the complex system.
+With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments on it.
+\subsection{Agent-based modeling and simulation design} % (fold)
+\label{sub:agent_based_modeling_and_simulation}
+\subsubsection{Model realization}
+% \begin{asparaenum}
+% \item Platform
+% \suspend{asparaenum}
+\begin{figure}[htbp]
+	\centering
+	\tiny
+	\begin{tikzpicture}
+	\input{figures/cCloudPlatform}
+	\end{tikzpicture}
+	\caption{Cloud Platform}
+	\label{fig:platform}
+\end{figure}
+% \resume{asparaenum}
+% \item User related
+% \suspend{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \tiny
+    \begin{tikzpicture}
+    \input{figures/cUser}
+    \input{figures/cProvider}
+\input{figures/cDemander}
+    \end{tikzpicture}
+    \caption{User related classes}
+    \label{fig:userclassed}
+\end{figure}
+% \resume{asparaenum}
+% \item Job related
+% \suspend{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \tiny
+    \begin{tikzpicture}
+    \input{figures/cJob}
+    \input{figures/cTask}
+    \input{figures/cServiceCall}
+    \end{tikzpicture}
+    \caption{Job related classes}
+    \label{fig:jobclassed}
+\end{figure}
+% \resume{asparaenum}
+% \item Machine related
+% \end{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \tiny
+    \begin{tikzpicture}
+    \input{figures/cMachine}
+    \input{figures/cResource}
+    \input{figures/cService}
+    \end{tikzpicture}
+    \caption{Machine related classes}
+    \label{fig:machineclassed}
+\end{figure}
 
-% subsection effect_of_1 (end)
+\subsubsection{Behavior interfaces and classes}
+% \begin{asparaenum}
+% \item Assign behavior
+% \suspend{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \tiny
+    \begin{tikzpicture}
+    \input{figures/iAssignBehavior}
+    \input{figures/iSelectBehavior}
+    \input{figures/iResponseBehavior}
+    \input{figures/iProcessBehavior}
+    \input{figures/iReleaseBehavior}
+    % \input{figures/cServiceAssign}
+    % \input{figures/cResourceAssign}
+    \end{tikzpicture}
+    \caption{Assign interface and related classes}
+    \label{fig:assigninterface}
+\end{figure}
 
-\subsection{effect of 2} % (fold)
-\label{sub:effect_of_2}
+% \resume{asparaenum}
+% \item Process behavior
+% \suspend{asparaenum}
 
-% subsection effect_of_2 (end)
+% \begin{figure}[htbp]
+%     \centering
+%     \scriptsize
+%     \begin{tikzpicture}
+%     \input{figures/iProcessBehavior}
+%     \input{figures/cProcessInTask}
+%     \input{figures/cProcessInServiceCall}
+%     \end{tikzpicture}
+%     \caption{Process interface and related classes}
+%     \label{fig:processinterface}
+% \end{figure}
+% \resume{asparaenum}
+% \item Release behavior
+% \suspend{asparaenum}
 
-% xxx
+% \begin{figure}[htbp]
+%     \centering
+%     \scriptsize
+%     \begin{tikzpicture}
+%     \input{figures/iReleaseBehavior}
+%     \input{figures/cResourceRelease}
+%     \input{figures/cServiceRelease}
+%     \end{tikzpicture}
+%     \caption{Release interface and related classes}
+%     \label{fig:releaseinterface}
+% \end{figure}
+% \resume{asparaenum}
+% \item Response behavior
+% \suspend{asparaenum}
 
-% section numerical_results (end)
+% \begin{figure}[htbp]
+%     \centering
+%     \scriptsize
+%     \begin{tikzpicture}
+%     \input{figures/iResponseBehavior}
+%     \input{figures/cResourceResponse}
+%     \input{figures/cServiceResponse}
+%     \end{tikzpicture}
+%     \caption{Response interface and related classes}
+%     \label{fig:reponseinterface}
+% \end{figure}
+% \resume{asparaenum}
+% \item Select behavior
+% \end{asparaenum}
+
+% \begin{figure}[htbp]
+%     \centering
+%     \scriptsize
+%     \begin{tikzpicture}
+%     \input{figures/iSelectBehavior}
+%     \input{figures/cSelectInTask}
+%     \input{figures/cSelectInServiceCall}
+%     \end{tikzpicture}
+%     \caption{Select interface and related classes}
+%     \label{fig:selectinterface}
+% \end{figure}
+
+\subsection{Experiments} % (fold)
+\label{ssub:case_design}
+We use the RanGen\cite{Demeulemeester2003,Vanhoucke2008} to generate the order data in the well-known Patterson format with the parameters setting listed in tab..., the control parameters are ....
+we design these experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}
+
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+  \caption{Experiments grouping}
+    \begin{tabular}{llcc}
+    \toprule
+          &       & With metabolism & Without metabolism \\
+    \midrule
+    \multicolumn{1}{l}{\multirow{2}[0]{*}{Service-incubate}} & with outsource & Exp. 11 &Exp. 12 \\\cline{2-4}
+    \multicolumn{1}{l}{} & without outsource & Exp. 21 & Exp. 22 \\\hline
+    \multicolumn{2}{l}{Resource-only} & Exp. 31 & Exp. 32 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:grouping}%
+\end{table}%
+
+% subsubsection case_design (end)
+
+\subsubsection{Parameters setting} % (fold)
+\label{ssub:parameters_setting}
+All the following experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
+% subsubsection parameters_setting (end)
+
+\subsubsection{Result and analysis} % (fold)
+\label{ssub:result_and_analysis}
+
+% subsubsection result_and_analysis (end)

### 2016-08-26 design.tex
re structure

@@
 
-Specifically, a simple instance with configuration \autoref{tab:simpleresourceconfiguration}--\ref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
-\begin{table}[htbp]
-  \centering
-  \scriptsize
-  \caption{Simple resource configuration}
-    \begin{tabular}{ccc}
-    \toprule
-    Resource & Type  & Capacity \\
-    \midrule
-    $r_1$ & 1     & 10 \\
-    $r_2$ & 2     & 10 \\
-    $r_3$ & 3     & 10 \\
-    $r_4$ & 3     & 10 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:simpleresourceconfiguration}%
-\end{table}%
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
+% \begin{table}[htbp]
+%   \centering
+%   \scriptsize
+%   \caption{Simple resource configuration}
+%     \begin{tabular}{ccc}
+%     \toprule
+%     Resource & Type  & Capacity \\
+%     \midrule
+%     $r_1$ & 1     & 10 \\
+%     $r_2$ & 2     & 10 \\
+%     $r_3$ & 3     & 10 \\
+%     $r_4$ & 3     & 10 \\
+%     \bottomrule
+%     \end{tabular}%
+%   \label{tab:simpleresourceconfiguration}%
+% \end{table}%
 \begin{table}[htbp]
@@
 \begin{table}[htbp]
+  \scriptsize
 \begin{tabularx}{\textwidth}{|lX|}
@@
 	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
-	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
+	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
 	$ms_l$ & Service that generated after the finish of $sc_l$\\
@@
 
-\begin{gather}
+\begin{equation}
 \max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
 Rank_m, \mathcal{L}_m \right) \\ 
-\text{s.t.}\notag
-\end{gather}
-\begin{numcases}{}
-q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
-R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
-\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
-\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
-k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
+% \text{s.t.}\notag
+\end{equation}
+\begin{numcases}{\text{s.t.}}
+% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
+% R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
+% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
+% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
+% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
 \bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
@@
 \bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
-\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
-\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
-\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
-l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
+% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
+% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
+% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
+% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
 l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
@@
 	\centering
-	\resizebox{.8\textwidth}{!}{\input{figures/service-call}}
+	\resizebox{.75\textwidth}{!}{\input{figures/service-call}}
 	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
@@
 \frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
-\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} &\\
+\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} & \\
 \delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
@@
 Scarcity can be defined as:
+
 \begin{subnumcases}{}
 \sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} } & $\alpha\in\mathcal{A}$ \label{eq:resourcescarcity}\\ 
-\abs{\mathcal{L}_{l,\tau}} \label{eq:servicescarcity}
+\abs{\mathcal{L}_{l,\tau}} & \label{eq:servicescarcity}
 \end{subnumcases}
@@
 	\centering
-	\resizebox{.85\textwidth}{!}{\input{figures/job-lock}}
+	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
 	\caption{Simple illustration of job lock problem}

### 2016-08-26 figures/scheduleChart.tex
re structure

@@
 \begin{tikzpicture}
-\foreach \x in {0,6,12,18}
+\foreach \x in {0,6.5,13,19.5}
 	\draw [->,thick] (15.7cm,\x cm) node{t} (0,\x cm) -- +(15.5cm, 0) ;
-\foreach \x in {0,6,12,18}
+\foreach \x in {0,6.5,13,19.5}
 	\draw [->,thick] (0,\x cm) -- +(0,5.2 cm);
-\foreach \x in {0,6,12,18}
+\foreach \x in {0,6.5,13,19.5}
 	\draw[yshift=5.35cm] (0,\x cm) node{Capacity};
-\foreach \x in {1,2,3,4}
-	\draw[yshift=23.5cm] (7.5cm,-6*\x cm) node{$r_\x$};
 \foreach \x in {1,...,15}
-	\foreach \y in {0,6,12,18}
+	\foreach \y in {0,6.5,13,19.5}
 		\draw (\x cm,\y cm) -- +(0,2mm);
 \foreach \x in {1,...,15}
-	\foreach \y in {0,6,12,18}
+	\foreach \y in {0,6.5,13,19.5}
 		\draw[yshift=-2mm] (\x cm,\y cm) node{$\x$};
-\foreach \y in {0,6,12,18}
+\foreach \y in {0,6.5,13,19.5}
 	\foreach \x in {1,...,10}
@@
 
-\fill[blue!20!,yshift=18cm] (6cm,4cm) rectangle (7cm,5cm);
-\draw[yshift=18cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
-\draw[dotted,yshift=18cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
-\draw[yshift=12cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
-\draw[dotted,yshift=12cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
-\draw[yshift=6cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
-\draw[dotted,yshift=6cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
+\draw (7.5cm,-7mm) node{$r_4$, initial capacity = 10, type = 3};
+\draw[yshift=6.5cm] (7.5cm,-7mm) node{$r_3$, initial capacity = 10, type = 3};
+\draw[yshift=13cm] (7.5cm,-7mm) node{$r_2$, initial capacity = 10, type = 2};
+\draw[yshift=19.5cm] (7.5cm,-7mm) node{$r_1$, initial capacity = 10, type = 1};
+
+\fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
+\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
+\draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
+\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
+\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
+\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
+\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
 \draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};

### 2016-08-26 result.tex
re structure

@@
 \subsubsection{Model realization}
-% \begin{asparaenum}
-% \item Platform
-% \suspend{asparaenum}
+\begin{asparaenum}
+\item Main agents
+\suspend{asparaenum}
 \begin{figure}[htbp]
@@
 \tiny
-	\begin{tikzpicture}
-	\input{figures/cCloudPlatform}
-	\end{tikzpicture}
-	\caption{Cloud Platform}
-	\label{fig:platform}
-\end{figure}
-% \resume{asparaenum}
-% \item User related
-% \suspend{asparaenum}
-\begin{figure}[htbp]
-    \centering
-    \tiny
-    \begin{tikzpicture}
-    \input{figures/cUser}
-    \input{figures/cProvider}
-\input{figures/cDemander}
-    \end{tikzpicture}
-    \caption{User related classes}
-    \label{fig:userclassed}
-\end{figure}
-% \resume{asparaenum}
-% \item Job related
-% \suspend{asparaenum}
-\begin{figure}[htbp]
-    \centering
-    \tiny
-    \begin{tikzpicture}
+\subfloat[Job related classes]{\begin{tikzpicture}
     \input{figures/cJob}
@@
     \end{tikzpicture}
-    \caption{Job related classes}
-    \label{fig:jobclassed}
-\end{figure}
-% \resume{asparaenum}
-% \item Machine related
-% \end{asparaenum}
-\begin{figure}[htbp]
-    \centering
-    \tiny
-    \begin{tikzpicture}
+    \label{fig:jobclassed}}\hspace{1pt}
+\subfloat[Machine related classes]{\begin{tikzpicture}
     \input{figures/cMachine}
@@
     \end{tikzpicture}
-    \caption{Machine related classes}
-    \label{fig:machineclassed}
+    \label{fig:machineclassed}}\\
+\subfloat[User related classes]{\begin{tikzpicture}
+    \input{figures/cUser}
+    \input{figures/cProvider}
+\input{figures/cDemander}
+    \end{tikzpicture}\label{fig:userclassed}}\hspace{3pt}
+\subfloat[Cloud Platform]{\begin{tikzpicture}
+	\input{figures/cCloudPlatform}
+	\end{tikzpicture}\label{fig:platform}}
 \end{figure}
 
-\subsubsection{Behavior interfaces and classes}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\tiny
+% 	\begin{tikzpicture}
+% 	\input{figures/cCloudPlatform}
+% 	\end{tikzpicture}
+% 	\caption{Cloud Platform}
+% 	\label{fig:platform}
+% \end{figure}
+% % \resume{asparaenum}
+% % \item User related
+% % \suspend{asparaenum}
+% \begin{figure}[htbp]
+%     \centering
+%     \tiny
+%     \begin{tikzpicture}
+%     \input{figures/cUser}
+%     \input{figures/cProvider}
+% \input{figures/cDemander}
+%     \end{tikzpicture}
+%     \caption{User related classes}
+%     \label{fig:userclassed}
+% \end{figure}
+% \resume{asparaenum}
+% \item Job related
+% \suspend{asparaenum}
+% \begin{figure}[htbp]
+%     \centering
+%     \tiny
+%     \begin{tikzpicture}
+%     \input{figures/cJob}
+%     \input{figures/cTask}
+%     \input{figures/cServiceCall}
+%     \end{tikzpicture}
+%     \caption{Job related classes}
+%     \label{fig:jobclassed}
+% \end{figure}
+% \resume{asparaenum}
+% \item Machine related
+% \end{asparaenum}
+% \begin{figure}[htbp]
+%     \centering
+%     \tiny
+%     \begin{tikzpicture}
+%     \input{figures/cMachine}
+%     \input{figures/cResource}
+%     \input{figures/cService}
+%     \end{tikzpicture}
+%     \caption{Machine related classes}
+%     \label{fig:machineclassed}
+% \end{figure}
+\resume{asparaenum}
+\item Behavior interfaces and classes
+\end{asparaenum}
 % \begin{asparaenum}
@@
 \label{ssub:case_design}
-We use the RanGen\cite{Demeulemeester2003,Vanhoucke2008} to generate the order data in the well-known Patterson format with the parameters setting listed in tab..., the control parameters are ....
-we design these experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}
+We use the RanGen\cite{Demeulemeester2003} to generate the order data in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}, and the control parameters in the model are
+
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+	\caption{General parameters setting}
+    \begin{tabular}{ccccccc}
+    \toprule
+    Number of activities & OS & CI & Number of resources & RF & RC \\
+    \midrule
+     100  &   0.3    &  [57,61]     &   30     &  0.13     &   0.6     \\
+    \bottomrule
+    \end{tabular}%
+    {\footnotetext{\tiny The meaning of the parameters are defined in \cite{Demeulemeester2003}}}
+  \label{tab:generalparameter}%
+\end{table}%
+
+% subsubsection case_design (end)
+
+\subsubsection{Parameters setting} % (fold)
+\label{ssub:parameters_setting}
+We design experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}
+All the following experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
 
@@
 \end{table}%
-
-% subsubsection case_design (end)
-
-\subsubsection{Parameters setting} % (fold)
-\label{ssub:parameters_setting}
-All the following experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
 % subsubsection parameters_setting (end)

### 2016-08-26 review.tex
re structure

@@
 % !TEX root = Eco-Model.tex
-\section{Literature review and the knowledge gap} % (fold)
+\section{Literature review and background} % (fold)
 \label{sec:literature_review}
@@
 XXX has been studied extensively in the literature....
-\subsection{Cloud manufacturing} % (fold)
+\subsection{Cloud manufacturing and its operation mode} % (fold)
 \label{sub:cloud_manufacturing review}
@@
 
-\subsection{Manufacturing ecosystem} % (fold)
-\label{sub:manufacturing_ecosystem}
 % xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.
@@
 As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network.
-\subsubsection{Different ecosystem analogies}
 
-\subsubsection{Manufacturing system}
 % Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.
@@
 % subsection manufacturing_ecosystem (end)
+\subsection{Study background} % (fold)
+\label{sub:background}
 
-\subsection{Operation model in cloud manufacturing}
-\label{sub:Operation model in cloud manufacturing}
+\subsubsection{List of basic terminology} % (fold)
+\label{sub:list_of_basic_terminology}
+here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
+\begin{itemize}
+	\item order
+	\item task correspond to capacity
+	\item resource
+	\item capacity is the function of a resource. like quantity
+	\item service is the bundle of capacities. the proportion of the capacities.
+	\item 
+\end{itemize}
 
-\subsection{Study of evolution on related fields} % (fold) 这段标题后期需要修改，要描述的是和演化相关的内容。
-\label{sub:complex_system}
-\subsubsection{System Dynamic}
+Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment as shown in \autoref{fig:structure}.
+% \begin{figure}[htbp]
+% \centering
+% \includegraphics[scale = .3, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
+% \caption{Cloud manufacturing architecture with main flows}
+% \label{fig:structure}
+% \end{figure}
 
-\subsubsection{Agent-based Modeling}
-% subsection complex_system (end)
+The architecture of cloud manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
+\item user,
+\item platform and
+\item physical base
+\end{inparaenum}, that are connected by material or information flows. A simple version of conception for cloud manufacturing architecture we study here can be described as follows:
+\begin{compactdesc}
+\item [User] part describes the generalized role who takes part in the trading activities in the cloud manufacturing system, basic role of user are manufacturing service provider and manufacturing service demander, whom can be called as \textit{provider} and \textit{demander} for short respectively, from the functional point of view.
+Meanwhile, these part can also be classified into enterprise user and customer, from the practical point of view.
+In addition, it's possible for user to act as both demander and provider simultaneously if administrator give the authority to the user, so we can categorize the user in 3 basic types as described in \autoref{fig:usertype} and \autoref{tab:usertype}.
+Both functional and practical are important perspective for later analysis in following sections.
+\item [Platform] is operating with the control of administrator and this part consists of 3 main layers namely
+	\begin{inparaenum}[1)]
+	\item application/interface layer,
+	\item service layer and
+	\item resource \& production layer
+	\end{inparaenum}.
+Service is the core concept in cloud manufacturing, so service layer is the core in the cloud manufacturing platform.
+With the help of related technology in servitization, manufacturing resource and production can be encapsulated into services, then these services can be acquired by users with the well designed applications or interfaces.
+\item [Physical Base] part includes the basic infrastructure, resource and production.
+It's worth mentioning that part of resources and production can even be virtualized with some services the platform provides.
+\end{compactdesc}
+
+As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.
+
+Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale = .3, trim = 0 15 0 10]{supplementary.pdf}
+\caption{Supplementary illustration for \autoref{fig:structure}}
+\label{fig:supplementary}
+\end{figure}
+
+With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in cloud manufacturing environment with the fore-mentioned flows that marked by circled number (i.e.
+\textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the cloud manufacturing system.
+In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively.
+The overlap among application districts implies the complexity of the system, so that we will analyze these applications coordinately from a systematic view.
+
+\subsubsection{Operation model of platform}
+\label{ssub:operation_model_of_platform}
+Platform carries most of the activities illustrated in \autoref{fig:supplementary}, so it's important to design an operation model for administrator to manage these activities.
+This model enables modules that appeared in xxx such as \textit{service packager}, \textit{task decomposer} , \textit{service search engine}, etc., but we only study the modules in for they're the core in the evolutionary process in this paper.
+
+\begin{table}[tb]
+	\caption{Core modules in operation model of platform}
+	\label{tab:core_module_in_platform}
+	\centering
+	\scriptsize
+	\begin{tabularx}{\textwidth}{llX}
+	\toprule
+
+	\textbf{Module} & \multicolumn{2}{l}{\textbf{Function with concise description}}  \\
+	\midrule
+	\multirow{2}*{Population controller}		& Adder: 		& To introduce resource provider into the system\\
+												& Subtracter: 	& To eliminate resource provider from the system\\
+	\hline
+	\multirow{2}*{Authority tuner}				& Raiser:	& Raise the authority value of the provider \\
+												& Reducer: & Reduce the authority value of the provider\\
+	\hline
+	\multirow{3}*{Recommender}					& Matcher: & Match task with a bunch of alternative services \\
+												& Adjuster: & Change provider's rank based on history\\
+												& Promoter: & To promote fresh resource provider \\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+platform model is about the part of decision making	agent of platform.
+
+\subsubsection{Operation model of users}
+\label{subs:Operation model of users}
+The \textit{demander} mentioned in \autoref{subs:cloud manufacturing architecture} publishes its demand as order that can be decomposed into tasks by \textit{task decomposer} module in platform, while the \textit{provider} mentioned in \autoref{subs:cloud manufacturing architecture} publishes its resource as capacity that can be packaged into services by \textit{service packager} module in Platform.
+In order to do more accurate study on users, we classified users into 3 basic types as shown in \autoref{fig:usertype}.
+With concise explanation in \autoref{tab:usertype}, we can illustrate the operation model in \autoref{fig:useroperation}.
+
+The main operational process of pure demander(\autoref{fig:demanderprocess}) starts with its decomposed task.
+Then, with the help of \textit{recommender} module, pure demander search and select appropriate service, trade with the one or multi service provider according to the \textit{task decomposer}, receive the product delivered by the provider at due date and commit the review of the product.
+The committed review will affect the authority value of the provider, that good review raise the value and vise versa.
+
+The main operational process of pure provider(\autoref{fig:providerprocess}) starts with a task call, then pure provider process the task with its resource.
+After the accomplishment of the task, pure provider deliver products to demander from the call.
+It will also commit the review of the demander and make a modification of its service area.
+By the way, this modification of provider's service area play key role in the evolution of user we will discuss in \autoref{ssub:microscopic_evolution}.
+
+The main operational process of complex user(\autoref{fig:complexprocess}) combines the two above process with additional decision step.
+This decision split the task into two parts, that one of them will be processed by itself as a provider user and the other one will be processed by other provider as if the complex user act as a demander.
+This operational process relies heavily on the service area of the complex user, so the modification of service area is the key to the study.
+
+user's model is the part of decision making agent of users.
+
+\subsection{The evolution of manufacturing ecosystem} % (fold)
+\label{sub:the_evolution_of_manufacturing_ecosystem}
+Before the realization of the operation model mentioned above(\autoref{subs:Operation model of users}), we will analyze the evolution path in both micro and macro view of manufacturing ecosystem w.r.t.
+the domain in cloud manufacturing.
+The overall evolution process is illustrated in \autoref{fig:overallevolution},
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{evolutionview}
+	\caption{Overall evolution process}
+	\label{fig:overallevolution}
+\end{figure}
+the microscopic evolution corresponds to the change of user status while the macroscopic evolution corresponds to the change of the system status.
+
+\subsubsection{Microscopic evolution} % (fold)
+\label{ssub:microscopic_evolution}
+
+by both type of agents, more on user agent, the platform agent will change a individual by affect the individual's decision, not directly means.
+
+User is the basic activity individual in the manufacturing ecosystem, and their \begin{inparaenum}[1)]
+\item type,
+\item status and 
+\item niche width
+\end{inparaenum} will be changed by the decision they've made. 
+All these changes contribute to microscopic evolution of the ecosystem.
+More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper.
+\autoref{tab:userchange} concludes the appearances that we will study in this paper.
+
+\subsubsection{Macroscopic evolution} % (fold)
+\label{ssub:macroscopic_evolution}
+Comes form both of the agents. more on platform agent.
+indirect: the group effect.
+
+Individual evolution will lead to the evolution of the whole ecosystem and the overall effect is greater than the sum of these individuals.
+
+the amount, diversity, operation pattern recognition and service cycle rate are the topics of macroscopic evolution.
+
+\begin{table}[htbp]
+ 	\caption{Macroscopic evolution}
+ 	\label{tab:macroevolution}
+ 	\centering
+ 	\scriptsize
+ 	\begin{tabularx}{\textwidth}{llX}
+ 	\toprule
+ 	\textbf{column 1} & \multicolumn{2}{l}{\textbf{Appearance with concise description}} \\
+ 	\midrule
+ 	Amount & & \\
+ 	Diversity & & \\
+ 	Service cycle rate & & \\
+ 	\bottomrule
+ 	\end{tabularx}
+ \end{table}
+
+% subsubsection macroscopic_evolution (end)
+
+\subsection{Main topics and their academic importance}
+% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。 目前云制造缺乏相关运作式的讨论，而商业模式中的不同行为会影响、改变、涌现。
+As shown in \autoref{fig:structure},
+
+the core is about the decision making all the time, individuals' decision making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution
+
+Rating system, decision support system, recommender system,
+detail info will seen in
+Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions.
+For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on
+
+so, the topic here is the design of both decision making agents.
+
 % section literature_review (end)

### 2016-08-28 result.tex
start to write the experiment part

@@
 \label{ssub:case_design}
-We use the RanGen\cite{Demeulemeester2003} to generate the order data in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}, and the control parameters in the model are
+We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}, and the control parameters in the model are
 
@@
     \midrule
-     100  &   0.3    &  [57,61]     &   30     &  0.13     &   0.6     \\
+     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5     \\
     \bottomrule
@@
 \label{ssub:parameters_setting}
-We design experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}
+We design experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}, 100 datasets represent 100 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
 All the following experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.

### 2016-08-28 Data/plot.py
add data

@@ -1,0 +1,67 @@
+# -*- coding: utf-8 -*-
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import pylab as pl
+from scipy import interpolate 
+
+data = np.loadtxt('test',dtype='string',delimiter=',')
+x = []
+y = []
+t = []
+for i in xrange((len(data)-1)/50):
+	line = data[(i+1)*50]
+	x.append(float(line[0]))
+	y.append(float(line[2]))
+	t.append(float(line[1]))
+
+
+
+plt.figure(figsize=(15,15))
+tck = interpolate.splrep(t,x)
+# tck_2 = interpolate.splrep(t)
+x_bspline = interpolate.splev(t,tck)
+# markers_on = [12, 17, 18, 19]
+# plt.plot(xs, ys, '-gD', markevery=markers_on)
+
+plt.subplot(421)
+plt.plot()
+plt.title(r'Number of resources($N_R$)')
+
+plt.subplot(422)
+plt.plot()
+plt.title(r'Number of providers($N_P$)')
+
+plt.subplot(423)
+plt.plot()
+plt.title(r'Number of tasks($N_T$)')
+
+plt.subplot(424)
+plt.plot()
+plt.title(r'Accumulation of finished tasks($N_F$)')
+
+plt.subplot(425)
+plt.plot(t,x_bspline,marker='o',markevery=8)
+plt.title(r'Maximum queue length($L$)')
+
+plt.subplot(426)
+plt.plot()
+plt.title(r'Maximum rank value($R$)')
+
+plt.subplot(427)
+plt.plot(t,x_bspline,marker='o',markevery=8)
+plt.title(r'Product quality($Q$)')
+
+plt.subplot(428)
+plt.axis('off')
+plt.plot(1,1,'-',marker='o')
+plt.plot(1,1,':',marker='o')
+plt.plot(1,1,'-',marker='s')
+plt.plot(1,1,':',marker='s')
+plt.plot(1,1,'-',marker='v')
+plt.plot(1,1,':',marker='v')
+plt.legend(['Mode 11','Mode 12','Mode 21','Mode 22','Mode 31','Mode 32'],loc='center')
+
+plt.savefig('out.pdf', transparent=True, bbox_inches='tight', pad_inches=0)
+
+

### 2016-08-28 result.tex
main content finished

@@
   \scriptsize
-	\caption{General parameters setting}
+	\caption{Order generating parameters setting}
     \begin{tabular}{ccccccc}
     \toprule
-    Number of activities & OS & CI & Number of resources & RF & RC \\
+    \textbf{Number of activities} & \textbf{OS} & \textbf{CI} & \textbf{Number of resources} & \textbf{RF} & \textbf{RC} \\
     \midrule
@@
 \label{ssub:parameters_setting}
-We design experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}, 100 datasets represent 100 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
-All the following experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
+We design experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
 
@@
   \scriptsize
-  \caption{Experiments grouping}
+  \caption{Experiments mode grouping}
     \begin{tabular}{llcc}
     \toprule
-          &       & With metabolism & Without metabolism \\
+          &       & Without metabolism & With metabolism \\
     \midrule
-    \multicolumn{1}{l}{\multirow{2}[0]{*}{Service-incubate}} & with outsource & Exp. 11 &Exp. 12 \\\cline{2-4}
-    \multicolumn{1}{l}{} & without outsource & Exp. 21 & Exp. 22 \\\hline
-    \multicolumn{2}{l}{Resource-only} & Exp. 31 & Exp. 32 \\
+    \multicolumn{2}{l}{Resource-only} & Mode 11 & Mode 12 \\\hline
+    \multicolumn{1}{l}{\multirow{2}[0]{*}{Service-incubate}} & without outsource & Mode 21 &Mode 22 \\\cline{2-4}
+    \multicolumn{1}{l}{} & with outsource & Mode 31 & Mode 32 \\
     \bottomrule
@@
 \label{ssub:result_and_analysis}
+All the experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
+Even though different random seed makes different initialization of the simulation and different initialization will affect the simulation a lot, the universal law of the model cannot be changed if it exists.
+After bunch of experiments with different random seeds, we discovered some laws in operation mode.
+Take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{Data/out.pdf}
+    \caption{Observed variable change with time}
+    \label{fig:out}
+\end{figure}
+\begin{table}[htbp]
+    \caption{Average observed values}
+    \label{tab:averagevalue}
+    \centering
+    \scriptsize
+    \begin{tabular}{lccccc}
+    \toprule
+    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
+    \midrule
+    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
+    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
+    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
+    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
+    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
+    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\
+
+    \bottomrule
+    \end{tabular}
+\end{table}
+we find: \begin{inparaenum}[1)]
+\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22, this combined mode even also need lower number of queue length.
+Full lines are not much above dotted lines in $N_F$ means that task processing velocity will be a little slower with the metabolism, exception also appears in Mode 22.
+\item $L$ and $N_T$ both represent the waiting of job, triangle and square line turned lower in $L$ meas that service-incubate mode can help reduce the waiting of job, these two type of line appeared above the circle line means the service-incubate mode do accelerate the processing velocity.
+\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsource mode needs more resources to operate and can only reduce the waiting of job a little.
+\item There is no big difference among all the 6 modes.
+Provider in metabolism mode will get lower rank value for they cannot stay in the system forever, the longer stay in the system, the higher rank value provider will get.
+Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without service-incubate mode.
+\item Mode 22 is a very special mode that reached the balance of the system, although all the mentioned modes will reach balance in the long run, with the average data value shown in \autoref{tab:averagevalue}, metabolism with service-incubate but not with outsource mode is the easiest combine mode to maintain the system, resource are self configured and controlled to just meet the task need.
+\end{inparaenum}
 

### 2016-08-28 review.tex
main content finished

@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale = .3, trim = 0 15 0 10]{supplementary.pdf}
-\caption{Supplementary illustration for \autoref{fig:structure}}
-\label{fig:supplementary}
-\end{figure}
+% \begin{figure}[htbp]
+% \centering
+% \includegraphics[scale = .3, trim = 0 15 0 10]{supplementary.pdf}
+% \caption{Supplementary illustration for \autoref{fig:structure}}
+% \label{fig:supplementary}
+% \end{figure}
 
@@
 The overall evolution process is illustrated in \autoref{fig:overallevolution},
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=.5\textwidth]{evolutionview}
-	\caption{Overall evolution process}
-	\label{fig:overallevolution}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=.5\textwidth]{evolutionview}
+% 	\caption{Overall evolution process}
+% 	\label{fig:overallevolution}
+% \end{figure}
 the microscopic evolution corresponds to the change of user status while the macroscopic evolution corresponds to the change of the system status.

### 2016-08-28 Data/plot.py

@@ -5,63 +5,124 @@ import pandas as pd
 import pylab as pl
 from scipy import interpolate 
 
-data = np.loadtxt('test',dtype='string',delimiter=',')
-x = []
-y = []
-t = []
-for i in xrange((len(data)-1)/50):
-	line = data[(i+1)*50]
-	x.append(float(line[0]))
-	y.append(float(line[2]))
-	t.append(float(line[1]))
+seed = '776189616'
+t = [(x+1)*50 for x in xrange(120)]
+
+def value(seed,mode,file,loc):
+	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',dtype='string',delimiter=',')
+
+	v = []
+	
+	for i in xrange((len(data)-1)/50):
+		line = data[(i+1)*50]
+		v.append(float(line[loc]))
+	tck = interpolate.splrep(t,v)
+	# tck_2 = interpolate.splrep(t)
+	v_bspline = interpolate.splev(t,tck)
+	return v_bspline
+
+def Quality(seed,mode,style):
+	data = np.loadtxt(seed+ '/Quality_m'+ mode +'.csv',dtype='string',delimiter=',')
+	tick = []
+	q = []
+	
+	for i in xrange((len(data)-1)/50):
+		line = data[(i+1)*50]
+		tick.append(float(line[0]))
+		q.append(float(line[1]))
+	f2 = interpolate.interp1d(tick, q, kind='cubic')
+	plt.plot(tick,f2(tick),style,markevery=8)
+
+def myplot(x,style):
+	plt.plot(t,x,style,markevery=8)
 
 
-
+styles = ['b-o','g:o','r-s','c:s','k-^','m:^']
+modes = ['11','12','21','22','31','32']
 plt.figure(figsize=(15,15))
-tck = interpolate.splrep(t,x)
+# tck = interpolate.splrep(t,N_T)
 # tck_2 = interpolate.splrep(t)
-x_bspline = interpolate.splev(t,tck)
+# x_bspline = interpolate.splev(t,tck)
 # markers_on = [12, 17, 18, 19]
 # plt.plot(xs, ys, '-gD', markevery=markers_on)
 
 plt.subplot(421)
-plt.plot()
+for i in range(6):
+	style = styles[i]
+	N_R = value(seed,modes[i],'Machine',1)
+	myplot(N_R,style)
+
 plt.title(r'Number of resources($N_R$)')
 
[…]

### 2016-08-29 figures/scheduleChart.tex
change without design.tex

@@
 
-\draw (7.5cm,-7mm) node{$r_4$, initial capacity = 10, type = 3};
-\draw[yshift=6.5cm] (7.5cm,-7mm) node{$r_3$, initial capacity = 10, type = 3};
-\draw[yshift=13cm] (7.5cm,-7mm) node{$r_2$, initial capacity = 10, type = 2};
-\draw[yshift=19.5cm] (7.5cm,-7mm) node{$r_1$, initial capacity = 10, type = 1};
+\draw[yshift=6.5cm] (7.5cm,-11mm) node{$r_4$, initial capacity = 10, type = 3};
+\draw[yshift=13cm] (7.5cm,-11mm) node{$r_3$, initial capacity = 10, type = 3};
+\draw[yshift=19.5cm] (7.5cm,-11mm) node{$r_2$, initial capacity = 10, type = 2};
+\draw[yshift=26cm] (7.5cm,-11mm) node{$r_1$, initial capacity = 10, type = 1};
 

### 2016-08-29 review.tex
change without design.tex

--- 2016-05-23 review.tex
@@
 % !TEX root = Eco-Model.tex
-\section{Literature review and the knowledge gap} % (fold)
+\section{Literature review and background} % (fold)
 \label{sec:literature_review}
-demonstrates that you know the field, justifies the reason for your research, allows you establish your theoretical and needs to be done.
-
-XXX has been studied extensively in the literature....
-\subsection{Cloud manufacturing} % (fold)
+\subsection{Cloud manufacturing and its operation mode} % (fold)
 \label{sub:cloud_manufacturing review}
 % This definition is quite abstract and thus despite its corretness not very useful.
-from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.
+
+Review on 1. Cloud manufacturing mode (any) study 
+2. res ser combination and decision making
+3. rank and review ecosystem (system changing)
+4. manufacturing system simulation
 
@@
 
-\textbf{Services and Tasks}
-
-Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub.
-In order to complete orders precisely, order will be splited into tasks.
-Similarly, resources will be bundled into services for the quick searhing.
-
-\textbf{Roles}
+Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions.
+For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on
 
@@
 \end{inparaenum}
-However, the roles in real world always not go like this model, since it parted roles only by their functions.
-While, users could get different function roles depend on what transaction they take, we should make some modifiacations on this model.
 
-% subsection cloud_manufacturing (end)
+\subsection{Study background} % (fold)
+\label{sub:background}
 
-\subsection{Manufacturing ecosystem} % (fold)
-\label{sub:manufacturing_ecosystem}
-% xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.
+here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
+\begin{itemize}
+	\item order
+	\item task correspond to capacity
+	\item resource
+	\item capacity is the function of a resource. like quantity
+	\item service is the bundle of capacities. the proportion of the capacities.
+	\item 
+\end{itemize}
 
-% From a bionomic perspective, organisms and organizations are nodes in networks of relationships.
-As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network.
-\subsubsection{Different ecosystem analogies}
+Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment
 
-\subsubsection{Manufacturing system}
-% Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.
+As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.
 
-% coevolved to form a vast living ecosystem
+Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.
 
-% 4 different stages for ecosystem:
-% birth, expansion, leadership, final(self-renew or death)
-
-% the major difference between ecological and social system is the role of conscious choice.
-
-% Accoring to xxx there are three critical success factors of a business ecosystem.
-% First, productivity
-% Second, Robustness
-% Third, have the ability to create niches and opportunities for new firms.
-
-% Complexity relevant concepts
-
-% Self-organization
-% Emergence
-% Coevolution
-% adaptation
-
-% subsection manufacturing_ecosystem (end)
-
-\subsection{Operation model in cloud manufacturing}
-\label{sub:Operation model in cloud manufacturing}
-
-\subsection{Study of evolution on related fields} % (fold) 这段标题后期需要修改，要描述的是和演化相关的内容。
-\label{sub:complex_system}
-\subsubsection{System Dynamic}
-
-\subsubsection{Agent-based Modeling}
-% subsection complex_system (end)
 % section literature_review (end)

### 2016-08-29 Data/plot.py

@@ -121,8 +121,8 @@ def mymean(seed,mode,file,loc):
 
 	# l = [mymean(seed,mode,'Task',0),mymean(seed,mode,'FinishCount',1),mymean(seed,mode,'Provider'，1)]#,mymean(seed,mode,'Machine',1),mymean(seed,mode,'Quality',1)]
 # mymean(seed,'11','Provider',1)
-for mode in modes:
-	# print "Mode " +mode + '\n'
-	l = [mymean(seed,mode,'Task',1),mymean(seed,mode,'Finish',1),mymean(seed,mode,'Provider',1),mymean(seed,mode,'Machine',1),mymean(seed,mode,'Quality',1)]
-	print l
+# for mode in modes:
+# 	# print "Mode " +mode + '\n'
+# 	l = [mymean(seed,mode,'Task',1),mymean(seed,mode,'Finish',1),mymean(seed,mode,'Provider',1),mymean(seed,mode,'Machine',1),mymean(seed,mode,'Quality',1)]
+# 	print l
 	# print '\n'

### 2016-08-29 design.tex
main content finished
start to draw diagram

@@
 
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
+% Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
+
 % \begin{table}[htbp]
@@
 %   \scriptsize
-%   \caption{Simple resource configuration}
-%     \begin{tabular}{ccc}
+%   \caption{Simple job configuration}
+%     \begin{tabular}{cccccc}
 %     \toprule
-%     Resource & Type  & Capacity \\
+%     \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
+%     \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
 %     \midrule
-%     $r_1$ & 1     & 10 \\
-%     $r_2$ & 2     & 10 \\
-%     $r_3$ & 3     & 10 \\
-%     $r_4$ & 3     & 10 \\
+%     $t_1$ & 0     & 5     & 7     & 0     & 7 \\
+%     $t_2$ & 7     & 5     & 7     & 4     & 5 \\
+%     $t_3$ & 6     & 0     & 5     & 2     & 3 \\
+%     $t_4$ & 9	 & 4  & 6 & 1 &2 \\
+%     $t_5$ & 1 & 0 & 3 & 2 & 3\\
+%     $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
+%     $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
 %     \bottomrule
 %     \end{tabular}%
-%   \label{tab:simpleresourceconfiguration}%
+%   \label{tab:simplejobconfiguration}%
 % \end{table}%
-\begin{table}[htbp]
-  \centering
-  \scriptsize
-  \caption{Simple job configuration}
-    \begin{tabular}{cccccc}
-    \toprule
-    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
-    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
-    \midrule
-    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
-    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
-    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
-    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
-    $t_5$ & 1 & 0 & 3 & 2 & 3\\
-    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
-    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:simplejobconfiguration}%
-\end{table}%
-\begin{figure}[htbp]
-	\centering
-	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
-	\caption{Simple instance schedule chart with 4 resources}
-	\label{fig:scheduleChart}
-\end{figure}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
+% 	\caption{Simple instance schedule chart with 4 resources}
+% 	\label{fig:scheduleChart}
+% \end{figure}
 This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period.
@@
     \hline
-    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
+    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomencalture}}} \\
     \multicolumn{2}{|l|}{} \\

### 2016-08-29 figures/origin_mode.tex
start to draw diagram

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
circle/.style={
rectangle,minimum size=1em,rounded corners=0.5em,
draw=black
}
]
\matrix[row sep=-1em,column sep=2em] {
% First row:
\node (order) {Order};& \node (task) [square]{Publish Tasks}; & & & & \\
 & &\node (match) [square]{Match \& Assign};&\node (coord) [square] {Resource Cooperate}; & \node (process)[square]{Process Task}; & \node (finish) {Product};\\
\node (provider) {Provider}; & \node (resource) [square]{Provider Resources}; & & & & \\
};
\path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
% \path (task) edge[->] (job);
% \node (ui1) [nonterminal] {unsigned integer};
% \node (dot) [terminal,right=of ui1] {.};
% \node (digit) [terminal,right=of dot] {digit};
% \node (E) [terminal,right=of digit] {E};
% \node (plus) [terminal,above right=of E] {+};
% \node (minus) [terminal,below right=of E] {-};
% \node (ui2) [nonterminal,below right=of plus] {unsigned integer};
\end{tikzpicture}

### 2016-08-29 result.tex
start to draw diagram

@@
 Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without service-incubate mode.
-\item Mode 22 is a very special mode that reached the balance of the system, although all the mentioned modes will reach balance in the long run, with the average data value shown in \autoref{tab:averagevalue}, metabolism with service-incubate but not with outsource mode is the easiest combine mode to maintain the system, resource are self configured and controlled to just meet the task need.
+\item Mode 22 is a very special mode that reached the balance of the system that the number of provider and resource changed little with time goes by and it means all the ..., theoretically all the metabolism related modes will reach balance in the long run because the coming order velocity less than the resources, but the appearance of service-call and metabolism itself is full of uncertainty and it's hard to predict when other metabolism related mode will get the balance.
+, with the average data value shown in \autoref{tab:averagevalue}, metabolism with service-incubate but not with outsource mode is the easiest combine mode to maintain the system, resource are self configured and controlled to just meet the task need.
 \end{inparaenum}

### 2016-08-29 review.tex
start to draw diagram

@@
 
-Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al.
-2012;Valilai and Houshmand 2013)
-
-Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions.
-For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on
+Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (\cite{Tao2012}\cite{Valilai2013}
 

### 2016-08-30 design.tex
add mode diagrams and rebuild the structure

--- 2016-08-26 design.tex
@@
 
-\subsubsection{Master plan} % (fold)
-\label{ssub:master_plam}
-With the cloud manufacturing platform operating, demander comes, signs up and publish orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations.
-Match module in platform informs the task messages to every matched resources and services.
-After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
-Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before.
-Most of resource related decision making are well controlled by platform with the review module.
-
-A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks which have to be processed.
-The tasks are interrelated by kinds of constraints.
-First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors, how to construct the predecessor will be explained later.
-Second, performing the tasks requires resources with limited capacities.
-Third, resources cooperation transmits and enhances these constraints.
-
-A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform.
-While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
-Each resource $mr_k$ has a limited capacity of $C_k(\tau)$ at any point in time $\tau$.
-
-A single service($s_l$) is a composition of all resources in set $R_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more.
-While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
-Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.
-
-A single service-call($sc_l$) comes out after the finish of one frequent task, so it have the same resource configuration the frequent task.
-Service-call can only be performed via resource cooperation with duration $p_l$, because the identity of resource, the capacity cannot be return to the resource after the finish of service-call, so the service-call brings new constrains to the related resources.
-Unlike the task, the amount of one type resource required in the service-call can be pieced together from more than one resource as long as they are in the same type.
-
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
-% \begin{table}[htbp]
-%   \centering
-%   \scriptsize
-%   \caption{Simple resource configuration}
-%     \begin{tabular}{ccc}
-%     \toprule
-%     Resource & Type  & Capacity \\
-%     \midrule
-%     $r_1$ & 1     & 10 \\
-%     $r_2$ & 2     & 10 \\
-%     $r_3$ & 3     & 10 \\
-%     $r_4$ & 3     & 10 \\
-%     \bottomrule
-%     \end{tabular}%
-%   \label{tab:simpleresourceconfiguration}%
-% \end{table}%
-\begin{table}[htbp]
-  \centering
-  \scriptsize
-  \caption{Simple job configuration}
-    \begin{tabular}{cccccc}
-    \toprule
-    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
-    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
-    \midrule
-    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
-    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
-    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
-    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
-    $t_5$ & 1 & 0 & 3 & 2 & 3\\
-    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
-    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:simplejobconfiguration}%
-\end{table}%
 \begin{figure}[htbp]
     \centering
-	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
-	\caption{Simple instance schedule chart with 4 resources}
-	\label{fig:scheduleChart}
+    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
+    \caption{Origin mode}
+    \label{fig:originmode}
 \end{figure}
-This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period.
-Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.
 
-% subsubsection master_plan (end)
-
-\subsubsection{Assumptions, nomenclature} % (fold)
+\subsubsection{Assumptions} % (fold)
 \label{ssub:assumptions_nomenclature}
@@
 % subsubsection assumptions_nomenclature (end)
+\subsubsection{Master plan} % (fold)
+\label{ssub:master_plam}
+
+A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks which have to be processed.
+The tasks are interrelated by kinds of constraints.
+First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors, how to construct the predecessor will be explained later.
+Second, performing the tasks requires resources with limited capacities.
+Third, resources cooperation transmits and enhances these constraints.
+
+A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform.
+While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
+Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$.
+
+% subsubsection master_plan (end)
+
 % subsection preliminaries (end)
 
-\subsection{Interactions and decisions} % (fold)
+\subsection{Individual decisions and ecosystem mode options} % (fold)
 \label{sub:interactions_and_decisions}
-\subsubsection{Demander}
+
+\subsubsection{Selection in resource candidates}
 \label{subs:Demander}
@@
 
-\begin{asparaenum}
-\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
-\suspend{asparaenum}
 \begin{equation}
@@
 \end{numcases}
+
+\subsubsection{Response in selected resource}
+\label{subs:Provider}
+Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call.
+As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks.
+Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:
+
+\begin{asparaenum}
+\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
+\suspend{asparaenum}
+\begin{subnumcases}{}
+A_{k,\tau} \ge q_{\alpha,ij} &\\
+P(mr_k) = \alpha & 
+\end{subnumcases}
+If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$.
+If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$.
+The available will be return back after the finish of $t_{ij}$.
+\resume{asparaenum}
+\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
+\suspend{asparaenum}
+\begin{subnumcases}{}
+C_{k,\tau} > 0 & \\
+P(mr_k) = \alpha
+\end{subnumcases}
+If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$.
+If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
+\begin{subnumcases}{}
+C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
+C_{k,\tau} := 0 & otherwise
+\end{subnumcases}
+
+Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed.
+Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
+\begin{subnumcases}{}
+\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
+R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
+\end{subnumcases}
+\resume{asparaenum}
+\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
+\end{asparaenum}
+Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
+\begin{subnumcases}{}
+q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
+\mathcal{A}_{ij} = \mathcal{B}_l
+\end{subnumcases}
+
+This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
+\begin{subnumcases}{}
+q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
+\mathcal{A}_{ij} = \mathcal{A}_l
+\end{subnumcases}
+% subsection interactions_and_decisions (end)
+
+\subsection{Incubation mode} % (fold)
+\label{sub:incubation_mode}
+The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure.
+Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:
+
+A single service($s_l$) is a composition of all resources in set $\bm{mr}_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more.
+While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
+Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.
+
+A single service-call($sc_l$) comes out after the finish of one frequent task, so it have the same resource configuration the frequent task.
+Service-call can only be performed via resource cooperation with duration $p_l$, because the identity of resource, the capacity cannot be return to the resource after the finish of service-call, so the service-call brings new constrains to the related resources.
+Unlike the task, the amount of one type resource required in the service-call can be pieced together from more than one resource as long as they are in the same type.
+
+\begin{figure}[htbp]
+    \centering
+    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
+    \caption{Service incubate mode}
+    \label{fig:serviceincubatemode}
+\end{figure}
+
+\begin{asparaenum}
+\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
+\suspend{asparaenum}
 
@@
 
-\subsubsection{Provider}
-\label{subs:Provider}
-Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call.
-As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks.
-Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:
-
-\begin{asparaenum}
-\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
-\suspend{asparaenum}
-\begin{subnumcases}{}
-A_{k,\tau} \ge q_{\alpha,ij} &\\
-P(mr_k) = \alpha & 
-\end{subnumcases}
-If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$.
-If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$.
-The available will be return back after the finish of $t_{ij}$.
-\resume{asparaenum}
-\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
-\suspend{asparaenum}
-\begin{subnumcases}{}
-C_{k,\tau} > 0 & \\
-P(mr_k) = \alpha
-\end{subnumcases}
-If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$.
-If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
-\begin{subnumcases}{}
-C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
-C_{k,\tau} := 0 & otherwise
-\end{subnumcases}
-
-Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed.
-Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
-\begin{subnumcases}{}
-\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
-R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
-\end{subnumcases}
-\resume{asparaenum}
-\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
-\end{asparaenum}
-Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
-\begin{subnumcases}{}
-q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
-\mathcal{A}_{ij} = \mathcal{B}_l
-\end{subnumcases}
-
-This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
-\begin{subnumcases}{}
-q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
-\mathcal{A}_{ij} = \mathcal{A}_l
-\end{subnumcases}
-% subsection interactions_and_decisions (end)
-
-\subsection{Operation mode} % (fold)
-\label{sub:operation_mode}
-The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure.
-Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:
 \begin{asparaenum}
@@
 \item Assign new service-call $sc_l$ in $mr_k$.
-\suspend{asparaenum}
+\end{asparaenum}
 
@@
 
-\resume{asparaenum}
-\item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
-\suspend{asparaenum}
+% \resume{asparaenum}
+% \item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
+% \suspend{asparaenum}
+
+% \resume{asparaenum}
+% \item Outsource the task in both active and inactive status.
+% \end{asparaenum}
+
+% subsection operation_mode (end)
+
+\subsection{Schedule the jobs in machine} % (fold)
+\label{sub:schedule_the_jobs_in_machine}
 
@@
 Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
+
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
+
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+  \caption{Simple job configuration}
+    \begin{tabular}{cccccc}
+    \toprule
+    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
+    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+    \midrule
+    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
+    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
+    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
+    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
+    $t_5$ & 1 & 0 & 3 & 2 & 3\\
+    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
+    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:simplejobconfiguration}%
+\end{table}%
+\begin{figure}[htbp]
+	\centering
+	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
+	\caption{Simple instance schedule chart with 4 resources}
+	\label{fig:scheduleChart}
+\end{figure}
+This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period.
+Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.
 
@@
 
-\resume{asparaenum}
-\item Outsource the task in both active and inactive status.
-\end{asparaenum}
+% subsection schedule_the_jobs_in_machine (end)
+
+\subsection{Outsource mode} % (fold)
+\label{sub:outsource_mode}
+
+\begin{figure}[htbp]
+    \centering
+    \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
+    \caption{Outsource mode}
+    \label{fig:outsourcemode}
+\end{figure}
 
@@
 This decision highly depends on the estimate of performance status in other resources and services.
+% subsection outsource_mode (end)
 
-% subsection operation_mode (end)
+\subsection{Metabolism mode} % (fold)
+\label{sub:metabolism mode}
 
-\subsection{Controlling rules} % (fold)
-\label{sub:controlling_rules}
+\begin{figure}[htbp]
+    \centering
+    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
+    \caption{Metabolism mode}
+    \label{fig:metabolismmode}
+\end{figure}
 The decision makings explained above are controlled by review and ranking mechanism provided by platform, the provider who have higher rank value will be safer to stay in the ecosystem, have more chance to succeed in generating services, his services and resources will get more preference.
@@
 
-\subsection{Tricky problems} % (fold)
+\subsection{Tricky problem} % (fold)
 \label{sub:tricky_problems}

### 2016-08-30 figures/metabolism.tex
add mode diagrams and rebuild the structure

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (add) {New Machine}; & \node (machinein) [square] {Arrival Restrictor}; & & & & & & &\\
\node (origin) {Origin Scarcity}; & & \node (compare) [circle] {\Large$\times$}; & & \node (scarcity) [square] {Machine Scarcity}; & \node (metabolism) [square] {Metabolism Module}; &\node (node) [coord] {}; &\node (end) [coord] {};\\
\node (task) {New Task}; & \node (p1) [coord] {};& & \node (p2) [coord] {}; & \node (reduce) [square] {Eliminate Machine}; & & & & \\
& & \node (tf) {Task Finish}; &  & & & & &\\
};
\path (add) edge[->] (machinein) (machinein.east) edge[->] (compare) (compare) edge[->] (scarcity) (scarcity) edge[->] (metabolism);
\path (origin) edge[->] (compare);
\path (tf) edge[->] (compare);
\path (reduce) edge (p2) (p2) edge[->] (compare);
\draw [->] (metabolism) -- (end) ;
\draw [->]  (task) -- (p1) -- (compare);
\path (node) edge[->,skip loop=5.5em] (machinein);
\draw [->] (node) |- (reduce);
\path (machinein.east) to node [near end,yshift=0.5em,xshift=0.5em] {$-$} (compare);
\path (tf) to node [near end,xshift=0.5em] {$-$} (compare);
\path (p1) to node [near end,xshift=0.8em] {$+$} (compare);
\path (p2) to node [near end,xshift=0.5em,yshift=0.3em] {$+$} (compare);
\path (node) to node [near end,xshift=2em,yshift=0.6em] {Decision value} (end);
\end{tikzpicture}

### 2016-08-30 figures/origin_mode.tex
add mode diagrams and rebuild the structure

@@
 ]
-\matrix[row sep=-1em,column sep=2em] {
+\matrix[row sep=0.5em,column sep=2em] {
 % First row:
-\node (order) {Order};& \node (task) [square]{Publish Tasks}; & & & & \\
- & &\node (match) [square]{Match \& Assign};&\node (coord) [square] {Resource Cooperate}; & \node (process)[square]{Process Task}; & \node (finish) {Product};\\
-\node (provider) {Provider}; & \node (resource) [square]{Provider Resources}; & & & & \\
+\node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
+\node (start) {}; & & & & & & \node (stop) {}; \\
+\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (candidate) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (coord) [square] {Cooperate \& Process};&\\
 };
-\path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
-% \path (task) edge[->] (job);
-% \node (ui1) [nonterminal] {unsigned integer};
-% \node (dot) [terminal,right=of ui1] {.};
-% \node (digit) [terminal,right=of dot] {digit};
-% \node (E) [terminal,right=of digit] {E};
-% \node (plus) [terminal,above right=of E] {+};
-% \node (minus) [terminal,below right=of E] {-};
-% \node (ui2) [nonterminal,below right=of plus] {unsigned integer};
+\draw[dotted,thick] (start.west) -- (stop.east);
+\path (task) edge[->,dashed] (response) (response) edge[->] (candidate) (candidate) edge[->] (select) (select) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (finish);
+% \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);
 \end{tikzpicture}

### 2016-08-30 figures/outsource.tex
add mode diagrams and rebuild the structure

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (origin) {Origin Length} ; & \node (compare) [circle] {\Large$\times$}; & & \node (length) [square] {Queue Length} ; & \node (outsource) [square] {Outsourcing Module} ; & \node (node) [coord] {} ; & \node (end) [coord] {}; \\
& & \node (p1) [coord] {} ; & \node	(out) [square] {Outsource Task} ; & & & \\
& \node (tf) {Task Finish}; & & & & &\\
};
\path (origin) edge[->] (compare) (tf) edge[->] (compare) (compare) edge[->] (length) (length) edge[->] (outsource) (outsource) edge[->] (end);
\path (out) edge (p1) (p1) edge[->] (compare);
\draw [->] (node) |- (out) ;
\path (tf) to node [near end,xshift=0.3em] {$+$} (compare) (p1) to node [near end,xshift=0.5em] {$-$} (compare) (outsource) to node [yshift=0.7em,xshift = 1.5em] {Decision value} (end);
\end{tikzpicture}

### 2016-08-30 figures/service-incubate.tex
add mode diagrams and rebuild the structure

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (origin) {Origin Frequency} ; & \node (compare) [circle] {\Large$\times$}; & & \node (frequency) [square] {Task Frequency} ; & \node (incubate) [square] {Incubation Module} ; & \node (node) [coord] {} ; & \node (end) [coord] {}; \\
& & \node (p1) [coord] {} ; & \node	(sc) [square] {Incubate Service} ; & & & \\
& \node (tf) {Task Finish}; & & & & &\\
};
\path (origin) edge[->] (compare) (tf) edge[->] (compare) (compare) edge[->] (frequency) (frequency) edge[->] (incubate) (incubate) edge[->] (end);
\path (sc) edge (p1) (p1) edge[->] (compare);
\draw [->] (node) |- (sc) ;
\path (tf) to node [near end,xshift=0.3em] {$+$} (compare) (p1) to node [near end,xshift=0.5em] {$-$} (compare) (incubate) to node [yshift=0.7em,xshift = 1.5em] {Decision value} (end);
\end{tikzpicture}

### 2016-08-30 intro.tex
start to study the operation model
describe operation model and microscopic evolution
添加新条目
re structure
main content finished
change without design.tex
start to draw diagram
add mode diagrams and rebuild the structure

--- 2015-08-18 intro.tex
@@
-% !Mode:: "TeX:UTF-8"
 % !TEX root = Eco-Model.tex
-\section{test}
+\section{Introduction}
+With the emergence of cloud manufacturing, the relationship among participants in the manufacturing system become more complicated then ever before since every single ind
+
+In this paper, we constructed a
+
+proposed 3 operation modes as options for platform to operate with named metabolism mode, incubation mode and outsourcing mode.

### 2016-08-30 review.tex
add mode diagrams and rebuild the structure

@@
 
+With the cloud manufacturing platform operating, demander comes, signs up and publish orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations.
+Match module in platform informs the task messages to every matched resources and services.
+After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
+Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before.
+Most of resource related decision making are well controlled by platform with the review module.
+
 here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.

### 2016-08-30 design.tex
rought script

@@
 \label{sub:preliminaries}
+Inspired by the cloud manufacturing architecture proposed by research predecessor,
+
+With the cloud manufacturing platform operating, demander arrives, signs up and publishes orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations.
+Match module in platform informs the task messages to every matched resource provider.
+After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
+Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before.
+Most of resource related decision making are well controlled by platform with the review module.
+
+Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
+\item Users/Customers,
+\item Application providers and
+\item Physical resource providers.
+\end{inparaenum}
 The manufacturing ecosystem we proposed in this paper consists of the structure of cloud manufacturing, the operation mode and the controlling rules.
@@
     \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
-    \caption{Origin mode}
+    \caption{Original mode}
     \label{fig:originmode}
@@
 
-\subsection{Individual decisions and ecosystem mode options} % (fold)
+\subsection{Individual decisions and extension modes} % (fold)
 \label{sub:interactions_and_decisions}

### 2016-08-30 figures/origin_mode.tex
rought script

@@
 \node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
-\node (start) {}; & & & & & & \node (stop) {}; \\
-\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (candidate) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (coord) [square] {Cooperate \& Process};&\\
+\node (start1) {}; & & & & & & \node (stop1) {}; \\
+\node (plt) {Platform} ; & &  \node (tb) [square] {Task Hub} ; & \node (candidate) [square] {Resource Candidates} ; & \node (coop) [square] {Cooperate Resources}; & \node (combine) [square] {Task Assembly};\\
+\node (start2) {}; & & & & & & \node (stop2) {}; & \\
+\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Process Task Part};  &\\
 };
-\draw[dotted,thick] (start.west) -- (stop.east);
-\path (task) edge[->,dashed] (response) (response) edge[->] (candidate) (candidate) edge[->] (select) (select) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (finish);
+\draw[dotted,thick] (start1.west) -- (stop1.east) (start2.west) -- (stop2.east);
+\path[->,dashed] (task.east) edge (tb.north) (tb) edge (response) (add) edge (candidate) (candidate) edge (select) (match) edge (coop) (coop.east) edge (process.west);
+\path[->] (response) edge (add) (select.east) edge (match.west) (process) edge (combine) (combine.north) edge (finish.west);
 % \path (order) edge[->] (task) (task) edge[->] (match) (match) edge[->] (coord) (coord) edge[->] (process) (process) edge[->] (finish) (provider) edge[->] (resource) (resource) edge[->] (match);

### 2016-08-30 head.tex
change without design.tex
rought script

@@
 \author[label1]{Shengkai Chen}
+\author[label1]{Shuiliang Fang}
 % \address[label1]{ZJU}
@@
 \begin{abstract}
-In Cloud Manufacturing, users engage in manufacturing business through the well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product.
+In Cloud Manufacturing, individuals engage in manufacturing business through the well-designed platform framework, where provider provide manufacturing resource for demander to search and purchase it as product.
 This business model allows centralized management of distributed massive manufacturing resources, and could potentially reduce the idle rate of those resources.
-
-However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model, makes it hard to meet demander's need.
-Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the individual in the ecosystem.
-As a consequence, the emergence of manufacturing service pattern will be accompanied by these transitions.
-
-In this paper, the author proposed an operation model for users to support their transitions by means of expanding or shrinking their scope of manufacturing service in the manufacturing ecosystem, and the author also proposed an adjustment approach, which depends on the ranking value of user, for the system to restrict the expanding or shrinking procedure and to control the number of users.
-Gradually this adjustment will guide the evolution of the ecosystem, meanwhile, good service pattern will be discovered by the user to survival.
-
-With the help of Repast Simphony, the author designed an agent-based model to simulate the evolution process.
-As the simulation output, manufacturing resource's quality is improving and its diversity is increasing as the evolution process goes by.
-The emergence pattern of service and resource optimization implies the effectiveness and validity of the proposed operation model and adjustment approach, user's rank-based transitions does improve the utilization of manufacturing resource.
-
+However, in the manufacturing ecosystem constructed, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating mode, makes it hard to meet demander's need.
+Meantime, in order to enhance the cash flow rate, provider make decisions to enhance the use rate of their own resources.
+The relationship among participants in this ecosystem become more complicated than that in normal manufacturing system, since the integrated advanced technologies within cloud environment makes it possible to let one individual make decisions depend on the surroundings and other's decisions.
+Hence, in this paper, we designed an original operation mode with 3 extension options for the cloud manufacturing ecosystem to support some decision makings for individuals and the platform operator.
+With the help of Repast Simphony, we designed an agent-based model and experiment to simulate these operation modes with any combinations to validate the effectiveness of them.
+As the experiment result, incubation mode can help reduce the waiting of job and accelerate the process velocity of resources, outsourcing mode reduce the job queue length but not as much as incubation mode and requires more resources, metabolism mode require lower resources than the other modes and will slow resource process velocity a little.
+The combination of incubation and metabolism mode is ideal for platform operators to maintain the manufacturing ecosystem.
 \end{abstract}
@@
 Resource servitization and optimization\sep
-Service pattern recognition\sep
+Operation mode\sep
 Manufacturing evolution\sep

### 2016-08-30 intro.tex
rought script

--- 2015-08-18 intro.tex
@@
-% !Mode:: "TeX:UTF-8"
 % !TEX root = Eco-Model.tex
-\section{test}
+\section{Introduction}
+With the emergence of cloud manufacturing, the relationship among participants in this manufacturing system become more complicated than that in normal manufacturing system, since the integrated advanced technologies within cloud environment makes it possible to let one individual make decisions depend on the surroundings and other's decisions.
+Demander prefer high quality performance on their needs while provider prefer high use rate of their resource, even the cloud platform operator prefer lower amount of registered resource when dealing with almost arriving needs for the easier maintenance.
+These preferences stimulate the emergence of good service pattern that will lead to the evolution of manufacturing pattern in the cloud circumstance like an ecosystem.
+Hence, hence it's important to identify good operation mode that help the evolution.
+
+In this paper, we designed an original operation mode for the cloud manufacturing ecosystem, then we proposed 3 extension modes named metabolism mode, incubation mode and outsourcing mode, that can be extended on the original mode with any combinations.
+Finally, we deigned an experiment to validate these synthetic operation modes in agent-based simulation method.

### 2016-08-30 review.tex
rought script

--- 2016-08-29 review.tex
@@
 
-Review on 1. Cloud manufacturing mode (any) study 
-2. res ser combination and decision making
-3. rank and review ecosystem (system changing)
-4. manufacturing system simulation
+In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}, modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework\cite{Tao2012,Valilai2013}, Lv use list of views to depict this multi-layer architecture\cite{LvJuly312012-Aug.22012}.
 
-In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}
+Servitization is the key philosophy in the operating of cloud manufacturing\cite{li2010cloud}, service can be created statically that come along with provider\cite{Tao2012} or can be created dynamically according to task pattern, such method as `Multi-Composition for Each Task'\cite{Liu2013} that combine incompetent service into a whole, also service can be created by AI planning-based automatic composition framework\cite{OhJan.-March2008}.
 
-Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (\cite{Tao2012}\cite{Valilai2013}
+Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}, and in the operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
+segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}.
+Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered research discuss trends are Internet and cloud based situation.
 
-Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
-\item Users/Customers,
-\item Application providers and
-\item Physical resource providers.
-\end{inparaenum}
-
-\subsection{Study background} % (fold)
+\subsection{Background} % (fold)
 \label{sub:background}
 
-here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
-\begin{itemize}
-	\item order
-	\item task correspond to capacity
-	\item resource
-	\item capacity is the function of a resource. like quantity
-	\item service is the bundle of capacities. the proportion of the capacities.
-	\item 
-\end{itemize}
-
-Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment
-
-As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.
-
-Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.
-
+In the next section, we will design the ecosystem from an original operation mode, then we formulize the each of the decision makings and the extension modes.
+Before the design of the ecosystem, we specify some basic concept as the study background.
+\begin{compactitem}
+	\item Provider: the individual in ecosystem who provide resources;
+	\item Resource: the basic task process visualized object with renewable capacity unique type;
+	\item Task: the basic visualized object need to be processed with certain type and capacity of resources;
+	\item Demander: the individual in ecosystem who publish orders that contain bunch of tasks;
+	\item Platform: the place where individual interact with others and environment.
+\end{compactitem}
 % section literature_review (end)

### 2016-08-31 design.tex
modify

--- 2016-08-30 design.tex
@@
 \label{sub:preliminaries}
-The manufacturing ecosystem we proposed in this paper consists of the structure of cloud manufacturing, the operation mode and the controlling rules.
-Before the detailed interpretation for these parts, we describe some basic settings as follows.
-
+With the cloud manufacturing platform operating, demander publish orders while provider provide resources, then they communicate with each other, arrange the resources to perform tasks that decomposed by orders.
+Finally, product is produced and delivered to the demander.
+Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
+\item Users/Customers,
+\item Application providers and
+\item Physical resource providers.
+\end{inparaenum}
+Inspired by the such model, we design the original mode shown in \autoref{fig:originmode} as the basis for the operating of the platform.
 \begin{figure}[htbp]
@@
     \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
-    \caption{Origin mode}
+    \caption{Original mode}
     \label{fig:originmode}
 \end{figure}
+In this mode, individual in each group execute activities that interact with others with object flow(full lines) and information flow(dashed lines).
+As the start of manufacturing activities procedure, the demander publish orders that can be depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations.
+Each task needs to performed with pre-determined configuration of resources, hence, after the response and assign procedure, the selected resource cannot start to process the task until all of other selected resources by this task are ready, we call this procedure as resource cooperating and what each resource actually process is the task part.
+Finally product will be delivered to demander after the process and assembly of these parts, then the review of the product will change the rank value of the selected resource owners.
+Task part is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider them as task parts.
+A little more about the cooperation procedure, this produce is necessary because the capacity limit of resources and task part should be processed simultaneously to make sure that the task is being processed with required resource capacities.
+We call the task part is active when being processed, semi-active when resource is waiting for synchronization, inactive when the part is just assigned to the job list.
 
@@
 \label{ssub:assumptions_nomenclature}
-Assumptions about quality
-
-about time
-
-schedule and outsource are event driven decision making
-
-resources are renewable
+To scope our research, we make some assumptions as follows:
+\begin{compactitem}
+\item Each single task should be assembled by part according to the pre-determined resources configuration, and these parts should be processed simultaneously;
+\item Since the cooperation, the quality of product is determined by the worst quality part of produced by selected resource;
+\item Resource are renewable that the available capacity will be return when the process produce finished;
+\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
+\item Cooperate and process produce cannot be interrupted;
+\item Provider can only schedule task part that in inactive status. 
+\end{compactitem}
+These assumptions are suitable for original mode, in other extension mode, some of the assumptions will be modified.
 
@@
 	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
-	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
-	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
+	$\mathcal{L}_{k,\tau}$ & The list of inactive job queue of $mr_k$ at $\tau$ with sequence\\
+	$\mathcal{H}_{k,\tau}$ & The list of semi-active job of $mr_k$ at $\tau$ \\
+	$\mathcal{G}_{k,\tau}$ & The set of active job of $mr_k$ at $\tau$ \\ 
 	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
@@
 	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
+	$q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$\\
+	$\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\
 	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
-	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
+	$\mathcal{G}_{l,\tau}$ & The set of active job of $ms_l$ at $\tau$ \\
 	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
@@
 \end{table}
-
-For the continuous coming of provider, demander, order, task, etc., the amount of them can not be determined at any time point, so we doesn't restrict the upper bound for subscript index amount of all these variables, and we will study the decision separately for these individual at the given time point $\tau$.
-Detailed design will be explained in the following sections.
+\vspace{-2.5em}
 % subsubsection assumptions_nomenclature (end)
-\subsubsection{Master plan} % (fold)
+\subsubsection{Master plan for original mode} % (fold)
 \label{ssub:master_plam}
-
-A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks which have to be processed.
-The tasks are interrelated by kinds of constraints.
-First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors, how to construct the predecessor will be explained later.
+A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
+First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors that come along within order and it can be added in the schedule produce.
 Second, performing the tasks requires resources with limited capacities.
-Third, resources cooperation transmits and enhances these constraints.
-
+Third, resources cooperation requires all the task parts in active status.
 A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform.
-While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
+While being processed via resource cooperation, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
 Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$.
-
+This plan is much like the settings in resource-constrained project scheduling problem\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.
 % subsubsection master_plan (end)
-
 % subsection preliminaries (end)
 
-\subsection{Individual decisions and ecosystem mode options} % (fold)
+\subsection{Individual decisions in original mode} % (fold)
 \label{sub:interactions_and_decisions}
+\subsubsection{Response for type matched task}
+\label{subs:Response_for_type_matched_task}
+Provider makes decision at time $\tau\ge r_i$ to response task if the belonged resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
+If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$.
+If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$ , the available capacity will be returned back after the finish of $t_{ij}$ part.
 
-\subsubsection{Selection in resource candidates}
-\label{subs:Demander}
-Demander makes decision about resources and services selection for the task.
-Without loss of generalization, we suppose at time period $\tau$, demander received bunch of matched resource and services as candidates for the performance of the published order $o_i$, it's obvious that $\tau \ge r_{i}$.
-The decision making for any task included in $o_i$, let's take $t_{ij}$, can be described in one of the following 3 situation:
-
+\subsubsection{Select from resource candidates}
+\label{subs:select_resource_candidates}
+Demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
+W.o.l.o.g, we suppose at time period $\tau \ge r_i$, the decision making of demander can be described as follows:
 \begin{equation}
-\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)
+\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
+R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
+\right) \label{eq:selectresaim}
 \end{equation}
 \begin{numcases}{\text{s.t.}}
-\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
-\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
-\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
-l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & 
+q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
+\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
+\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
+\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
+k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
 \end{numcases}
 
-\subsubsection{Response in selected resource}
-\label{subs:Provider}
-Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call.
-As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks.
-Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:
+The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length.
+\autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type of required configuration.
 
-\begin{asparaenum}
-\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
-\suspend{asparaenum}
+\subsubsection{Assign in selected resource} % (fold)
+\label{subs:assign_in_select_resource}
+If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ or $\mathcal{L}_{k,\tau}$ according to:
 \begin{subnumcases}{}
-A_{k,\tau} \ge q_{\alpha,ij} &\\
-P(mr_k) = \alpha & 
-\end{subnumcases}
-If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$.
-If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$.
-The available will be return back after the finish of $t_{ij}$.
-\resume{asparaenum}
-\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
-\suspend{asparaenum}
-\begin{subnumcases}{}
-C_{k,\tau} > 0 & \\
-P(mr_k) = \alpha
-\end{subnumcases}
-If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$.
-If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
-\begin{subnumcases}{}
-C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
-C_{k,\tau} := 0 & otherwise
+\mathcal{H}_{k,\tau} := \mathcal{H}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \label{eq:addtobuffer}\\
+\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
 \end{subnumcases}
 
-Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed.
-Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
-\begin{subnumcases}{}
-\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
-R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
-\end{subnumcases}
-\resume{asparaenum}
-\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
-\end{asparaenum}
-Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
-\begin{subnumcases}{}
-q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
-\mathcal{A}_{ij} = \mathcal{B}_l
-\end{subnumcases}
-
-This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
-\begin{subnumcases}{}
-q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
-\mathcal{A}_{ij} = \mathcal{A}_l
-\end{subnumcases}
+If all the part of $t_{ij}$ are in type matched resources' $\mathcal{H}_{k,\tau}$, then these providers will change all the task part status from semi-active to active and add $t_{ij}$ to their $\mathcal{G}_{k,\tau}$.
+% subsubsection assign_in_selected_resource (end)
 % subsection interactions_and_decisions (end)
@@
 \label{sub:incubation_mode}
-The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure.
-Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:
-
-A single service($s_l$) is a composition of all resources in set $\bm{mr}_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more.
-While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
-Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.
-
-A single service-call($sc_l$) comes out after the finish of one frequent task, so it have the same resource configuration the frequent task.
-Service-call can only be performed via resource cooperation with duration $p_l$, because the identity of resource, the capacity cannot be return to the resource after the finish of service-call, so the service-call brings new constrains to the related resources.
-Unlike the task, the amount of one type resource required in the service-call can be pieced together from more than one resource as long as they are in the same type.
-
+Incubation mode is one extension mode for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resource with certain quota in a contract.
+Manufacturing service will be incubated as shown in \autoref{fig:serviceincubatemode}.
 \begin{figure}[htbp]
@@
     \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
-    \caption{Service incubate mode}
+    \caption{Incubation mode}
     \label{fig:serviceincubatemode}
 \end{figure}
+After the finish of task part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.
+
+The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance and each required resource type can also be cooperated by different resources, which means after the performance of service-call, capacity of selected resource will not be returned to.
+The product of service-call is the service, which is actually a contract of resources that may come from any provider in the system, it's possible for more than one resource with same type to make contribute to the formation of service.
+No more cooperation and assembly are part of pros of service and product quality will no more restricted to the worst quality of resources since the complementary effect, while the cons of service include that it can only perform  corresponding configured task.
+Now we can mark task and service-call as job, resource and service as machine.
+
+\subsubsection{Response for type matched job} % (fold)
+\label{ssub:response_in_type_matched_resource}
+Apart from $mr_k$ response for $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
+\begin{asparaenum}
+\item $mr_k$ response for $sc_l$
+\suspend{asparaenum}
+If $mr_k$ was type matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will response the service-call.
+If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be returned back even after the finish of $sc_l$ part.
+Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
+\resume{asparaenum}
+\item $ms_l$ response for $t_{ij}$
+\end{asparaenum}
+Service is task-oriented machine, so if type matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will response $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
+
+% subsubsection response_in_type_matched_resource (end)
+
+\subsubsection{Select from machine candidates} % (fold)
+\label{ssub:selection_in_resource_candidates_for_service_call}
+Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
 
 \begin{asparaenum}
-\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
+\item Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau} = \mathcal{A}_l$
 \suspend{asparaenum}
 
+The decision making of select from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, and the difference is that the every part of $\bm{l}_{\alpha}$ in decision variable $\bm{l}$ here is also a set of selected resources followed by \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
+\begin{subnumcases}{}
+C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
+C_{k,\tau} := 0 & otherwise \label{eq:cap0}
+\end{subnumcases}
+
 \resume{asparaenum}
-\item  $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$, while $\abs{\mathcal{S}_{ij,\tau}}=0$.
+\item Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
 \suspend{asparaenum}
 
+This situation implies that the resource candidates are not enough while there exists service candidates, demander can just select service. 
 \begin{equation}
-\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
-R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
-\right)
+\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
 \end{equation}
+\begin{numcases}{\text{s.t.}}
+\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
+\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
+\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
+l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
+\end{numcases}
 
-\begin{numcases}{\text{s.t.}}
-q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\\
-R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\\
-\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
-\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \\
-k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$
-\end{numcases}
-For each required resource type $\alpha$
+Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low waiting queue length.
+\autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.
 
 \resume{asparaenum}
-\item  $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$, while $\abs{\mathcal{S}_{ij,\tau}}>0$.
+\item Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
 \end{asparaenum}
 
+In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one.
 \begin{equation}
 \max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
-Rank_m, \mathcal{L}_m \right) \\ 
+Rank_m, \mathcal{L}_m \right) \\ \label{eq:combaim} 
 % \text{s.t.}\notag
@@
 R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
-\right)\right) & \\
-Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
-\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
-\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
+\right)\right) & \label{eq:optk}\\
+Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \label{eq:temprank}\\
+\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \label{eq:templength}\\
+\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \label{eq:tempqualitystart}\\
 \mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
@@
 \bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
-\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
+\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \label{eq:tempqualityend}\\
 % \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
@@
 % l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
-l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
+l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \label{eq:optl}\\
 Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
 \mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
-m \in \left\{ l^*,\bm{k}^* \right\} 
+m \in \left\{ l^*,\bm{k}^* \right\} \label{eq:newdicisionvariable}
 \end{numcases}
 
+Similar to other situations, \autoref{eq:combaim} is a a multi-objective function that aims at high quality, high rank and low waiting queue length.
+\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate produce.
+\autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.
+
+% subsubsection selection_in_resource_candidates_for_service_call (end)
+
+\subsubsection{Assign in selected machine} % (fold)
+Apart from $mr_k$ assign $t_{ij}$ when selected as we explained in \autoref{subs:assign_in_select_resource}, there are 2 other cases in incubation mode:
+
 \begin{asparaenum}
-\item Assign new task $t_{ij}$ in $mr_k$.
+\item Assign $sc_l$ to $mr_k$
 \suspend{asparaenum}
 
-With the select decision of $t_{ij}$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
+If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict than that in \autoref{eq:addtobuffer}, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
+Then, the provider of $mr_k$ should change the predecessor set:
 \begin{equation}
-	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau},sc \text{ is service-call} \right\} \cup \mathcal{G}_{k,\tau}
+	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{H}_{k,\tau}
 \end{equation}
-Then, the provider will add $t_{ij}$ to queue or process buffer according to:
+and all the task assign after $\tau$, we say $\tau'>\tau$ will set:
+\begin{equation}
+	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau'},sc \text{ is service-call} \right\} \cup \mathcal{H}_{k,\tau'}
+\end{equation}
+And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.
+\resume{asparaenum}
+\item Assign $t_{ij}$ to $ms_l$
+\end{asparaenum}
+Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence:
 \begin{subnumcases}{}
-\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \\
-\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
+\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
+\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
 \end{subnumcases}
 
-\resume{asparaenum}
-\item Assign new service-call $sc_l$ in $mr_k$.
-\end{asparaenum}
-
-With the select decision of $sc_l$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
-\begin{equation}
-	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{G}_{k,\tau}
-\end{equation}
-Then, the provider will add $sc_l$ to queue or process buffer according to:
-\begin{subnumcases}{}
-\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_l\} & if $\abs{\mathcal{L}_{k,\tau}\cup\mathcal{G}_{k,\tau}}=0$ \\
-\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
-\end{subnumcases}
-
-% \resume{asparaenum}
-% \item Schedule the tasks in $\mathcal{L}_{k,\tau}$.
-% \suspend{asparaenum}
-
-% \resume{asparaenum}
-% \item Outsource the task in both active and inactive status.
-% \end{asparaenum}
-
+% subsubsection assign_in_selected_machine (end)
 % subsection operation_mode (end)
@@
 \label{sub:schedule_the_jobs_in_machine}
-
-The assignment of new service-call will not driven these decision making event because of the resource capacity consuming feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
+In order to enhance the user rate, provider will schedule the inactive jobs on the provided machines.
+Since all the jobs in the service are tasks and they have identical configuration, so the schedule in service is a single machine scheduling problem that is not what we focus on in this study, we only discuss the scheduling of jobs in resources.
+Since the assignment of new service-call will not trigger the schedule procedure because of the resource capacity dominance feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
 \begin{figure}[htbp]

### 2016-08-31 design.tex
first finish

@@
 Task part is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider them as task parts.
-A little more about the cooperation procedure, this produce is necessary because the capacity limit of resources and task part should be processed simultaneously to make sure that the task is being processed with required resource capacities.
+A little more about the cooperation procedure, this procedure is necessary because the capacity limit of resources and task part should be processed simultaneously to make sure that the task is being processed with required resource capacities.
 We call the task part is active when being processed, semi-active when resource is waiting for synchronization, inactive when the part is just assigned to the job list.
@@
 \item Since the cooperation, the quality of product is determined by the worst quality part of produced by selected resource;
-\item Resource are renewable that the available capacity will be return when the process produce finished;
+\item Resource are renewable that the available capacity will be return when the process procedure finished;
 \item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
-\item Cooperate and process produce cannot be interrupted;
+\item Cooperate and process procedure cannot be interrupted;
 \item Provider can only schedule task part that in inactive status. 
@@
 \end{table}
-\vspace{-2.5em}
+% \vspace{-2.5em}
 % subsubsection assumptions_nomenclature (end)
@@
 A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
-First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors that come along within order and it can be added in the schedule produce.
+First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors that come along within order and it can be added in the schedule procedure.
 Second, performing the tasks requires resources with limited capacities.
@@
 Similar to other situations, \autoref{eq:combaim} is a a multi-objective function that aims at high quality, high rank and low waiting queue length.
-\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate produce.
+\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate procedure.
 \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.
@@
 \label{sub:schedule_the_jobs_in_machine}
-In order to enhance the user rate, provider will schedule the inactive jobs on the provided machines.
-Since all the jobs in the service are tasks and they have identical configuration, so the schedule in service is a single machine scheduling problem that is not what we focus on in this study, we only discuss the scheduling of jobs in resources.
-Since the assignment of new service-call will not trigger the schedule procedure because of the resource capacity dominance feature, so it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job come after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
+In order to enhance the user rate, provider will schedule the inactive jobs on their machines.
+Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
+Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
 \begin{figure}[htbp]
 	\centering
-	\resizebox{.75\textwidth}{!}{\input{figures/service-call}}
+	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
 	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
@@
 
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will help describe the setting more clearly.
+
+This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when each of  its part are in semi-activate status, the shadow in the figure shows the waiting period between the status transition from semi-activate to active.
+Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
+Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.
 
@@
 	\centering
+	\normalsize
 	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
-	\caption{Simple instance schedule chart with 4 resources}
+	\caption{Simple instance schedule chart with 4 resources in 3 different types}
 	\label{fig:scheduleChart}
 \end{figure}
-This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period.
-Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.
 
-A schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right],n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}}$.
-Since the task in $\mathcal{L}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, type subscript $\alpha$ can be ignored for all the job assigned here matches the resource type, so the schedule model is:
+A schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
+Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched.
+The schedule model is:
 
 \begin{equation}
-\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right)
+\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
 \end{equation}
 \begin{numcases}{\text{s.t.}}
-L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\right\} & \\
-f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\\
-G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \\
-f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \\
+L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
+f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
+G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
+f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
 \sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
-f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
+f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
 \end{numcases}
 
-Like the RCPSP.
-Since \autoref{eq:caplimitwithtime} is a time dependent function the schedule model cannot be
-solved with mixed integer programming (MIP) techniques. In order to solve
-the RCPSP with MIP{solvers such as CPLEX (cf. Bixby 1996), one has to
-employ the 0{1 problem formulation of Pritsker et al. (1969).}}
+The schedule aim for each resource is to minimum the maximum delay of jobs \autoref{eq:scheduleaim}.
+\autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself.
+\autoref{eq:alreadydefined} means that the finish time of activate job is determined.
+\autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
+Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
+solved with mixed integer programming (MIP) techniques.
 
@@
 
-\subsection{Outsource mode} % (fold)
+\subsection{Outsourcing mode} % (fold)
 \label{sub:outsource_mode}
-
+Outsourcing mode is one extension mode for the original mode and will be active when incubation mode is on for only service can perform this procedure. As shown in \autoref{fig:outsourcemode}, 
 \begin{figure}[htbp]
@@
     \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
-    \caption{Outsource mode}
+    \caption{Outsourcing mode}
     \label{fig:outsourcemode}
 \end{figure}
-
-Since only matched task can be assigned and processed in the certain service, the decision making about schedule tasks in service $ms_l$ is a simple problem that it is similar to 1 machine scheduling problem, so we will not discuss the situation about schedule the task in $\mathcal{L}_{l,\tau}$ here.
-However, service can perform task in a flexible mode, provider can outsource the task in both active and inactive status.
-
+the idea of outsourcing for service is to republish active or inactive task to platform again to reduce queue length to enhance the probability to be selected by new tasks.
 For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status will decrease.
 This decision highly depends on the estimate of performance status in other resources and services.
+Outsourcing mode makes it possible to paralleled process one job.
 % subsection outsource_mode (end)
@@
 \label{sub:metabolism mode}
-
+Metabolism mode is one extension mode for the original mode that control the number of individual in the system by both restrict the arrival and eliminate the current members.
+As shown in \autoref{fig:metabolismmode},
 \begin{figure}[htbp]
@@
 \end{figure}
-The decision makings explained above are controlled by review and ranking mechanism provided by platform, the provider who have higher rank value will be safer to stay in the ecosystem, have more chance to succeed in generating services, his services and resources will get more preference.
-Hence, here we will explain some controlling rules related to the rank value changing:
-\begin{asparaenum}
-\item Review from demander when his task $t_{ij}$ was finished by resource cooperation $mr_{\bm{k}}$:
-\suspend{asparaenum}
+machine scarcity is the control variable that can be defined as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$ for resource in type $\alpha$ and the sum of task minus the sum of service in each type.
 
-We will ignore resource type subscript $\alpha$ here for the reason that resources perform the task already meet the type needs.
-With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
+Platform restrict the arrival new machine by block the registration, eliminate the current machine by their quality and owner's rank.
+Rank value is initialized to 0 and will be changed by demander's review after the finish of task as:
 \begin{subnumcases}{}
@@
 \end{subnumcases} 
-
-\resume{asparaenum} 
-\item Review from demander when his task $t_{ij}$ was finished by service $ms_l$:
-\suspend{asparaenum}
 Rank value changing with regard to service can be determined easier:
@@
 
-\resume{asparaenum}
-\item Eliminate resource or service on the platform
-\end{asparaenum}
-
-This decision making is a control method for platform to keep the performance of tasks with content quality and efficiency.
-We denote the list of all resources with type $\alpha$ as $\bm{mr}_\alpha$ and the list of all services as $\bm{ms}$ at time $\tau$, after the sort these lists according to the scarcity and quality, the unqualified resources and services.
-Scarcity can be defined as:
-
-\begin{subnumcases}{}
-\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} } & $\alpha\in\mathcal{A}$ \label{eq:resourcescarcity}\\ 
-\abs{\mathcal{L}_{l,\tau}} & \label{eq:servicescarcity}
-\end{subnumcases}
-
-The scarcity of one service can be calculated with \autoref{eq:servicescarcity} while the scarcity of one type of resource can be calculated with \autoref{eq:resourcescarcity}.
 % subsection controlling_rules (end)
@@
 \label{sub:tricky_problems}
-Even though the schedule mode exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
+Even though the schedule procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
 Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock},
@@
 \end{figure}
-$t_{i2}$ is active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is active in $mr_1$ and inactive in $mr_2$, because of the capacity limit, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and will they will block the other tasks from being processed.
+$t_{i2}$ is semi-active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is semi-active in $mr_1$ and inactive in $mr_2$, however, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and they will block the other tasks from being processed.
 
-The method to solve the job-lock problem is to add the status changed task to the predecessor set of all the other tasks in the same inactive queue list.
+One feasible solution for the job-lock problem is to add the semi-inactive task to the predecessor set of all the other tasks in the same inactive queue list as soon as the status changes.
 % subsection tricky_problems (end)

### 2016-08-31 discussion.tex
first finish

--- 2015-09-23 discussion.tex
@@
 % !TEX root = Eco-Model.tex
-\section{Discussion} % (fold)
-\label{sec:discussion}
-
-% section discussion (end)
+\section{Limitations, and Future Research} % (fold)
+\label{sec:contributions_limitations_and_future_research}
+We only proposed 3 extension modes to combine and it may not fully describe the operation mode of the cloud manufacturing system, limited mode option may limit the evolution direction of the ecosystem, hence we will try to design more extension modes to test.
+The assignment of service-call is oversimplified to prevent complex consequence, we will design new method to assign this job.
+The job-lock problem may have better solutions.
+% section contributions_limitations_and_future_research (end)

### 2016-08-31 result.tex
add mode diagrams and rebuild the structure
first finish

--- 2016-08-28 result.tex
@@
 
-Entities in the manufacturing ecosystem we designed above have these traits, they are: \begin{inparaenum}
+Entities in the manufacturing ecosystem we designed above have these traits: \begin{inparaenum}[1)]
 \item autonomous and self-directed, 
@@
 With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments on it.
-\subsection{Agent-based modeling and simulation design} % (fold)
-\label{sub:agent_based_modeling_and_simulation}
-\subsubsection{Model realization}
-\begin{asparaenum}
-\item Main agents
-\suspend{asparaenum}
-\begin{figure}[htbp]
-\centering
-\tiny
-\subfloat[Job related classes]{\begin{tikzpicture}
-    \input{figures/cJob}
-    \input{figures/cTask}
-    \input{figures/cServiceCall}
-    \end{tikzpicture}
-    \label{fig:jobclassed}}\hspace{1pt}
-\subfloat[Machine related classes]{\begin{tikzpicture}
-    \input{figures/cMachine}
-    \input{figures/cResource}
-    \input{figures/cService}
-    \end{tikzpicture}
-    \label{fig:machineclassed}}\\
-\subfloat[User related classes]{\begin{tikzpicture}
-    \input{figures/cUser}
-    \input{figures/cProvider}
-\input{figures/cDemander}
-    \end{tikzpicture}\label{fig:userclassed}}\hspace{3pt}
-\subfloat[Cloud Platform]{\begin{tikzpicture}
-	\input{figures/cCloudPlatform}
-	\end{tikzpicture}\label{fig:platform}}
-\end{figure}
+
+% \subsection{Agent-based modeling and simulation design} % (fold)
+% \label{sub:agent_based_modeling_and_simulation}
+% \subsubsection{Model realization}
+% \begin{asparaenum}
+% \item Main agents
+% \suspend{asparaenum}
+% \begin{figure}[htbp]
+% \centering
+% \tiny
+% \subfloat[Job related classes]{\begin{tikzpicture}
+%     \input{figures/cJob}
+%     \input{figures/cTask}
+%     \input{figures/cServiceCall}
+%     \end{tikzpicture}
+%     \label{fig:jobclassed}}\hspace{1pt}
+% \subfloat[Machine related classes]{\begin{tikzpicture}
+%     \input{figures/cMachine}
+%     \input{figures/cResource}
+%     \input{figures/cService}
+%     \end{tikzpicture}
+%     \label{fig:machineclassed}}\\
+% \subfloat[User related classes]{\begin{tikzpicture}
+%     \input{figures/cUser}
+%     \input{figures/cProvider}
+% \input{figures/cDemander}
+%     \end{tikzpicture}\label{fig:userclassed}}\hspace{3pt}
+% \subfloat[Cloud Platform]{\begin{tikzpicture}
+% 	\input{figures/cCloudPlatform}
+% 	\end{tikzpicture}\label{fig:platform}}
+% \end{figure}
+
+% \resume{asparaenum}
+% \item Behavior interfaces and classes
+% \end{asparaenum}
 
@@
 %     \begin{tikzpicture}
-% 	\input{figures/cCloudPlatform}
+%     \input{figures/iAssignBehavior}
+%     \input{figures/iSelectBehavior}
+%     \input{figures/iResponseBehavior}
+%     \input{figures/iProcessBehavior}
+%     \input{figures/iReleaseBehavior}
+%     % \input{figures/cServiceAssign}
+%     % \input{figures/cResourceAssign}
 %     \end{tikzpicture}
-% 	\caption{Cloud Platform}
-% 	\label{fig:platform}
-% \end{figure}
-% % \resume{asparaenum}
-% % \item User related
-% % \suspend{asparaenum}
-% \begin{figure}[htbp]
-%     \centering
-%     \tiny
-%     \begin{tikzpicture}
-%     \input{figures/cUser}
-%     \input{figures/cProvider}
-% \input{figures/cDemander}
-%     \end{tikzpicture}
-%     \caption{User related classes}
-%     \label{fig:userclassed}
-% \end{figure}
-% \resume{asparaenum}
-% \item Job related
-% \suspend{asparaenum}
-% \begin{figure}[htbp]
-%     \centering
-%     \tiny
-%     \begin{tikzpicture}
-%     \input{figures/cJob}
-%     \input{figures/cTask}
-%     \input{figures/cServiceCall}
-%     \end{tikzpicture}
-%     \caption{Job related classes}
-%     \label{fig:jobclassed}
-% \end{figure}
-% \resume{asparaenum}
-% \item Machine related
-% \end{asparaenum}
-% \begin{figure}[htbp]
-%     \centering
-%     \tiny
-%     \begin{tikzpicture}
-%     \input{figures/cMachine}
-%     \input{figures/cResource}
-%     \input{figures/cService}
-%     \end{tikzpicture}
-%     \caption{Machine related classes}
-%     \label{fig:machineclassed}
-% \end{figure}
-\resume{asparaenum}
-\item Behavior interfaces and classes
-\end{asparaenum}
-% \begin{asparaenum}
-% \item Assign behavior
-% \suspend{asparaenum}
-\begin{figure}[htbp]
-    \centering
-    \tiny
-    \begin{tikzpicture}
-    \input{figures/iAssignBehavior}
-    \input{figures/iSelectBehavior}
-    \input{figures/iResponseBehavior}
-    \input{figures/iProcessBehavior}
-    \input{figures/iReleaseBehavior}
-    % \input{figures/cServiceAssign}
-    % \input{figures/cResourceAssign}
-    \end{tikzpicture}
-    \caption{Assign interface and related classes}
-    \label{fig:assigninterface}
-\end{figure}
-
-% \resume{asparaenum}
-% \item Process behavior
-% \suspend{asparaenum}
-
-% \begin{figure}[htbp]
-%     \centering
-%     \scriptsize
-%     \begin{tikzpicture}
-%     \input{figures/iProcessBehavior}
-%     \input{figures/cProcessInTask}
-%     \input{figures/cProcessInServiceCall}
-%     \end{tikzpicture}
-%     \caption{Process interface and related classes}
-%     \label{fig:processinterface}
-% \end{figure}
-% \resume{asparaenum}
-% \item Release behavior
-% \suspend{asparaenum}
-
-% \begin{figure}[htbp]
-%     \centering
-%     \scriptsize
-%     \begin{tikzpicture}
-%     \input{figures/iReleaseBehavior}
-%     \input{figures/cResourceRelease}
-%     \input{figures/cServiceRelease}
-%     \end{tikzpicture}
-%     \caption{Release interface and related classes}
-%     \label{fig:releaseinterface}
-% \end{figure}
-% \resume{asparaenum}
-% \item Response behavior
-% \suspend{asparaenum}
-
-% \begin{figure}[htbp]
-%     \centering
-%     \scriptsize
-%     \begin{tikzpicture}
-%     \input{figures/iResponseBehavior}
-%     \input{figures/cResourceResponse}
-%     \input{figures/cServiceResponse}
-%     \end{tikzpicture}
-%     \caption{Response interface and related classes}
-%     \label{fig:reponseinterface}
-% \end{figure}
-% \resume{asparaenum}
-% \item Select behavior
-% \end{asparaenum}
-
-% \begin{figure}[htbp]
-%     \centering
-%     \scriptsize
-%     \begin{tikzpicture}
-%     \input{figures/iSelectBehavior}
-%     \input{figures/cSelectInTask}
-%     \input{figures/cSelectInServiceCall}
-%     \end{tikzpicture}
-%     \caption{Select interface and related classes}
-%     \label{fig:selectinterface}
+%     \caption{Assign interface and related classes}
+%     \label{fig:assigninterface}
 % \end{figure}
@@
 \label{ssub:case_design}
-We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}, and the control parameters in the model are
-
+We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}. 
 \begin{table}[htbp]
@@
   \caption{Order generating parameters setting}
-    \begin{tabular}{ccccccc}
+    \begin{tabular}{cccccccccc}
     \toprule
-    \textbf{Number of activities} & \textbf{OS} & \textbf{CI} & \textbf{Number of resources} & \textbf{RF} & \textbf{RC} \\
+    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
     \midrule
-     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5     \\
+     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
     \bottomrule
     \end{tabular}%
-    {\footnotetext{\tiny The meaning of the parameters are defined in \cite{Demeulemeester2003}}}
+    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
+    }
   \label{tab:generalparameter}%
 \end{table}%
+We assume provider and demander are arriving as the poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, we make sure that:
+\begin{equation}
+\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
+\end{equation}
 
-% subsubsection case_design (end)
-
-\subsubsection{Parameters setting} % (fold)
-\label{ssub:parameters_setting}
-We design experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
+We design experiments to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
 
@@
 
-\subsubsection{Result and analysis} % (fold)
+\subsection{Result and analysis} % (fold)
 \label{ssub:result_and_analysis}
 All the experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
-Even though different random seed makes different initialization of the simulation and different initialization will affect the simulation a lot, the universal law of the model cannot be changed if it exists.
 After bunch of experiments with different random seeds, we discovered some laws in operation mode.
@@
 we find: \begin{inparaenum}[1)]
-\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22, this combined mode even also need lower number of queue length.
+\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22.
 Full lines are not much above dotted lines in $N_F$ means that task processing velocity will be a little slower with the metabolism, exception also appears in Mode 22.
-\item $L$ and $N_T$ both represent the waiting of job, triangle and square line turned lower in $L$ meas that service-incubate mode can help reduce the waiting of job, these two type of line appeared above the circle line means the service-incubate mode do accelerate the processing velocity.
-\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsource mode needs more resources to operate and can only reduce the waiting of job a little.
-\item There is no big difference among all the 6 modes.
-Provider in metabolism mode will get lower rank value for they cannot stay in the system forever, the longer stay in the system, the higher rank value provider will get.
-Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without service-incubate mode.
-\item Mode 22 is a very special mode that reached the balance of the system, although all the mentioned modes will reach balance in the long run, with the average data value shown in \autoref{tab:averagevalue}, metabolism with service-incubate but not with outsource mode is the easiest combine mode to maintain the system, resource are self configured and controlled to just meet the task need.
+\item $L$ and $N_T$ both represent the queue length of jobs, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do accelerate the processing velocity.
+\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the waiting of job a little.
+\item There is no big difference among all the 6 modes in rank change.
+Provider in metabolism mode will get lower rank value for they cannot stay in the system for long, the longer stay in the system, the higher rank value provider will get.
+Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without incubation mode.
+\item Mode 22 is a very special mode that reached the balance in 6000 ticks, that the number of provider and resource changes little with time goes by.
+Because our experiment setting comply \autoref{eq:balance}, the coming need capacity velocity is less than the coming capacity, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism itself is full of uncertainty and it's hard to predict when other metabolism related mode will get the balance.
+\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is the easiest combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
 \end{inparaenum}

### 2016-09-06 design.tex
改版

@@
 \label{sub:preliminaries}
-With the cloud manufacturing platform operating, demander publish orders while provider provide resources, then they communicate with each other, arrange the resources to perform tasks that decomposed by orders.
-Finally, product is produced and delivered to the demander.
+Before the design of the ecosystem, we specify some basic concepts: 
+\begin{compactitem}
+	\item Provider: the individual who provide resource;
+	\item Resource: the basic task process object with renewable capacity and unique type;
+	\item Demander: the individual who publish order that contain bunch of tasks;
+	\item Order: the task bundle like a project;
+	\item Task: the basic object need to be processed with certain type and capacity of resource;
+	\item Task-part: virtual segmentation unit of one task;
+	\item Product: the perform result of task;
+	\item Platform: the place where individual interact with other and environment.
+\end{compactitem}
+
+With the cloud manufacturing platform operating, demander publish order while provider provide resource, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
 Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
-\item Users/Customers,
-\item Application providers and
-\item Physical resource providers.
+\item users/customers,
+\item application providers and
+\item physical resource providers.
 \end{inparaenum}
-Inspired by the such model, we design the original mode shown in \autoref{fig:originmode} as the basis for the operating of the platform.
+Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
 \begin{figure}[htbp]
@@
 \end{figure}
-In this mode, individual in each group execute activities that interact with others with object flow(full lines) and information flow(dashed lines).
-As the start of manufacturing activities procedure, the demander publish orders that can be depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations.
-Each task needs to performed with pre-determined configuration of resources, hence, after the response and assign procedure, the selected resource cannot start to process the task until all of other selected resources by this task are ready, we call this procedure as resource cooperating and what each resource actually process is the task part.
-Finally product will be delivered to demander after the process and assembly of these parts, then the review of the product will change the rank value of the selected resource owners.
-Task part is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider them as task parts.
-A little more about the cooperation procedure, this procedure is necessary because the capacity limit of resources and task part should be processed simultaneously to make sure that the task is being processed with required resource capacities.
-We call the task part is active when being processed, semi-active when resource is waiting for synchronization, inactive when the part is just assigned to the job list.
+In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines).
+The demander publish order that can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation.
+Each task needs to be performed with pre-determined configuration of resources.
+Hence, even after response and assign procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts.
+Product, the performance result after the process and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.
+Cooperation procedure is necessary because of resource capacity is limited, but task-parts belonging to one task should be processed simultaneously to make sure the required resource capacities are available.
+We call the task-part is active when being processed, semi-active when selected resource is cooperating, inactive when this part is just assigned to the job queue.
 
@@
 \begin{compactitem}
-\item Each single task should be assembled by part according to the pre-determined resources configuration, and these parts should be processed simultaneously;
-\item Since the cooperation, the quality of product is determined by the worst quality part of produced by selected resource;
-\item Resource are renewable that the available capacity will be return when the process procedure finished;
+\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
+\item The quality of product is determined by the worst quality of the selected resource;
+\item Resource are renewable that the available capacity will be return to when the process procedure finished;
 \item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
 \item Cooperate and process procedure cannot be interrupted;
-\item Provider can only schedule task part that in inactive status. 
+\item Provider can only schedule task-parts in inactive status. 
 \end{compactitem}
-These assumptions are suitable for original mode, in other extension mode, some of the assumptions will be modified.
+These assumptions are suitable for the original mode, while in other extension, some of the assumptions will be modified.
 
@@
     \multicolumn{2}{|l|}{} \\
-	$o_i$ & Order that come with demander \\
-	$\mathcal{T}_i$ & Task set of $o_i$ \\
-	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
+	$\mathcal{T}_i$ & Order that come with demander, who can be quired by $F(\cdot)$ \\
+	$t_{ij}$ & Task belongs to $\mathcal{T}_i$, $t_{ij}\in\mathcal{T}_i$ \\
 	$p_{ij}$ & Process duration of $t_{ij}$\\
 	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
-	$r_i$ & Release time of $o_i$\\
+	$r_i$ & Release time of all $t_{ij}\in\mathcal{T}_i$\\
 	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
-	$f_{i}$ & Finish time of $o_i$\\
-	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
-	$mr_k$ & Resource that come with provider \\
-	$\delta_k$ & Product quality produced via resource $mr_k$ \\
+	% $f_{i}$ & Finish time of $\mathcal{T}_i$\\
+	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assign procedure\\
+	$mr_k$ & Resource that come with provider, who can be quired by $F(\cdot)$ \\
+	$\delta_k$ & Task-part quality produced via resource $mr_k$ \\
 	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
@@
 	$\mathcal{G}_{k,\tau}$ & The set of active job of $mr_k$ at $\tau$ \\ 
-	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
-	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
-	$\mathcal{A}$ & Resource type set \\
-	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
-	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
+	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule at $\tau_0$ . \\
+	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule at $\tau_0$. \\
+	% $\mathcal{A}$ & Resource type set \\
+	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$\\ %, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
+	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$, $\alpha\in\mathcal{A}_{ij}$\\
 	$sc_l$ & Service-call generated by provider\\
@@
 	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
-	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
+	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ \\ %, $\mathcal{A}_l\subset\mathcal{A}$\\
 	$ms_l$ & Service that generated after the finish of $sc_l$\\
@@
 	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
-	$q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$\\
+	$q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$,$\alpha\in\mathcal{A}_{l}$\\
 	$\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\
@@
 \end{table}
+Since demander and provider continuous arrives, there is no upper bound of the subscripts 
+$(i,j,k,l,\alpha)$. when in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.
 % \vspace{-2.5em}
@@
 \label{ssub:master_plam}
-A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
-First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors that come along within order and it can be added in the schedule procedure.
+A single order consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
+First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
 Second, performing the tasks requires resources with limited capacities.
-Third, resources cooperation requires all the task parts in active status.
-A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform.
-While being processed via resource cooperation, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$.
-Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$.
-This plan is much like the settings in resource-constrained project scheduling problem\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.
+Third, resources cooperation requires all the task-parts in active status.
+A single resource($mr_k$) belongs to only one type.
+While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$.
+Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$.
+This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.
 % subsubsection master_plan (end)
@@
 \label{sub:interactions_and_decisions}
-\subsubsection{Response for type matched task}
+\subsubsection{Provider response for type matched task}
 \label{subs:Response_for_type_matched_task}
-Provider makes decision at time $\tau\ge r_i$ to response task if the belonged resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
+Provider makes decision at time $\tau\ge r_i$ to response task if the belonging resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
 If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$.
-If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$ , the available capacity will be returned back after the finish of $t_{ij}$ part.
+If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$, the available capacity will be returned back to after the finish of $t_{ij}$ part.
 
-\subsubsection{Select from resource candidates}
+\subsubsection{Demander select from resource candidates}
 \label{subs:select_resource_candidates}
-Demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
-W.o.l.o.g, we suppose at time period $\tau \ge r_i$, the decision making of demander can be described as follows:
+Demander make decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
+Without loss of generality, we suppose at time $\tau \ge r_i$, the decision making of demander can be described as follows:
 \begin{equation}
@@
 The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length.
-\autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type of required configuration.
+\autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type.
 
-\subsubsection{Assign in selected resource} % (fold)
+\subsubsection{Provider assign task-part in selected resource} % (fold)
 \label{subs:assign_in_select_resource}
-If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ or $\mathcal{L}_{k,\tau}$ according to:
-\begin{subnumcases}{}
-\mathcal{H}_{k,\tau} := \mathcal{H}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \label{eq:addtobuffer}\\
-\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
-\end{subnumcases}
-
-If all the part of $t_{ij}$ are in type matched resources' $\mathcal{H}_{k,\tau}$, then these providers will change all the task part status from semi-active to active and add $t_{ij}$ to their $\mathcal{G}_{k,\tau}$.
+If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$, or to  $\mathcal{L}_{k,\tau}$ otherwise.
+% \begin{subnumcases}{}
+% \mathcal{H}_{k,\tau} := \mathcal{H}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \label{eq:addtobuffer}\\
+% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
+% \end{subnumcases}
+If all the part of $t_{ij}$ are in semi-active status, then these providers will change all the task-part status from semi-active to active and add $t_{ij}$ to $\mathcal{G}_{k,\tau}$.
 % subsubsection assign_in_selected_resource (end)
@@
 \label{sub:incubation_mode}
-Incubation mode is one extension mode for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resource with certain quota in a contract.
-Manufacturing service will be incubated as shown in \autoref{fig:serviceincubatemode}.
+Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperate and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.
 \begin{figure}[htbp]
@@
 \end{figure}
-After the finish of task part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.
+After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.
 
-The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance and each required resource type can also be cooperated by different resources, which means after the performance of service-call, capacity of selected resource will not be returned to.
-The product of service-call is the service, which is actually a contract of resources that may come from any provider in the system, it's possible for more than one resource with same type to make contribute to the formation of service.
-No more cooperation and assembly are part of pros of service and product quality will no more restricted to the worst quality of resources since the complementary effect, while the cons of service include that it can only perform  corresponding configured task.
+The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call.
+The process result of one service-call is manufacturing service, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service.
+No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
 Now we can mark task and service-call as job, resource and service as machine.
 
-\subsubsection{Response for type matched job} % (fold)
+\subsubsection{Provider response for type matched job} % (fold)
 \label{ssub:response_in_type_matched_resource}
@@
 
-\subsubsection{Select from machine candidates} % (fold)
+\subsubsection{Demander select from machine candidates} % (fold)
 \label{ssub:selection_in_resource_candidates_for_service_call}
-Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
+Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
 
@@
 \suspend{asparaenum}
-
-The decision making of select from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, and the difference is that the every part of $\bm{l}_{\alpha}$ in decision variable $\bm{l}$ here is also a set of selected resources followed by \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
+Provider of $sc_l$ select resource from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, but the difference is that the $\bm{l}_{\alpha}$ here is also a set of selected resources with type $\alpha$, $\bm{l}_{\alpha}$ is subset of decision variable $\bm{l}$.
+Selected resources capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
 \begin{subnumcases}{}
@@
 \suspend{asparaenum}
-
-This situation implies that the resource candidates are not enough while there exists service candidates, demander can just select service. 
+This situation implies that the resource candidates are not enough and there exists service candidates. 
 \begin{equation}
@@
 
-Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low waiting queue length.
+Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length.
 \autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.
@@
 \end{asparaenum}
-
 In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one.
@@
 
-Similar to other situations, \autoref{eq:combaim} is a a multi-objective function that aims at high quality, high rank and low waiting queue length.
+Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length.
 \autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate procedure.
@@
 
-\subsubsection{Assign in selected machine} % (fold)
+\subsubsection{Provider assign task to selected machine} % (fold)
 Apart from $mr_k$ assign $t_{ij}$ when selected as we explained in \autoref{subs:assign_in_select_resource}, there are 2 other cases in incubation mode:
@@
 \suspend{asparaenum}
-
-If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict than that in \autoref{eq:addtobuffer}, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
+If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict than that in \autoref{subs:assign_in_select_resource}, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
 Then, the provider of $mr_k$ should change the predecessor set:
@@
 \end{asparaenum}
-Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence:
-\begin{subnumcases}{}
-\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
-\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
-\end{subnumcases}
+Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.
+% \begin{subnumcases}{}
+% \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
+% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
+% \end{subnumcases}
 
@@
 
-\subsection{Schedule the jobs in machine} % (fold)
+\subsection{Provider schedule the jobs in machine} % (fold)
 \label{sub:schedule_the_jobs_in_machine}
-In order to enhance the user rate, provider will schedule the inactive jobs on their machines.
+In order to reduce the idle rate, provider will schedule the inactive jobs on their machines.
 Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
@@
 
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will help describe the setting more clearly.
-
-This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when each of  its part are in semi-activate status, the shadow in the figure shows the waiting period between the status transition from semi-activate to active.
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
+This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transition.
 Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
@@
 
-A schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
+In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
 Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched.
@@
 
-The schedule aim for each resource is to minimum the maximum delay of jobs \autoref{eq:scheduleaim}.
+The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs.
 \autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself.
@@
 \label{sub:outsource_mode}
-Outsourcing mode is one extension mode for the original mode and will be active when incubation mode is on for only service can perform this procedure. As shown in \autoref{fig:outsourcemode}, 
+Outsourcing mode is one extension on the original mode and will be active when incubation mode is on that only service can perform this procedure. As shown in \autoref{fig:outsourcemode}, 
 \begin{figure}[htbp]
@@
 \end{figure}
-the idea of outsourcing for service is to republish active or inactive task to platform again to reduce queue length to enhance the probability to be selected by new tasks.
-For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status will decrease.
-This decision highly depends on the estimate of performance status in other resources and services.
+the idea of outsourcing for service is to republish active or inactive task to platform again in order to reduce its job queue length to enhance the probability to be selected by new tasks.
+For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status decreases.
+This decision highly depends on the estimation of other resources and services' performance status.
 Outsourcing mode makes it possible to paralleled process one job.
@@
 \label{sub:metabolism mode}
-Metabolism mode is one extension mode for the original mode that control the number of individual in the system by both restrict the arrival and eliminate the current members.
+Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members.
 As shown in \autoref{fig:metabolismmode},
@@
 
-Platform restrict the arrival new machine by block the registration, eliminate the current machine by their quality and owner's rank.
-Rank value is initialized to 0 and will be changed by demander's review after the finish of task as:
+Platform restrict the arrival of new machine by block the registration, eliminate the current machine by their quality and owner's rank.
+Rank value is initialized to $0$ and will be changed by demander's review after the finish of task:
 \begin{subnumcases}{}
@@
 \end{subnumcases} 
-Rank value changing with regard to service can be determined easier:
+The change of rank value can be determined by:
 \begin{equation}
@@
 
-\subsection{Tricky problem} % (fold)
-\label{sub:tricky_problems}
-Even though the schedule procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
+% \subsection{Tricky problem} % (fold)
+% \label{sub:tricky_problems}
+% Even though the schedule procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
 Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock},
-\begin{figure}[htbp]
-	\centering
-	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
-	\caption{Simple illustration of job lock problem}
-	\label{fig:joblock}
-\end{figure}
-$t_{i2}$ is semi-active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is semi-active in $mr_1$ and inactive in $mr_2$, however, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and they will block the other tasks from being processed.
+% \begin{figure}[htbp]
+% 	\centering
+% 	\resizebox{.75\textwidth}{!}{\input{figures/job-lock}}
+% 	\caption{Simple illustration of job lock problem}
+% 	\label{fig:joblock}
+% \end{figure}
+% $t_{i2}$ is semi-active in $mr_2$ and inactive in $mr_1$, while $t_{i1}$ is semi-active in $mr_1$ and inactive in $mr_2$, however, there is no more space for inactive tasks to stack in, so no matter how long the resource will wait, $t_{i1}$ and $t_i2$ will not be processed and they will block the other tasks from being processed.
 
-One feasible solution for the job-lock problem is to add the semi-inactive task to the predecessor set of all the other tasks in the same inactive queue list as soon as the status changes.
+% One feasible solution for the job-lock problem is to add the semi-inactive task to the predecessor set of all the other tasks in the same inactive queue list as soon as the status changes.
 % subsection tricky_problems (end)

### 2016-09-06 discussion.tex
改版

--- 2015-09-23 discussion.tex
@@
 % !TEX root = Eco-Model.tex
-\section{Discussion} % (fold)
-\label{sec:discussion}
+\section{Limitations, and Future Research} % (fold)
+\label{sec:contributions_limitations_and_future_research}
+We only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions.
+The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.
+% section contributions_limitations_and_future_research (end)
 
-% section discussion (end)
+\section{Acknowledgments} % (fold)
+\label{sec:acknowledgments}
+This work is supported by the National Natural Science Foundation of China (No. 71571161), and the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101). 
+% section acknowledgments (end)

### 2016-09-06 figures/origin_mode.tex
modify
改版

@@
 % First row:
-\node (order) {Demander};& \node (task) [square]{Publish Tasks}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
+\node (order) {Demander};& \node (task) [square]{Publish Orders}; &  & \node (select) [square]{Selection}; & & &  \node (finish) {Product}; \\
 \node (start1) {}; & & & & & & \node (stop1) {}; \\
@@
 \node (start2) {}; & & & & & & \node (stop2) {}; & \\
-\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Process Task Part};  &\\
+\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response for Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Processing Task-part};  &\\
 };

### 2016-09-06 head.tex
改版

@@
 
-\author[label1]{Shengkai Chen}
-\author[label1]{Shuiliang Fang}
+\author[add1]{Shengkai Chen}
+\author[add1,add2]{Shuiliang Fang\corref{cor1}}
+% \ead{me_fangsl@zju.edu.cn}
 % \address[label1]{ZJU}
 % \address[label1]{Address One}
-\address[label1]{Zhejiang University, Institute of manufacturing engineering and automation, Hangzhou City, Zhejiang Province, China}
+\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
+\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
+% \author[a,b,*]{Third Author}
 
+% \address[a]{First affiliation, Address, City and Postcode, Country}
+% \address[b]{Second affiliation, Address, City and Postcode, Country}
 % \fntext[label4]{Small city}
 
+\cortext[cor1]{Corresponding author. Tel.: +86-135-8880-3980; Email: me\_fangsl@zju.edu.cn}
+
 \begin{abstract}
-In Cloud Manufacturing, individuals engage in manufacturing business through the well-designed platform framework, where provider provide manufacturing resource for demander to search and purchase it as product.
-This business model allows centralized management of distributed massive manufacturing resources, and could potentially reduce the idle rate of those resources.
-However, in the manufacturing ecosystem constructed, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating mode, makes it hard to meet demander's need.
-Meantime, in order to enhance the cash flow rate, provider make decisions to enhance the use rate of their own resources.
-The relationship among participants in this ecosystem become more complicated than that in normal manufacturing system, since the integrated advanced technologies within cloud environment makes it possible to let one individual make decisions depend on the surroundings and other's decisions.
-Hence, in this paper, we designed an original operation mode with 3 extension options for the cloud manufacturing ecosystem to support some decision makings for individuals and the platform operator.
-With the help of Repast Simphony, we designed an agent-based model and experiment to simulate these operation modes with any combinations to validate the effectiveness of them.
-As the experiment result, incubation mode can help reduce the waiting of job and accelerate the process velocity of resources, outsourcing mode reduce the job queue length but not as much as incubation mode and requires more resources, metabolism mode require lower resources than the other modes and will slow resource process velocity a little.
-The combination of incubation and metabolism mode is ideal for platform operators to maintain the manufacturing ecosystem.
+In cloud manufacturing, individuals engage in manufacturing business through the well-designed platform, where provider provide manufacturing resource for demander to search and purchase it.
+This business model allows platform operator to manage distributed massive manufacturing resources, which may help provider reduce the idle rate of their resources.
+However, in such manufacturing ecosystem, the heterogeneity attribute of resource makes it tough to classify them, and the chaotic operation mode makes it hard to meet demander's need.
+Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others' with the help of integrated advanced technologies.
+Thus, in this paper, we designed an original operation mode with 3 extensions for the cloud manufacturing ecosystem to help describe some decision makings in individuals and the platform operator.
+With the help of Repast Simphony, we designed an agent-based simulation model and an experiment to validate the effectiveness of these operation modes.
+The experiment result shows: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little.
+The combination of incubation and metabolism mode is one ideal mode to maintain the manufacturing ecosystem with.
 \end{abstract}
@@
 \end{keyword}
+% \belowfrontmatterskip0pt

### 2016-09-06 intro.tex
改版

--- 2016-08-30 intro.tex
@@
 \section{Introduction}
-With the emergence of cloud manufacturing, the relationship among participants in the manufacturing system become more complicated then ever before since every single ind
+The relationship among individuals in cloud manufacturing system become more complicated than that in normal manufacturing system, since the integrated advanced technologies makes it possible to let one individual make decisions depend on the surroundings and others'.
+Demander prefer high quality performance while provider prefer high use rate of their resource, the cloud platform operator prefer lower amount of registered resource when dealing with almost arriving needs for an easier maintenance.
+These preferences stimulate the emergence of good service pattern that will lead to the evolution of manufacturing pattern in the cloud manufacturing ecosystem.
+Hence, it's important to identify good operation mode that help the evolution.
 
-In this paper, we constructed a
-
-proposed 3 operation modes as options for platform to operate with named metabolism mode, incubation mode and outsourcing mode.
+In this paper, we designed an original operation mode to describe the basic decision makings in cloud manufacturing ecosystem, then we proposed 3 extensions named metabolism mode, incubation mode and outsourcing mode.
+Finally, we deigned an experiment to validate these synthetic operation modes in an agent-based simulation method.

### 2016-09-06 result.tex
改版

@@
 
-Entities in the manufacturing ecosystem we designed above have these traits: \begin{inparaenum}[1)]
+Individuals in the manufacturing ecosystem are: \begin{inparaenum}[1)]
 \item autonomous and self-directed, 
@@
 \item self-contained.
-\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study of the complex system.
-With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments on it.
+\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study in such complex system.
+With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments with it.
 
@@
 
-We design experiments to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
+We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
 
@@
 \label{ssub:result_and_analysis}
-All the experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
-After bunch of experiments with different random seeds, we discovered some laws in operation mode.
-Take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
+Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
+After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
 \begin{figure}[htbp]
@@
 \end{table}
-we find: \begin{inparaenum}[1)]
+we find: \begin{asparaenum}[1)]
 \item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22.
-Full lines are not much above dotted lines in $N_F$ means that task processing velocity will be a little slower with the metabolism, exception also appears in Mode 22.
-\item $L$ and $N_T$ both represent the queue length of jobs, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do accelerate the processing velocity.
-\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the waiting of job a little.
+Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22.
+\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
+\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.
 \item There is no big difference among all the 6 modes in rank change.
-Provider in metabolism mode will get lower rank value for they cannot stay in the system for long, the longer stay in the system, the higher rank value provider will get.
-Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without incubation mode.
-\item Mode 22 is a very special mode that reached the balance in 6000 ticks, that the number of provider and resource changes little with time goes by.
-Because our experiment setting comply \autoref{eq:balance}, the coming need capacity velocity is less than the coming capacity, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism itself is full of uncertainty and it's hard to predict when other metabolism related mode will get the balance.
-\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is the easiest combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
-\end{inparaenum}
+Provider in metabolism mode will get lower rank value for they cannot stay in the system for a longer time to get higher rank value.
+Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast if without incubation mode.
+\item Mode 22 is a very special mode that reached the balance within 6000 ticks, that the number of provider and resource changes little with time goes by.
+Because our experiment setting comply \autoref{eq:balance}, the coming need capacity rate is lower than the coming capacity rate, Mode 12,22,32 will finally reach balance in the long run theoretically, but the appearance of service-call and metabolism mode itself is full of uncertainty, thus it's hard to predict when other metabolism related mode will reach the balance.
+\item With the average data value shown in \autoref{tab:averagevalue}, metabolism with incubation but not with outsourcing mode is one ideal combine mode to maintain the system, resource will self-configured and controlled to justly meet the task need.
+\end{asparaenum}
 

### 2016-09-06 review.tex
改版

--- 2016-08-29 review.tex
@@
 % !TEX root = Eco-Model.tex
-\section{Literature review and background} % (fold)
+\section{Review on cloud manufacturing} % (fold)
 \label{sec:literature_review}
-\subsection{Cloud manufacturing and its operation mode} % (fold)
-\label{sub:cloud_manufacturing review}
+
 % This definition is quite abstract and thus despite its corretness not very useful.
 
-Review on 1. Cloud manufacturing mode (any) study 
-2. res ser combination and decision making
-3. rank and review ecosystem (system changing)
-4. manufacturing system simulation
+In cloud manufacturing context, platform operator can manage  manufacturing service that encapsulated with distributed manufacturing resources intensively with appropriate business model\cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build the cloud manufacturing platform or system framework\cite{Tao2012,Valilai2013}, Lv use list of views to depict this multi-layer architecture\cite{LvJuly312012-Aug.22012}.
 
-In cloud manufacturing context, centralized management for manufacturing services that encapsulated with distributed manufacturing resources can be realized by an appropriate business model\cite{Xu2012}
+Servitization is the key philosophy to operate cloud manufacturing\cite{li2010cloud}, service can be created statically which come along with provider\cite{Tao2012} or can be created dynamically according to task pattern, such method as `Multi-Composition for Each Task'\cite{Liu2013} that combines incompetent service into a whole, service can also be created by AI planning-based automatic composition framework\cite{OhJan.-March2008}.
 
-Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (\cite{Tao2012}\cite{Valilai2013}
-
-Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
-\item Users/Customers,
-\item Application providers and
-\item Physical resource providers.
-\end{inparaenum}
-
-\subsection{Study background} % (fold)
-\label{sub:background}
-
-here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
-\begin{itemize}
-	\item order
-	\item task correspond to capacity
-	\item resource
-	\item capacity is the function of a resource. like quantity
-	\item service is the bundle of capacities. the proportion of the capacities.
-	\item 
-\end{itemize}
-
-Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment
-
-As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.
-
-Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.
+Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}.
+In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
+segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}.
+Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered that research trends are Internet and cloud based situation.
 

### 2016-09-08 design.tex
draft for cfp

@@
 \label{ssub:assumptions_nomenclature}
-To scope our research, we make some assumptions as follows:
+To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
 \begin{compactitem}
@@
 \end{compactitem}
-These assumptions are suitable for the original mode, while in other extension, some of the assumptions will be modified.
 
@@
 Since demander and provider continuous arrives, there is no upper bound of the subscripts 
-$(i,j,k,l,\alpha)$. when in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.
+$(i,j,k,l,\alpha)$. When in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.
 % \vspace{-2.5em}
@@
 
-\subsection{Provider schedule the jobs in machine} % (fold)
+\subsubsection{Provider schedule the jobs in machine} % (fold)
 \label{sub:schedule_the_jobs_in_machine}
@@
 \end{figure}
-Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
+Therefore, we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
 
 Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
-This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transition.
+This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transitions.
 Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
@@
 
-In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
+% In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
 Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched.
@@
 
-\begin{equation}
-\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
-\end{equation}
-\begin{numcases}{\text{s.t.}}
-L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
-f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
-G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
-f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
-\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
-f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
-\end{numcases}
+% \begin{equation}
+% \min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
+% \end{equation}
+% \begin{numcases}{\text{s.t.}}
+% L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
+% f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
+% G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
+% f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
+% \sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
+% f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
+% \end{numcases}
 
-The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs.
+% The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs.
 \autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself.
@@
 \autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
-Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
-solved with mixed integer programming (MIP) techniques.
+% Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
+% solved with mixed integer programming (MIP) techniques.
 
@@
 \end{figure}
-machine scarcity is the control variable that can be defined as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$ for resource in type $\alpha$ and the sum of task minus the sum of service in each type.
+we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.
 

### 2016-09-08 result.tex
draft for cfp

@@
 \end{table}%
-We assume provider and demander are arriving as the poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, we make sure that:
+We assume provider and demander are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, and we make sure that:
 \begin{equation}
@@
 
-We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
+We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, and each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{Data/out.pdf}
+    \includegraphics[width=\textwidth]{Data/out.eps}
     \caption{Observed variable change with time}
@@
 Full lines are not much above dotted lines in $N_F$ means that task finish rate will be a little lower with the metabolism, exception also appears in Mode 22.
-\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ meas that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
+\item $L$ and $N_T$ both represent the job queue length, triangle and square line turned lower in $L$ means that incubation mode can help reduce the waiting of job, these two type of line above the circle line means the incubation mode do reduce the resource idle rate.
 \item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsourcing mode needs more resources to operate and can only reduce the job queue length a little.

### 2016-09-08 review.tex
draft for cfp

@@
 
-Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}.
+Simulation approach have been widely used in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}.
 In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine

### 2016-09-08 Data/plot.py

@@ -5,8 +5,8 @@ import pandas as pd
 import pylab as pl
 from scipy import interpolate 
 
-seed = '776189616'
-t = [(x+1)*50 for x in xrange(120)]
+seed = '1212'
+t = [(x+1)*50 for x in xrange(240)]
 
 def value(seed,mode,file,loc):
 	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',dtype='string',delimiter=',')
@@ -39,7 +39,7 @@ def myplot(x,style):
 
 styles = ['b-o','g:o','r-s','c:s','k-^','m:^']
 modes = ['11','12','21','22','31','32']
-plt.figure(figsize=(15,15))
+plt.figure(figsize=(16,15))
 # tck = interpolate.splrep(t,N_T)
 # tck_2 = interpolate.splrep(t)
 # x_bspline = interpolate.splev(t,tck)
@@ -105,7 +105,8 @@ for style in styles:
 
 plt.legend(['Mode 11','Mode 12','Mode 21','Mode 22','Mode 31','Mode 32'],loc='center')
 
-plt.savefig('out.pdf', transparent=True, bbox_inches='tight', pad_inches=0)
+plt.savefig('out_new.pdf', transparent=True, bbox_inches='tight', pad_inches=0)
+plt.savefig('out_new.eps', transparent=True, bbox_inches='tight', pad_inches=0)
 
 
 def mymean(seed,mode,file,loc):

### 2016-09-08 design.tex
modify the abstract

--- 2016-09-06 design.tex
@@
 \label{ssub:master_plam}
-A single order consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
-First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
+A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
+First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
 Second, performing the tasks requires resources with limited capacities.
 Third, resources cooperation requires all the task-parts in active status.
-A single resource($mr_k$) belongs to only one type.
+A single \textbf{resource}($mr_k$) belongs to only one type.
 While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$.
@@
 
-The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call.
-The process result of one service-call is manufacturing service, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service.
+The first thing of incubation is to publish a job named \textbf{service-call}, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call.
+The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service.
 No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
-Now we can mark task and service-call as job, resource and service as machine.
+Now we can classify task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.
 
@@
 
-\subsection{Provider schedule the jobs in machine} % (fold)
-\label{sub:schedule_the_jobs_in_machine}
-In order to reduce the idle rate, provider will schedule the inactive jobs on their machines.
-Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
-Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
-\begin{figure}[htbp]
-	\centering
-	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
-	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
-	\label{fig:simplejoblist}
-\end{figure}
-Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
-
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
-This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transition.
-Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
-Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.
-
-\begin{table}[htbp]
-  \centering
-  \scriptsize
-  \caption{Simple job configuration}
-    \begin{tabular}{cccccc}
-    \toprule
-    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
-    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
-    \midrule
-    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
-    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
-    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
-    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
-    $t_5$ & 1 & 0 & 3 & 2 & 3\\
-    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
-    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
-    \bottomrule
-    \end{tabular}%
-  \label{tab:simplejobconfiguration}%
-\end{table}%
-\begin{figure}[htbp]
-	\centering
-	\normalsize
-	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
-	\caption{Simple instance schedule chart with 4 resources in 3 different types}
-	\label{fig:scheduleChart}
-\end{figure}
-
-In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
-Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched.
-The schedule model is:
-
-\begin{equation}
-\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
-\end{equation}
-\begin{numcases}{\text{s.t.}}
-L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
-f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
-G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
-f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
-\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
-f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
-\end{numcases}
-
-The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs.
-\autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself.
-\autoref{eq:alreadydefined} means that the finish time of activate job is determined.
-\autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
-Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
-solved with mixed integer programming (MIP) techniques.
-
-% subsection schedule_the_jobs_in_machine (end)
-
 \subsection{Outsourcing mode} % (fold)
@@
 \end{figure}
-machine scarcity is the control variable that can be defined as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$ for resource in type $\alpha$ and the sum of task minus the sum of service in each type.
+we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.
 
 Platform restrict the arrival of new machine by block the registration, eliminate the current machine by their quality and owner's rank.
-Rank value is initialized to $0$ and will be changed by demander's review after the finish of task:
-\begin{subnumcases}{}
-rank := rank +
-\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
-\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} & \\
-\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
-\end{subnumcases} 
-The change of rank value can be determined by:
-\begin{equation}
-	rank := rank + \frac{ \left(\sum_{q\in\bm{q}_l}p_{ij}\cdot q \right)\left( \Delta_l -\gamma_{ij}\right) }{ e^{\left( f_{ij} - p_{ji} -r_{ij} \right)} }
-\end{equation}
+
+% Rank value is initialized to $0$ and will be changed by demander's review after the finish of task:
+% \begin{subnumcases}{}
+% rank := rank +
+% \frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
+% \delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} & \\
+% \delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
+% \end{subnumcases} 
+% The change of rank value can be determined by:
+% \begin{equation}
+% 	rank := rank + \frac{ \left(\sum_{q\in\bm{q}_l}p_{ij}\cdot q \right)\left( \Delta_l -\gamma_{ij}\right) }{ e^{\left( f_{ij} - p_{ji} -r_{ij} \right)} }
+% \end{equation}
 
 % subsection controlling_rules (end)
+
+\subsection{Provider schedule the jobs in machine} % (fold)
+\label{sub:schedule_the_jobs_in_machine}
+In order to reduce the idle rate, provider will schedule the inactive jobs on their machines.
+Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
+Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
+\begin{figure}[htbp]
+	\centering
+	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
+	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
+	\label{fig:simplejoblist}
+\end{figure}
+Therefore, we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
+
+\begin{table}[htbp]
+  \centering
+  \scriptsize
+  \caption{Simple job configuration}
+    \begin{tabular}{cccccc}
+    \toprule
+    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
+    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+    \midrule
+    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
+    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
+    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
+    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
+    $t_5$ & 1 & 0 & 3 & 2 & 3\\
+    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
+    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
+    \bottomrule
+    \end{tabular}%
+  \label{tab:simplejobconfiguration}%
+\end{table}%
+
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
+This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transitions.
+Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
+Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.
+
+\begin{figure}[htbp]
+	\centering
+	\normalsize
+	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
+	\caption{Simple instance schedule chart with 4 resources in 3 different types}
+	\label{fig:scheduleChart}
+\end{figure}
+
+In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
+Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched.
+The schedule model is:
+
+\begin{equation}
+\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
+\end{equation}
+\begin{numcases}{\text{s.t.}}
+L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
+f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
+G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
+f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
+\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
+f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
+\end{numcases}
+
+The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs.
+\autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself.
+\autoref{eq:alreadydefined} means that the finish time of activate job is determined.
+\autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
+Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
+solved with mixed integer programming (MIP) techniques.
+
+% subsection schedule_the_jobs_in_machine (end)
 

### 2016-09-08 head.tex
draft for cfp
modify the abstract

@@
 % \address[label1]{Address One}
+\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
 \address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
-\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
 % \author[a,b,*]{Third Author}
@@
 \begin{abstract}
-In cloud manufacturing, individuals engage in manufacturing business through the well-designed platform, where provider provide manufacturing resource for demander to search and purchase it.
-This business model allows platform operator to manage distributed massive manufacturing resources, which may help provider reduce the idle rate of their resources.
-However, in such manufacturing ecosystem, the heterogeneity attribute of resource makes it tough to classify them, and the chaotic operation mode makes it hard to meet demander's need.
-Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others' with the help of integrated advanced technologies.
-Thus, in this paper, we designed an original operation mode with 3 extensions for the cloud manufacturing ecosystem to help describe some decision makings in individuals and the platform operator.
-With the help of Repast Simphony, we designed an agent-based simulation model and an experiment to validate the effectiveness of these operation modes.
-The experiment result shows: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little.
-The combination of incubation and metabolism mode is one ideal mode to maintain the manufacturing ecosystem with.
+In cloud manufacturing, individuals engage in manufacturing business through a well-designed platform, where the operator is able to manage distributed massive manufacturing resources. 
+Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others'.
+In this paper, we designed an original operation mode with 3 extensions named incubation, outsourcing and metabolism for the ecosystem.
+We designed an agent-based simulation model to validate the effectiveness of these modes.
+Experiment result shows evolution in ecosystem: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little.
+
 \end{abstract}
@@
 Cloud manufacturing ecosystem \sep
-Resource servitization and optimization\sep
+Decision making\sep
 Operation mode\sep
-Manufacturing evolution\sep
+Ecosystem evolution\sep
 Agent-based simulation

### 2016-09-09 intro.tex
revision from Tao's comment

--- 2016-08-30 intro.tex
@@
 \section{Introduction}
-With the emergence of cloud manufacturing, the relationship among participants in the manufacturing system become more complicated then ever before since every single ind
+The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information.
+Demanders prefer high quality of performance, while providers prefer high use rate of resource.
+A cloud platform operator prefers a fewer amount of registered resource when dealing with almost arriving needs for an easier maintenance.
+These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem.
+Hence, it's important to identify a suitable operation mode to meet most of individuals' preference.
 
-In this paper, we constructed a
-
-proposed 3 operation modes as options for platform to operate with named metabolism mode, incubation mode and outsourcing mode.
+In this paper, an original operation mode is designed to describe the basic decision-makings in cloud manufacturing ecosystem, then three extensions, namely metabolism mode, incubation mode and outsourcing mode are proposed.
+Finally, an experiment to validate these synthetic operation modes are designed using an agent-based simulation method.

### 2016-09-09 review.tex
revision from Tao's comment

--- 2016-09-06 review.tex
@@
 
-In cloud manufacturing context, platform operator can manage  manufacturing service that encapsulated with distributed manufacturing resources intensively with appropriate business model\cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build the cloud manufacturing platform or system framework\cite{Tao2012,Valilai2013}, Lv use list of views to depict this multi-layer architecture\cite{LvJuly312012-Aug.22012}.
+In cloud manufacturing context, platform operator can manage  manufacturing service that encapsulated with distributed manufacturing resources intensively with appropriate business model \cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build a cloud manufacturing platform or system framework \cite{Tao2012,Valilai2013}, Lv used the list of views to depict this multi-layer architecture \cite{LvJuly312012-Aug.22012}.
 
-Servitization is the key philosophy to operate cloud manufacturing\cite{li2010cloud}, service can be created statically which come along with provider\cite{Tao2012} or can be created dynamically according to task pattern, such method as `Multi-Composition for Each Task'\cite{Liu2013} that combines incompetent service into a whole, service can also be created by AI planning-based automatic composition framework\cite{OhJan.-March2008}.
+Servitization is the key philosophy to operate cloud manufacturing \cite{li2010cloud}.
+A  service can be created statically which comes along with a provider \cite{Tao2012}, or can be created dynamically according to task pattern, such method as `Multi-Composition for Each Task' \cite{Liu2013} that combines incompetent service as a whole.
+A service can also be created by AI planning-based automatic composition framework \cite{OhJan.-March2008}.
 
-Simulation approach have been widely use in manufacturing system on operations planning and scheduling, real-time control, operating polities, performance analysis\cite{Smith2003}.
-In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions\cite{Sabuncuoglu2003}, machine
-segmentation policies can be simulated in a combined MRP and Kanban production system\cite{Felberbauer9-12Dec.2012}.
-Mourtzis et al.\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practice and considered that research trends are Internet and cloud based situation.
+Simulation approach has been widely used in manufacturing systems on operation planning and scheduling, real-time control, operating policies, performance analysis \cite{Smith2003}.
+In operating policies field, scheduling policies can be tested with simulation performance under given machine conditions \cite{Sabuncuoglu2003}, machine
+segmentation policies can be simulated in a combined MRP and Kanban production system \cite{Felberbauer9-12Dec.2012}.
+Mourtzis et al.
+\cite{Mourtzis2015} explored a series of simulation-based solutions in industrial practices and concluded that research trends are in  Internet- and cloud-based situations.
 

### 2016-09-09 background.tex

@@
 
-platform model is about the part of decision making	agent of platform.
+platform model is about the part of decision-making	agent of platform.
 
@@
 
-user's model is the part of decision making agent of users.
+user's model is the part of decision-making agent of users.
 
@@
 
-the core is about the decision making all the time, individuals' decision making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution
+the core is about the decision-making all the time, individuals' decision-making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution
 
@@
 
-so, the topic here is the design of both decision making agents.
+so, the topic here is the design of both decision-making agents.
 % subsection the_evolution_of_manufacturing_ecosystem (end)

### 2016-09-09 design.tex

@@
 \label{sec:design_of_the_ecosystem}
-\subsection{Preliminaries} % (fold)
-\label{sub:preliminaries}
-Before the design of the ecosystem, we specify some basic concepts: 
+% \subsection{Preliminaries} % (fold)
+% \label{sub:preliminaries}
+Before introducing the design of the ecosystem, we specify some basic concepts:
 \begin{compactitem}
-	\item Provider: the individual who provide resource;
+	\item Provider: the individual who provides resource;
 	\item Resource: the basic task process object with renewable capacity and unique type;
-	\item Demander: the individual who publish order that contain bunch of tasks;
+	\item Demander: the individual who publishes orders that contain bunch of tasks;
 	\item Order: the task bundle like a project;
-	\item Task: the basic object need to be processed with certain type and capacity of resource;
+	\item Task: the basic object that needs to be processed with certain type and capacity of resource;
 	\item Task-part: virtual segmentation unit of one task;
-	\item Product: the perform result of task;
-	\item Platform: the place where individual interact with other and environment.
+	\item Product: the perform result of a task;
+	\item Platform: the place where individuals interact with other and ecosystem.
 \end{compactitem}
 
-With the cloud manufacturing platform operating, demander publish order while provider provide resource, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
-Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
+With the cloud manufacturing platform operating, demanders publish orders while provider provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
+Most recent researchers e.g.
+Wu et al.
+\cite{Wu2013}, describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
 \item users/customers,
@@
 Each task needs to be performed with pre-determined configuration of resources.
-Hence, even after response and assign procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts.
-Product, the performance result after the process and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.
+Hence, even after response and assignment procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts.
+Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.
 Cooperation procedure is necessary because of resource capacity is limited, but task-parts belonging to one task should be processed simultaneously to make sure the required resource capacities are available.
@@
 \item The quality of product is determined by the worst quality of the selected resource;
-\item Resource are renewable that the available capacity will be return to when the process procedure finished;
+\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
 \item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
-\item Cooperate and process procedure cannot be interrupted;
+\item Cooperate and processing procedure cannot be interrupted;
 \item Provider can only schedule task-parts in inactive status.
@@
 	% $f_{i}$ & Finish time of $\mathcal{T}_i$\\
-	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assign procedure\\
+	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assignment procedure\\
 	$mr_k$ & Resource that come with provider, who can be quired by $F(\cdot)$ \\
@@
 Since demander and provider continuous arrives, there is no upper bound of the subscripts
-$(i,j,k,l,\alpha)$. When in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.
+$(i,j,k,l,\alpha)$. When in scheduling procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.
 % \vspace{-2.5em}
@@
 \label{sub:interactions_and_decisions}
-\subsubsection{Provider response for type matched task}
+\subsubsection{Provider respond to type-matched task}
 \label{subs:Response_for_type_matched_task}
-Provider makes decision at time $\tau\ge r_i$ to response task if the belonging resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
-If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$.
-If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$, the available capacity will be returned back to after the finish of $t_{ij}$ part.
+A provider makes decision at time $\tau\ge r_i$ to respond  to task if the belonging resource $mr_k$ was type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
+If $A_{k,\tau} \ge q_{\alpha,ij}$, the provider will respond to the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$.
+If $mr_k$ is finally selected, available capacity of $mr_k$ will change to $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$.
+This available capacity will be restored back to after the finish of $t_{ij}$ part.
 
@@
 \label{subs:select_resource_candidates}
-Demander make decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
-Without loss of generality, we suppose at time $\tau \ge r_i$, the decision making of demander can be described as follows:
+A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
+Without loss of generality, we suppose at time $\tau \ge r_i$, the decision-making of demander can be described as follows,
 \begin{equation}
@@
 The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length.
-\autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type.
+\autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.
 
@@
 \label{sub:incubation_mode}
-Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperate and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.
+Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.
 \begin{figure}[htbp]
@@
 \end{figure}
-After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.
+After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
 
-The first thing of incubation is to publish a job named \textbf{service-call}, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call.
-The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service.
-No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
+The first thing of incubation is to publish a job named \textbf{service-call}, which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the performance of a service-call.
+The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources of a same type to make contributions to the formation of one service.
+No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
 Now we can classify task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.
 
-\subsubsection{Provider response for type matched job} % (fold)
+\subsubsection{Provider respond to type-matched job} % (fold)
 \label{ssub:response_in_type_matched_resource}
-Apart from $mr_k$ response for $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
+Apart from $mr_k$ respond to $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
 \begin{asparaenum}
-\item $mr_k$ response for $sc_l$
+\item $mr_k$ respond to $sc_l$
 \suspend{asparaenum}
-If $mr_k$ was type matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will response the service-call.
-If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be returned back even after the finish of $sc_l$ part.
+If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call.
+If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part.
 Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
 \resume{asparaenum}
-\item $ms_l$ response for $t_{ij}$
+\item $ms_l$ respond to $t_{ij}$
 \end{asparaenum}
-Service is task-oriented machine, so if type matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will response $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
+Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
 
@@
 Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length.
-\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate procedure.
+\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculation procedure.
 \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.
@@
 In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
-Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched.
+Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type-matched.
 The schedule model is:
@@
 % \label{sub:tricky_problems}
-% Even though the schedule procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
+% Even though the scheduling procedure exclude the interference of service-call, one tricky problem will occur that it will block some tasks from being processed.
 Suppose that $t_{i1}$ and $t_{i2}$ both need resource $mr_1$ and $mr_2$, as shown in \autoref{fig:joblock},

### 2016-09-09 discussion.tex

@@
 \label{sec:acknowledgments}
-This work is supported by the National Natural Science Foundation of China (No. 71571161), and the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101). 
+This work is supported by the National Natural Science Foundation of China (No.
+71571161), the National High Technology Research and Development Program of China (863 Program) (No.
+2015AA042101), and the Youth Funds of the Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province(No.
+2015QN01).
 % section acknowledgments (end)

### 2016-09-09 figures/origin_mode.tex

@@
 \node (start2) {}; & & & & & & \node (stop2) {}; & \\
-\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Response for Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Processing Task-part};  &\\
+\node (provider) {Provider};  & \node (resource) [square]{Provide Resources}; & \node (response) [square] {Respond to the Task}; & \node (add) [square]{Add to Candidates}; & \node (match) [square]{Assign Task}; & \node (process) [square] {Processing Task-part};  &\\
 };

### 2016-09-09 figures/scheduleChart.tex

@@
 \draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
-\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
-\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
+\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,4.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3.5cm) node{$t_4$};
+\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
 \draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};

### 2016-09-09 head.tex

@@
 
-\title{The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture
+\title{Operation Mode Study in Cloud Manufacturing Ecosystem
 %Cloud Manufacturing Ecosystem - Scheduling And Evolving
@@
 \author[add1]{Shengkai Chen}
-\author[add1,add2]{Shuiliang Fang\corref{cor1}}
+\author[add2,add1]{Shuiliang Fang\corref{cor1}}
+\author[add2,add1]{Tao Peng}
 % \ead{me_fangsl@zju.edu.cn}
@@
 
-\cortext[cor1]{Corresponding author. Tel.: +86-135-8880-3980; Email: me\_fangsl@zju.edu.cn}
+\cortext[cor1]{Corresponding author. Email: me\_fangsl@zju.edu.cn}
 
@@
 Cloud manufacturing ecosystem \sep
-Decision making\sep
+Decision-making\sep
 Operation mode\sep

### 2016-09-09 method.tex
start to describe the philosophy
scratch

@@
 
-core of the paper: agent simulation, decision making.
+core of the paper: agent simulation, decision-making.
 
@@
 \label{ssub:platform_agent}
-matching the 
-\begin{figure}
 
-\begin{tikzpicture}
-\begin{class}[text width=8cm]{Job}{0,0}
-    \attribute{needCapacity : Map}
-    \operation{lala(haha): void}
-\end{class}
-\end{tikzpicture}
-\caption{Test UML Diagram}
-
-\end{figure}
 % subsubsection platform_agent (end)
@@
 
-\subsubsection{Design philosopher} % (fold)
-\label{ssub:design_philosopher}
+\subsubsection{Design philosophy} % (fold)
+\label{ssub:design_philosophy}
 platform create demander and provider
@@
 
-% subsubsection design_philosopher (end)
+% subsubsection design_philosophy (end)
 
@@
 
-Decision making involves choosing some course of action among various alternatives. For a decision maker, fulfilling the con
+Decision-making involves choosing some course of action among various alternatives. For a decision maker, fulfilling the con
 
@@
 \label{sub:agent_based_modeling_and_simulation}
-\subsubsection{Agent design}
+\subsubsection{Agent Classes}
+\begin{asparaenum}
+\item User related
+\suspend{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/cUser}
+    \input{figures/cProvider}
+\input{figures/cDemander}
+    \end{tikzpicture}
+    \caption{User related classes}
+    \label{fig:userclassed}
+\end{figure}
+\resume{asparaenum}
+\item Job related
+\suspend{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/cJob}
+    \input{figures/cTask}
+    \input{figures/cServiceCall}
+    \end{tikzpicture}
+    \caption{Job related classes}
+    \label{fig:jobclassed}
+\end{figure}
+\resume{asparaenum}
+\item Machine related
+\end{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/cMachine}
+    \input{figures/cResource}
+    \input{figures/cService}
+    \end{tikzpicture}
+    \caption{Machine related classes}
+    \label{fig:machineclassed}
+\end{figure}
+\subsubsection{Behavior interface and classes}
+\begin{asparaenum}
+\item Assign behavior
+\suspend{asparaenum}
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/iAssignBehavior}
+    \input{figures/cServiceAssign}
+    \input{figures/cResourceAssign}
+    \end{tikzpicture}
+    \caption{Assign interface and related classes}
+    \label{fig:assigninterface}
+\end{figure}
 
-\subsubsection{Logical process}
+\resume{asparaenum}
+\item Process behavior
+\suspend{asparaenum}
 
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/iProcessBehavior}
+    \input{figures/cProcessInTask}
+    \input{figures/cProcessInServiceCall}
+    \end{tikzpicture}
+    \caption{Process interface and related classes}
+    \label{fig:processinterface}
+\end{figure}
+\resume{asparaenum}
+\item Release behavior
+\suspend{asparaenum}
+
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/iReleaseBehavior}
+    \input{figures/cResourceRelease}
+    \input{figures/cServiceRelease}
+    \end{tikzpicture}
+    \caption{Release interface and related classes}
+    \label{fig:releaseinterface}
+\end{figure}
+\resume{asparaenum}
+\item Response behavior
+\suspend{asparaenum}
+
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/iResponseBehavior}
+    \input{figures/cResourceResponse}
+    \input{figures/cServiceResponse}
+    \end{tikzpicture}
+    \caption{Response interface and related classes}
+    \label{fig:reponseinterface}
+\end{figure}
+\resume{asparaenum}
+\item Select behavior
+\end{asparaenum}
+
+\begin{figure}[htbp]
+    \centering
+    \scriptsize
+    \begin{tikzpicture}
+    \input{figures/iSelectBehavior}
+    \input{figures/cSelectInTask}
+    \input{figures/cSelectInServiceCall}
+    \end{tikzpicture}
+    \caption{Select interface and related classes}
+    \label{fig:selectinterface}
+\end{figure}
 \subsubsection{Interaction among agents}

### 2016-09-09 result.tex
modify the abstract

@@
 \item self-contained.
-\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study in such complex system.
-With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments with it.
+\end{inparaenum} They optimize their multi-objective decision-makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique \cite{Macal2009,north2007managing} is suitable for the study in such a complex system.
+With the help of Repast Simphony \cite{North2013} package was utilized in this experiment.
 
@@
 \label{ssub:case_design}
-We use the RanGen\cite{Demeulemeester2003} to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}. 
+RanGen \cite{Demeulemeester2003} was used to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}.
 \begin{table}[htbp]
@@
 \end{table}%
-We assume provider and demander are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the coming resource capacity rate in average to prevent the task explosion, and we make sure that:
+We assume that providers and demanders are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the average coming resource capacity rate in average to prevent the task explosion, and we make sure that,
 \begin{equation}
@@
 After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=\textwidth]{Data/out.eps}
-    \caption{Observed variable change with time}
-    \label{fig:out}
-\end{figure}
 \begin{table}[htbp]
@@
 \end{asparaenum}
-
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{Data/out.eps}
+    \caption{Observed variable change with time}
+    \label{fig:out}
+\end{figure}
 % subsubsection result_and_analysis (end)

### 2016-09-09 design.tex
tao's comment

@@
 
-\subsubsection{Assumptions} % (fold)
-\label{ssub:assumptions_nomenclature}
+% \subsubsection{Assumptions} % (fold)
+% \label{ssub:assumptions_nomenclature}
 To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.

### 2016-09-10 head.tex
tao's comment
shorten the abstract near 100 words

@@
 \begin{abstract}
-In cloud manufacturing, individuals engage in manufacturing business through a well-designed platform, where the operator is able to manage distributed massive manufacturing resources.
-Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others'.
-In this paper, we designed an original operation mode with 3 extensions named incubation, outsourcing and metabolism for the ecosystem.
-We designed an agent-based simulation model to validate the effectiveness of these modes.
-Experiment result shows evolution in ecosystem: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little.
+In cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
+Cloud manufacturing ecosystem has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information.
+In this paper, an original operation mode with three extensions namely incubation, outsourcing and metabolism mode are proposed.
+We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.
 
@@
 Cloud manufacturing ecosystem \sep
-Decision-making\sep
-Operation mode\sep
-Ecosystem evolution\sep
-Agent-based simulation
+decision-making\sep
+operation mode\sep
+ecosystem evolution\sep
+agent-based simulation
 

### 2016-09-11 design.tex
合并各个子小节，插入了一张service 剖析图

--- 2016-09-09 design.tex
@@
 % \label{sub:preliminaries}
-Before introducing the design of the ecosystem, we specify some basic concepts:
+Before introducing the design of the ecosystem, we specify some basic definitions:
 \begin{compactitem}
@@
 	\item Order: the task bundle like a project;
-	\item Task: the basic object that needs to be processed with certain type and capacity of resource;
-	\item Task-part: virtual segmentation unit of one task;
+	\item Task: the basic object that needs to be processed with resource-type cooperation;
+	\item Task-part: virtual resource-type segmentation unit of one task;
 	\item Product: the perform result of a task;
-	\item Platform: the place where individuals interact with other and ecosystem.
+    \item Service-call: the basic object that needs to be processed with both resource-type and resource-capacity cooperation;
+    \item Job: the generalization of task and service-call;
+    \item Service: the perform result of a service-call, a group of tasks;
+    \item Machine: the generalization of resource and service;
+	\item Platform: the place where individuals interact with others;
+    \item Resource-type cooperation: resource in specific type to process a job simultaneously;
+    \item Resource-capacity cooperation: part of resources in same type to process a service-call simultaneously.
 \end{compactitem}
 
-With the cloud manufacturing platform operating, demanders publish orders while provider provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
+With the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
 Most recent researchers e.g.
@@
 Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
-\begin{figure}[htbp]
-    \centering
-    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
-    \caption{Original mode}
-    \label{fig:originmode}
-\end{figure}
 In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines).
-The demander publish order that can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation.
-Each task needs to be performed with pre-determined configuration of resources.
-Hence, even after response and assignment procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts.
+A single order can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation.
+Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part as show in \autoref{fig:simplejoblist}, we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:simplejoblist}, \textbf{inactive} when this part is just assigned to the job queue.
 Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.
-Cooperation procedure is necessary because of resource capacity is limited, but task-parts belonging to one task should be processed simultaneously to make sure the required resource capacities are available.
-We call the task-part is active when being processed, semi-active when selected resource is cooperating, inactive when this part is just assigned to the job queue.
 
-\subsubsection{Assumptions} % (fold)
+\subsection{Nomenclature and assumptions} % (fold)
 \label{ssub:assumptions_nomenclature}
-To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
-\begin{compactitem}
-\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
-\item The quality of product is determined by the worst quality of the selected resource;
-\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
-\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
-\item Cooperate and processing procedure cannot be interrupted;
-\item Provider can only schedule task-parts in inactive status.
-\end{compactitem}
-
 \begin{table}[htbp]
@@
     \hline
-    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomencalture}}} \\
+    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomenclature}}} \\
     \multicolumn{2}{|l|}{} \\
@@
     $\mathcal{G}_{k,\tau}$ & The set of active job of $mr_k$ at $\tau$ \\
-	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule at $\tau_0$ . \\
+    % $job_\theta$ & Task that need to be scheduled at $\tau_0$,  $\theta = 1,...,\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{G}^{(s)}_{k,\tau_0}}$\\
+    $f^{(s)}_\theta$ & Ideal finish time of $job_\theta$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule at $\tau_0$ . \\
     $re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule at $\tau_0$. \\
@@
 Since demander and provider continuous arrives, there is no upper bound of the subscripts
-$(i,j,k,l,\alpha)$. When in scheduling procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.
+$(i,j,k,l,\alpha)$.
+To scope our research, we make some assumptions as follows for the original mode, while in other extensions, some of the assumptions will be modified.
+\begin{compactitem}
+\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
+\item The quality of product is determined by the worst quality of the selected resource;
+\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
+\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
+\item Cooperation and processing procedure cannot be interrupted;
+\item Provider can only schedule task-parts in inactive status.
+\end{compactitem}
+
 % \vspace{-2.5em}
 % subsubsection assumptions_nomenclature (end)
-\subsubsection{Master plan for original mode} % (fold)
+\subsection{Master plan for original and extended modes} % (fold)
 \label{ssub:master_plam}
-A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
+In original mode, a single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
 First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
@@
 Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$.
-This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.
+This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need to be processed with resource cooperation.
+
+The relation of proposed extended modes is shown in \autoref{fig:modes},
+\begin{figure}[htbp]
+    \centering
+    \resizebox{\textwidth}{!}{\input{figures/modes}}
+    \caption{Three Extended modes}
+    \label{fig:modes}
+\end{figure}
+incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because task that processed by service can be outsourced.
+
 % subsubsection master_plan (end)
@@
 
-\subsection{Individual decisions in original mode} % (fold)
+\subsection{Original mode} % (fold)
 \label{sub:interactions_and_decisions}
-\subsubsection{Provider respond to type-matched task}
-\label{subs:Response_for_type_matched_task}
+% \subsubsection{Provider respond to type-matched task}
+% \label{subs:Response_for_type_matched_task}
+
+\begin{figure}[htbp]
+    \centering
+    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
+    \caption{Original mode}
+    \label{fig:originmode}
+\end{figure}
+
 A provider makes decision at time $\tau\ge r_i$ to respond  to task if the belonging resource $mr_k$ was type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
@@
 
-\subsubsection{Demander select from resource candidates}
-\label{subs:select_resource_candidates}
+% \subsubsection{Demander select from resource candidates}
+% \label{subs:select_resource_candidates}
 A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
@@
 
-\subsubsection{Provider assign task-part in selected resource} % (fold)
-\label{subs:assign_in_select_resource}
+% \subsubsection{Provider assign task-part in selected resource} % (fold)
+% \label{subs:assign_in_select_resource}
 If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$, or to  $\mathcal{L}_{k,\tau}$ otherwise.
@@
 Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.
+% \begin{figure}[htbp]
+%     \centering
+%     \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
+%     \caption{Incubation mode}
+%     \label{fig:serviceincubatemode}
+% \end{figure}
+service
+
 \begin{figure}[htbp]
     \centering
-    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
-    \caption{Incubation mode}
-    \label{fig:serviceincubatemode}
+    \scriptsize
+    \resizebox{.65\textwidth}{!}{\input{figures/service}}
+    \caption{Service illustration}
+    \label{fig:servicefigure}
 \end{figure}
+
 After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
@@
 
-\subsubsection{Provider respond to type-matched job} % (fold)
-\label{ssub:response_in_type_matched_resource}
+% \subsubsection{Provider respond to type-matched job} % (fold)
+% \label{ssub:response_in_type_matched_resource}
 Apart from $mr_k$ respond to $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
@@
 
-\subsubsection{Demander select from machine candidates} % (fold)
-\label{ssub:selection_in_resource_candidates_for_service_call}
+% \subsubsection{Demander select from machine candidates} % (fold)
+% \label{ssub:selection_in_resource_candidates_for_service_call}
 Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
@@
 
-\subsubsection{Provider assign task to selected machine} % (fold)
+% \subsubsection{Provider assign task to selected machine} % (fold)
 Apart from $mr_k$ assign $t_{ij}$ when selected as we explained in \autoref{subs:assign_in_select_resource}, there are 2 other cases in incubation mode:
@@
 Outsourcing mode is one extension on the original mode and will be active when incubation mode is on that only service can perform this procedure. As shown in \autoref{fig:outsourcemode},
-\begin{figure}[htbp]
-    \centering
-    \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
-    \caption{Outsourcing mode}
-    \label{fig:outsourcemode}
-\end{figure}
+% \begin{figure}[htbp]
+%     \centering
+%     \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
+%     \caption{Outsourcing mode}
+%     \label{fig:outsourcemode}
+% \end{figure}
 the idea of outsourcing for service is to republish active or inactive task to platform again in order to reduce its job queue length to enhance the probability to be selected by new tasks.
@@
 As shown in \autoref{fig:metabolismmode},
-\begin{figure}[htbp]
-    \centering
-    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
-    \caption{Metabolism mode}
-    \label{fig:metabolismmode}
-\end{figure}
+% \begin{figure}[htbp]
+%     \centering
+%     \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
+%     \caption{Metabolism mode}
+%     \label{fig:metabolismmode}
+% \end{figure}
 we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.
@@
 	\centering
+    \large
 	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
@@
 \end{figure}
-Therefore, we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$
+Therefore, provider can only makes decision on the schedule of tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of these inactive task to be scheduled as $\mathcal{L}^{(s)}_{k,\tau_0}$.
 
@@
   \caption{Simple job configuration}
-    \begin{tabular}{cccccc}
+    \begin{tabular}{ccccccc}
     \toprule
-    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
-    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+    % \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
+    % \multicolumn{1}{c}{} & $Type 1$ & $Type 2$ & $Type 3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+    Job ($\theta$) & Entity class& $q_{1,\theta}$ & $q_{2,\theta}$ & $q_{3,\theta}$ & $r_\theta$ & $p_\theta$ \\
     \midrule
-    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
-    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
-    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
-    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
-    $t_5$ & 1 & 0 & 3 & 2 & 3\\
-    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
-    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
+    $job_1$ & task& 0     & 5     & 7     & 0     & 7 \\
+    $job_2$ & task& 7     & 5     & 5     & 4     & 5 \\
+    $job_3$ & task& 6     & 0     & 5     & 2     & 3 \\
+    $job_4$ & task& 9	 & 4  & 6 & 1 &2 \\
+    $job_5$ & task& 1 & 0 & 3 & 2 & 3\\
+    $job_6$ & service-call& 1     & 0     & 3    & 0     & 1 \\
+    $job_7$ & service-call& 0     & 5     & 7     & 7     & 1 \\
     \bottomrule
@@
 
-Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
-This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transitions.
-Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
+Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the settings.
+Since the task may come from different orders, we here use the single uniform denotation $job_\theta$ to distinguish these tasks and their related variables.
+In this instance, as shown in \autoref{fig:simplejoblist}, horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
 Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.
@@
 	\centering
-	\normalsize
+	\large
 	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
@@
 
-In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$.
-Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type-matched.
+In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}}$.
+Even though provider will not schedule $job_\theta\in\mathcal{H}_{k,\tau_0}$, the finish time $f_\theta$ of these job cannot be determined because the waiting in the cooperation.
+We ignore the type subscript $\alpha$ because all the job assigned here are already type-matched.
 The schedule model is:
@@
 \begin{equation}
-\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right) \label{eq:scheduleaim}
+\min_{\forall\bm{f}^{(s)}}\left( \max_{\theta\in L^{(s)}}\left\{ f_j^{(s)} - r_\theta - p_\theta \right\} \right) \label{eq:scheduleaim}
 \end{equation}
 \begin{numcases}{\text{s.t.}}
-L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
-f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\label{eq:subsequence}\\
-G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
-f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \label{eq:alreadydefined}\\
-\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
-f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$ \label{eq:finishconstrain}
+L^{(s)} = \left\{\theta| job_{\theta}\in \mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}\right\} & \label{eq:subscript}\\
+f^{(s)}_h \le f_\theta^{(s)} - p_\theta & $h\in\mathcal{P}_\theta$,$\theta\in L^{(s)}$\label{eq:subsequence}\\
+G^{(s)} = \left\{\theta | job_{\theta}\in \mathcal{G}_{k,\tau_0}\right\} & \label{eq:activesubscript}\\
+f^{(s)}_\theta =  \tau_0 + re_\theta & $\theta\in G^{(s)}$ \label{eq:alreadydefined}\\
+\sum_{\theta\in\left\{  \theta' |t_{\theta'} \in\mathcal{G}_{k,\tau}\right\}} q_\theta \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
+f^{(s)}_\theta \ge \tau_0 + p_\theta & $\theta\in L^{(s)}$ \label{eq:finishconstrain}
 \end{numcases}

### 2016-09-11 figures/metabolism.tex
合并各个子小节，插入了一张service 剖析图

@@
 % First row:
-\node (add) {New Machine}; & \node (machinein) [square] {Arrival Restrictor}; & & & & & & &\\
-\node (origin) {Origin Scarcity}; & & \node (compare) [circle] {\Large$\times$}; & & \node (scarcity) [square] {Machine Scarcity}; & \node (metabolism) [square] {Metabolism Module}; &\node (node) [coord] {}; &\node (end) [coord] {};\\
-\node (task) {New Task}; & \node (p1) [coord] {};& & \node (p2) [coord] {}; & \node (reduce) [square] {Eliminate Machine}; & & & & \\
-& & \node (tf) {Task Finish}; &  & & & & &\\
+&&&&& & & \node (machinein) [square] {Arrival Restrictor}; & \node (add) {};  &  & &\\
+&&&&&&&&&&&\\
+&&&&&&&&&&&\\
+& & && &\node (origin2) {};  & \node (compare2) [circle] {\Large$\times$}; &  \node (scarcity) [square] {Machine Scarcity}; & \node (metabolism) [square] {Metabolism Module}; &\node (node2) [coord] {}; &\node (end2) [coord] {};\\
+&&&&&\node (task) {}; &  & \node (reduce) [square] {Eliminate Machine}; &  & & &\\
+&&&&& &  &  & & & & &&  \\
 };
-\path (add) edge[->] (machinein) (machinein.east) edge[->] (compare) (compare) edge[->] (scarcity) (scarcity) edge[->] (metabolism);
-\path (origin) edge[->] (compare);
-\path (tf) edge[->] (compare);
-\path (reduce) edge (p2) (p2) edge[->] (compare);
-\draw [->] (metabolism) -- (end) ;
-\draw [->]  (task) -- (p1) -- (compare);
-\path (node) edge[->,skip loop=5.5em] (machinein);
-\draw [->] (node) |- (reduce);
-\path (machinein.east) to node [near end,yshift=0.5em,xshift=0.5em] {$-$} (compare);
-\path (tf) to node [near end,xshift=0.5em] {$-$} (compare);
-\path (p1) to node [near end,xshift=0.8em] {$+$} (compare);
-\path (p2) to node [near end,xshift=0.5em,yshift=0.3em] {$+$} (compare);
-\path (node) to node [near end,xshift=2em,yshift=0.6em] {Decision value} (end);
+\path (add) edge[->] (machinein) (machinein.west) edge[->] (compare2) (compare2) edge[->] (scarcity) (scarcity) edge[->] (metabolism);
+\path (origin2) edge[->] (compare2);
+% \path (tf) edge[->] (compare2);
+\path (reduce.west)  edge[->] (compare2);
+\draw [->] (metabolism) -- (end2) ;
+\draw [->]  (task) -- (compare2);
+\path (node2) edge[->,skip loop=2.2em] (machinein);
+\draw [->] (node2) |- (reduce);
+\path (machinein.west) to node [near end,yshift=-0.5em,xshift=0.5em] {$-$} (compare2);
+% \path (tf) to node [near end,xshift=0.5em] {$-$} (compare2);
+\path (task) to node [near end,xshift=0.8em] {$+$} (compare2);
+\path (reduce) to node [near end,xshift=-0.6em,yshift=-0.8em] {$+$} (compare2);
+\path (node2) to node [near end,xshift=2em,yshift=0.6em] {Decision var.} (end2);
+\path (add) to node [near start, xshift=7em] {New Registered Resource}(machinein) (origin2) to node [near start,xshift=-4em]{Origin Scarcity}(compare2) (task.east) to node [near start,xshift=-3em]{New Task} (compare2);
 \end{tikzpicture}

### 2016-09-11 figures/modes.tex
合并各个子小节，插入了一张service 剖析图

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (s1) [coord] {}; & & & & & \node (s2) [coord]{} ; & & & & & & \\
& & &   \node   (out) [square] {Outsource Task} ; &  \node (originl) {Origin Length} ; &  &\node (origin) {Origin Frequency} ; & \node (compare) [circle] {\Large$\times$}; &  \node (frequency) [square] {Task Frequency} ; & \node (incubate) [square] {Incubation Module} ; & \node (node) [coord] {} ; & \node (end) [coord] {}; \\
\node (end1)  {}; & \node (node1) [coord] {} ; & \node (outsource) [square] {Outsourcing Module} ; &\node (length) [square] {Queue Length} ; & \node (compare1) [circle] {\Large$\times$};  & & & & \node (sc) [square] {Incubate Service} ; & & & \\
\\
&& \node (o1){};& &\node (o2){}; \\
\node (s3) [coord]{}; &  & & & & \node (s4) [coord]{}; &  & & & & &\\
\node (tfs) {};& & \node (metam1) {};& &\node (metam2) {};& &  \node (tf) {Task Finish}; & &\node (incm1){}; & \node (incm2){};& &\node (tfe) {};\\
&&&&& & & \node (machinein) [square] {Arrival Restrictor}; & \node (add) {};  &  & &\\
&&&&&&&&&&&\\
&&&&&&&&&&&\\
& & && &\node (origin2) {};  & \node (compare2) [circle] {\Large$\times$}; &  \node (scarcity) [square] {Machine Scarcity}; & \node (metabolism) [square] {Metabolism Module}; &\node (node2) [coord] {}; &\node (end2) [coord] {};\\
&&&&&\node (task) {}; &  & \node (reduce) [square] {Eliminate Machine}; &  & & &\\
&&&&& &  &  & & & & &&  \\
};
\path (origin) edge[->] (compare) (tf) edge[->] (compare) (compare) edge[->] (frequency) (frequency) edge[->] (incubate) (incubate) edge[->] (end);
\path (sc.west) edge[->] (compare);
\draw [->] (node) |- (sc) ;
\path (tf) to node [near end,xshift=2em,yshift=1em] {$+$} (compare) (sc) to node [near end,xshift=0.5em] {$-$} (compare) (incubate) to node [yshift=0.7em,xshift = 1.5em] {Decision var.} (end);
\draw[dashed] (s1) -- (s2) -- (s4) -- (s3) -- (s1);
\draw[dashed,thick](tfs.west) -- (tf.west) (tf.east) -- (tfe.east);

\path (originl) edge[->] (compare1) (compare1) edge[->] (length) (length) edge[->] (outsource) (outsource) edge[->] (end1);
\path (out.east) edge[->] (compare1);
\draw [->] (node1) |- (out) ;
\path (out) to node [near end,xshift=0.5em,yshift=0.7em] {$-$} (compare1) (outsource) to node [near end,yshift=-0.7em,xshift = -0.5em] {Decision var.} (end1);

\draw[->] (tf) edge (compare1) (tf) edge (compare2);
\path (tf) to node [yshift=0.9em,xshift=-0.8em,near end] {$+$} (compare1) (tf) to node [xshift=-0.8em,yshift=-0.5em,near end] {$-$} (compare2);

\draw (sc.south) edge[->] (machinein.north);

\path (add) edge[->] (machinein) (machinein.west) edge[->] (compare2) (compare2) edge[->] (scarcity) (scarcity) edge[->] (metabolism);
\path (origin2) edge[->] (compare2);
% \path (tf) edge[->] (compare2);
\path (reduce.west)  edge[->] (compare2);
\draw [->] (metabolism) -- (end2) ;
\draw [->]  (task) -- (compare2);
\path (node2) edge[->,skip loop=2.2em] (machinein);
\draw [->] (node2) |- (reduce);
\path (machinein.west) to node [near end,yshift=-0.5em,xshift=0.5em] {$-$} (compare2);
% \path (tf) to node [near end,xshift=0.5em] {$-$} (compare2);
\path (task) to node [near end,xshift=0.8em] {$+$} (compare2);
\path (reduce) to node [near end,xshift=-0.6em,yshift=-0.8em] {$+$} (compare2);
\path (node2) to node [near end,xshift=2em,yshift=0.6em] {Decision var.} (end2);
\path (add) to node [near start, xshift=7em] {New Registered Resource}(machinein) (origin2) to node [near start,xshift=-4.8em]{Origin Scarcity}(compare2) (task) to node [near start,xshift=-3.8em,yshift=-0.5em]{New Task} (compare2);

\path (o1) to node {\textbf{Outsource mode} (only with service)} (o2);
\path (incm1) to node [yshift=1em]{\textbf{Incubation mode}} (incm2) (incm1) to node [yshift=-1em]{\textbf{Metabolism mode}} (incm2);
\end{tikzpicture}

### 2016-09-11 figures/outsource.tex
合并各个子小节，插入了一张service 剖析图

@@
 % First row:
-\node (origin) {Origin Length} ; & \node (compare) [circle] {\Large$\times$}; & & \node (length) [square] {Queue Length} ; & \node (outsource) [square] {Outsourcing Module} ; & \node (node) [coord] {} ; & \node (end) [coord] {}; \\
-& & \node (p1) [coord] {} ; & \node	(out) [square] {Outsource Task} ; & & & \\
-& \node (tf) {Task Finish}; & & & & &\\
+& & &   \node	(out) [square] {Outsource Task} ; &  \node (originl) {Origin Length} ; & \\
+\node (end1) [coord] {}; & \node (node1) [coord] {} ; & \node (outsource) [square] {Outsourcing Module} ; &\node (length) [square] {Queue Length} ; & \node (compare1) [circle] {\Large$\times$};  & \\
+&  & &  & &\\
 };
-\path (origin) edge[->] (compare) (tf) edge[->] (compare) (compare) edge[->] (length) (length) edge[->] (outsource) (outsource) edge[->] (end);
-\path (out) edge (p1) (p1) edge[->] (compare);
-\draw [->] (node) |- (out) ;
-\path (tf) to node [near end,xshift=0.3em] {$+$} (compare) (p1) to node [near end,xshift=0.5em] {$-$} (compare) (outsource) to node [yshift=0.7em,xshift = 1.5em] {Decision value} (end);
+\path (originl) edge[->] (compare1) (compare1) edge[->] (length) (length) edge[->] (outsource) (outsource) edge[->] (end1);
+\path (out.east) edge[->] (compare1);
+\draw [->] (node1) |- (out) ;
+\path (out) to node [near end,xshift=0.5em,yshift=0.7em] {$-$} (compare1) (outsource) to node [near end,yshift=-0.7em,xshift = -0.7em] {Decision var.} (end1);
 \end{tikzpicture}

### 2016-09-11 figures/scheduleChart.tex
合并各个子小节，插入了一张service 剖析图

--- 2016-08-26 figures/scheduleChart.tex
@@
 
-\draw (7.5cm,-7mm) node{$r_4$, initial capacity = 10, type = 3};
-\draw[yshift=6.5cm] (7.5cm,-7mm) node{$r_3$, initial capacity = 10, type = 3};
-\draw[yshift=13cm] (7.5cm,-7mm) node{$r_2$, initial capacity = 10, type = 2};
-\draw[yshift=19.5cm] (7.5cm,-7mm) node{$r_1$, initial capacity = 10, type = 1};
+\draw[yshift=6.5cm] (7.5cm,-11mm) node{$mr_4$, $C_{4,0} = 10$, $P(mr_4) = 3$};
+\draw[yshift=13cm] (7.5cm,-11mm) node{$mr_3$, $C_{3,0} = 10$, $P(mr_3) = 3$};
+\draw[yshift=19.5cm] (7.5cm,-11mm) node{$mr_2$, $C_{2,0} = 10$, $P(mr_2) = 2$};
+\draw[yshift=26cm] (7.5cm,-11mm) node{$mr_1$, $C_{1,0} = 10$, $P(mr_1) = 1$};
 
-\fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
-\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
-\draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
-\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
-\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
-\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
-\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
-\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
-\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
+% \fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
+\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm) (0,4.5cm) rectangle (1cm,5cm)  (4.5cm,1.6cm) node{$job_3$} (10.5cm,1.8cm) node{$job_2$} (2cm,2.25cm) node{$job_4$} (4.5cm,3.25cm) node{$job_5$} (0.5cm,4.75cm) node{$job_6$};
+\draw[dotted,yshift=19.5cm] (3cm,4.5cm) -- +(12cm,0);
+
+\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,2.5cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,4.5cm)  (3.5cm,1.35cm) node{$job_1$} (7.5cm,3.75cm) node{$job_7$} (10.5cm, 1.35cm) node{$job_2$}  (2cm,3.5cm) node{$job_4$};
+\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (8cm,2.5cm) -- (15cm,2.5cm);
+
+\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,3cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm)  (8cm,0) rectangle (13cm,2.5cm) (3.5cm,1.85cm) node{$job_1$} (7.5cm,4cm) node{$job_7$} (4.5cm,4.25cm) node{$job_5$} (10.5cm,1.25cm) node{$job_2$};
+\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,3cm) -- (15cm,3cm) (8cm,3cm) -- (8cm,2.5cm);
+
+\fill[blue!20!] (6cm,2cm) rectangle (7cm,3.5cm);
+\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm)  (1cm,0) rectangle (3cm,3cm) (6cm,2cm) rectangle (8cm,3.5cm) (4.5cm, 1.35cm) node {$job_3$} (0.5cm,4.3cm) node{$job_6$}  (2cm,1.5cm) node{$job_4$} (7cm,2.75cm) node{$job_7$};
+\draw[dotted] (0,3.5cm) -- (6cm,3.5cm) (1cm,0) -- (1cm,3.5cm) (8cm,2cm) -- (15cm,2cm) (7cm,2cm) -- +(0,1.5cm) (8cm,2cm) -- (8cm,0);
 \end{tikzpicture}

### 2016-09-11 figures/service.tex
合并各个子小节，插入了一张service 剖析图

% !TEX root = flow_head.tex

\begin{tikzpicture}
\fill[blue!20!] (10mm,0) rectangle (20mm,4mm);
\draw (0,0) rectangle (20mm,4mm) (24mm,2mm) node{$mr_2$};
\draw (5mm,2mm) node{5} (15mm,2mm) node{5} (-1cm,2mm) node{$\alpha=2$} (12mm,2mm);
\draw[dotted] (10mm,0) -- (10mm,4mm);

\draw[->] (15mm,0) edge (15mm,-4mm) (17mm,-12mm) edge (23mm,-8mm) (46mm,-12mm) edge (30mm,-8mm);
% \draw[->,xshift=30mm](41mm,-12mm) edge (20mm,-8mm);

\draw[dotted,yshift=-2mm] (-1.5cm,0) -- (5.5cm,0);

\draw[yshift=-8mm,xshift=10mm] (0,0) rectangle (24mm,4mm) (34mm,2mm) node{$ms_l$ (new)};
\draw[yshift=-8mm,xshift=10mm] (10mm,0) -- (10mm,4mm);
\draw[yshift=-8mm,dotted,xshift=10mm] (16mm,0) -- (16mm,4mm);
\draw[yshift=-8mm,xshift=10mm] (5mm,2mm) node{5} (13mm,2mm) node{3} (20mm,2mm) node{4} (-2cm,2mm) node{Service};

\draw[dotted,yshift=-10mm] (-1.5cm,0) -- (5.5cm,0);

\fill[blue!20!,yshift=-16mm] (14mm,0) rectangle (20mm,4mm);
\fill[blue!20!,yshift=-16mm,xshift=30mm](20mm,4mm) rectangle +(-8mm,-4mm);
\draw[yshift=-16mm] (0,0) rectangle (20mm,4mm) (24mm,2mm) node{$mr_4$};
\draw[yshift=-16mm,xshift=30mm] (0,0) rectangle (20mm,4mm) (24mm,2mm) node{$mr_3$};
\draw[yshift=-16mm,dotted] (14mm,0) -- +(0,4mm) ;
\draw[yshift=-16mm,dotted,xshift=30mm] (12mm,0) -- +(0,4mm);
\draw[yshift=-16mm] (7mm,2mm) node{7} (17mm,2mm) node{3} (-1cm,2mm) node{$\alpha=3$};
\draw[yshift=-16mm,xshift=30mm] (6mm,2mm) node{6} (16mm,2mm) node{4};
\end{tikzpicture}

### 2016-09-11 design.tex
incubation

@@
 \end{figure}
-incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because task that processed by service can be outsourced.
+incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.
 
@@
 \label{sub:incubation_mode}
-Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.
+Incubation mode is one extension for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in incubation part of \autoref{fig:modes}.
 % \begin{figure}[htbp]
@@
 % \end{figure}
-service
-
 \begin{figure}[htbp]
@@
     \resizebox{.65\textwidth}{!}{\input{figures/service}}
-    \caption{Service illustration}
+    \caption{Service incubation illustration}
     \label{fig:servicefigure}
 \end{figure}
-
 After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
-
-The first thing of incubation is to publish a job named \textbf{service-call}, which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the performance of a service-call.
-The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources of a same type to make contributions to the formation of one service.
-No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
-Now we can classify task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.
+For example, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_6$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing.
+The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service.
+No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while one con of service include that service can only perform specified task.
+Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.
 

### 2016-09-13 design.tex
submitted

@@
 If $mr_k$ is finally selected, available capacity of $mr_k$ will change to $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$.
-This available capacity will be restored back to after the finish of $t_{ij}$ part.
+This available capacity will be restored after the finish of $t_{ij}$ part.
 
@@
 The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length.
-\autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.
+\autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task-part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.
 
@@
 % \label{ssub:response_in_type_matched_resource}
-Apart from $mr_k$ respond to $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
+Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:
 \begin{asparaenum}
@@
 % \label{ssub:selection_in_resource_candidates_for_service_call}
-Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
+Apart from demander of $t_{ij}$ select $mr_k$ that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
 
@@
 % \subsubsection{Provider assign task to selected machine} % (fold)
-Apart from $mr_k$ assign $t_{ij}$ when selected as we explained in \autoref{subs:assign_in_select_resource}, there are 2 other cases in incubation mode:
+Apart from $mr_k$ assign $t_{ij}$, there are 2 other cases in incubation mode:
 
@@
 \suspend{asparaenum}
-If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict than that in \autoref{subs:assign_in_select_resource}, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
+If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
 Then, the provider of $mr_k$ should change the predecessor set:
@@
 \label{sub:outsource_mode}
-Outsourcing mode is one extension on the original mode and will be active when incubation mode is on that only service can perform this procedure. As shown in \autoref{fig:outsourcemode},
+Outsourcing mode is one extension for the original mode when incubation mode is applied. As outsourcing part shown in \autoref{fig:modes},
 % \begin{figure}[htbp]
@@
 \label{sub:metabolism mode}
-Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members.
-As shown in \autoref{fig:metabolismmode},
+Metabolism mode is one extension for the original mode to control the number of individual in the system by both restrict the arrival and eliminate the current members.
+As metabolism part shown in \autoref{fig:modes},
 % \begin{figure}[htbp]
@@
 The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs.
-\autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself.
+\autoref{eq:subsequence} ensures that all predecessors of each job finished before the job itself.
 \autoref{eq:alreadydefined} means that the finish time of activate job is determined.
-\autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
+\autoref{eq:caplimitwithtime} ensures the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
 Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be

### 2016-09-13 discussion.tex
submitted

@@
 % !TEX root = Eco-Model.tex
-\section{Limitations, and Future Research} % (fold)
+\section{Conclusions, Limitations, and Future Research} % (fold)
 \label{sec:contributions_limitations_and_future_research}
-We only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions.
+In the extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate.
+The combine of incubation and metabolism mode makes the maintenance of platform much easier.
+However, we only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions.
 The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.

### 2016-09-13 result.tex
submitted

@@
 
-Individuals in the manufacturing ecosystem are: \begin{inparaenum}[1)]
-\item autonomous and self-directed,
-\item social, interacting with other entities,
-\item controlled by the environment,
-\item self-contained.
-\end{inparaenum} They optimize their multi-objective decision-makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique \cite{Macal2009,north2007managing} is suitable for the study in such a complex system.
-With the help of Repast Simphony \cite{North2013} package was utilized in this experiment.
+Because of the  autonomous and self-directed features of individuals in the manufacturing ecosystem, we use agent-based modeling and simulation(ABMS) technique \cite{Macal2009,north2007managing} to study such a complex system.
+Repast Simphony \cite{North2013} package was utilized in this experiment.
 
@@
 \label{ssub:case_design}
-RanGen \cite{Demeulemeester2003} was used to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}.
+We design experiments to repeatedly simulate the operating of ecosystem with 6 different mode combinations in \autoref{tab:grouping} group by group, which are the prototypes of feasible cloud manufacturing operating modes.
+Every single simulation goes with the main flow as show in \autoref{fig:originmode}.
+We use  RanGen \cite{Demeulemeester2003} to generate dataset in the well-known Patterson format as the the continuously arriving order for the simulation input, related parameter settings are listed in \autoref{tab:generalparameter}.
 \begin{table}[htbp]
@@
 \end{table}%
+
 We assume that providers and demanders are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the average coming resource capacity rate in average to prevent the task explosion, and we make sure that,
@@
 \end{equation}
-
-We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, and each of them contains 10 tasks with different configuration on 12 types of resources to perform with.
 

### 2016-09-13 design.tex
modify before the submission

@@
 	\item Task: the basic object that needs to be processed with resource-type cooperation;
-	\item Task-part: virtual resource-type segmentation unit of one task;
+	\item Task-part: virtual resource-type segmentation unit of one task as squares in \autoref{fig:scheduleChart};
 	\item Product: the perform result of a task;
@@
     \item Resource-type cooperation: resource in specific type to process a job simultaneously;
-    \item Resource-capacity cooperation: part of resources in same type to process a service-call simultaneously.
+    \item Resource-capacity cooperation: part of resources in same type to process a service-call simultaneously as in \autoref{fig:servicefigure}.
 \end{compactitem}
 
-With the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
+Platform is the cradle of the ecosystem and the incubator for manufacturing service, with the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
 Most recent researchers e.g.
@@
 Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
-In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines).
-A single order can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation.
-Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part as show in \autoref{fig:simplejoblist}, we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:simplejoblist}, \textbf{inactive} when this part is just assigned to the job queue.
+In this mode, individual executes activities that interact with others depicted by object flow (full lines) and information flow (dashed lines).
+A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation.
+Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part and we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:scheduleChart}, \textbf{inactive} when this part is just assigned to the job queue.
 Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.
@@
 \begin{compactitem}
+\item Operate of the ecosystem starts from the very beginning that no demander or provider is registered;
 \item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
@@
 \label{ssub:master_plam}
-In original mode, a single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
+In original mode, operating of ecosystem begins with void, then there comes the registration of provider and demander.
+A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
 First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
@@
 
-The relation of proposed extended modes is shown in \autoref{fig:modes},
+The life cycle management of resource contains its vicissitude, which is the design basis of proposed extended modes \autoref{fig:modes}.
 \begin{figure}[htbp]
@@
 \end{figure}
-incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.
+Incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.
 
@@
     \resizebox{.65\textwidth}{!}{\input{figures/service}}
-    \caption{Service incubation illustration}
+    \caption{Service incubation from $job_7$ in \autoref{tab:simplejobconfiguration}}
     \label{fig:servicefigure}
@@
 After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
-For example, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_6$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing.
+As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing.
 The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service.

### 2016-09-13 head.tex
modify before the submission

@@
 \author[add2,add1]{Shuiliang Fang\corref{cor1}}
-\author[add2,add1]{Tao Peng}
+\author[add2]{Tao Peng}
+\author[add2]{Renzhong Tang}
 % \ead{me_fangsl@zju.edu.cn}
@@
 \begin{abstract}
-In cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
-Cloud manufacturing ecosystem has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information.
-In this paper, an original operation mode with three extensions namely incubation, outsourcing and metabolism mode are proposed.
+With cloud manufacturing, platform operator is able to manage distributed massive manufacturing resources for manufacturing business.
+Ecosystem of cloud manufacturing has more complicated relationship among individuals than that in existing manufacturing system, every individual makes decisions depend on enriched information, which will help optimize for the overall industry.
+In this paper, an original operation mode with three extensions are proposed to describe the life cycle vicissitude of each resource.
 We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.

### 2016-09-13 intro.tex
modify before the submission

@@
 Demanders prefer high quality of performance, while providers prefer high use rate of resource.
-A cloud platform operator prefers a fewer amount of registered resource when dealing with almost arriving needs for an easier maintenance.
+A cloud platform operator prefers a suitable amount of registered resources to satisfy the needs of the market and for an easier life cycle management of resources.
 These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem.
-Hence, it's important to identify a suitable operation mode to meet most of individuals' preference.
+Hence, it's important to identify a suitable operation mode to meet most of individuals' preference and to optimize the resource management.
 

### 2016-09-13 result.tex
modify before the submission

@@
 \label{ssub:case_design}
-We design experiments to repeatedly simulate the operating of ecosystem with 6 different mode combinations in \autoref{tab:grouping} group by group, which are the prototypes of feasible cloud manufacturing operating modes.
+We design experiments to repeatedly simulate the operating of ecosystem from the very beginning with mode combinations in \autoref{tab:grouping} group by group, which are the prototypes of feasible cloud manufacturing operating modes.
 Every single simulation goes with the main flow as show in \autoref{fig:originmode}.

### 2016-09-21 Data/plot.py
for py3

@@ -5,16 +5,15 @@ import pandas as pd
 import pylab as pl
 from scipy import interpolate 
 
-seed = '1212'
-t = [(x+1)*50 for x in xrange(240)]
+seed = '776189616'
+t = [(x+1)*50 for x in range(120)]
 
 def value(seed,mode,file,loc):
-	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',dtype='string',delimiter=',')
+	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',delimiter=',',dtype='S20',skiprows=1)
 
 	v = []
-	
-	for i in xrange((len(data)-1)/50):
-		line = data[(i+1)*50]
+	for i in range(int((len(data))/50)):
+		line = data[(i+1)*50-1]
 		v.append(float(line[loc]))
 	tck = interpolate.splrep(t,v)
 	# tck_2 = interpolate.splrep(t)
@@ -22,12 +21,12 @@ def value(seed,mode,file,loc):
 	return v_bspline
 
 def Quality(seed,mode,style):
-	data = np.loadtxt(seed+ '/Quality_m'+ mode +'.csv',dtype='string',delimiter=',')
+	data = np.loadtxt(seed+ '/Quality_m'+ mode +'.csv',delimiter=',',dtype='S20',skiprows=1)
 	tick = []
 	q = []
 	
-	for i in xrange((len(data)-1)/50):
-		line = data[(i+1)*50]
+	for i in range(int((len(data))/50)):
+		line = data[(i+1)*50-1]
 		tick.append(float(line[0]))
 		q.append(float(line[1]))
 	f2 = interpolate.interp1d(tick, q, kind='cubic')
@@ -110,11 +109,11 @@ plt.savefig('out_new.eps', transparent=True, bbox_inches='tight', pad_inches=0)
 
 
 def mymean(seed,mode,file,loc):
-	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',dtype='string',delimiter=',')
+	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',delimiter=',',dtype='S20',skiprow=1)
 
 	v = []
 	
-	for i in xrange((len(data)-1)):
+	for i in range(int((len(data)))):
 		line = data[(i+1)]
 		v.append(float(line[loc]))
 	

### 2016-09-21 head.tex
ready for merge

@@
 \author[add2,add1]{Shuiliang Fang\corref{cor1}}
-\author[add2]{Tao Peng}
-\author[add2]{Renzhong Tang}
+\author[add1]{Tao Peng}
+\author[add1]{Renzhong Tang}
 % \ead{me_fangsl@zju.edu.cn}
@@
 In this paper, an original operation mode with three extensions are proposed to describe the life cycle vicissitude of each resource.
-We designed an agent-based simulation model and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.
+We designed an agent-based model to simulate the ecosystem from the very beginning, and the validation experiment result shows platform have: 1) shorter job queue length and lower resource idle rate with incubation mode; 2) a little shorter job queue length and fewer amount of registered resource with outsourcing mode; 3) the fewest amount of registered resource but a little higher resource idle rate with metabolism mode.
 

### 2016-09-21 Data/plot.py

@@ -5,8 +5,8 @@ import pandas as pd
 import pylab as pl
 from scipy import interpolate 
 
-seed = '1212'
-t = [(x+1)*50 for x in xrange(240)]
+seed = '776189616'
+t = [(x+1)*50 for x in xrange(120)]
 
 def value(seed,mode,file,loc):
 	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',dtype='string',delimiter=',')
@@ -66,7 +66,7 @@ for i in range(6):
 	style = styles[i]
 	N_T = value(seed,modes[i],'Task',1)
 	myplot(N_T,style)
-plt.title(r'Number of tasks($N_T$)')
+plt.title(r'Number of tasks($N_T$) in system')
 
 plt.subplot(424)
 for i in range(6):
@@ -80,14 +80,14 @@ for i in range(6):
 	style = styles[i]
 	N_R = value(seed,modes[i],'Qualities',1)
 	myplot(N_R,style)
-plt.title(r'Maximum queue length($L$)')
+plt.title(r'Maximum queue length($L$), $\forall mr_k$ in system')
 
 plt.subplot(426)
 for i in range(6):
 	style = styles[i]
 	R = value(seed,modes[i],'Qualities',4)
 	myplot(R,style)
-plt.title(r'Maximum rank value($R$)')
+plt.title(r'Maximum rank value($R$), for all provider in system')
 plt.xlabel("Time tick")
 plt.subplot(427)
 # f = Quality(seed,modes[0])
@@ -106,7 +106,7 @@ for style in styles:
 plt.legend(['Mode 11','Mode 12','Mode 21','Mode 22','Mode 31','Mode 32'],loc='center')
 
 plt.savefig('out_new.pdf', transparent=True, bbox_inches='tight', pad_inches=0)
-plt.savefig('out_new.eps', transparent=True, bbox_inches='tight', pad_inches=0)
+plt.savefig('out_new.png', transparent=True, bbox_inches='tight', pad_inches=0)
 
 
 def mymean(seed,mode,file,loc):

### 2016-09-21 Data/plot.py
modify the plot code

@@ -10,7 +10,7 @@ seed = '776189616'
 t = [(x+1)*50 for x in range(120)]
 
 def value(seed,mode,file,loc):
-	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',delimiter=',',dtype='S20',skiprows=1)
+	data = np.loadtxt(seed+ '/' + 'm'+ mode + '/'+ file +'.csv',delimiter=',',dtype='S20',skiprows=1)
 
 	v = []
 	for i in range(int((len(data))/50)):
@@ -22,7 +22,7 @@ def value(seed,mode,file,loc):
 	return v_bspline
 
 def Quality(seed,mode,style):
-	data = np.loadtxt(seed+ '/Quality_m'+ mode +'.csv',delimiter=',',dtype='S20',skiprows=1)
+	data = np.loadtxt(seed+ '/' + 'm' + mode + '/Quality.csv',delimiter=',',dtype='S20',skiprows=1)
 	tick = []
 	q = []
 	
@@ -110,7 +110,7 @@ plt.savefig('out_new.png', transparent=True, bbox_inches='tight', pad_inches=0)
 
 
 def mymean(seed,mode,file,loc):
-	data = np.loadtxt(seed+ '/' + file +'_m'+ mode +'.csv',delimiter=',',dtype='S20',skiprow=1)
+	data = np.loadtxt(seed+ '/' + 'm' + mode + '/' + file + '.csv',delimiter=',',dtype='S20',skiprow=1)
 
 	v = []
 	

### 2016-09-21 design.tex
modify the strcuture begin

@@
 % \label{ssub:response_in_type_matched_resource}
+\begin{asparaenum}
+\item Respond behavior
+\suspend{asparaenum}
 Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:
-\begin{asparaenum}
-\item $mr_k$ respond to $sc_l$
-\suspend{asparaenum}
 If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call.
@@
 Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
-\resume{asparaenum}
-\item $ms_l$ respond to $t_{ij}$
-\end{asparaenum}
+
 Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
@@
 
-\begin{asparaenum}
-\item Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau} = \mathcal{A}_l$
+\resume{asparaenum}
+\item Select behavior
 \suspend{asparaenum}
+Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau}\subset\mathcal{A}_l$
+
 Provider of $sc_l$ select resource from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, but the difference is that the $\bm{l}_{\alpha}$ here is also a set of selected resources with type $\alpha$, $\bm{l}_{\alpha}$ is subset of decision variable $\bm{l}$.
 Selected resources capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
+
 \begin{subnumcases}{}
@@
 
-\resume{asparaenum}
-\item Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
-\suspend{asparaenum}
+Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
+
 This situation implies that the resource candidates are not enough and there exists service candidates.
@@
 
-\resume{asparaenum}
-\item Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
-\end{asparaenum}
+Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
+
 In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one.
@@
 % \subsubsection{Provider assign task to selected machine} % (fold)
-Apart from $mr_k$ assign $t_{ij}$, there are 2 other cases in incubation mode:
-
-\begin{asparaenum}
-\item Assign $sc_l$ to $mr_k$
-\suspend{asparaenum}
+\resume{asparaenum}
+\item Assign behavior
+\end{asparaenum}
 If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
@@
 And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.
-\resume{asparaenum}
-\item Assign $t_{ij}$ to $ms_l$
-\end{asparaenum}
+
+Assign $t_{ij}$ to $ms_l$
+
 Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.

### 2016-09-21 design.tex
start to modify

@@
 \suspend{asparaenum}
+Similar to
+
 Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:

### 2016-09-22 design.tex
shorten the paper

--- 2016-09-21 design.tex
@@
 \suspend{asparaenum}
-Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:
-If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call.
-If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part.
+Similar with response of $mr_k$ to $t_{ij}$ in original mode, provider of $mr_k$ can also respond to type-matched service-call $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$.
+If $mr_k$ was finally selected, both available capacity and capacity will be changed as required, and these capacity will not be restored even after the finish of $sc_l$ part.
 Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
-
-Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
+When service $ms_l$ was type-matched with $t_{ij}$ ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of $ms_l$ will respond to $t_{ij}$ as soon as possible, demander of $t_{ij}$ will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
 
@@
 % \label{ssub:selection_in_resource_candidates_for_service_call}
-Apart from demander of $t_{ij}$ select $mr_k$ that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:
 
@@
 \suspend{asparaenum}
-Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau}\subset\mathcal{A}_l$
+Apart from the condition that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, provider of $sc_l$ will select $mr_k$ when $\mathcal{B}_{l,\tau}\subset\mathcal{A}_l$, and the difference is that the $\bm{l}_{\alpha}$ (subset of decision variable $\bm{l}$) here is also a set of selected resources with type $\alpha$.
+Capacities of selected resources will be changed, and if the sum of capacity value in $\bm{l}_{\alpha}$ is less than the value $sc_l$ required, this selection will not to be executed.
+% \begin{subnumcases}{}
+% C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
+% C_{k,\tau} := 0 & otherwise \label{eq:cap0}
+% \end{subnumcases}
+Demander of $t_{ij}$ will select $ms_l$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$ and this implies that the resource candidates are not enough and there exists service candidates.
 
-Provider of $sc_l$ select resource from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, but the difference is that the $\bm{l}_{\alpha}$ here is also a set of selected resources with type $\alpha$, $\bm{l}_{\alpha}$ is subset of decision variable $\bm{l}$.
-Selected resources capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
-
-\begin{subnumcases}{}
-C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
-C_{k,\tau} := 0 & otherwise \label{eq:cap0}
-\end{subnumcases}
-
-Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
-
-This situation implies that the resource candidates are not enough and there exists service candidates.
 \begin{equation}
@@
 \end{numcases}
-
 Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length.
@@
 
-Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
-
-In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one.
+In more general condition where $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service.
 \begin{equation}
@@
 If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one.
-Then, the provider of $mr_k$ should change the predecessor set:
-\begin{equation}
-	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{H}_{k,\tau}
-\end{equation}
-and all the task assign after $\tau$, we say $\tau'>\tau$ will set:
-\begin{equation}
-	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau'},sc \text{ is service-call} \right\} \cup \mathcal{H}_{k,\tau'}
-\end{equation}
-And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.
-
-Assign $t_{ij}$ to $ms_l$
-
 Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.

### 2016-09-23 design.tex
modify

@@
 Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
-Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
-\begin{figure}[htbp]
-	\centering
-    \large
-	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
-	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
-	\label{fig:simplejoblist}
-\end{figure}
+Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished.
+% as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.
+% \begin{figure}[htbp]
+% 	\centering
+%     \large
+% 	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
+% 	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
+% 	\label{fig:simplejoblist}
+% \end{figure}
 Therefore, provider can only makes decision on the schedule of tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of these inactive task to be scheduled as $\mathcal{L}^{(s)}_{k,\tau_0}$.
@@
 Since the task may come from different orders, we here use the single uniform denotation $job_\theta$ to distinguish these tasks and their related variables.
-In this instance, as shown in \autoref{fig:simplejoblist}, horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
+In this instance, as shown in \autoref{fig:scheduleChart}, horizontal dotted line constrained the available capacity of the resource for the subsequent jobs.
 Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.
@@
 f^{(s)}_\theta =  \tau_0 + re_\theta & $\theta\in G^{(s)}$ \label{eq:alreadydefined}\\
-\sum_{\theta\in\left\{  \theta' |t_{\theta'} \in\mathcal{G}_{k,\tau}\right\}} q_\theta \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
+\sum_{\theta\in\left\{  \theta' |job_{\theta'} \in\mathcal{G}_{k,\tau}\right\}} q_\theta \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
 f^{(s)}_\theta \ge \tau_0 + p_\theta & $\theta\in L^{(s)}$ \label{eq:finishconstrain}

### 2016-10-31 design.tex
fix two figures

@@
 \label{ssub:master_plam}
+(describe these models more clearly, understand it more easily)
+
 In original mode, operating of ecosystem begins with void, then there comes the registration of provider and demander.

### 2016-10-31 discussion.tex
modify before the submission
fix two figures

@@
 \label{sec:contributions_limitations_and_future_research}
+(This part is too short, not cover everything!!!!)
+
 In the extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate.
@@
 71571161), the National High Technology Research and Development Program of China (863 Program) (No.
-2015AA042101), and the Youth Funds of the Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province(No.
+2015AA042101), and the Fund of Key Lab of AMT of Zhejiang Province (No.
 2015QN01).

### 2016-10-31 Response.tex
add response

% !Mode:: "TeX:UTF-8"
\documentclass{article}
\author{Shengkai Chen}
\date{\today}
\title{Response to Reviewers' Comments}
\begin{document}
\maketitle

We would like to thank the Editor and reviewers for their insightful comments and suggestions. The issues raised by the reviewers have been addressed and a detailed response are given below.

\setlength\parindent{0pt}

\section*{Reviewer 1's comment}
I think that the initial background information given in the introduction could be explained a little bit better on simpler terms.

\textbf{Response:}

\subsection*{Comment 1} % (fold)
The literature review was good but could cover a little more. Additionally, the conclusion section seemed a little bit too short. It was dense but did not cover enough. Results section was good.

\textbf{Response:}

\subsection*{Comment 2} % (fold)
There are several issues of tense I found throughout the paper as well as grammar issues, especially in the terms section.

\textbf{Response:}

I'm so sorry to make such mistakes, related modifications have been made in new manuscript. Thank you.

\subsection*{Comment 3} % (fold)
One issue that I would address is that the figures such as figures one and two are not clear enough.  They need to be more crisp instead of blurry. The plots and graphs seem to be good on the other hand.

\textbf{Response:}

Thank you for the suggestion. I've changed the Fig. 1 into parallel style that enlarges the words in this figure, I've also redrawn Fig. 2 and Fig. 1 with \textit{MS Visio} so that they are more crisp now. 
\section*{Review 2's comment} % (fold)  
The authors should get in touch with the study's relevance with the environmental issues. Otherwise, the article's relevance with the conference is regarded to be low.
I would recommend the authors to describe the 3 modes (incubation, outsourcing, and metabolism modes) so that the readers can understand them more easily.

\textbf{Response:}

\end{document}

### 2016-10-31 intro.tex
add response

@@
 \section{Introduction}
+(use a bit simpler terms)
+
 The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information.

### 2016-11-01 design.tex
add new vector figures to MS Word

@@
 Without loss of generality, we suppose at time $\tau \ge r_i$, the decision-making of demander can be described as follows,
-\begin{equation}
-\max_{\forall \bm{k}}\left( \delta_{\bm{k}},
-R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
-\right) \label{eq:selectresaim}
-\end{equation}
-\begin{numcases}{\text{s.t.}}
-q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
-\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
-\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
-\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
-k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
-\end{numcases}
+% \begin{equation}
+% \max_{\forall \bm{k}}\left( \delta_{\bm{k}},
+% R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
+% \right) \label{eq:selectresaim}
+% \end{equation}
+% \begin{numcases}{\text{s.t.}}
+% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
+% \mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
+% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
+% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
+% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
+% \end{numcases}
 
@@
 
-\begin{equation}
-\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
-\end{equation}
-\begin{numcases}{\text{s.t.}}
-\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
-\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
-\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
-l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
-\end{numcases}
+% \begin{equation}
+% \max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
+% \end{equation}
+% \begin{numcases}{\text{s.t.}}
+% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
+% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
+% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
+% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
+% \end{numcases}
 Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length.
@@
 \mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \label{eq:templength}\\
-\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \label{eq:tempqualitystart}\\
-\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
-\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
-\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
-\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \label{eq:tempqualityend}\\
+% \Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \label{eq:tempqualitystart}\\
+% \mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
+% \sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
+% \bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
+% \bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \label{eq:tempqualityend}\\
 % \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
@@
 	\large
-	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
+	\resizebox{.95\textwidth}{!}{\input{figures/scheduleChart}}
 	\caption{Simple instance schedule chart with 4 resources in 3 different types}

### 2016-11-01 Response.tex
clearify what to change

@@
 1 with \textit{MS Visio} so that they are more crisp now.
+All the figures now are vectorgraphs.
+
 \section*{Review 2's comment} % (fold)  
@@
 
+Thank you for your suggestion.
+Previous manuscript considered environmental issues in the view of the life cycle vicissitude of resource in cloud manufacturing, so we designed bunches of operation modes to study how to optimize the manufacturing resources for the overall industry.
+I must admit that these contents are not obvious enough, so apart from changing the representations, I also add a section (2.1 Background) to describe the environmental issues with regard to cloud manufacturing.
+Additional simpler description of the proposed 3 modes are add to 3.4, 3.5, 3.6 respectively, and I also simplified the description of the original mode in 3.3.
 \end{document}

### 2016-11-01 design.tex
clearify what to change

@@
     $\Delta_l$ & Product quality produced via service $ms_l$\\
-    $\bm{mr}_l$ & Resource member set of $ms_l$\\
-    $\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
+    % $\bm{mr}_l$ & Resource member set of $ms_l$\\
+    % $\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
     $q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$,$\alpha\in\mathcal{A}_{l}$\\
-    $\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\
+    % $\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\
     $\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
@@
     $P(\cdot)$ & Type inquire function about resource type\\
-    $\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
+    % $\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
     \hline
@@
 % \label{subs:select_resource_candidates}
-A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$.
-Without loss of generality, we suppose at time $\tau \ge r_i$, the decision-making of demander can be described as follows,
+A demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. Without loss of generality, we suppose at time $\tau \ge r_i$,
+the decision-making of demander can be formulated as the special case of general model, which aims at multi-objective function as \autoref{eq:optk}.
 % \begin{equation}
@@
 % \end{numcases}
-
-The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length.
-\autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task-part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.
 
@@
 After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
-As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature , which means capacity of selected resource will not be restored after the processing.
+As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature, which means capacity of selected resource will not be restored after the processing.
 The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service.
@@
 Demander of $t_{ij}$ will select $ms_l$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$ and this implies that the resource candidates are not enough and there exists service candidates.
+This decision-making of demander can also be formulated as the special case of general model, which aims at multi-objective function as \autoref{eq:optl}.
 
@@
 % \end{numcases}
-Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length.
-\autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.
 
@@
 
-Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length.
-\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculation procedure.
+% The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length.
+\autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task-part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.
+
+% Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length.
+\autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.
+
+The decision variable $\bm{k}$ is a vector that wraps $k_\alpha$ up ($\alpha\in\mathcal{A}_{ij}$). 
+\autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length.
+\autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions.
+\autoref{eq:temprank} determines the virtual rank value while \autoref{eq:templength} determines virtual queue length that are set in the worst cases.
+% \autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculation procedure.
 \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.
+The determination of $\Delta_{\bm{k}^*}$ is tedious and insignificant so that we are not going to show the details.
 
@@
 	\large
-	\resizebox{.95\textwidth}{!}{\input{figures/scheduleChart}}
+	\resizebox{.9\textwidth}{!}{\input{figures/scheduleChart}}
 	\caption{Simple instance schedule chart with 4 resources in 3 different types}
@@
 
-In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}}$.
+In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)}$ wraps $f^{(s)}_\theta$ up ($job_\theta\in\mathcal{L}^{(s)}_{k,\tau_0}$).
 Even though provider will not schedule $job_\theta\in\mathcal{H}_{k,\tau_0}$, the finish time $f_\theta$ of these job cannot be determined because the waiting in the cooperation.

### 2016-11-02 intro.tex
add background, need the environmental

--- 2016-09-09 intro.tex
@@
 \section{Introduction}
-The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information.
-Demanders prefer high quality of performance, while providers prefer high use rate of resource.
-A cloud platform operator prefers a fewer amount of registered resource when dealing with almost arriving needs for an easier maintenance.
-These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem.
-Hence, it's important to identify a suitable operation mode to meet most of individuals' preference.
+Manufacturing activities consume kinds of resources (e.g.
+material, equipment, manpower, nature resource), which will resulting in substantial environmental issues.
+Properly arrange these resources to collaborate a manufacturing process is one of feasible approaches to reduce the waste during the consumption of resources, the concept of cloud manufacturing \cite{li2010cloud,Xu2012} provides a operating framework to realize the arrangement.
 
-In this paper, an original operation mode is designed to describe the basic decision-makings in cloud manufacturing ecosystem, then three extensions, namely metabolism mode, incubation mode and outsourcing mode are proposed.
+However, the relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information.
+In particular, \autoref{fig:originmode} shows the basic procedures that need three main entities to make decisions on.
+\textbf{Demander} is the entity that publish manufacturing task, it prefers high quality of task performance; \textbf{Provider} is the entity that processes the task with the resources it provided prefer high use rate of resource; \textbf{Platform} it the intermediary entity that promotes the manufacturing activities, it prefers a suitable amount of registered resources to satisfy the needs of the market and an optimal life cycle management of resources.
+Entities' preferences stimulate the emergence of good resource arrangement pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem.
+Hence, it's important to identify a suitable operation mode to meet most of entities' preferences and to optimize the resource management.
+
+In this paper, an original operation mode is designed to describe the basic decision-makings of entity in cloud manufacturing ecosystem, then three extensions, namely metabolism mode, incubation mode and outsourcing mode are proposed.
 Finally, an experiment to validate these synthetic operation modes are designed using an agent-based simulation method.

### 2016-11-02 review.tex
add response
clearify what to change
add background, need the environmental

@@
 % !TEX root = Eco-Model.tex
-\section{Review on cloud manufacturing} % (fold)
+\section{Background and literatures} % (fold)
 \label{sec:literature_review}
+\subsection{Background} % (fold)
+\label{sub:background}
+1. environmental issues
 
-% This definition is quite abstract and thus despite its corretness not very useful.
+In cloud manufacturing context, provider entity publishes manufacturing resources, demander entity publishes manufacturing tasks, platform arranges these resources properly to perform the tasks.
+As one object in research scope of this paper, the mode to generate manufacturing service, which is an arrangement of resources, is discussed along with another object that the mode to keep resource in high quality instead of low quality.
 
-In cloud manufacturing context, platform operator can manage  manufacturing service that encapsulated with distributed manufacturing resources intensively with appropriate business model \cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build a cloud manufacturing platform or system framework \cite{Tao2012,Valilai2013}, Lv used the list of views to depict this multi-layer architecture \cite{LvJuly312012-Aug.22012}.
+% subsection background (end)
+
+\subsection{Literatures} % (fold)
+\label{sub:literatures}
+
+Platform operator can manage manufacturing service that encapsulated distributed manufacturing resources intensively with appropriate business model \cite{Xu2012}, modular approaches and multi-layer architectures are the most common approaches to build a cloud manufacturing platform or system framework \cite{Tao2012,Valilai2013}, Lv used the list of views to depict this multi-layer architecture \cite{LvJuly312012-Aug.22012}.
 
@@
 
+% subsection literatures (end)
 % section literature_review (end)

### 2016-11-03 design.tex
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

@@
 
-Platform is the cradle of the ecosystem and the incubator for manufacturing service, with the cloud manufacturing platform operating, demanders publish orders while providers provide resources, then they make decisions to  arrange the resources to perform tasks that decomposed from order.
+Platform is the cradle of the ecosystem and the incubator for manufacturing service, demander and provider make decisions through it to arrange the resources for task performance.
 Most recent researchers e.g.
 Wu et al.
-\cite{Wu2013}, describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
+\cite{Wu2013}, described this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
 \item users/customers,
@@
 Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
-In this mode, individual executes activities that interact with others depicted by object flow (full lines) and information flow (dashed lines).
+In original mode, entities interact with each others is depicted by object flow (full lines) and information flow (dashed lines).
 A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation.

### 2016-11-03 discussion.tex
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

@@
 \label{sec:contributions_limitations_and_future_research}
-(This part is too short, not cover everything!!!!)
+The operation modes proposed in this paper represented ways to the arrangement of resource to handle the environmental burden, and the $RE$ value showed in \autoref{tab:averagevalue}, reduced wast and idle of manufacturing resources have partially achieved, if Mode 11 was selected as the reference standard, since this value means the amount of task that can be manufactured per unit of resource.
 
-In the extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate.
-The combine of incubation and metabolism mode makes the maintenance of platform much easier.
+As for extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate.
+The combine of incubation and metabolism mode turns out to be a ideal maintenance pattern for operating.
+
 However, we only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions.
@@
 2015QN01).
+The authors also gratefully acknowledge the insightful comments from anonymous reviewers which have helped to
+improve significantly on the earlier version of this paper.
 % section acknowledgments (end)

### 2016-11-03 result.tex
ready for merge
add result figure in figures
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

@@
 Experiment on each mode in one group are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
-After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue},
+After bunch of experiments with different random seeds, take random seed 776189616 as example, we run the simulation for 6000 tick time and the experiment's results are displayed in \autoref{fig:out} and \autoref{tab:averagevalue}, meaning of new most symbols are defined as the title of all the plots in \autoref{fig:out}, $RE$ denotes the resource efficiency determined by \autoref{eq:re}
+\begin{equation}
+  RE = \frac{\bar N_F}{\bar N_R} \label{eq:re}
+\end{equation}
 \begin{table}[htbp]
@@
     \scriptsize
-    \begin{tabular}{lccccc}
+    \begin{tabular}{lcccccc}
     \toprule
-    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$\\
+    \textbf{Mode} & $\bar N_T$ & $\bar N_F$ & $\bar N_P$ & $\bar N_R $ & $\bar Q$ & $RE$\\
     \midrule
-    Mode 11 & 1159.36 &  1644.201 &  1177.601 &  2053.727 &  8.388\\
-    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016\\
-    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174\\
-    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057\\
-    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251}\\
-    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652}\\
+    Mode 11 & 1159.360 &  1644.201 &  1177.601 &  2053.727 &  8.388 & 0.801\\
+    Mode 21 & \textit{636.769} &  \textit{2031.215} &  \textbf{692.716} &  \textbf{1066.947} &  16.016 & 1.904\\
+    Mode 31 & 779.413 &  1996.021 &  \textit{782.272} &  \textit{1203.748} &  15.174 & 1.658\\
+    Mode 12 & 1439.831 &  1522.923 &  1797.883 &  2954.113 &  14.057 & 0.516\\
+    Mode 22 & \textbf{343.444} &  \textbf{2464.407} &  1316.952 &  1957.226 &  \textit{20.251} & 1.259\\
+    Mode 32 & 1164.409 &  1907.011 &  1597.742 &  2428.155 &  \textbf{20.652} & 0.785\\
 
@@
     \centering
-    \includegraphics[width=\textwidth]{Data/out.eps}
+    \includegraphics[width=\textwidth]{figures/out_new.pdf}
     \caption{Observed variable change with time}

### 2016-11-03 review.tex
modify the conclusion and intro, background, acknowledge
now I need to modify the the model description to keep it simple and stupid

@@
 \label{sub:background}
-1. environmental issues
+Resource consumption in manufacturing activities is inevitable, waste and idle of these resources  are pervasive in existing manufacturing systems \cite{Smith2012}.
+Effective utilization of resources and resource productivity driven manufacturing innovation is one key consideration to handle the environmental burden \cite{Dornfeld2014,Li2012}.
 
 In cloud manufacturing context, provider entity publishes manufacturing resources, demander entity publishes manufacturing tasks, platform arranges these resources properly to perform the tasks.
-As one object in research scope of this paper, the mode to generate manufacturing service, which is an arrangement of resources, is discussed along with another object that the mode to keep resource in high quality instead of low quality.
+In scope are the mode to generate manufacturing service, which is an arrangement of resources, and the mode to keep resource in high quality instead of low quality.
 

### 2016-11-03 design.tex
modify the design part

@@
 % \label{sub:preliminaries}
-Before introducing the design of the ecosystem, we specify some basic definitions:
+Before introduce the design of the ecosystem, we specify some basic definitions first:
 \begin{compactitem}
-	\item Provider: the individual who provides resource;
+	\item Provider: the entity that provides resource;
 	\item Resource: the basic task process object with renewable capacity and unique type;
-	\item Demander: the individual who publishes orders that contain bunch of tasks;
-	\item Order: the task bundle like a project;
+	\item Demander: the entity that publishes orders that contain bunch of tasks;
+	\item Order: the task bundle as a project;
 	\item Task: the basic object that needs to be processed with resource-type cooperation;
@@
     \item Machine: the generalization of resource and service;
-	\item Platform: the place where individuals interact with others;
+	\item Platform: the place where entities interact with each others;
     \item Resource-type cooperation: resource in specific type to process a job simultaneously;
@@
 \end{inparaenum}
-Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
-In original mode, entities interact with each others is depicted by object flow (full lines) and information flow (dashed lines).
-A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation.
-Each task needs to be performed with resource-type cooperation as listed in \autoref{tab:simplejobconfiguration}, and the selected resource cannot start to process the task until all of other selected resources are ready, what each resource actually processes is the task-part and we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:scheduleChart}, \textbf{inactive} when this part is just assigned to the job queue.
-Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product.
+Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis, interaction among entities is depicted by object flow (full lines) and information flow (dashed lines).
+A single order can be described by an activity-on-node (AON) network where the node represent the task and the arc the precedence relation of task.
+Each task needs to be performed with types of resources as listed in \autoref{tab:simplejobconfiguration}, and all the selected resource need to be start the processing simultaneously, what each resource actually processes is the task-part and we call the task-part is \textbf{active} when being processed, \textbf{semi-active} when selected resource is waiting as shadow in \autoref{fig:scheduleChart}, \textbf{inactive} when this part is just assigned to the job queue.
+Product, the performance result after the processing and assembly procedure, will be delivered to demander, then demander change the rank value of the owner according to the review of the product.
 
@@
     \multicolumn{2}{|l|}{} \\
-    $\mathcal{T}_i$ & Order that come with demander, who can be quired by $F(\cdot)$ \\
-    $t_{ij}$ & Task belongs to $\mathcal{T}_i$, $t_{ij}\in\mathcal{T}_i$ \\
+    $\mathcal{T}_i$ & Order that comes with demander, it can be quired by $F(\cdot)$ \\
+    $t_{ij}$ & Task that belongs to $\mathcal{T}_i$, $t_{ij}\in\mathcal{T}_i$ \\
     $p_{ij}$ & Process duration of $t_{ij}$\\
-    $\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
+    $\gamma_{ij}$ & Expect quality of product as the process result of $t_{ij}$\\
     $r_i$ & Release time of all $t_{ij}\in\mathcal{T}_i$\\
@@
     $\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assignment procedure\\
-    $mr_k$ & Resource that come with provider, who can be quired by $F(\cdot)$ \\
-    $\delta_k$ & Task-part quality produced via resource $mr_k$ \\
+    $mr_k$ & Resource that comes with provider, it can be quired by $F(\cdot)$ \\
+    $\delta_k$ & Quality of task-part that processed via resource $mr_k$ \\
     $C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
@@
     % $job_\theta$ & Task that need to be scheduled at $\tau_0$,  $\theta = 1,...,\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{G}^{(s)}_{k,\tau_0}}$\\
-    $f^{(s)}_\theta$ & Ideal finish time of $job_\theta$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule at $\tau_0$ . \\
+    $f^{(s)}_\theta$ & Theoretical finish time of $job_\theta$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule at $\tau_0$ . \\
     $re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule at $\tau_0$. \\
     % $\mathcal{A}$ & Resource type set \\
-    $\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$\\ %, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
+    $\mathcal{A}_{ij}$ & Subset of resource type required by $t_{ij}$\\ %, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
     $q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$, $\alpha\in\mathcal{A}_{ij}$\\
@@
     $r_l$ & Release time of $sc_l$\\
-    $\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
-    $\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ \\ %, $\mathcal{A}_l\subset\mathcal{A}$\\
-    $ms_l$ & Service that generated after the finish of $sc_l$\\
+    $\mathcal{P}_{l}$ & Predecessor set of $sc_{l}$\\
+    $\mathcal{A}_l$ & Subset of resource type required by $sc_l$ or provided by $ms_l$ \\ %, $\mathcal{A}_l\subset\mathcal{A}$\\
+    $ms_l$ & Service that incubated after the finish of $sc_l$\\
     $\Delta_l$ & Product quality produced via service $ms_l$\\
@@
     $\mathcal{G}_{l,\tau}$ & The set of active job of $ms_l$ at $\tau$ \\
-    $\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
-    $\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
-    $\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
-    $\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
-    $\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
+    $\mathcal{R}_{ij,\tau}$ & Resource candidate set for $t_{ij}$ to select\\
+    $\mathcal{B}_{ij,\tau}$ & Resource candidate type set for $t_{ij}$\\
+    $\mathcal{S}_{ij,\tau}$ & Service candidate set for $t_{ij}$ to select\\
+    $\mathcal{R}_{l,\tau}$ & Resource candidate set for $sc_l$ to select\\
+    $\mathcal{B}_{l,\tau}$ & Resource candidate type set for $sc_l$\\
     $R(\cdot)$ & Rank inquire function about provider\\
@@
 \end{table}
-Since demander and provider continuous arrives, there is no upper bound of the subscripts
+Since demander and provider arrives successively, there is no upper bound of the subscripts
 $(i,j,k,l,\alpha)$.
-To scope our research, we make some assumptions as follows for the original mode, while in other extensions, some of the assumptions will be modified.
+To scope our research, we make some assumptions as follows for the original mode, some of them will be modified in the extension modes.
 \begin{compactitem}
-\item Operate of the ecosystem starts from the very beginning that no demander or provider is registered;
+\item Operation of the ecosystem starts from the very beginning that no demander or provider is registered;
 \item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
 \item The quality of product is determined by the worst quality of the selected resource;
-\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
-\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
+\item Resource are renewable that the available capacity will be restored after the processing procedure;
+% \item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
 \item Cooperation and processing procedure cannot be interrupted;
-\item Provider can only schedule task-parts in inactive status.
+\item Provider can only schedule task-parts that in inactive status.
 \end{compactitem}
@@
 \label{ssub:master_plam}
-(describe these models more clearly, understand it more easily)
 
-In original mode, operating of ecosystem begins with void, then there comes the registration of provider and demander.
-A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints.
+In original mode, ecosystem starts with void, then there comes the registration of provider and demander.
+A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, which are interrelated by kinds of constraints.
 First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
 Second, performing the tasks requires resources with limited capacities.
-Third, resources cooperation requires all the task-parts in active status.
+Third, resource-type cooperation requires all the task-parts in active status.
 A single \textbf{resource}($mr_k$) belongs to only one type.
@@
 Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$.
-This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need to be processed with resource cooperation.
+This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need to be processed with resource-type cooperation.
 
-The life cycle management of resource contains its vicissitude, which is the design basis of proposed extended modes \autoref{fig:modes}.
+The life cycle management of resource contains its vicissitude, which is the basis of the following extended modes \autoref{fig:modes}.
 \begin{figure}[htbp]
@@
 \end{figure}
-Incubation and outsourcing mode are options for provider, while metabolism mode is option for platform operator, and the outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.
+Incubation mode and outsourcing mode are options for provider, while metabolism mode is option for platform operator.
+Outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.
 
@@
 
-A provider makes decision at time $\tau\ge r_i$ to respond  to task if the belonging resource $mr_k$ was type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
-If $A_{k,\tau} \ge q_{\alpha,ij}$, the provider will respond to the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$.
+A provider makes decision at time $\tau\ge r_i$ to respond to task if the belonging resource $mr_k$ is type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$).
+If $A_{k,\tau} \ge q_{\alpha,ij}$, the provider will respond to the task, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$.
 If $mr_k$ is finally selected, available capacity of $mr_k$ will change to $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$.
-This available capacity will be restored after the finish of $t_{ij}$ part.
+This available capacity will be restored after the processing of $t_{ij}$ part.
 
@@
 % \label{subs:assign_in_select_resource}
-If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$, or to  $\mathcal{L}_{k,\tau}$ otherwise.
+If $mr_k$ is selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$, or to  $\mathcal{L}_{k,\tau}$ otherwise.
 % \begin{subnumcases}{}
@@
 \label{sub:incubation_mode}
-Incubation mode is one extension for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in incubation part of \autoref{fig:modes}.
+Incubation mode is one extension for the original mode, which describes the generating process of  manufacturing service, the purpose of this mode is to remove the cooperation and assembly procedure among resources in advance by wrapping types of resources with certain quota up.
+A service is incubated as shown in incubation part of \autoref{fig:modes}.
 % \begin{figure}[htbp]
@@
 \end{figure}
-After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
+After the finish of task-part, provider records the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
 As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature, which means capacity of selected resource will not be restored after the processing.
@@
 \label{sub:metabolism mode}
-Metabolism mode is one extension for the original mode to control the number of individual in the system by both restrict the arrival and eliminate the current members.
+Metabolism mode is one extension for the original mode to control the number of entity in the system by both restrict the arrival and eliminate the current entities.
 As metabolism part shown in \autoref{fig:modes},

### 2016-11-03 design.tex
modified

@@
     \multicolumn{2}{|l|}{} \\
-    $\mathcal{T}_i$ & Order that comes with demander, it can be quired by $F(\cdot)$ \\
+    $\mathcal{T}_i$ & Order that comes with demander, it can be inquired by $F(\cdot)$ \\
     $t_{ij}$ & Task that belongs to $\mathcal{T}_i$, $t_{ij}\in\mathcal{T}_i$ \\
@@
     $\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assignment procedure\\
-    $mr_k$ & Resource that comes with provider, it can be quired by $F(\cdot)$ \\
+    $mr_k$ & Resource that comes with provider, it can be inquired by $F(\cdot)$ \\
     $\delta_k$ & Quality of task-part that processed via resource $mr_k$ \\
@@
 A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, which are interrelated by kinds of constraints.
-First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$.
+First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors in $\mathcal{P}_{ij}$.
 Second, performing the tasks requires resources with limited capacities.
@@
 
-The life cycle management of resource contains its vicissitude, which is the basis of the following extended modes \autoref{fig:modes}.
+The life cycle management of resource contains its vicissitude, which is the basis of the following extended modes in \autoref{fig:modes}.
 \begin{figure}[htbp]
@@
 \end{figure}
-Incubation mode and outsourcing mode are options for provider, while metabolism mode is option for platform operator.
+Incubation mode and outsourcing mode are options for provider, while metabolism mode is an option for platform operator.
 Outsourcing mode can only be applied if incubation mode is applied because only the task that processed by service can be outsourced.
@@
 \end{figure}
-After the finish of task-part, provider records the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such a task-specified service for the future performance.
-As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} was finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature, which means capacity of selected resource will not be restored after the processing.
-The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resources in a same type to make contributions to the incubation of one service.
-No more cooperation and assembly procedure are one pro of service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect, while one con of service include that service can only perform specified task.
-Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.
+After the finish of task-part, provider records the resource configuration as task frequency, when the frequency value reaches some point, provider will decide to incubate such a task-specified service for the future performance.
+As the example in \autoref{fig:servicefigure}, if task $job_1$ in \autoref{tab:simplejobconfiguration} is finished, the first thing of incubation for the resource provider is to publish a job named \textbf{service-call} ($job_7$), which is similar to task except for the capacity dominance feature, which means capacity of selected resource will be restored after the processing.
+The process result of one service-call is manufacturing \textbf{service} as shown in \autoref{fig:servicefigure}, which is actually a bunch of resources that come from selected providers in the system, it's possible for more than one resources in same type to make contributions to the incubation of one service.
+There is no more cooperation and assembly procedure in service, and product quality will no longer be restricted to the worst quality of resources for the complementary effect.
+However service can only perform specified task.
+Now we can generalize task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss. Few behaviors will be discussed to explain how these decisions make.
 
@@
 Similar with response of $mr_k$ to $t_{ij}$ in original mode, provider of $mr_k$ can also respond to type-matched service-call $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$.
-If $mr_k$ was finally selected, both available capacity and capacity will be changed as required, and these capacity will not be restored even after the finish of $sc_l$ part.
+If $mr_k$ is finally selected, both available capacity and capacity will be changed as required, and these capacity will not be restored even after the finish of $sc_l$ part.
 Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
-When service $ms_l$ was type-matched with $t_{ij}$ ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of $ms_l$ will respond to $t_{ij}$ as soon as possible, demander of $t_{ij}$ will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
+When service $ms_l$ is type-matched with $t_{ij}$ ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of $ms_l$ will respond to $t_{ij}$ as soon as possible, demander of $t_{ij}$ will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.
 
@@
 % \end{subnumcases}
-Demander of $t_{ij}$ will select $ms_l$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$ and this implies that the resource candidates are not enough and there exists service candidates.
+Demander of $t_{ij}$ will select $ms_l$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$ and this implies that the resource candidates are not enough but there exists service candidates.
 This decision-making of demander can also be formulated as the special case of general model, which aims at multi-objective function as \autoref{eq:optl}.
@@
 
-In more general condition where $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service.
+In more general condition where $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$, demander of $t_{ij}$ will select ether a bunch of resources or one single service.
 \begin{equation}
@@
 \label{sub:outsource_mode}
-Outsourcing mode is one extension for the original mode when incubation mode is applied. As outsourcing part shown in \autoref{fig:modes},
+Outsourcing mode is one extension for the original mode when incubation mode is applied, the meaning of this mode is to transfer task to idle resource.
+As outsourcing part shown in \autoref{fig:modes},
 % \begin{figure}[htbp]
@@
 \label{sub:metabolism mode}
-Metabolism mode is one extension for the original mode to control the number of entity in the system by both restrict the arrival and eliminate the current entities.
+Metabolism mode is one extension for the original mode to control the number of entity in the system by both restrict the arrival and eliminate the current entities, the meaning of this mode is to keep high quality resource instead of low quality that will lead to a good evolution in manufacturing industrial.
 As metabolism part shown in \autoref{fig:modes},
@@
 % \end{figure}
-we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.
+we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$, this indicator will guide the metabolism module to execute, the object of metabolism is to improve overall resource quality without loss of manufacturing efficiency.
 
@@
 In order to reduce the idle rate, provider will schedule the inactive jobs on their machines.
-Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
+% Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource.
 Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished.

### 2016-11-03 discussion.tex
modified

@@
 \label{sec:contributions_limitations_and_future_research}
-The operation modes proposed in this paper represented ways to the arrangement of resource to handle the environmental burden, and the $RE$ value showed in \autoref{tab:averagevalue}, reduced wast and idle of manufacturing resources have partially achieved, if Mode 11 was selected as the reference standard, since this value means the amount of task that can be manufactured per unit of resource.
+The operation modes proposed in this paper represented ways to the arrangement of resource to handle the environmental burden, and the $RE$ value showed in \autoref{tab:averagevalue}, reduced waste and idle of manufacturing resources have partially achieved, if Mode 11 was selected as the reference standard, since this value means the amount of task that can be manufactured per unit of resource.
 

### 2016-11-09 Response.tex
add background, need the environmental
finally modified

--- 2016-10-31 Response.tex
@@
 \documentclass{article}
-\author{Shengkai Chen}
+\author{Shengkai Chen, Shuiliang Fang, Tao Peng, Renzhong Tang}
 \date{\today}
@@
 
+Thank you for the suggestions.
+We modified the initial background information in Sec.
+1 and in Sec 2., explained the relationship between the operation mode research and the environmental issues.
+Resource consumption in manufacturing activities leads to substantial environmental, to overcome this burden, we can arrange manufacturing through proper operational modes.
+
 \subsection*{Comment 1} % (fold)
@@
 \textbf{Response:}
+
+Thank you for the suggestions.
+We extended Sec 2.
+with more information that contains a bit more literature reviews, which are in the scope of environmental issues in manufacturing.
+In the conclusion section, we added a new factor $RE$ in consideration to represent the resource efficiency, $RE$ value of Mode 11 is the baseline for comparison.
 
@@
 
-I'm so sorry to make such mistakes, related modifications have been made in new manuscript. Thank you.
+We're so sorry to make such mistakes, related modifications have been made in new manuscript. Thank you.
 
@@
 Thank you for the suggestion.
-I've changed the Fig.
+We've changed the Fig.
 1 into parallel style that enlarges the words in this figure, I've also redrawn Fig.
 2 and Fig.
-1 with \textit{MS Visio} so that they are more crisp now.
+1 so that they are more crisp now.
+All the figures now are vectorgraphs.
+
 \section*{Review 2's comment} % (fold)  
@@
 
+Thank you for your suggestion.
+Previous manuscript considered environmental issues in the view of the life cycle vicissitude of resource in cloud manufacturing, so we designed bunches of operation modes to study how to optimize the manufacturing resources for the overall industry.
+We must admit that these contents are not obvious enough, so apart from changing the representations, we also add more details in Sec 1.
+and Sec 2.
+to describe the environmental issues with regard to cloud manufacturing.
+Additional simpler description of the proposed 3 modes are add to 3.4, 3.5, 3.6 respectively, and we also simplified the description of the original mode in 3.3.
 \end{document}
